### 2017-05-16 design.Rmd
Initial commit

---
title: "Experimental design"
date: "Last run: `r format(Sys.time(), '%F')`"
bibliography: Manuscript/bibliography.bib
---

## Goal

The ultimate goal of our research project is to use Bayesian analysis is to test if the region of practical equivalence around the null value (i.e. the proposition that the average treatment effect of NGO crackdown is zero) excludes the posterior 95% HDI.

In this initial pilot study, we use standard frequentist methods to [perform power analysis](power.html) and estimate the desired sample size. We will use the effect size estimates from this study to inform the prior distribution of parameter values in future Bayesian-based experiments [@Kruschke:2015, 362].

## Experimental conditions

| Condition            | 1 | 2 | 3 | 4 | 5 | 6 | 7 | 8 |
|----------------------|:-:|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
| **Crackdown**        |   |   |   |   |   |   |   |   |
| Yes                  | • | • | • | • |   |   |   |   |
| No                   |   |   |   |   | • | • | • | • |
| *Expected donations* | + | + | + | + | ∅ | ∅ | ∅ | ∅ |
|                      |   |   |   |   |   |   |   |   |
| **Issue area**       |   |   |   |   |   |   |   |   |
| Humanitarian service | • | • |   |   | • | • |   |   |
| Human rights         |   |   | • | • |   |   | • | • |
| *Expected donations* | + | + | − | − | + | + | − | − |
|                      |   |   |   |   |   |   |   |   |
| **Type of funding**  |   |   |   |   |   |   |   |   |
| Government           | • |   | • |   | • |   | • |   |
| Private              |   | • |   | • |   | • |   | • |
| *Expected donations* | − | + | − | + | − | + | − | + |

## References

### 2017-05-16 experiment.Rmd
Initial commit

---
title: "Experiment"
date: "Last run: `r format(Sys.time(), '%F')`"
---

## Description

This survey was hosted on [Qualtrics](https://www.qualtrics.com) and participants were randomly sorted into one of eight variations (see [Design](design.html)).

Participants were recruited through [Amazon Mechanical Turk](https://www.mturk.com/mturk/welcome) and were paid $X for their response.

## Survey experiment {.survey}

### Consent

***Q1.1***: Consent form here…

*Q1.2*: I have read the above information, and I consent to take part in the study.

:   Single answer

    - Yes
    - No

---

### Crackdown and private giving

![](img/irc_logo.png "IRC logo"){.img-responsive .center}

\

***Q2.1***: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.

A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.

*Q2.2*: How likely would you be to donate to IRC?

:   Single answer

    - Extremely likely
    - Somewhat likely
    - Neither likely nor unlikely
    - Somewhat unlikely
    - Extremely unlikely

*Q2.3*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)

:   Numeric slider, options must sum to 100

    - Donate to IRC (0–100)
    - Keep for yourself (0–100)

*Q2.4*: Why would you donate that amount?

:   Text field

---

### Crackdown and corporate social responsibility (CSR)

![](img/google_irc_logo.png "Google and IRC logos"){.img-responsive .center}

\

***Q3.1***: In December 2016, Google held a Giving Weekend and raised $X and did YYY to support International Rescue Committee’s (IRC) efforts in {ISSUE AREA: providing humanitarian assistance for refugees | advocating human rights for refugees} {in countries where nonprofit organizations are harshly restricted}.

A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.

*Q3.2*: How favorable do you feel towards Google?

:   Single answer

    - Extremely positive
    - Somewhat positive
    - Neither positive nor negative
    - Somewhat negative
    - Extremely negative

*Q3.3*: How generous do you feel Google is?

:   Single answer

    - Extremely generous
    - Very generous
    - Moderately generous
    - Slightly generous
    - Not generous at all

*Q3.4*: Rate how strongly you feel Google is committed to philanthropy:

:   Single answer

    - Extremely committed
    - Very committed
    - Moderately committed
    - Slightly committed
    - Not committed at all

*Q3.5*: Where would you most like to see Google donate its money?

:   Single answer

    - Nonprofit organizations or foundations working mostly in California
    - Nonprofit organizations or foundations working throughout the United States
    - Nonprofit organizations or foundations working mostly in foreign countries

*Q3.6*: Why do you think Google should donate money to organizations working in X?

:   Text field

---

### Demographics

***Q4.1***: Almost done! This is the last page of the study.

*Q4.2*: How often do you donate to charity (either cash or in-kind)?

:   Single answer

    - Once a week
    - Once a month
    - Once every three months
    - Once every six months
    - Once a year
    - Once every few years
    - Never

*Q4.3*: Have you volunteered in the past 12 months?

:   Single answer

    - Yes
    - No

*Q4.4*: How closely do you follow politics in the news?

:   Single answer

    - Extremely closely
    - Very closely
    - Closely
    - Barely
    - Not at all

*Q4.5*: How would you describe your political views?

:   Single answer

    - Strong liberal
    - Liberal
    - Independent, leaning liberal
    - Independent
    - Independent, leaning conservative
    - Conservative
    - Very conservative

*Q4.6*: What is the highest degree or level of school you have completed?

:   Single answer

    - Less than high school
    - High school graduate
    - Some college
    - 2 year degree
    - 4 year degree
    - Graduate or professional degree
    - Doctorate

*Q4.7*: Aside from weddings and funerals, how often do you attend religious services?

:   Single answer

    - More than once a week
    - Once a week
    - Once or twice a month
    - A few times a year
    - Seldom
    - Never
    - Don't know

*Q4.8*: Please select blue from the following list:

:   Single answer

    - Red
    - Yellow
    - Blue
    - Green

*Q4.9*: What is your gender?

:   Single answer

    - Female
    - Male
    - Transgender
    - Other:
    - Prefer not to say

*Q4.10*: What is your total household income?

:   Single answer

    - Less than $10,000
    - $10,000 - $19,999
    - $20,000 - $29,999
    - $30,000 - $39,999
    - $40,000 - $49,999
    - $50,000 - $59,999
    - $60,000 - $69,999
    - $70,000 - $79,999
    - $80,000 - $89,999
    - $90,000 - $99,999
    - $100,000 - $149,999
    - More than $150,000

*Q4.11*: How old are you?

:   Single answer

    - Under 18
    - 18 - 24
    - 25 - 34
    - 35 - 44
    - 45 - 54
    - 55 - 64
    - 65 - 74
    - 75 - 84
    - 85 or older

### 2017-05-16 index.Rmd
Initial commit

---
title: "NGO Crackdowns and Philanthropy"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

\\(•◡•)/

### 2017-05-16 power.Rmd
Initial commit

---
title: "Power analysis"
date: "Last run: `r format(Sys.time(), '%F')`"
---

## $f^2$ power analysis

```{r power-calculations}
library(pwr)
u_mine <- 1
# f2_mine <- cohen.ES(test = "f2", size = "small")$effect.size
f2_mine <- 0.02
sig_level_mine <- 0.05
power_mine = 0.90

survey_power <- pwr.f2.test(u=u_mine, v=NULL, f2=f2_mine, 
                            sig.level=sig_level_mine, power=power_mine)

# n = u + v + 1
n_total <- survey_power$u + survey_power$v + 1
n_group <- n_total / (2 * 2 * 2)
```

Cohen's rules of thumb for $f^2$ power are 0.02, 0.15, and 0.35 for small, medium, and large effect sizes.

We are using a 2 × 2 × 2 design, manipulating the experimental condition, the issue area for the NGO, and the source of funding for the NGO. The formula for calculating the $f^2$-based sample size with [`pwr.f2.test`](https://www.rdocumentation.org/packages/pwr/versions/1.2-0/topics/pwr.f2.test) requires the following values:

- `u`: degrees of freedom for the numerator. This is a 2 × 2 × 2 design, so the degrees of freedom = $(2 - 1) \times (2 - 1) \times (2 - 1) = 1$
- `f2`: effect size. Here we use a small size, or `r f2_mine`.
- `sig.level`: significance level, or Type I error probability. Here we use `r sig_level_mine`.
- `power`: power of test, or 1 − Type II error probability. Here we use `r power_mine`.

Given these parameters, `pwr.f2.test` yields `v`, or the degrees of freedom for the denominator. The final sample size `n` is calculated as `u + v + 1`.

Thus, the total sample size is **`r round(n_total, 2)`**, with **`r round(n_group, 2)`** spread across 8 groups.

### 2017-05-16 preregistration.Rmd
Initial commit

---
title: "Preregistration"
date: "Last run: `r format(Sys.time(), '%F')`"
---

## Center for Open Science preregistration

We have preregistered this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).

We are also participating in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:

- Voluntas
- International Interactions
- Journal of Experimental Political Science
- Political Science Research Methods
- Research and Politics

## Preregistration protocol

Our protocol is available at OSF and is included below.

### 2017-05-29 experiment.Rmd
New political knowledge question

@@
 
-*Q4.4*: How closely do you follow politics in the news?
+*Q4.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not.
+Others aren't that interested.
+Would you say that you follow what's going on in government and public affairs…
 
@@
 
-    - Extremely closely
-    - Very closely
-    - Closely
-    - Barely
-    - Not at all
+    - Most of the time
+    - Some of the time
+    - Only now and then
+    - Hardly at all
 

### 2017-05-29 experiment.Rmd
Determine payment

@@
 
-Participants were recruited through [Amazon Mechanical Turk](https://www.mturk.com/mturk/welcome) and were paid $X for their response.
+Participants were recruited through [Amazon Mechanical Turk](https://www.mturk.com/mturk/welcome) and were paid \$0.75 for their response, which is equivalent to a \$9/hour wage:
+
+```{r calculate-payment}
+hourly.wage <- 9
+survey.length.minutes <- 5
+
+payment <- survey.length.minutes * (hourly.wage / 60)
+payment
+```
 

### 2017-05-29 experiment.Rmd
Consent form

@@
 
-***Q1.1***: Consent form here…
+***Q1.1***: You have been invited to participate in an academic research survey about international nongovernmental organizations.
+This study is being conducted by Suparna Chaudhry from Dartmouth College and Andrew Heiss from Duke University.
+The experiment should take about **5 minutes** to complete.
+You will be paid **$0.75** for your participation.
+
+Your participation in this study is entirely voluntary and you are free to skip any question or withdraw from the experiment at any time.
+The experiment contains no trick questions.
+You will not be asked to provide any personal information, and your answers will remain anonymous.
+There are no reasonably foreseeable risks or discomforts associated with participating in this study.
+
+You will receive no direct benefits from participating in this research study, but your responses may reveal important and useful insights about international NGOs and philanthropy.
+
+If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (Suparna.Chaudhry@dartmouth.edu; Dickey Center for International Understanding, Hanover, NH 03755) or Andrew Heiss (andrew.heiss@duke.edu; Sanford School of Public Policy, Durham, NC 27712) at andrew.heiss@duke.edu.
+This research has been reviewed by the Committee for the Protection of Human Subjects at Dartmouth College (603-646-6842; cphs.tasks@dartmouth.edu) and the Human Subjects Committee at Duke University (919-684-3030; campusirb@duke.edu).
+
+By clicking "I agree" below you are indicating that you are at least 18 years old, have read and understood this consent form and agree to participate in this research study.
+Please print a copy of this page for your records.
 

### 2017-05-29 experiment.Rmd
Attention check

@@
     - No
+
+---
+
+*Q1.3*: Please read the paragraph below carefully.
+
+What is your favorite color?
+While we are interested in learning about your preferences on a variety of topics, including colors, we also want to make sure that you are reading the questions we have written.
+To demonstrate that you’ve read this much, just go ahead and select both green and yellow from among the alternatives listed below, no matter what your favorite color is.
+Yes, ignore the first sentence and select both green and yellow.
+
+: Multiple answers allowed (*must be green and yellow*)
+
+    - Pink
+    - Red
+    - Green
+    - White
+    - Yellow
+    - Blue
 

### 2017-06-06 experiment.Rmd
Add Duke IRB approval

@@
 Your participation in this study is entirely voluntary and you are free to skip any question or withdraw from the experiment at any time.
-The experiment contains no trick questions.
 You will not be asked to provide any personal information, and your answers will remain anonymous.
 There are no reasonably foreseeable risks or discomforts associated with participating in this study.
+There will be questions designed to check that you’re paying attention to the details of the experiment.
+If you answer these incorrectly, the survey will end early and you may not receive compensation.
 
-You will receive no direct benefits from participating in this research study, but your responses may reveal important and useful insights about international NGOs and philanthropy.
+Beyond your payment, you will receive no direct benefits from participating in this research study, but your responses may reveal important and useful insights about international NGOs and philanthropy.
 
@@
 Yes, ignore the first sentence and select both green and yellow.
+
+**(End survey without payment if this question is incorrect.)**
 

### 2017-06-06 preregistration.Rmd
Italicize journal titles
Add Duke IRB approval

@@
 ---
-title: "Preregistration"
+title: "Preregistration & IRB"
 date: "Last run: `r format(Sys.time(), '%F')`"
@@
 
-## Center for Open Science preregistration
+## Experiment preregistration
 
@@
 
+<p><a href="#" class="btn btn-primary btn-md btn-success disabled" target="_blank">
+<i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
+OSF preregistration protocol &raquo;
+</a></p>
+
 We are also participating in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:
 
-- Voluntas
-- International Interactions
-- Journal of Experimental Political Science
-- Political Science Research Methods
-- Research and Politics
+- *Voluntas*
+- *International Interactions*
+- *Journal of Experimental Political Science*
+- *Political Science Research Methods*
+- *Research and Politics*
 
-## Preregistration protocol
+---
 
-Our protocol is available at OSF and is included below.
+## Human subjects and IRB approval
+
+This project has received IRB approval from the human subjects research committees at both Duke and Dartmouth. We have included a generic version of our protocol below.
+
+<p><a href="files/duke-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
+<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
+Duke IRB approval
+</a> 
+&nbsp;
+<a href="#" class="btn btn-primary btn-md btn-success disabled" target="_blank">
+<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
+Dartmouth IRB approval
+</a></p>
+
+### Project title
+
+Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy
+
+### Purpose of the study
+
+State repression of civil society organizations, in particular NGOs, has become ubiquitous over the last few decades.
+Besides undertaking violence towards costly organizations, states have also increasingly used legislation to crack down on NGOs.
+By creating barriers to their entry, funding, and operations, these laws restrict the space available for NGOs to engage in advocacy and provide services.
+How do such legal restrictions on NGOs impact private donors?
+With states increasingly providing funding for NGOs working in non-contentious issue areas, and a lack of philanthropic culture in many developing countries, numerous NGO rely on funds from private donors in Western countries.
+We use a survey experiment to examine the impact of state repression of NGOs on the preferences of private donors, as well as their actual behavior donating to besieged NGOs.
+In particular, we explore how state crackdown against NGOs changes private donors’ preferences and behavior based on the issue area of the organization, and the main source of its funds.
+Our results have important implications for understanding donor behavior, as well as for the sustainability of civil society organizations in developing countries.
+
+### Participant activities
+
+Participants will fill out a survey experiment that (1) describes a prominent international NGO—the International Rescue Committee (IRC)—and (2) requests participants how much money they would hypothetically donate to the organization.
+We manipulate the vignette describing IRC’s work in three different ways to isolate the effect of civil society legal crackdowns on private philanthropy:
+
+> The International Rescue Committee (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.
+> 
+> A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.
+
+The survey also offers a vignette related to corporate philanthropy, describing Google’s partnership with IRC in late 2016.
+We manipulate the vignette using the same scenarios (presence or absence of a legal crackdown, issue area, and funding source) to isolate the effect of legal crackdowns on corporate social responsibility campaigns and perceptions of companies engaging in corporate philanthropy.
+
+Finally, the survey asks participants a series of general questions related to their views of philanthropy, political knowledge, and general demographic features.
+
+### Subject selection and recruitment
+
+Participants of the survey experiment will be recruited via Amazon Mechanical Turk (MTurk), an online crowdsourcing platform that has been extensively used in social science research in recent years.
+MTurk allows researchers to recruit participants to perform tasks such as filling out surveys and opinion polls, participating in experiments, or coding the content of documents.
+Researchers advertise their studies as a human intelligence task (HIT) on MTurk, and participants choose only those HITs that interest them, given the promised price and estimated duration of the task.
+Participants are paid for completing HITs, and payment is transferred directly to participants’ credit cards immediately after the completion of a study.
+
+Our study will be listed as “Survey on international nonprofit organizations” and will take approximately 5 minutes to complete.
+Participants will be paid \$0.75 for completing the experiment, commensurate with a \$9/hour wage.
+After selecting our HIT, participants will be taken directly to the survey experiment, which will be hosted on Qualtrics.
+MTurk rules state that participants can terminate the study by returning the HIT at any time, without penalty.
+
+### Data security and participant privacy
+
+We will not collect personally identifiable data.
+MTurk workers are assigned a semi-random alphanumeric worker ID, which is the only information exposed to us as researchers.
+We collect MTurk worker IDs to distribute compensation after completion of the experiment and to exclude workers from future iterations of the study.
+Worker IDs will not be shared with anyone outside of the research team, will be removed from the data set, and will not be associated with any survey responses.
+Both Amazon and Qualtrics use SSL encryption (HTTPS) when collecting data from workers and transferring data to servers, so responses will remain confidential during the administration of the survey.
+
+After collecting data and paying participants, we plan on creating a clean, anonymous, non-identifiable dataset to use for our analysis and for public distribution following the publication of the results of the study.
+This data will not contain any worker-identifiable information and will be safe to store and use without extra security measures.
+
+Suparna Chaudhry and Andrew Heiss are co-investigators and will both have access to the clean, anonymized. Both have independently submitted IRB applications to their respective institutions.
+
+### Compensation
+
+Participants will be paid \$0.75 for successfully completing the experiment, commensurate with a \$9/hour wage.
+
+Previous studies have found that including simple questions to screen for attention can improve the results of MTurk experiments and filter out workers who try to get through the HIT as quickly as possible without reading the questions.[^1] To ensure that participants only receive compensation for completing the full experiment, we include two attention check questions.
+The first (Q1.3) involves reading several sentences and following instructions to select specific responses.
+The second (Q4.8) is simpler and asks the respondent to select a single color from a list.
+
+[^1]: Adam J.
+Berinsky, Michele F.
+Margolis, and Michael W.
+Sances, “Separating the Shirkers from the Workers?
+Making Sure Respondents Pay Attention on Self-Administered Surveys,” *American Journal of Political Science* 58, no.
+3 (July 2014): 739–53.
+doi: [10.1111/ajps.12081](https://dx.doi.org/10.1111/ajps.12081)
+
+Each attention check question serves a different purpose.
+The longer question (Q1.3) is designed to filter out respondents who are not paying attention at all and are trying to get a quick payout.
+Respondents who fail this question will exit the experiment and will not receive compensation.
+In an effort to not waste worker time, this is the first question after the consent form, so little participant time will have been wasted.
+
+The shorter question (Q4.8) is designed to quickly check if the respondent is still paying attention near the end.
+Participants who fail this question will still be compensated, but we will account for their lack of attention in our statistical analysis and may omit their response.
+
+### Risks and benefits
+
+The study poses minimal risks to participants.
+The experiment does not include false information—the manipulations we make in the vignettes (shown between curly braces (`{}`)) only serve to make each fact about the International Rescue Committee (IRC) and Google more salient:
+
+- “providing humanitarian assistance for refugees | advocating human rights for refugees”: IRC provides humanitarian assistance and engages in human rights advocacy for refugees
+- “in countries where nonprofit organizations are harshly restricted”: IRC works in some countries that have passed anti-NGO laws, such as Egypt and Turkey, as well as countries with no such laws
+- “A substantial proportion of IRC’s funding comes from government | private donors”: According to IRC’s most recent annual report, >25% of their income came from each of these sources
+- Google has hosted several events to raise money for IRC, including initiatives in 2015 and 2016. We do not manipulate the amount of money raised.

### 2018-02-09 experiment.Rmd
Rearrange site structure

@@
 
-## Description
+# Description
 
-This survey was hosted on [Qualtrics](https://www.qualtrics.com) and participants were randomly sorted into one of eight variations (see [Design](design.html)).
+This survey was hosted on [Qualtrics](https://www.qualtrics.com) and participants were randomly sorted into [one of eight conditions](preregistration.html#experimental_conditions).
 
@@
 ```{r calculate-payment}
-hourly.wage <- 9
-survey.length.minutes <- 5
+hourly_wage <- 9
+survey_length_minutes <- 5
 
-payment <- survey.length.minutes * (hourly.wage / 60)
+payment <- survey_length_minutes * (hourly_wage / 60)
 payment
@@
 
-## Survey experiment {.survey}
+# Survey experiment {.survey}
 
-### Consent
+## Consent
 
 ***Q1.1***: You have been invited to participate in an academic research survey about international nongovernmental organizations.
-This study is being conducted by Suparna Chaudhry from Dartmouth College and Andrew Heiss from Duke University.
+This study is being conducted by Suparna Chaudhry from Christopher Newport University and Andrew Heiss from Brigham Young University.
 The experiment should take about **5 minutes** to complete.
@@
 
-If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (Suparna.Chaudhry@dartmouth.edu; Dickey Center for International Understanding, Hanover, NH 03755) or Andrew Heiss (andrew.heiss@duke.edu; Sanford School of Public Policy, Durham, NC 27712) at andrew.heiss@duke.edu.
-This research has been reviewed by the Committee for the Protection of Human Subjects at Dartmouth College (603-646-6842; cphs.tasks@dartmouth.edu) and the Human Subjects Committee at Duke University (919-684-3030; campusirb@duke.edu).
+If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (suparna.chaudhry@cnu.edu; Reiff Center for Human Rights and Conflict Resolution, Christopher Newport University, Newport News, VA 23606) or Andrew Heiss (andrew_heiss@byu.edu; Romney Institute of Public Management, Brigham Young University, Provo, UT 84602) at andrew_heiss@byu.edu.
+This research has been reviewed by the Institutional Review Board at Christopher Newport University (757-594-7461; IRB@cnu.edu) and the IRB administrator at Brigham Young University (801-422-1461; irb@byu.edu).
 
@@
 
-### Crackdown and private giving
+## Crackdown and private giving
+
+*Q2.1*: How do you feel about the following types of organizations?
+
+:   Matrix table
+
+    |                                                                          | Very unfavorable | Unfavorable | Neutral | Favorable | Very favorable |
+    |--------------------------------------------------------------------------|:----------------:|:-----------:|:-------:|:---------:|:--------------:|
+    | Nonprofit organizations that provide humanitarian relief                 |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
+    | Nonprofit organizations that advocate for human rights                   |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
+    | Nonprofit organizations that help with development and alleviate poverty |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
+
+---
 
@@
 
-***Q2.1***: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.
+*Q2.2*: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.
 
@@
 
-*Q2.2*: How likely would you be to donate to IRC?
+*Q2.3*: How likely would you be to donate to IRC?
 
@@
 
-*Q2.3*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)
+*Q2.4*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)
 
@@
 
-*Q2.4*: Why would you donate that amount?
+*Q2.5*: Why did you select that amount?
 
@@
 
-### Crackdown and corporate social responsibility (CSR)
+## Demographics
 
-![](img/google_irc_logo.png "Google and IRC logos"){.img-responsive .center}
+*Q3.1*: Almost done! This is the last page of the study.
 
-\
-
-***Q3.1***: In December 2016, Google held a Giving Weekend and raised $X and did YYY to support International Rescue Committee’s (IRC) efforts in {ISSUE AREA: providing humanitarian assistance for refugees | advocating human rights for refugees} {in countries where nonprofit organizations are harshly restricted}.
-
-A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.
-
-*Q3.2*: How favorable do you feel towards Google?
-
-:   Single answer
-
-    - Extremely positive
-    - Somewhat positive
-    - Neither positive nor negative
-    - Somewhat negative
-    - Extremely negative
-
-*Q3.3*: How generous do you feel Google is?
-
-:   Single answer
-
-    - Extremely generous
-    - Very generous
-    - Moderately generous
-    - Slightly generous
-    - Not generous at all
-
-*Q3.4*: Rate how strongly you feel Google is committed to philanthropy:
-
-:   Single answer
-
-    - Extremely committed
-    - Very committed
-    - Moderately committed
-    - Slightly committed
-    - Not committed at all
-
-*Q3.5*: Where would you most like to see Google donate its money?
-
-:   Single answer
-
-    - Nonprofit organizations or foundations working mostly in California
-    - Nonprofit organizations or foundations working throughout the United States
-    - Nonprofit organizations or foundations working mostly in foreign countries
-
-*Q3.6*: Why do you think Google should donate money to organizations working in X?
-
-:   Text field
-
----
-
-### Demographics
-
-***Q4.1***: Almost done! This is the last page of the study.
-
-*Q4.2*: How often do you donate to charity (either cash or in-kind)?
+*Q3.2*: How often do you donate to charity (either cash or in-kind)?
 
@@
 
-*Q4.3*: Have you volunteered in the past 12 months?
+*Q3.3*: Have you volunteered in the past 12 months?
 
@@
 
-*Q4.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not.
+*Q3.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not.
 Others aren't that interested.
@@
 
-*Q4.5*: How would you describe your political views?
+*Q3.5*: How would you describe your political views?
 
@@
 
-*Q4.6*: What is the highest degree or level of school you have completed?
+*Q3.6*: What is the highest degree or level of school you have completed?
 
@@
 
-*Q4.7*: Aside from weddings and funerals, how often do you attend religious services?
+*Q3.7*: Aside from weddings and funerals, how often do you attend religious services?
 
@@
 
-*Q4.8*: Please select blue from the following list:
+*Q3.8*: Please select blue from the following list:
 
@@
 
-*Q4.9*: What is your gender?
+*Q3.9*: What is your gender?
 
@@
 
-*Q4.10*: What is your total household income?
+*Q3.10*: What is your total household income?
 
@@
 
-*Q4.11*: How old are you?
+*Q3.11*: How old are you?
 

### 2018-02-09 preregistration.Rmd
Rearrange site structure

@@
 ---
-title: "Preregistration & IRB"
+title: "Preregistration, design, IRB"
 date: "Last run: `r format(Sys.time(), '%F')`"
+bibliography: manuscript/bibliography.bib
 ---
 
-## Experiment preregistration
+# Preregistration
 
-We have preregistered this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).
+We will preregister this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).
 
@@
 
-We are also participating in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:
+We will also participate in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:
 
@@
 
-## Human subjects and IRB approval
+# Design
+
+## Experimental conditions
+
+| Condition            | 1 | 2 | 3 | 4 | 5 | 6 | 7 | 8 |
+|----------------------|:-:|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
+| **Crackdown**        |   |   |   |   |   |   |   |   |
+| Yes                  | • | • | • | • |   |   |   |   |
+| No                   |   |   |   |   | • | • | • | • |
+| *Expected donations* | + | + | + | + | ∅ | ∅ | ∅ | ∅ |
+|                      |   |   |   |   |   |   |   |   |
+| **Issue area**       |   |   |   |   |   |   |   |   |
+| Humanitarian service | • | • |   |   | • | • |   |   |
+| Human rights         |   |   | • | • |   |   | • | • |
+| *Expected donations* | + | + | − | − | + | + | − | − |
+|                      |   |   |   |   |   |   |   |   |
+| **Type of funding**  |   |   |   |   |   |   |   |   |
+| Government           | • |   | • |   | • |   | • |   |
+| Private              |   | • |   | • |   | • |   | • |
+| *Expected donations* | − | + | − | + | − | + | − | + |
+
+## $f^2$ power analysis
+
+The ultimate goal of our research project is to use Bayesian analysis is to test if the region of practical equivalence around the null value (i.e.
+the proposition that the average treatment effect of NGO crackdown is zero) excludes the posterior 95% HDI.
+
+In this initial pilot study, we use standard frequentist methods to perform power analysis and estimate the desired sample size.
+We will use the effect size estimates from this study to inform the prior distribution of parameter values in future Bayesian-based experiments [@Kruschke:2015, 362].
+
+```{r power-calculations}
+library(pwr)
+u_mine <- 1
+# f2_mine <- cohen.ES(test = "f2", size = "small")$effect.size
+f2_mine <- 0.02
+sig_level_mine <- 0.05
+power_mine = 0.90
+
+survey_power <- pwr.f2.test(u = u_mine, v = NULL, f2 = f2_mine, 
+                            sig.level = sig_level_mine, power = power_mine)
+
+# n = u + v + 1
+n_total <- survey_power$u + survey_power$v + 1
+n_group <- n_total / (2 * 2 * 2)
+```
+
+Cohen's rules of thumb for $f^2$ power are 0.02, 0.15, and 0.35 for small, medium, and large effect sizes.
+
+We are using a 2 × 2 × 2 design, manipulating the experimental condition, the issue area for the NGO, and the source of funding for the NGO.
+The formula for calculating the $f^2$-based sample size with [`pwr.f2.test`](https://www.rdocumentation.org/packages/pwr/versions/1.2-0/topics/pwr.f2.test) requires the following values:
+
+- `u`: degrees of freedom for the numerator. This is a 2 × 2 × 2 design, so the degrees of freedom = $(2 - 1) \times (2 - 1) \times (2 - 1) = 1$
+- `f2`: effect size. Here we use a small size, or `r f2_mine`.
+- `sig.level`: significance level, or Type I error probability. Here we use `r sig_level_mine`.
+- `power`: power of test, or 1 − Type II error probability. Here we use `r power_mine`.
+
+Given these parameters, `pwr.f2.test` yields `v`, or the degrees of freedom for the denominator. The final sample size `n` is calculated as `u + v + 1`.
+
+Thus, the total sample size is **`r round(n_total, 2)`**, with **`r round(n_group, 2)`** spread across 8 groups.
+
+---
+
+# Human subjects and IRB approval
 
@@
 
-### Project title
+## Project title
 
@@
 
-### Purpose of the study
+## Purpose of the study
 
@@
 
-### Participant activities
+## Participant activities
 
@@
 
-### Subject selection and recruitment
+## Subject selection and recruitment
 
@@
 
-### Data security and participant privacy
+## Data security and participant privacy
 
@@
 
-### Compensation
+## Compensation
 
@@
 
-Previous studies have found that including simple questions to screen for attention can improve the results of MTurk experiments and filter out workers who try to get through the HIT as quickly as possible without reading the questions.[^1] To ensure that participants only receive compensation for completing the full experiment, we include two attention check questions.
+Previous studies have found that including simple questions to screen for attention can improve the results of MTurk experiments and filter out workers who try to get through the HIT as quickly as possible without reading the questions [@BerinskyMargolisSances:2014].
+To ensure that participants only receive compensation for completing the full experiment, we include two attention check questions.
 The first (Q1.3) involves reading several sentences and following instructions to select specific responses.
 The second (Q4.8) is simpler and asks the respondent to select a single color from a list.
-
-[^1]: Adam J.
-Berinsky, Michele F.
-Margolis, and Michael W.
-Sances, “Separating the Shirkers from the Workers?
-Making Sure Respondents Pay Attention on Self-Administered Surveys,” *American Journal of Political Science* 58, no.
-3 (July 2014): 739–53.
-doi: [10.1111/ajps.12081](https://dx.doi.org/10.1111/ajps.12081)
 
@@
 
-### Risks and benefits
+## Risks and benefits
 
@@
 - Google has hosted several events to raise money for IRC, including initiatives in 2015 and 2016. We do not manipulate the amount of money raised.
+
+# References

### 2018-02-09 01_clean-data.Rmd
Move stuff from older R files to Rmd

---
title: "Clean data"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r clean-data}
library(tidyverse)
library(here)

results_file <- file.path(here(), "Data", "test_data.csv")

# Possible answers
favorability <- c("Very unfavorable", "Unfavorable", "Neutral", 
                  "Favorable", "Very favorable")
likelihood <- c("Extremely unlikely", "Somewhat unlikely", 
                "Neither likely nor unlikely", 
                "Somewhat likely", "Extremely likely")
frequency_charity <- c("Once a week", "Once a month", "Once every three months", 
                       "Once every six months", "Once a year", "Once every few years", 
                       "Never")
frequency_religion <- c("More than once a week", "Once a week", "Once or twice a month", 
                        "A few times a year", "Seldom", "Never", "Don't know")
income <- c("Less than $10,000", "$10,000 – $19,999", "$20,000 – $29,999", 
            "$30,000 – $39,999", "$40,000 – $49,999", "$50,000 – $59,999", 
            "$60,000 – $69,999", "$70,000 – $79,999", "$80,000 – $89,999", 
            "$90,000 – $99,999", "$100,000 – $149,999", "More than $150,000", 
            "Prefer not to say")
age <- c("Under 18", "18 – 24", "25 – 34", "35 – 44", "45 – 54", 
         "55 – 64", "65 – 74", "75 – 84", "85 or older")

# Qualtrics stores question information in the first 3 rows. All we care about
# are the column names in the first row.
results_meta <- read_csv(results_file, n_max = 2)

# The first 8 rows need to be skipped because the consent question has a bunch
# of line breaks and it messes with CSV line counting. The actual responses
# start on row 9. This doesn't entirely make sense, since read_csv can read the
# line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
results_raw <- read_csv(results_file, skip = 8,
                        col_names = colnames(results_meta))

results <- results_raw %>%
  # Only select necessary columns
  select(id = ResponseId, duration = `Duration (in seconds)`,
         start_date = StartDate, end_date = EndDate,
         crackdown, issue, funding, starts_with("Q")) %>%
  rename(favor_humanitarian = Q2.1_1, favor_human_rights = Q2.1_2, 
         favor_development = Q2.1_3, donate_likely = Q2.3, 
         amount_donate = Q2.4_1, amount_keep = Q2.4_2, amount_why = Q2.5,
         give_charity = Q3.2, volunteer = Q3.3, political_knowledge = Q3.4,
         ideology = Q3.5, education = Q3.6, religiosity = Q3.7,
         gender = Q3.9, gender_other = Q3.9_4_TEXT, income = Q3.10, age = Q3.11) %>%
  # Clean up experimental condition columns
  mutate(issue = recode(issue, `human rights for refugees` = "Human rights",
                        `humanitarian assistance for refugees` = "Humanitarian assistance"),
         funding = recode(funding, `government donors` = "Government",
                          `individual, private donors` = "Private")) %>%
  mutate(crackdown = ifelse(str_detect(crackdown, "harshly restrict"), 
                            "Crackdown", "No crackdown"))
```

### 2018-02-09 02_results.Rmd
Move stuff from older R files to Rmd

---
title: "Results"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r skeleton, eval=FALSE}

# Check distribution of experimental conditions
results %>% count(crackdown, issue, funding)

# Average amount donated, by condition
# Individual frames
results %>% group_by(crackdown) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(issue) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(funding) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, funding) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, issue) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, issue, funding) %>% summarize(avg_donation = mean(amount_donate))

# Amount / propensity to donate based on predisposition towards nonprofits
# Amount / propensity to donate based on charitableness
# Amount / propensity to donate based on voluntarism
# Amount / propensity to donate based on political knowledge
# Amount / propensity to donate based on political ideology
# Amount / propensity to donate based on education
# Amount / propensity to donate based on religiosity
# Amount / propensity to donate based on gender
# Amount / propensity to donate based on income
# Amount / propensity to donate based on age

# Control for all those things

```

```{r stuff}
#   mutate(likelihood_bin = fct_recode(likelihood,
#                                      Unlikely = "Extremely unlikely",
#                                      Unlikely = "Somewhat unlikely",
#                                      Unlikely = "Neither likely nor unlikely",
#                                      Likely = "Somewhat likely",
#                                      Likely = "Extremely likely"))
#   
# plot(results$likelihood)
# plot(results$likelihood_bin)
```

```{r var-summary}
# results_summary <- results %>%
#   select(favorability, donation, keep,
#          crackdown, issue, funding)
```

```{r check-balance}
# balance <- results %>%
#   group_by(crackdown) %>%
#   summarise_at(vars(volunteered), mean)  # THIS IS WRONG THOUGH
```

```{r}
# wilcox.test(donation ~ crackdown, data = results) 
# t.test(donation ~ crackdown, data = results)
```

- Demographic balance across main crackdown condition

- Differences of these across conditions:

    - Mean likelihood
    - Mean likelihood collapsed to binary
    - Mean donation to NGO
    - Mean amount kept for person

- Modeling:

    - donation ~ frames (OLS)
    - likelihood binary  ~ frames (multinomial)
    - likelihood ~ frames (multinomial)
    - those models with controls

### 2018-03-13 01_clean-data.Rmd
Factorize and dichotomize variables

@@
 
-```{r clean-data}
+```{r clean-data, warning=FALSE, message=FALSE}
 library(tidyverse)
@@
                   "Favorable", "Very favorable")
+
 likelihood <- c("Extremely unlikely", "Somewhat unlikely", 
@@
                 "Somewhat likely", "Extremely likely")
+
 frequency_charity <- c("Once a week", "Once a month", "Once every three months", 
@@
                        "Never")
+
+frequency_public_affairs <- c("Most of the time", "Some of the time", 
+                              "Only now and then", "Hardly at all")
+
+levels_ideology <- c("Strong liberal", "Liberal", "Independent, leaning liberal", 
+                     "Independent", "Independent, leaning conservative", 
+                     "Conservative", "Very conservative")
+
+levels_education <- c("Less than high school", "High school graduate", 
+                      "Some college", "2 year degree", "4 year degree", 
+                      "Graduate or professional degree", "Doctorate")
+
 frequency_religion <- c("More than once a week", "Once a week", "Once or twice a month", 
                         "A few times a year", "Seldom", "Never", "Don't know")
-income <- c("Less than $10,000", "$10,000 – $19,999", "$20,000 – $29,999", 
+
+levels_gender <- c("Female", "Male", "Transgender", "Other", "Prefer not to say")
+
+levels_income <- c("Less than $10,000", "$10,000 – $19,999", "$20,000 – $29,999", 
                    "$30,000 – $39,999", "$40,000 – $49,999", "$50,000 – $59,999", 
@@
                    "Prefer not to say")
-age <- c("Under 18", "18 – 24", "25 – 34", "35 – 44", "45 – 54", 
+
+levels_age <- c("Under 18", "18 – 24", "25 – 34", "35 – 44", "45 – 54", 
                 "55 – 64", "65 – 74", "75 – 84", "85 or older")
+
+attention1_answer <- c("Green", "Yellow")
+attention2_answer <- "Blue"
+levels_attention <- c("Correct", "Incorrect")
 
@@
   mutate(crackdown = ifelse(str_detect(crackdown, "harshly restrict"), 
-                            "Crackdown", "No crackdown"))
+                            "Crackdown", "No crackdown")) %>% 
+  # Attention checks
+  mutate(attention1_correct = str_split(Q1.3, ",") %>% 
+           map_lgl(~ all(attention1_answer %in% .) & length(.) == length(attention1_answer)),
+         attention2_correct = Q3.8 == attention2_answer) %>% 
+  # Factorize variables
+  mutate(donate_likely = factor(donate_likely, levels = likelihood, ordered = TRUE)) %>% 
+  mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
+            funs(factor(., levels = favorability, ordered = TRUE))) %>% 
+  mutate(give_charity = factor(give_charity, 
+                               levels = frequency_charity, ordered = TRUE),
+         political_knowledge = factor(political_knowledge, 
+                                      levels = frequency_public_affairs, ordered = TRUE),
+         ideology = factor(ideology, levels = levels_ideology, ordered = TRUE),
+         education = factor(education, levels = levels_education, ordered = TRUE),
+         religiosity = factor(religiosity, levels = frequency_religion, ordered = TRUE),
+         gender = recode(gender, `Other:` = "Other"),
+         gender = factor(gender, levels = levels_gender, ordered = TRUE),
+         income = factor(income, levels = levels_income, ordered = TRUE),
+         age = factor(age, levels = levels_age, ordered = TRUE),
+         check1 = factor(attention1_correct, levels = c(TRUE, FALSE),
+                         labels = levels_attention, ordered = TRUE),
+         check2 = factor(attention2_correct, levels = c(TRUE, FALSE),
+                         labels = levels_attention, ordered = TRUE)) %>% 
+  # Dichotomize variables
+  mutate(donate_likely_bin = fct_recode(donate_likely,
+                                        `Not likely` = "Extremely unlikely",
+                                        `Not likely` = "Somewhat unlikely",
+                                        `Not likely` = "Neither likely nor unlikely",
+                                        Likely = "Somewhat likely",
+                                        Likely = "Extremely likely")) %>% 
+  mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
+            funs(bin = fct_recode(., 
+                                  `Not favorable` = "Very unfavorable",
+                                  `Not favorable` = "Unfavorable",
+                                  `Not favorable` = "Neutral",
+                                  Favorable = "Favorable",
+                                  Favorable = "Very favorable")))
+
+saveRDS(results, file.path(here(), "data", "results_clean.rds"))
 ```

### 2018-03-13 lib/graphics.R
Movec general settings out

@@ -1,0 +1,36 @@
+# Color palette from ColorBrewer, diverging spectral, 5 categories
+# http://colorbrewer2.org/#type=diverging&scheme=Spectral&n=3
+#
+# library(RColorBrewer)
+# RColorBrewer::brewer.pal(5, "Spectral")
+ngo_red <- "#D7191C"
+ngo_orange <- "#FDAE61"
+ngo_yellow <- "#FFFFBF"
+ngo_green <- "#ABDDA4"
+ngo_blue <- "#2B83BA"
+
+favorability_cols_5 <- data_frame(value = c("Very unfavorable", "Unfavorable", "Neutral", 
+                                            "Favorable", "Very favorable"),
+                                  color = c(ngo_red, ngo_orange, ngo_yellow,
+                                            ngo_green, ngo_blue))
+
+theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed") {
+  update_geom_defaults("label", list(family = "Encode Sans Condensed Medium"))
+  update_geom_defaults("text", list(family = "Encode Sans Condensed Medium"))
+  
+  ret <- theme_bw(base_size, base_family) +
+    theme(plot.title = element_text(size = rel(1.4), face = "plain",
+                                    family = "Encode Sans Condensed SemiBold"),
+          plot.subtitle = element_text(size = rel(1), face = "plain",
+                                       family = "Encode Sans Condensed Light"),
+          plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
+                                      family = "Encode Sans Condensed Light"),
+          strip.text = element_text(size = rel(1), face = "plain",
+                                    family = "Encode Sans Condensed SemiBold"),
+          panel.border = element_blank(), 
+          axis.ticks = element_blank(),
+          strip.background = element_rect(fill = "#ffffff", colour = NA),
+          legend.title = element_text(size = rel(0.8)),
+          legend.position = "bottom")
+  ret
+}

### 2018-03-13 lib/pander_options.R

@@ -1,0 +1,7 @@
+panderOptions("table.split.table", Inf)
+panderOptions("table.split.cells", Inf)
+panderOptions("missing", "")
+panderOptions("big.mark", ",")
+panderOptions("digits", 3)
+panderOptions("round", 3)
+panderOptions("table.alignment.default", "left")

### 2018-03-13 02_analysis.Rmd
Magic summary stats table

---
title: "Results"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggstance)
library(pander)
library(scales)
library(skimr)
library(janitor)
library(here)

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))

# Helpful functions
safe_mean <- function(x, ...) suppressWarnings(mean(as.numeric(x), ...))
safe_sd <- function(x, ...) suppressWarnings(sd(as.numeric(x), ...))

my_as_numeric <- function(x) {
  is_num <- suppressWarnings(!any(is.na(as.numeric(x))))

  if (is_num) {
    as.numeric(x)
  } else {
    x
  }
}

level_summary <- function(x, variable, df = results) {
  variable <- as.character(variable)
  if (is.factor(df[[variable]])) {
    x_levels <- levels(df[[variable]])
  } else {
    x_levels <- unique(df[[variable]])
  }

  data_frame(x) %>% 
    count(x) %>%
    mutate(pct = n / sum(n),
           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
           x = factor(x, levels = x_levels, ordered = TRUE)) %>% 
    arrange(x) %>% 
    pull(fancy) %>% 
    paste(collapse = " | ")
}

numeric_summary <- function(x) {
  paste0("Mean: ", round(mean(x, na.rm = TRUE), 2), 
         " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2),
         " | ", inline_hist(x))
}

my_summary <- function(x, variable, df) {
  x <- my_as_numeric(x)

  if (is.numeric(x)) {
    numeric_summary(x)
  } else {
    level_summary(x, variable, df)
  }
}
```

# Overview of data

## Balance of experimental conditions

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  janitor::adorn_totals(where = "row") %>% 
  pandoc.table()
```

## Descriptive statistics

```{r tbl-descriptive-statistics, results="asis", warning=FALSE}
vars_to_summarize <- tribble(
  ~variable, ~clean_name,
  "donate_likely", "Likelihood of donation",
  "donate_likely_bin", "Likelihood of donation (binary)",
  "amount_donate", "Amount hypothetically donated ($)",
  "favor_humanitarian", "Prior favorability towards humanitarian NGOs",
  "favor_humanitarian_bin", "Prior favorability towards humanitarian NGOs (binary)",
  "favor_human_rights", "Prior favorability towards human rights NGOs",
  "favor_human_rights_bin", "Prior favorability towards human rights NGOs (binary)",
  "favor_development", "Prior favorability towards development NGOs",
  "favor_development_bin", "Prior favorability towards development NGOs (binary)",
  "give_charity", "Frequency of charitable donations",
  "volunteer", "Volunteered in past 12 months",
  "political_knowledge", "Frequency of following public affairs",
  "ideology", "Political views",
  "education", "Education",
  "religiosity", "Frequency of attending religious services",
  "gender", "Gender",
  "income", "Income",
  "age", "Age",
  "check1", "Attention check 1",
  "check2", "Attention check 2"
)

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  gather(variable, value) %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(N = data %>% map_int(~ nrow(.)),
         Details = map2_chr(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
  arrange(variable) %>% 
  select(-data, -variable) %>% 
  select(Variable = clean_name, everything())

results_summary_stats %>% knitr::kable()
```

```{r fig-ngo-favorability, fig.width=7, fig.height=4}
ngo_favorability_raw <- results %>%
  select(favor_humanitarian, favor_human_rights, favor_development) %>% 
  gather(variable, value) %>% 
  count(variable, value) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  left_join(favorability_cols_5, by = "value") %>% 
  mutate(clean_name = str_replace(clean_name, "towards", "towards\n")) %>% 
  mutate(value = factor(value, levels = levels(results$favor_humanitarian), ordered = TRUE),
         clean_name = fct_inorder(clean_name, ordered = TRUE)) %>%
  arrange(value) %>% 
  mutate(color = fct_inorder(color, ordered = TRUE))

ngo_favorability_high <- ngo_favorability_raw %>% 
  filter(!str_detect(value, "nfav")) %>% 
  mutate(n = ifelse(value == "Neutral", n / 2, n),
         n_plot = n,
         value = fct_rev(value), color = fct_rev(color))

ngo_favorability_low <- ngo_favorability_raw %>% 
  filter(str_detect(value, "nfav") | value == "Neutral") %>% 
  mutate(n = ifelse(value == "Neutral", n / 2, n),
         n_plot = -n)

ggplot(mapping = aes(x = n_plot, y = clean_name, fill = color)) +
  geom_barh(data = ngo_favorability_high, stat = "identity") +
  geom_barh(data = ngo_favorability_low, stat = "identity") +
  geom_vline(xintercept = 0, color = "black") +
  scale_x_continuous(labels = abs) +
  scale_fill_identity(labels = levels(ngo_favorability_raw$value), 
                      breaks = levels(ngo_favorability_raw$color),
                      guide = "legend", name = NULL) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank())
```

```{r skeleton, eval=FALSE}
# Amount donated by binary likelihood of donation
results %>% group_by(donate_likely_bin) %>% summarize(avg_donation = mean(amount_donate))

# Individual frames
results %>% group_by(crackdown) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(issue) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(funding) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, funding) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, issue) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, issue, funding) %>% summarize(avg_donation = mean(amount_donate))

# Amount / propensity to donate based on predisposition towards nonprofits
# Amount / propensity to donate based on charitableness
# Amount / propensity to donate based on voluntarism
# Amount / propensity to donate based on political knowledge
# Amount / propensity to donate based on political ideology
# Amount / propensity to donate based on education
# Amount / propensity to donate based on religiosity
# Amount / propensity to donate based on gender
# Amount / propensity to donate based on income
# Amount / propensity to donate based on age

# Control for all those things

```

```{r}
# wilcox.test(donation ~ crackdown, data = results) 
# t.test(donation ~ crackdown, data = results)
```

- Demographic balance across main crackdown condition

- Differences of these across conditions:

    - Mean likelihood
    - Mean likelihood collapsed to binary
    - Mean donation to NGO
    - Mean amount kept for person

- Modeling:

    - donation ~ frames (OLS)
    - likelihood binary  ~ frames (multinomial)
    - likelihood ~ frames (multinomial)
    - those models with controls

### 2018-03-15 01_clean-data.Rmd
Make conditions factors

@@
                             "Crackdown", "No crackdown")) %>% 
+  mutate(crackdown = factor(crackdown, levels = c("No crackdown", "Crackdown"), 
+                            ordered = TRUE),
+         issue = factor(issue, levels = c("Human rights", "Humanitarian assistance"), 
+                        ordered = TRUE),
+         funding = factor(funding, levels = c("Government", "Private"), 
+                          ordered = TRUE)) %>% 
   # Attention checks

### 2018-03-15 lib/graphics.R
Add some axis title margin

@@ -28,8 +28,10 @@ theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed") {
           strip.text = element_text(size = rel(1), face = "plain",
                                     family = "Encode Sans Condensed SemiBold"),
           panel.border = element_blank(), 
-          axis.ticks = element_blank(),
           strip.background = element_rect(fill = "#ffffff", colour = NA),
+          axis.ticks = element_blank(),
+          axis.title.x = element_text(margin = margin(t = 10)),
+          legend.margin = margin(t = 0),
           legend.title = element_text(size = rel(0.8)),
           legend.position = "bottom")
   ret

### 2018-03-15 02_analysis.Rmd
PHEW. ANOVA-like modeling with rstanarm and 3-way interactions

@@
 library(tidyverse)
+library(rstanarm)
+library(broom)
+library(coda)
 library(ggstance)
@@
 library(janitor)
+library(huxtable)
 library(here)
@@
 source(file.path(here(), "lib", "pander_options.R"))
+source(file.path(here(), "lib", "modeling.R"))
 
@@
 }
+
+if (isTRUE(getOption('knitr.in.progress'))) {
+  file_format <- rmarkdown::all_output_formats(knitr::current_input())
+} else {
+  file_format <- ""
+}
+
+print_hux <- function(x) {
+  if ("html_document" %in% file_format) {
+    print_html(x)
+  } else if ("pdf_document" %in% file_format) {
+    print_latex(x)
+  } else if ("word_document" %in% file_format) {
+    print_md(x)
+  } else {
+    print(x)
+  }
+}
 ```
@@
 
-## Descriptive statistics
+## Descriptive statistics table
 
@@
 
+## Visualize important variables
+
 ```{r fig-ngo-favorability, fig.width=7, fig.height=4}
@@
 
-```{r skeleton, eval=FALSE}
-# Amount donated by binary likelihood of donation
-results %>% group_by(donate_likely_bin) %>% summarize(avg_donation = mean(amount_donate))
+## Average likelihood and amount donated across conditions
 
-# Individual frames
-results %>% group_by(crackdown) %>% summarize(avg_donation = mean(amount_donate))
-results %>% group_by(issue) %>% summarize(avg_donation = mean(amount_donate))
-results %>% group_by(funding) %>% summarize(avg_donation = mean(amount_donate))
-results %>% group_by(crackdown, funding) %>% summarize(avg_donation = mean(amount_donate))
-results %>% group_by(crackdown, issue) %>% summarize(avg_donation = mean(amount_donate))
-results %>% group_by(crackdown, issue, funding) %>% summarize(avg_donation = mean(amount_donate))
+```{r tbl-results-conditions, results="asis"}
+conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
+                                group_by(results, crackdown, issue) %>% nest(),
+                                group_by(results, crackdown) %>% nest(),
+                                results %>% nest()) %>% 
+  arrange(crackdown, issue, funding) %>% 
+  mutate(summary = data %>%
+           map(~ summarize(., pct_likely = table(donate_likely_bin)[["Likely"]] /
+                             length(donate_likely_bin),
+                           mean_donation = mean(amount_donate, na.rm = TRUE),
+                           sd_donation = sd(amount_donate, na.rm = TRUE),
+                           N = nrow(.)))) %>% 
+  unnest(summary) %>% select(-data)
 
-# Amount / propensity to donate based on predisposition towards nonprofits
-# Amount / propensity to donate based on charitableness
-# Amount / propensity to donate based on voluntarism
-# Amount / propensity to donate based on political knowledge
-# Amount / propensity to donate based on political ideology
-# Amount / propensity to donate based on education
-# Amount / propensity to donate based on religiosity
-# Amount / propensity to donate based on gender
-# Amount / propensity to donate based on income
-# Amount / propensity to donate based on age
+conditions_summary_clean <- conditions_summary %>% 
+  mutate(funding = ifelse(is.na(funding) & !is.na(issue) , "*Total*", as.character(funding)),
+         issue = ifelse(is.na(issue) & !is.na(crackdown), "*Total*", as.character(issue)),
+         crackdown = ifelse(is.na(crackdown), "*Total*", as.character(crackdown))) %>% 
+  group_by(crackdown) %>% 
+  mutate(issue = replace(issue, duplicated(issue), NA)) %>% 
+  ungroup() %>% 
+  mutate(crackdown = replace(crackdown, duplicated(crackdown), NA)) %>% 
+  mutate(pct_likely = percent(pct_likely)) %>% 
+  rename(`Crackdown condition` = crackdown, `Issue condition` = issue,
+         `Funding condition` = funding, `% likely to donate` = pct_likely,
+         `Amount donated (mean)` = mean_donation, `Amount donated (sd)` = sd_donation)
 
-# Control for all those things
-
+conditions_summary_clean %>% pandoc.table()
 ```
 
-```{r}
-# wilcox.test(donation ~ crackdown, data = results) 
-# t.test(donation ~ crackdown, data = results)
+\
+
+# Interpreting models
+
+This is like using ANOVA, but more complex and flexible. Coefficients represent changes from the baseline intercept value.
+
+# Amount donated
+
+## Models
+
+```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
+# Basic interaction models
+m_amount_crackdown <- 
+  stan_glm(amount_donate ~ crackdown,
+           data = results, family = gaussian(),
+           prior = student_t(df = 1, location = 0),
+           prior_intercept = student_t(df = 1, location = 0),
+           chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+m_amount_crackdown_issue <- 
+  update(m_amount_crackdown, . ~ . + issue + crackdown * issue)
+
+m_amount_crackdown_issue_funding <- 
+  update(m_amount_crackdown, . ~ . + 
+           issue + funding + crackdown * issue + crackdown * funding + 
+           issue * funding + crackdown * issue * funding)
+
+# Interaction models with extra controls
+m_amount_crackdown_full <- 
+  update(m_amount_crackdown, . ~ . + 
+           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+
+m_amount_crackdown_issue_full <- 
+  update(m_amount_crackdown_issue, . ~ . + 
+           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+
+m_amount_crackdown_issue_funding_full <- 
+  update(m_amount_crackdown_issue_funding, . ~ . + 
+           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+
+# m_propensity_small <- stan_glm(donate_likely_bin ~ crackdown + issue + funding + 
+#                                  crackdown * issue + crackdown * funding + issue * funding +
+#                                  crackdown * issue * funding,
+#                                data = results, family = binomial(link = "logit"),
+#                                prior = student_t(df = 1, location = 0),
+#                                prior_intercept = student_t(df = 1, location = 0),
+#                                chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
 ```
 
-- Demographic balance across main crackdown condition
+```{r models-table, results="asis"}
+huxreg(m_amount_crackdown, m_amount_crackdown_issue, 
+       m_amount_crackdown_issue_funding, 
+       m_amount_crackdown_full, m_amount_crackdown_issue_full, 
+       m_amount_crackdown_issue_funding_full,
+       coefs = clean_coefs_named,
+       statistics = model_stats_bayes,
+       stars = NULL) %>% 
+  print_hux()
+```
 
-- Differences of these across conditions:
+## Coefficient plot
 
-    - Mean likelihood
-    - Mean likelihood collapsed to binary
-    - Mean donation to NGO
-    - Mean amount kept for person
+```{r models-plot}
+coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
+                           model = list(m_amount_crackdown_issue_funding,
+                                        m_amount_crackdown_issue_funding_full)) %>% 
+  mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
+                                         conf.method = "HPDinterval"))) %>% 
+  unnest(tidy) %>% 
+  left_join(clean_coefs, by = "term") %>% 
+  filter(term_clean != "Intercept")
 
-- Modeling:
+ggplot(coefs_amount, aes(x = estimate, y = fct_rev(term_clean_fct), 
+                         color = fct_rev(model_name))) +
+  geom_pointrangeh(aes(xmin = conf.high, xmax = conf.low), 
+                   position = position_dodgev(height = 0.5)) +
+  geom_vline(xintercept = 0) + 
+  scale_color_manual(values = c(ngo_red, ngo_blue), 
+                     guide = guide_legend(title = NULL, reverse = TRUE)) +
+  labs(x = "Posterior median estimate + 90% credible interval", y = NULL) +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+```
 
-    - donation ~ frames (OLS)
-    - likelihood binary  ~ frames (multinomial)
-    - likelihood ~ frames (multinomial)
-    - those models with controls
+## Predicted medians
+
+```{r models-predicted}
+newdata_conditions <- results %>% 
+  expand(nesting(crackdown, issue, funding))
+
+posterior_fit <- posterior_predict(m_amount_crackdown_issue_funding, 
+                                   newdata = newdata_conditions,
+                                   re.form = NA, draws = 50, seed = BAYES_SEED)
+
+nested_draws <- posterior_fit %>% 
+  as_data_frame() %>% 
+  gather(id, value) %>% 
+  group_by(id) %>%
+  nest()
+
+all_posterior_draws <- bind_cols(newdata_conditions, nested_draws) %>% unnest(data)
+
+newdata <- newdata_conditions %>% 
+  bind_cols(tidyMCMC(as.mcmc(posterior_fit), conf.int = TRUE, 
+                     conf.level = 0.9, conf.method = "HPDinterval"))
+
+ggplot(newdata, aes(y = estimate, x = funding)) + 
+  geom_point(data = all_posterior_draws, aes(y = value, x = funding), 
+             color = "grey50", size = 1.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
+  scale_y_continuous(labels = dollar) +
+  labs(x = "Funding", y = "Average amount donated") +
+  coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  facet_wrap(~ crackdown + issue)
+```

### 2018-03-15 lib/modeling.R

@@ -1,0 +1,44 @@
+# Stan stuff
+CHAINS <- 4
+ITER <-2000
+WARMUP <- 1000
+BAYES_SEED <- 1234
+options(mc.cores = parallel::detectCores())
+
+# By default, R uses polynomial contrasts for ordered factors in linear models
+# options("contrasts") 
+# So make ordered factors use treatment contrasts instead
+options(contrasts = rep("contr.treatment", 2))
+# Or do it on a single variable:
+# contrasts(df$x) <- "contr.treatment"
+
+
+clean_coefs <- tribble(
+  ~term, ~term_clean,
+  "(Intercept)", "Intercept",
+  "crackdownCrackdown", "Crackdown (yes)",
+  "issueHumanitarian assistance", "Issue (humanitarian)",
+  "fundingPrivate", "Funding (private)",
+  "crackdownCrackdown:issueHumanitarian assistance", "Crackdown × Issue",
+  "crackdownCrackdown:fundingPrivate", "Crackdown × Funding",
+  "issueHumanitarian assistance:fundingPrivate", "Issue × Funding",
+  "crackdownCrackdown:issueHumanitarian assistance:fundingPrivate", "Crackdown × Issue × Funding",
+  "favor_humanitarian_binFavorable", "Prior favorability towards humanitarian NGOs",
+  "favor_human_rights_binFavorable", "Prior favorability towards human rights NGOs",
+  "favor_development_binFavorable", "Prior favorability towards development NGOs"
+) %>% 
+  mutate(term_clean_fct = fct_inorder(term_clean, ordered = TRUE))
+
+model_stats_ols = c(Observations = "nobs", 
+                    R2 = "r.squared", 
+                    `Adjusted R2` = "adj.r.squared",
+                    `Residual Std. Error` = "sigma",
+                    `Residual Std. Error (df)` = "df.residual",
+                    "AIC")
+
+model_stats_bayes <- c(Observations = "nobs",
+                       `Posterior sample size` = "pss",
+                       Sigma = "sigma")
+
+clean_coefs_named <- clean_coefs %>% pull(term) %>% 
+  set_names(clean_coefs$term_clean)

### 2018-03-15 02_analysis.Rmd
Add explanation of which coefficients to add

@@
 
-# Interpreting models
+# Interpreting interactions in models
 
-This is like using ANOVA, but more complex and flexible. Coefficients represent changes from the baseline intercept value.
+Ordinarily, people use ANOVA to analyze 3-way, 2 × 2 × 2 factorial designs, [like this](https://mypages.valdosta.edu/mwhatley/3600/2x2x2.htm).
+A more flexible ([yet identical!](https://www.theanalysisfactor.com/why-anova-and-linear-regression-are-the-same-analysis/)) way to do this is to use a regular regression model with interaction terms for each of the conditions, like so (here we use three, since we can use simper models to get averages for the larger umbrella groups, like just crackdowns and crackdown + issue):
+
+- Model 1:
+
+    $$
+    y = \beta_0 + \beta_1 \text{Crackdown}
+    $$
+
+- Model 2:
+
+    $$
+    \begin{aligned}
+    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue } + \\
+    & \beta_3 \text{Crackdown} \times \text{Issue}
+    \end{aligned}
+    $$
+
+- Model 3:
+
+    $$
+    \begin{aligned}
+    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue} + \beta_3 \text{Funding } + \\
+    & \beta_4 \text{Crackdown} \times \text{Issue } + \\
+    & \beta_5 \text{Crackdown} \times \text{Funding } + \\
+    & \beta_6 \text{Issue} \times \text{Funding } + \\
+    & \beta_7 \text{Crackdown} \times \text{Issue} \times \text{Funding}
+    \end{aligned}
+    $$
+
+Adding different combinations of the coefficients provides the average values for each combination of factors, which corresponds to the average likelihood and amount donated table above.
+
+```{r interaction-interpretation, results="asis"}
+model1 <- "1"
+model2 <- "2"
+model3 <- "3"
+
+interpretation <- tribble(
+  ~Model, ~`Coefficients to add together`,
+  model3, "Intercept",
+  model3, "Intercept + Funding",
+  model2, "Intercept",
+  model3, "Intercept + Issue",
+  model3, "Intercept + Issue + Funding + (Issue × Funding)",
+  model2, "Intercept + Issue",
+  model1, "Intercept",
+  model3, "Intercept + Crackdown",
+  model3, "Intercept + Crackdown + Funding + (Crackdown × Funding)",
+  model2, "Intercept + Crackdown",
+  model3, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
+  model3, "Intercept + Crackdown + Issue + Funding + (Crackdown × Issue) + (Crackdown × Funding) + (Issue × Funding) + (Crackdown × Issue × Funding)",
+  model2, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
+  model1, "Intercept + Crackdown"
+)
+
+conditions_summary_clean %>% 
+  select(1:3) %>% 
+  slice(-n()) %>% 
+  bind_cols(interpretation) %>% 
+  pandoc.table()
+```
 

### 2018-03-15 02_analysis.Rmd
Plot predicted medians

@@
 
-```{r models-predicted}
-newdata_conditions <- results %>% 
-  expand(nesting(crackdown, issue, funding))
+**Just the crackdown condition**
+
+```{r models-predicted-crackdown}
+newdata_conditions <- results %>% expand(nesting(crackdown))
+
+posterior_fit <- posterior_predict(m_amount_crackdown, 
+                                   newdata = newdata_conditions,
+                                   re.form = NA, draws = 50, seed = BAYES_SEED)
+
+nested_draws <- posterior_fit %>% 
+  as_data_frame() %>% 
+  gather(id, value) %>% 
+  group_by(id) %>%
+  nest()
+
+all_posterior_draws <- bind_cols(newdata_conditions, nested_draws) %>% unnest(data)
+
+newdata <- newdata_conditions %>% 
+  bind_cols(tidyMCMC(as.mcmc(posterior_fit), conf.int = TRUE, 
+                     conf.level = 0.9, conf.method = "HPDinterval"))
+
+ggplot(newdata, aes(y = estimate, x = crackdown)) + 
+  geom_point(data = all_posterior_draws, aes(y = value, x = crackdown), 
+             color = "grey50", size = 1.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
+  scale_y_continuous(labels = dollar) +
+  labs(x = "Crackdown condition", y = "Median amount donated") +
+  coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos()
+```
+
+**Crackdown and issue conditions**
+
+```{r models-predicted-crackdown-issue}
+newdata_conditions <- results %>% expand(nesting(crackdown, issue))
+
+posterior_fit <- posterior_predict(m_amount_crackdown, 
+                                   newdata = newdata_conditions,
+                                   re.form = NA, draws = 50, seed = BAYES_SEED)
+
+nested_draws <- posterior_fit %>% 
+  as_data_frame() %>% 
+  gather(id, value) %>% 
+  group_by(id) %>%
+  nest()
+
+all_posterior_draws <- bind_cols(newdata_conditions, nested_draws) %>% unnest(data)
+
+newdata <- newdata_conditions %>% 
+  bind_cols(tidyMCMC(as.mcmc(posterior_fit), conf.int = TRUE, 
+                     conf.level = 0.9, conf.method = "HPDinterval"))
+
+ggplot(newdata, aes(y = estimate, x = crackdown)) + 
+  geom_point(data = all_posterior_draws, aes(y = value, x = crackdown), 
+             color = "grey50", size = 1.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
+  scale_y_continuous(labels = dollar) +
+  labs(x = "Crackdown condition", y = "Median amount donated") +
+  coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  facet_wrap(~ issue)
+```
+
+**Crackdown, issue, and funding conditions**
+
+```{r models-predicted-crackdown-issue-funding}
+newdata_conditions <- results %>% expand(nesting(crackdown, issue, funding))
 
@@
 
-ggplot(newdata, aes(y = estimate, x = funding)) + 
-  geom_point(data = all_posterior_draws, aes(y = value, x = funding), 
+ggplot(newdata, aes(y = estimate, x = crackdown)) + 
+  geom_point(data = all_posterior_draws, aes(y = value, x = crackdown), 
              color = "grey50", size = 1.5, alpha = 0.25) +
@@
   scale_y_continuous(labels = dollar) +
-  labs(x = "Funding", y = "Average amount donated") +
+  labs(x = "Crackdown condition", y = "Median amount donated") +
   coord_cartesian(ylim = c(0, 100)) +
   theme_ngos() +
-  facet_wrap(~ crackdown + issue)
+  facet_wrap(~ issue + funding)
 ```

### 2018-03-16 lib/graphics.R
Add density option

@@ -14,7 +14,7 @@ favorability_cols_5 <- data_frame(value = c("Very unfavorable", "Unfavorable", "
                                   color = c(ngo_red, ngo_orange, ngo_yellow,
                                             ngo_green, ngo_blue))
 
-theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed") {
+theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", density = FALSE) {
   update_geom_defaults("label", list(family = "Encode Sans Condensed Medium"))
   update_geom_defaults("text", list(family = "Encode Sans Condensed Medium"))
   
@@ -34,5 +34,14 @@ theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed") {
           legend.margin = margin(t = 0),
           legend.title = element_text(size = rel(0.8)),
           legend.position = "bottom")
-  ret
+  
+  if (density) {
+    ret <- ret +
+      theme(panel.grid = element_blank(),
+            axis.title.y = element_blank(),
+            axis.text.y = element_blank(),
+            strip.text = element_text(margin = margin(5, 0, 2, 0, "pt")))
+  } else {
+    ret
+  }
 }

### 2018-03-16 02_analysis.Rmd
🎉 ¡Differences between groups! 🎉

--- 2018-03-15 02_analysis.Rmd
@@
 library(ggstance)
+library(patchwork)
 library(pander)
@@
   }
+}
+
+mcmc_pairwise_diffs <- function(chains) {
+  # Calculate the pairwise differences between columns
+  # Adapted from http://stackoverflow.com/a/28187446/120898
+  pair_names <- outer(colnames(chains), colnames(chains),
+                      paste, sep = " − ")
+  pairs_to_omit <- which(lower.tri(pair_names, diag = TRUE))
+
+  mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
+                      function(x, y) chains[,x] - chains[,y]) %>% 
+    magrittr::set_colnames(pair_names) %>% 
+    select(-pairs_to_omit)
+
+  return(mcmc_diffs)
+}
+
+tidy_diffs <- function(diffs_pairs) {
+  diffs_pairs %>% 
+    gather(pair, value) %>% 
+    group_by(pair) %>% 
+    summarise(mean = mean(value),
+              median = median(value),
+              q2.5 = quantile(value, probs = 0.025),
+              q5 = quantile(value, probs = 0.05),
+              q25 = quantile(value, probs = 0.25),
+              q75 = quantile(value, probs = 0.75),
+              q95 = quantile(value, probs = 0.95),
+              q97.5 = quantile(value, probs = 0.975),
+              p.greater0 = mean(value > 0),
+              p.less0 = mean(value < 0))
 }
@@
 # Basic interaction models
-m_amount_crackdown <- 
-  stan_glm(amount_donate ~ crackdown,
+m_amount_c <- stan_glm(amount_donate ~ crackdown,
                        data = results, family = gaussian(),
@@
 
-m_amount_crackdown_issue <- 
-  update(m_amount_crackdown, . ~ . + issue + crackdown * issue)
+m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)
 
-m_amount_crackdown_issue_funding <- 
-  update(m_amount_crackdown, . ~ . + 
+m_amount_cif <- update(m_amount_c, . ~ . + 
                          issue + funding + crackdown * issue + crackdown * funding + 
@@
 # Interaction models with extra controls
-m_amount_crackdown_full <- 
-  update(m_amount_crackdown, . ~ . + 
+m_amount_c_full <- update(m_amount_c, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
 
-m_amount_crackdown_issue_full <- 
-  update(m_amount_crackdown_issue, . ~ . + 
+m_amount_ci_full <- update(m_amount_ci, . ~ . + 
                              favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
 
-m_amount_crackdown_issue_funding_full <- 
-  update(m_amount_crackdown_issue_funding, . ~ . + 
+m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                              favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
@@
 ```{r models-table, results="asis"}
-huxreg(m_amount_crackdown, m_amount_crackdown_issue, 
-       m_amount_crackdown_issue_funding, 
-       m_amount_crackdown_full, m_amount_crackdown_issue_full, 
-       m_amount_crackdown_issue_funding_full,
+huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
+       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
        coefs = clean_coefs_named,
@@
 coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
-                           model = list(m_amount_crackdown_issue_funding,
-                                        m_amount_crackdown_issue_funding_full)) %>% 
+                           model = list(m_amount_cif,
+                                        m_amount_cif_full)) %>% 
   mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
@@
 
-```{r models-predicted}
-newdata_conditions <- results %>% 
-  expand(nesting(crackdown, issue, funding))
+The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution.
+But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates.
+If I use the full force of `posterior_predict()`, I add more uncertainty with each added coefficient (so in a 2×2×2 version, the 8th condition is actually the sum of all 8 coefficients, which means it gets 8 levels of uncertainity, which is probably excessive).
+But we do it both ways too, just to be on the safe side.
 
-posterior_fit <- posterior_predict(m_amount_crackdown_issue_funding, 
-                                   newdata = newdata_conditions,
-                                   re.form = NA, draws = 50, seed = BAYES_SEED)
+```{r amount-median-c}
+newdata_conditions_c <- results %>% expand(nesting(crackdown))
 
-nested_draws <- posterior_fit %>% 
+chains_fitted_c <- posterior_linpred(m_amount_c, 
+                                   newdata = newdata_conditions_c)
+
+# posterior_fit <- posterior_predict(m_amount_c, 
+#                                    newdata = newdata_conditions_c,
+#                                    draws = 50, seed = BAYES_SEED)
+
+coef_summary_c <- newdata_conditions_c %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+# newdata <- newdata_conditions %>% 
+#   bind_cols(tidyMCMC(as.mcmc(posterior_fit), estimate.method = "median",
+#                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_amount_c <- ggplot(coef_summary_c, aes(y = estimate, x = crackdown)) + 
+  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
+  #            color = "grey50", size = 0.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  scale_y_continuous(labels = dollar) +
+  labs(x = NULL, y = "Median amount donated") +
+  # coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank())
+```
+
+```{r amount-median-ci}
+newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))
+
+chains_fitted_ci <- posterior_linpred(m_amount_ci, 
+                                   newdata = newdata_conditions_ci)
+
+coef_summary_ci <- newdata_conditions_ci %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_ci), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_amount_ci <- ggplot(coef_summary_ci, aes(y = estimate, x = crackdown)) + 
+  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
+  #            color = "grey50", size = 0.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
+  scale_y_continuous(labels = dollar) +
+  labs(x = NULL, y = "Median amount donated") +
+  # coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank(),
+        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
+  facet_wrap(~ issue)
+```
+
+```{r amount-median-cif}
+newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))
+
+chains_fitted_cif <- posterior_linpred(m_amount_cif, 
+                                   newdata = newdata_conditions_cif)
+
+coef_summary_cif <- newdata_conditions_cif %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_cif), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_amount_cif <- ggplot(coef_summary_cif, aes(y = estimate, x = crackdown)) + 
+  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
+  #            color = "grey50", size = 0.5, alpha = 0.5) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
+  scale_y_continuous(labels = dollar) +
+  labs(x = NULL, y = "Median amount donated") +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank(),
+        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
+  facet_wrap(~ issue + funding)
+```
+
+```{r plot-all-amount-medians, fig.width=8, fig.height=6}
+((plot_amount_c + 
+   labs(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
+        subtitle = "90% credible intervals shown around each point")) / 
+   plot_amount_ci) | plot_amount_cif
+```
+
+## Differences in medians
+
+```{r amount-diffs-c}
+diffs_coef_pairs_c <- chains_fitted_c %>% 
   as_data_frame() %>% 
-  gather(id, value) %>% 
-  group_by(id) %>%
+  magrittr::set_colnames(levels(newdata_conditions_c$crackdown)) %>% 
+  mcmc_pairwise_diffs()
+
+diffs_coef_pairs_detail_c <- tidy_diffs(diffs_coef_pairs_c)
+
+pairs_plot_data_c <- diffs_coef_pairs_c %>%
+  gather(pair, value) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+
+plot_diffs_c <- ggplot() + 
+  geom_density(data = pairs_plot_data_c, aes(x = value),
+               fill = ngo_green, colour = NA, alpha = 0.4) + 
+  geom_segment(data = diffs_coef_pairs_detail_c, 
+               aes(x = q5, xend = q95, y = 0, yend = 0),
+               size = 3) +
+  geom_vline(data = diffs_coef_pairs_detail_c, aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  guides(fill = FALSE, color = FALSE) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ pair)
+```
+
+```{r amount-diffs-ci}
+# Nest each fitted chain into a single row that corresponds to each newdata_condition
+chains_nested_ci <- chains_fitted_ci %>% 
+  as_data_frame() %>% 
+  mutate(id = 1:n()) %>% 
+  gather(condition, value, -id) %>% 
+  group_by(condition) %>% 
   nest()
 
-all_posterior_draws <- bind_cols(newdata_conditions, nested_draws) %>% unnest(data)
+# Add the fitted chains to the conditions, spread the main crackdown condition
+# into two columns, then nest everything by issue
+all_chains_ci <- bind_cols(newdata_conditions_ci, chains_nested_ci) %>% 
+  unnest(data) %>% 
+  select(-condition) %>% 
+  group_by(issue) %>% 
+  spread(crackdown, value) %>% 
+  select(-id) %>% 
+  nest()
 
-newdata <- newdata_conditions %>% 
-  bind_cols(tidyMCMC(as.mcmc(posterior_fit), conf.int = TRUE, 
-                     conf.level = 0.9, conf.method = "HPDinterval"))
+# All the pairwise differences in a single data frame, grouped by issue
+pairs_conditions_ci <- all_chains_ci %>% 
+  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
+         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))
 
-ggplot(newdata, aes(y = estimate, x = funding)) + 
-  geom_point(data = all_posterior_draws, aes(y = value, x = funding), 
-             color = "grey50", size = 1.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
-  scale_y_continuous(labels = dollar) +
-  labs(x = "Funding", y = "Average amount donated") +
-  coord_cartesian(ylim = c(0, 100)) +
-  theme_ngos() +
-  facet_wrap(~ crackdown + issue)
+# Extract coefficient details and plot data
+diffs_coef_pairs_detail_ci <- pairs_conditions_ci %>% 
+  unnest(diffs_coef_pairs_detail) %>% 
+  select(-data, -diffs_coef_pairs)
+
+pairs_plot_data_ci <- pairs_conditions_ci %>% 
+  select(issue, diffs_coef_pairs) %>% 
+  unnest(diffs_coef_pairs) %>%
+  gather(pair, value, -issue) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+
+plot_diffs_ci <- ggplot() + 
+  geom_density(data = pairs_plot_data_ci, aes(x = value),
+               fill = ngo_blue, colour = NA, alpha = 0.4) + 
+  geom_segment(data = diffs_coef_pairs_detail_ci, 
+               aes(x = q5, xend = q95, y = 0, yend = 0),
+               size = 3) +
+  geom_vline(data = diffs_coef_pairs_detail_ci, aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  guides(fill = FALSE, color = FALSE) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ issue + pair)
 ```
+
+```{r amount-diffs-cif}
+# Nest each fitted chain into a single row that corresponds to each newdata_condition
+chains_nested_cif <- chains_fitted_cif %>% 
+  as_data_frame() %>% 
+  mutate(id = 1:n()) %>% 
+  gather(condition, value, -id) %>% 
+  group_by(condition) %>% 
+  nest()
+
+# Add the fitted chains to the conditions, spread the main crackdown condition
+# into two columns, then nest everything by issue
+all_chains_cif <- bind_cols(newdata_conditions_cif, chains_nested_cif) %>% 
+  unnest(data) %>% 
+  select(-condition) %>% 
+  group_by(issue, funding) %>% 
+  spread(crackdown, value) %>% 
+  select(-id) %>% 
+  nest()
+
+# All the pairwise differences in a single data frame, grouped by issue
+pairs_conditions_cif <- all_chains_cif %>% 
+  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
+         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))
+
+# Extract coefficient details and plot data
+diffs_coef_pairs_detail_cif <- pairs_conditions_cif %>% 
+  unnest(diffs_coef_pairs_detail) %>% 
+  select(-data, -diffs_coef_pairs)
+
+pairs_plot_data_cif <- pairs_conditions_cif %>% 
+  select(issue, funding, diffs_coef_pairs) %>% 
+  unnest(diffs_coef_pairs) %>%
+  gather(pair, value, -issue, -funding) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+
+plot_diffs_cif <- ggplot() + 
+  geom_density(data = pairs_plot_data_cif, aes(x = value),
+               fill = ngo_red, colour = NA, alpha = 0.4) + 
+  geom_segment(data = diffs_coef_pairs_detail_cif, 
+               aes(x = q5, xend = q95, y = 0, yend = 0),
+               size = 3) +
+  geom_vline(data = diffs_coef_pairs_detail_cif, aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  guides(fill = FALSE, color = FALSE) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ issue + funding + pair)
+```
+
+```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
+((plot_diffs_c + 
+   labs(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
+        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
+   plot_diffs_ci) | plot_diffs_cif
+```
+
+```{r tbl-all-amount-diffs, results="asis"}
+bind_rows(diffs_coef_pairs_detail_c,
+          diffs_coef_pairs_detail_ci,
+          diffs_coef_pairs_detail_cif) %>% 
+  select(Issue = issue, Funding = funding, 
+         `No crackdown − crackdown (median)` = median, 
+         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
+  pandoc.table(missing = "—", 
+               caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions')
+```

### 2018-03-16 02_analysis.Rmd
Rearrange and add skeleton for likelihood
Add link to Stan discussions over posterior_linepred

@@
 
-## Visualize important variables
+## Average likelihood and amount donated across conditions
+
+```{r tbl-results-conditions, results="asis"}
+conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
+                                group_by(results, crackdown, issue) %>% nest(),
+                                group_by(results, crackdown) %>% nest(),
+                                results %>% nest()) %>% 
+  arrange(crackdown, issue, funding) %>% 
+  mutate(summary = data %>%
+           map(~ summarize(., pct_likely = table(donate_likely_bin)[["Likely"]] /
+                             length(donate_likely_bin),
+                           mean_donation = mean(amount_donate, na.rm = TRUE),
+                           sd_donation = sd(amount_donate, na.rm = TRUE),
+                           N = nrow(.)))) %>% 
+  unnest(summary) %>% select(-data)
+
+conditions_summary_clean <- conditions_summary %>% 
+  mutate(funding = ifelse(is.na(funding) & !is.na(issue) , "*Total*", as.character(funding)),
+         issue = ifelse(is.na(issue) & !is.na(crackdown), "*Total*", as.character(issue)),
+         crackdown = ifelse(is.na(crackdown), "*Total*", as.character(crackdown))) %>% 
+  group_by(crackdown) %>% 
+  mutate(issue = replace(issue, duplicated(issue), NA)) %>% 
+  ungroup() %>% 
+  mutate(crackdown = replace(crackdown, duplicated(crackdown), NA)) %>% 
+  mutate(pct_likely = percent(pct_likely)) %>% 
+  rename(`Crackdown condition` = crackdown, `Issue condition` = issue,
+         `Funding condition` = funding, `% likely to donate` = pct_likely,
+         `Amount donated (mean)` = mean_donation, `Amount donated (sd)` = sd_donation)
+
+conditions_summary_clean %>% pandoc.table()
+```
+
+\
+
+# Visualize important variables
+
+## Prior favorability towards NGOs
 
@@
         panel.grid.major.y = element_blank())
-```
-
-## Average likelihood and amount donated across conditions
-
-```{r tbl-results-conditions, results="asis"}
-conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
-                                group_by(results, crackdown, issue) %>% nest(),
-                                group_by(results, crackdown) %>% nest(),
-                                results %>% nest()) %>% 
-  arrange(crackdown, issue, funding) %>% 
-  mutate(summary = data %>%
-           map(~ summarize(., pct_likely = table(donate_likely_bin)[["Likely"]] /
-                             length(donate_likely_bin),
-                           mean_donation = mean(amount_donate, na.rm = TRUE),
-                           sd_donation = sd(amount_donate, na.rm = TRUE),
-                           N = nrow(.)))) %>% 
-  unnest(summary) %>% select(-data)
-
-conditions_summary_clean <- conditions_summary %>% 
-  mutate(funding = ifelse(is.na(funding) & !is.na(issue) , "*Total*", as.character(funding)),
-         issue = ifelse(is.na(issue) & !is.na(crackdown), "*Total*", as.character(issue)),
-         crackdown = ifelse(is.na(crackdown), "*Total*", as.character(crackdown))) %>% 
-  group_by(crackdown) %>% 
-  mutate(issue = replace(issue, duplicated(issue), NA)) %>% 
-  ungroup() %>% 
-  mutate(crackdown = replace(crackdown, duplicated(crackdown), NA)) %>% 
-  mutate(pct_likely = percent(pct_likely)) %>% 
-  rename(`Crackdown condition` = crackdown, `Issue condition` = issue,
-         `Funding condition` = funding, `% likely to donate` = pct_likely,
-         `Amount donated (mean)` = mean_donation, `Amount donated (sd)` = sd_donation)
-
-conditions_summary_clean %>% pandoc.table()
 ```
@@
 ```
+
+\
 
@@
 
-The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution.
+The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution (like, [they didn't even want to invent it, and then when they did they wanted to hide it](https://github.com/stan-dev/rstanarm/issues/85), and it has a big warning in the documentation).
 But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates.
@@
 ```
+
+\
+
+# Likelihood of donation
+
+## Models
+
+## Coefficient plot
+
+## Predicted medians
+
+## Differences in medians

### 2018-03-17 02_analysis.Rmd
Add analysis of donation likelihood

@@
                              favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
-
-# m_propensity_small <- stan_glm(donate_likely_bin ~ crackdown + issue + funding + 
-#                                  crackdown * issue + crackdown * funding + issue * funding +
-#                                  crackdown * issue * funding,
-#                                data = results, family = binomial(link = "logit"),
-#                                prior = student_t(df = 1, location = 0),
-#                                prior_intercept = student_t(df = 1, location = 0),
-#                                chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
 ```
 
-```{r models-table, results="asis"}
+```{r tbl-models-amount, results="asis"}
 huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
@@
 
+```{r build-models-likely, warning=FALSE, message=FALSE, cache=TRUE}
+# Basic interaction models
+# Weakly informative normal priors, since these coefficients are log-odds
+m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
+                       data = results, family = binomial(link = "logit"),
+                       prior = normal(-1, 1),
+                       prior_intercept = normal(-1, 1),
+                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)
+
+m_likely_cif <- update(m_likely_c, . ~ . + 
+                         issue + funding + crackdown * issue + crackdown * funding + 
+                         issue * funding + crackdown * issue * funding)
+
+# Interaction models with extra controls
+m_likely_c_full <- update(m_likely_c, . ~ . + 
+                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+
+m_likely_ci_full <- update(m_likely_ci, . ~ . + 
+                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+
+m_likely_cif_full <-update(m_likely_cif, . ~ . + 
+                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+```
+
+```{r tbl-models-likely, results="asis"}
+huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
+       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
+       coefs = clean_coefs_named,
+       statistics = model_stats_bayes,
+       stars = NULL) %>% 
+  print_hux()
+```
+
 ## Coefficient plot
@@
 
+```{r likely-median-c}
+newdata_conditions_c <- results %>% expand(nesting(crackdown))
+
+# transform = TRUE does the same thing as plogis(as.matrix(m_likely_c))
+chains_fitted_likely_c <- posterior_linpred(m_likely_c, 
+                                            newdata = newdata_conditions_c, 
+                                            transform = TRUE)
+
+coef_summary_likely_c <- newdata_conditions_c %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_c), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_likely_c <- ggplot(coef_summary_likely_c, aes(y = estimate, x = crackdown)) + 
+  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
+  #            color = "grey50", size = 0.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  scale_y_continuous(labels = percent) +
+  labs(x = NULL, y = "Probability of donating") +
+  # coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank())
+```
+
+```{r likely-median-ci}
+newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))
+
+chains_fitted_likely_ci <- posterior_linpred(m_likely_ci, 
+                                             newdata = newdata_conditions_ci,
+                                             transform = TRUE)
+
+coef_summary_likely_ci <- newdata_conditions_ci %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_ci), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_likely_ci <- ggplot(coef_summary_likely_ci, aes(y = estimate, x = crackdown)) + 
+  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
+  #            color = "grey50", size = 0.5, alpha = 0.25) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
+  scale_y_continuous(labels = percent) +
+  labs(x = NULL, y = "Probability of donating") +
+  # coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank(),
+        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
+  facet_wrap(~ issue)
+```
+
+```{r likely-median-cif}
+newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))
+
+chains_fitted_likely_cif <- posterior_linpred(m_likely_cif, 
+                                              newdata = newdata_conditions_cif,
+                                              transform = TRUE)
+
+coef_summary_likely_cif <- newdata_conditions_cif %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_cif), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_likely_cif <- ggplot(coef_summary_likely_cif, aes(y = estimate, x = crackdown)) + 
+  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
+  #            color = "grey50", size = 0.5, alpha = 0.5) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
+  scale_y_continuous(labels = percent) +
+  labs(x = NULL, y = "Probability of donating") +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank(),
+        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
+  facet_wrap(~ issue + funding)
+```
+
+```{r plot-all-likely-medians, fig.width=8, fig.height=6}
+((plot_likely_c + 
+   labs(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
+        subtitle = "90% credible intervals shown around each point")) / 
+   plot_likely_ci) | plot_likely_cif
+```
+
 ## Differences in medians
+
+```{r likely-diffs-c}
+diffs_coef_likely_pairs_c <- chains_fitted_likely_c %>% 
+  as_data_frame() %>% 
+  magrittr::set_colnames(levels(newdata_conditions_c$crackdown)) %>% 
+  mcmc_pairwise_diffs()
+
+diffs_coef_likely_pairs_detail_c <- tidy_diffs(diffs_coef_likely_pairs_c)
+
+pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c %>%
+  gather(pair, value) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+
+plot_diffs_likely_c <- ggplot() + 
+  geom_density(data = pairs_likely_plot_data_c, aes(x = value),
+               fill = ngo_green, colour = NA, alpha = 0.4) + 
+  geom_segment(data = diffs_coef_likely_pairs_detail_c, 
+               aes(x = q5, xend = q95, y = 0, yend = 0),
+               size = 3) +
+  geom_vline(data = diffs_coef_likely_pairs_detail_c, 
+             aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  guides(fill = FALSE, color = FALSE) +
+  scale_x_continuous(labels = percent) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ pair)
+```
+
+```{r likely-diffs-ci}
+# Nest each fitted chain into a single row that corresponds to each newdata_condition
+chains_nested_likely_ci <- chains_fitted_likely_ci %>% 
+  as_data_frame() %>% 
+  mutate(id = 1:n()) %>% 
+  gather(condition, value, -id) %>% 
+  group_by(condition) %>% 
+  nest()
+
+# Add the fitted chains to the conditions, spread the main crackdown condition
+# into two columns, then nest everything by issue
+all_chains_likely_ci <- bind_cols(newdata_conditions_ci, 
+                                  chains_nested_likely_ci) %>% 
+  unnest(data) %>% 
+  select(-condition) %>% 
+  group_by(issue) %>% 
+  spread(crackdown, value) %>% 
+  select(-id) %>% 
+  nest()
+
+# All the pairwise differences in a single data frame, grouped by issue
+pairs_likely_conditions_ci <- all_chains_likely_ci %>% 
+  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
+         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))
+
+# Extract coefficient details and plot data
+diffs_coef_likely_pairs_detail_ci <- pairs_likely_conditions_ci %>% 
+  unnest(diffs_coef_pairs_detail) %>% 
+  select(-data, -diffs_coef_pairs)
+
+pairs_likely_plot_data_ci <- pairs_likely_conditions_ci %>% 
+  select(issue, diffs_coef_pairs) %>% 
+  unnest(diffs_coef_pairs) %>%
+  gather(pair, value, -issue) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+
+plot_diffs_likely_ci <- ggplot() + 
+  geom_density(data = pairs_likely_plot_data_ci, aes(x = value),
+               fill = ngo_blue, colour = NA, alpha = 0.4) + 
+  geom_segment(data = diffs_coef_likely_pairs_detail_ci, 
+               aes(x = q5, xend = q95, y = 0, yend = 0),
+               size = 3) +
+  geom_vline(data = diffs_coef_likely_pairs_detail_ci, 
+             aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  guides(fill = FALSE, color = FALSE) +
+  scale_x_continuous(labels = percent) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ issue + pair)
+```
+
+```{r likely-diffs-cif}
+# Nest each fitted chain into a single row that corresponds to each newdata_condition
+chains_nested_likely_cif <- chains_fitted_likely_cif %>% 
+  as_data_frame() %>% 
+  mutate(id = 1:n()) %>% 
+  gather(condition, value, -id) %>% 
+  group_by(condition) %>% 
+  nest()
+
+# Add the fitted chains to the conditions, spread the main crackdown condition
+# into two columns, then nest everything by issue
+all_chains_likely_cif <- bind_cols(newdata_conditions_cif, 
+                                   chains_nested_likely_cif) %>% 
+  unnest(data) %>% 
+  select(-condition) %>% 
+  group_by(issue, funding) %>% 
+  spread(crackdown, value) %>% 
+  select(-id) %>% 
+  nest()
+
+# All the pairwise differences in a single data frame, grouped by issue
+pairs_likely_conditions_cif <- all_chains_likely_cif %>% 
+  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
+         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))
+
+# Extract coefficient details and plot data
+diffs_coef_likely_pairs_detail_cif <- pairs_likely_conditions_cif %>% 
+  unnest(diffs_coef_pairs_detail) %>% 
+  select(-data, -diffs_coef_pairs)
+
+pairs_likely_plot_data_cif <- pairs_likely_conditions_cif %>% 
+  select(issue, funding, diffs_coef_pairs) %>% 
+  unnest(diffs_coef_pairs) %>%
+  gather(pair, value, -issue, -funding) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+
+plot_diffs_likely_cif <- ggplot() + 
+  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
+               fill = ngo_red, colour = NA, alpha = 0.4) + 
+  geom_segment(data = diffs_coef_likely_pairs_detail_cif, 
+               aes(x = q5, xend = q95, y = 0, yend = 0),
+               size = 3) +
+  geom_vline(data = diffs_coef_likely_pairs_detail_cif, 
+             aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  guides(fill = FALSE, color = FALSE) +
+  scale_x_continuous(labels = percent) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ issue + funding + pair)
+```
+
+```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
+((plot_diffs_likely_c + 
+   labs(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
+        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
+   plot_diffs_likely_ci) | plot_diffs_likely_cif
+```
+
+```{r tbl-all-likely-diffs, results="asis"}
+bind_rows(diffs_coef_likely_pairs_detail_c,
+          diffs_coef_likely_pairs_detail_ci,
+          diffs_coef_likely_pairs_detail_cif) %>% 
+  select(Issue = issue, Funding = funding, 
+         `No crackdown − crackdown (median)` = median, 
+         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
+  pandoc.table(missing = "—", 
+               caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions')
+```

### 2018-03-20 01_clean-data.Rmd
Dichotomize everything

@@
 
+# Calculate the quantile (and median) of an ordered factor
+# Borrowed from @jrnold: https://gist.github.com/jrnold/6759254
+#
+# In the case of ties, the first in order will win. For instance, 
+# bloop <- factor(c("A", "A", "B", "B"), ordered = TRUE)
+# median(bloop)  # "A"
+quantile.ordered <- function(x, probs = seq(0, 1, 0.25)) {
+  tab <- table(x)
+  cdf <- cumsum(tab / sum(tab))
+  idx <- sapply(probs, function(p) min(which(cdf >= p)))
+  levels(x)[idx] 
+}
+
+quantile.factor <- quantile.ordered
+median.ordered <- function(x) quantile(x, 0.5)
+median.factor <- median.ordered
+
+# Load data
 results_file <- file.path(here(), "Data", "test_data.csv")
@@
                                levels = frequency_charity, ordered = TRUE),
+         volunteer = factor(volunteer, levels = c("No", "Yes"), ordered = TRUE),
          political_knowledge = factor(political_knowledge, 
@@
                                   Favorable = "Favorable",
-                                  Favorable = "Very favorable")))
+                                  Favorable = "Very favorable"))) %>% 
+  mutate(give_charity_3 = fct_recode(give_charity,
+                                     `At least once a month` = "Once a week",
+                                     `At least once a month` = "Once a month",
+                                     `Once a month-once a year` = "Once every three months",
+                                     `Once a month-once a year` = "Once every six months",
+                                     `Once a month-once a year` = "Once a year",
+                                     Rarely = "Once every few years",
+                                     Rarely = "Never") %>% fct_rev()) %>% 
+  mutate(political_knowledge_bin = fct_recode(political_knowledge,
+                                              `Often` = "Most of the time",
+                                              `Often` = "Some of the time",
+                                              `Not often` = "Only now and then",
+                                              `Not often` = "Hardly at all") %>% fct_rev()) %>% 
+  mutate(ideology_3 = fct_recode(ideology,
+                                 `Liberal` = "Strong liberal",
+                                 `Liberal` = "Liberal",
+                                 `Liberal` = "Independent, leaning liberal",
+                                 `Independent` = "Independent",
+                                 `Conservative` = "Independent, leaning conservative",
+                                 `Conservative` = "Conservative",
+                                 `Conservative` = "Very conservative") %>% fct_rev()) %>% 
+  mutate(ideology_bin = fct_recode(ideology_3,
+                                   `Not liberal` = "Independent",
+                                   `Not liberal` = "Conservative")) %>% 
+  mutate(education_bin = fct_recode(education,
+                                    `No BA` = "Less than high school",
+                                    `No BA` = "High school graduate",
+                                    `No BA` = "Some college",
+                                    `No BA` = "2 year degree",
+                                    `BA and above` = "4 year degree",
+                                    `BA and above` = "Graduate or professional degree",
+                                    `BA and above` = "Doctorate")) %>% 
+  mutate(religiosity_bin = fct_recode(religiosity,
+                                      `At least once a month` = "More than once a week",
+                                      `At least once a month` = "Once a week",
+                                      `At least once a month` = "Once or twice a month",
+                                      `Rarely` = "A few times a year",
+                                      `Rarely` = "Seldom",
+                                      `Rarely` = "Never",
+                                      NULL = "Don't know") %>% fct_rev()) %>% 
+  mutate(income_clean = fct_recode(income, NULL = "Prefer not to say"),
+         income_bin = factor(income_clean >= median(.$income), levels = c(FALSE, TRUE),
+                             labels = paste(c("Less than", "At least"), median(.$income)))) %>% 
+  mutate(age_bin = factor(age >= median(.$age), levels = c(FALSE, TRUE),
+                          labels = paste(c("Less than", "At least"), median(.$age))))
 

### 2018-03-20 02_analysis.Rmd
Use actual full models

@@
 m_amount_c_full <- update(m_amount_c, . ~ . + 
-                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
+                            give_charity_3 + volunteer + political_knowledge_bin +
+                            ideology_bin + education_bin + religiosity_bin +
+                            income_bin + age_bin)
 
 m_amount_ci_full <- update(m_amount_ci, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
 
 m_amount_cif_full <-update(m_amount_cif, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
 ```
@@
 m_likely_c_full <- update(m_likely_c, . ~ . + 
-                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
+                            give_charity_3 + volunteer + political_knowledge_bin +
+                            ideology_bin + education_bin + religiosity_bin +
+                            income_bin + age_bin)
 
 m_likely_ci_full <- update(m_likely_ci, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
 
 m_likely_cif_full <-update(m_likely_cif, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
+                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
 ```
@@
        stars = NULL) %>% 
+  quick_docx()
   print_hux()

### 2018-03-20 lib/modeling.R

@@ -25,7 +25,16 @@ clean_coefs <- tribble(
   "crackdownCrackdown:issueHumanitarian assistance:fundingPrivate", "Crackdown × Issue × Funding",
   "favor_humanitarian_binFavorable", "Prior favorability towards humanitarian NGOs",
   "favor_human_rights_binFavorable", "Prior favorability towards human rights NGOs",
-  "favor_development_binFavorable", "Prior favorability towards development NGOs"
+  "favor_development_binFavorable", "Prior favorability towards development NGOs",
+  "give_charity_3Once a month-once a year", "Give to charity once a month–once a year",
+  "give_charity_3At least once a month", "Give to charity at least once a month",
+  "volunteerYes", "Volunteered in past year",
+  "political_knowledge_binOften", "Follow current political evens often",
+  "ideology_binLiberal", "Liberal political views",
+  "education_binBA and above", "Bachelor's degree or higher",
+  "religiosity_binAt least once a month", "Attend religious services at least once a month",
+  "income_binAt least $60,000 – $69,999", "Income $60,000 or higher",
+  "age_binAt least 45 – 54", "Age 45 or higher"
 ) %>% 
   mutate(term_clean_fct = fct_inorder(term_clean, ordered = TRUE))
 

### 2018-03-21 02_analysis.Rmd
Specify better priors

@@
                        data = results, family = gaussian(),
-                       prior = student_t(df = 1, location = 0),
-                       prior_intercept = student_t(df = 1, location = 0),
+                       prior = cauchy(location = 0, scale = 2.5),
+                       prior_intercept = cauchy(location = 0, scale = 10),
                        chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
@@
 # Basic interaction models
-# Weakly informative normal priors, since these coefficients are log-odds
+# Weakly informative student t priors, since these coefficients are log-odds
+# See https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations#prior-for-the-regression-coefficients-in-logistic-regression-non-sparse-case and https://arxiv.org/abs/1507.07170
 m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
                        data = results, family = binomial(link = "logit"),
-                       prior = normal(-1, 1),
-                       prior_intercept = normal(-1, 1),
+                       prior = student_t(3, 0, 2.5),
+                       prior_intercept = student_t(3, 0, 10),
                        chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
@@
        stars = NULL) %>% 
-  quick_docx()
   print_hux()

### 2018-03-24 01_clean-data.Rmd
Modify to work with real data

@@
 # Load data
-results_file <- file.path(here(), "Data", "test_data.csv")
+# results_file <- file.path(here(), "data", "test_data.csv")
+results_file <- file.path(here(), "private", 
+                          "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")
 
@@
 
-# The first 8 rows need to be skipped because the consent question has a bunch
+# The first 10 rows need to be skipped because the consent question has a bunch
 # of line breaks and it messes with CSV line counting. The actual responses
-# start on row 9. This doesn't entirely make sense, since read_csv can read the
+# start on row 11. This doesn't entirely make sense, since read_csv can read the
 # line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
-results_raw <- read_csv(results_file, skip = 8,
+results_raw <- read_csv(results_file, skip = 10,
                         col_names = colnames(results_meta))
 
+# Confirmation codes to exclude. These are people who failed the attention
+# checks or who took the survey outside of MTurk.
+#
+# The code for determining these is in a script that is excluded from the main
+# repository because of privacy issues (it deals directly with MTurk worker
+# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
+codes_to_exclude <- readLines(file.path(here(), "data", "codes_to_exclude.txt")) %>% 
+  as.numeric()
+
+# Clean everything
 results <- results_raw %>%
   # Only select necessary columns
-  select(id = ResponseId, duration = `Duration (in seconds)`,
+  select(id = ResponseId, confirmation_code = mTurkCode, duration = `Duration (in seconds)`,
          start_date = StartDate, end_date = EndDate,
@@
          attention2_correct = Q3.8 == attention2_answer) %>% 
+  # This person contacted me separately to say that they accidentally did the first
+  # attention check wrong, but that they did pay attention: 6518634
+  mutate(attention1_correct = ifelse(confirmation_code == 6518634,
+                                     TRUE, attention1_correct)) %>% 
+  filter(!(confirmation_code %in% codes_to_exclude)) %>%
   # Factorize variables
@@
 saveRDS(results, file.path(here(), "data", "results_clean.rds"))
+write_csv(results, file.path(here(), "data", "results_clean.csv"))
 ```

### 2018-03-24 lib/modeling.R

@@ -33,8 +33,8 @@ clean_coefs <- tribble(
   "ideology_binLiberal", "Liberal political views",
   "education_binBA and above", "Bachelor's degree or higher",
   "religiosity_binAt least once a month", "Attend religious services at least once a month",
-  "income_binAt least $60,000 – $69,999", "Income $60,000 or higher",
-  "age_binAt least 45 – 54", "Age 45 or higher"
+  "income_binAt least $50,000 – $59,999", "Income $50,000 or higher",
+  "age_binAt least 35 – 44", "Age 35 or higher"
 ) %>% 
   mutate(term_clean_fct = fct_inorder(term_clean, ordered = TRUE))
 

### 2018-03-30 02_analysis.Rmd
Output figures and tables

@@
               p.greater0 = mean(value > 0),
-              p.less0 = mean(value < 0))
+              p.less0 = mean(value < 0),
+              p.diff.not0 = ifelse(median > 0, p.greater0, p.less0))
 }
+```
+
+# Miscellaneous details
+
+## Average time to complete survey
+
+```{r avg-time}
+results %>% summarize(min = min(duration),
+                      max = max(duration),
+                      mean = mean(duration),
+                      sd = sd(duration),
+                      median = median(duration))
+```
+
+## Attention check #2
+
+```{r attention-check-2}
+results %>% count(attention2_correct)
 ```
@@
 results %>% count(crackdown, issue, funding) %>% 
-  janitor::adorn_totals(where = "row") %>% 
-  pandoc.table()
+  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
+  janitor::adorn_totals(where = "row") %T>% 
+  pandoc.table() %>% 
+  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-experimental-conditions.md"))
 ```
@@
   "amount_donate", "Amount hypothetically donated ($)",
+  "gender", "Gender",
+  "age", "Age",
+  "income", "Income",
+  "education", "Education",
+  "religiosity", "Frequency of attending religious services",
+  "ideology", "Political views",
+  "political_knowledge", "Frequency of following public affairs",
+  "give_charity", "Frequency of charitable donations",
+  "volunteer", "Volunteered in past 12 months",
   "favor_humanitarian", "Prior favorability towards humanitarian NGOs",
@@
   "favor_development_bin", "Prior favorability towards development NGOs (binary)",
-  "give_charity", "Frequency of charitable donations",
-  "volunteer", "Volunteered in past 12 months",
-  "political_knowledge", "Frequency of following public affairs",
-  "ideology", "Political views",
-  "education", "Education",
-  "religiosity", "Frequency of attending religious services",
-  "gender", "Gender",
-  "income", "Income",
-  "age", "Age",
-  "check1", "Attention check 1",
   "check2", "Attention check 2"
@@
 
-results_summary_stats %>% knitr::kable()
+results_summary_stats %>% 
+  select(-N) %>% 
+  pandoc.table.return(caption = "Descriptive statistics {#tbl:descriptive-stats}",
+                      split.cell = 80, split.table = Inf) %T>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-descriptive-stats.md")) %>% 
+  cat()
 ```
@@
 
-conditions_summary_clean %>% pandoc.table()
+conditions_summary_clean %T>% 
+  pandoc.table() %>% 
+  pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-avg-results.md"))
 ```
@@
   slice(-n()) %>% 
-  bind_cols(interpretation) %>% 
-  pandoc.table()
+  bind_cols(interpretation) %T>% 
+  pandoc.table() %>% 
+  pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-coefficients-to-add.md"))
 ```
@@
 
-```{r tbl-models-amount, results="asis"}
+```{r tbl-models-amount, warning=FALSE, results="asis"}
 huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
@@
        statistics = model_stats_bayes,
-       stars = NULL) %>% 
-  print_hux()
+       stars = NULL) %T>% 
+  print_hux() %>% 
+  to_md(max_width = 100) %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
 ```
@@
    plot_amount_ci) | plot_amount_cif
+
+((plot_amount_c / plot_amount_ci) | 
+    plot_amount_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
+         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
+         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
 ```
@@
    plot_diffs_ci) | plot_diffs_cif
+
+((plot_diffs_c / plot_diffs_ci) | 
+    plot_diffs_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
+         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.png"),
+         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
 ```
@@
          `No crackdown − crackdown (median)` = median, 
-         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
-  pandoc.table(missing = "—", 
-               caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions')
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(missing = "—", 
+                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions') %T>%
+  cat() %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
 ```
@@
 
-```{r tbl-models-likely, results="asis"}
+```{r tbl-models-likely, warning=FALSE, results="asis"}
 huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
@@
        statistics = model_stats_bayes,
-       stars = NULL) %>% 
-  print_hux()
+       stars = NULL) %T>% 
+  print_hux() %>% 
+  to_md(max_width = 100) %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood.md"))
 ```
@@
    plot_likely_ci) | plot_likely_cif
+
+((plot_likely_c / plot_likely_ci) | 
+    plot_likely_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
+         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
+         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
 ```
@@
    plot_diffs_likely_ci) | plot_diffs_likely_cif
+
+((plot_diffs_likely_c / plot_diffs_likely_ci) | 
+    plot_diffs_likely_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),
+         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.png"),
+         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
 ```
@@
          `No crackdown − crackdown (median)` = median, 
-         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
-  pandoc.table(missing = "—", 
-               caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions')
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(missing = "—", 
+                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions') %T>%
+  cat() %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
 ```

### 2018-03-30 lib/graphics.R

@@ -24,7 +24,8 @@ theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", de
           plot.subtitle = element_text(size = rel(1), face = "plain",
                                        family = "Encode Sans Condensed Light"),
           plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
-                                      family = "Encode Sans Condensed Light"),
+                                      family = "Encode Sans Condensed Light",
+                                      margin = margin(t = 10)),
           strip.text = element_text(size = rel(1), face = "plain",
                                     family = "Encode Sans Condensed SemiBold"),
           panel.border = element_blank(), 

### 2018-03-30 01_clean-data.Rmd
Use CSVY to be cool

@@
 library(here)
+library(csvy)
 
@@
 saveRDS(results, file.path(here(), "data", "results_clean.rds"))
-write_csv(results, file.path(here(), "data", "results_clean.csv"))
+write_csvy(results, file = file.path(here(), "data", "results_clean.csv"),
+           metadata = file.path(here(), "data", "results_clean.yaml"), na = "NA")
 ```

### 2018-03-30 02_analysis.Rmd
Use actual plots instead of faked unicode sparkbars

@@
 library(scales)
-library(skimr)
 library(janitor)
@@
 
-  data_frame(x) %>% 
+  factor_summary <- data_frame(x) %>% 
     count(x) %>%
@@
            fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
-           x = factor(x, levels = x_levels, ordered = TRUE)) %>% 
-    arrange(x) %>% 
-    pull(fancy) %>% 
-    paste(collapse = " | ")
-}
-
-numeric_summary <- function(x) {
-  paste0("Mean: ", round(mean(x, na.rm = TRUE), 2), 
-         " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2),
-         " | ", inline_hist(x))
+           x = factor(x, levels = x_levels, ordered = TRUE))
+
+  inline_summary <- factor_summary %>% arrange(x) %>% 
+    pull(fancy) %>% paste(collapse = " | ")
+
+  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
+    geom_bar(stat = "identity", fill = "black") +
+    theme_spark()
+
+  file_name <- gsub("\\.| ", "_", tolower(variable))
+  md_img <- paste0("![](../output/figures/summary-table/", file_name, ".pdf)")
+
+  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
+                                       paste0(file_name, ".pdf")), 
+         width = 1, height = 0.2, device = cairo_pdf)
+  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
+                                       paste0(file_name, ".png")), 
+         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)
+
+  output <- data_frame(spark = md_img, summary = inline_summary)
+}
+
+numeric_summary <- function(x, variable) {
+  inline_summary <- paste0("Median: ", round(median(x, na.rm = TRUE), 2),
+                           " | Mean: ", round(mean(x, na.rm = TRUE), 2), 
+                           " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2))
+
+  fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
+    geom_histogram(fill = "black", binwidth = 10) +
+    theme_spark()
+
+  file_name <- gsub("\\.| ", "_", tolower(variable))
+  md_img <- paste0("![](../output/figures/summary-table/", file_name, ".pdf)")
+
+  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
+                                        paste0(file_name, ".pdf")), 
+         width = 1, height = 0.2, device = cairo_pdf)
+  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
+                                        paste0(file_name, ".png")), 
+         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)
+
+  output <- data_frame(spark = md_img, summary = inline_summary)
 }
@@
   if (is.numeric(x)) {
-    numeric_summary(x)
+    numeric_summary(x, variable)
   } else {
@@
   mutate(N = data %>% map_int(~ nrow(.)),
-         Details = map2_chr(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
+         summary = map2(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
   left_join(vars_to_summarize, by = "variable") %>% 
@@
   select(-data, -variable) %>% 
-  select(Variable = clean_name, everything())
+  unnest(summary) %>% 
+  select(Variable = clean_name, N, ` ` = spark, Details = summary)
 

### 2018-03-30 lib/graphics.R

@@ -14,6 +14,14 @@ favorability_cols_5 <- data_frame(value = c("Very unfavorable", "Unfavorable", "
                                   color = c(ngo_red, ngo_orange, ngo_yellow,
                                             ngo_green, ngo_blue))
 
+theme_spark <- function() {
+  theme(line = element_blank(), rect = element_blank(), text = element_blank(), 
+        panel.border = element_blank(),
+        panel.background = element_rect(fill = "transparent", color = NA),
+        plot.background = element_rect(fill = "transparent", color = NA),
+        plot.margin = unit(c(0, 0, -0.25, -0.25), "lines"))
+}
+
 theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", density = FALSE) {
   update_geom_defaults("label", list(family = "Encode Sans Condensed Medium"))
   update_geom_defaults("text", list(family = "Encode Sans Condensed Medium"))

### 2018-03-30 02_analysis.Rmd
Use gray instead of black

@@
   fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
-    geom_bar(stat = "identity", fill = "black") +
+    geom_bar(stat = "identity", fill = "grey50") +
     theme_spark()
@@
   fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
-    geom_histogram(fill = "black", binwidth = 10) +
+    geom_histogram(fill = "grey50", binwidth = 10) +
     theme_spark()

### 2018-04-07 lib/graphics.R
Better section titles

@@ -1,5 +1,7 @@
+# Colors ------------------------------------------------------------------
+
 # Color palette from ColorBrewer, diverging spectral, 5 categories
-# http://colorbrewer2.org/#type=diverging&scheme=Spectral&n=3
+# http://colorbrewer2.org/#type=diverging&scheme=Spectral&n=5
 #
 # library(RColorBrewer)
 # RColorBrewer::brewer.pal(5, "Spectral")
@@ -13,6 +15,9 @@ favorability_cols_5 <- data_frame(value = c("Very unfavorable", "Unfavorable", "
                                             "Favorable", "Very favorable"),
                                   color = c(ngo_red, ngo_orange, ngo_yellow,
                                             ngo_green, ngo_blue))
+
+
+# ggplot themes -----------------------------------------------------------
 
 theme_spark <- function() {
   theme(line = element_blank(), rect = element_blank(), text = element_blank(), 

### 2018-04-07 lib/pander_options.R

@@ -1,3 +1,5 @@
+# Universal pandoc options ------------------------------------------------
+
 panderOptions("table.split.table", Inf)
 panderOptions("table.split.cells", Inf)
 panderOptions("missing", "")

### 2018-04-07 02_analysis.Rmd
Move helper functions out

@@
 }
-
-if (isTRUE(getOption('knitr.in.progress'))) {
-  file_format <- rmarkdown::all_output_formats(knitr::current_input())
-} else {
-  file_format <- ""
-}
-
-print_hux <- function(x) {
-  if ("html_document" %in% file_format) {
-    print_html(x)
-  } else if ("pdf_document" %in% file_format) {
-    print_latex(x)
-  } else if ("word_document" %in% file_format) {
-    print_md(x)
-  } else {
-    print(x)
-  }
-}
-
-mcmc_pairwise_diffs <- function(chains) {
-  # Calculate the pairwise differences between columns
-  # Adapted from http://stackoverflow.com/a/28187446/120898
-  pair_names <- outer(colnames(chains), colnames(chains),
-                      paste, sep = " − ")
-  pairs_to_omit <- which(lower.tri(pair_names, diag = TRUE))
-
-  mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
-                      function(x, y) chains[,x] - chains[,y]) %>% 
-    magrittr::set_colnames(pair_names) %>% 
-    select(-pairs_to_omit)
-
-  return(mcmc_diffs)
-}
-
-tidy_diffs <- function(diffs_pairs) {
-  diffs_pairs %>% 
-    gather(pair, value) %>% 
-    group_by(pair) %>% 
-    summarise(mean = mean(value),
-              median = median(value),
-              q2.5 = quantile(value, probs = 0.025),
-              q5 = quantile(value, probs = 0.05),
-              q25 = quantile(value, probs = 0.25),
-              q75 = quantile(value, probs = 0.75),
-              q95 = quantile(value, probs = 0.95),
-              q97.5 = quantile(value, probs = 0.975),
-              p.greater0 = mean(value > 0),
-              p.less0 = mean(value < 0),
-              p.diff.not0 = ifelse(median > 0, p.greater0, p.less0))
-}
-```
-
-# Miscellaneous details
-
-## Average time to complete survey
-
-```{r avg-time}
-results %>% summarize(min = min(duration),
-                      max = max(duration),
-                      mean = mean(duration),
-                      sd = sd(duration),
-                      median = median(duration))
 ```

### 2018-04-07 lib/modeling.R

@@ -1,9 +1,49 @@
-# Stan stuff
+# Stan details ------------------------------------------------------------
+
 CHAINS <- 4
 ITER <-2000
 WARMUP <- 1000
 BAYES_SEED <- 1234
 options(mc.cores = parallel::detectCores())
+
+
+# Helper functions for comparing models -----------------------------------
+
+# Calculate the pairwise differences between columns
+# Adapted from http://stackoverflow.com/a/28187446/120898
+mcmc_pairwise_diffs <- function(chains) {
+  pair_names <- outer(colnames(chains), colnames(chains),
+                      paste, sep = " − ")
+  pairs_to_omit <- which(lower.tri(pair_names, diag = TRUE))
+  
+  mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
+                      function(x, y) chains[,x] - chains[,y]) %>% 
+    magrittr::set_colnames(pair_names) %>% 
+    select(-pairs_to_omit)
+  
+  return(mcmc_diffs)
+}
+
+# Summarize the differences between MCMC pairs
+tidy_diffs <- function(diffs_pairs) {
+  diffs_pairs %>% 
+    gather(pair, value) %>% 
+    group_by(pair) %>% 
+    summarise(mean = mean(value),
+              median = median(value),
+              q2.5 = quantile(value, probs = 0.025),
+              q5 = quantile(value, probs = 0.05),
+              q25 = quantile(value, probs = 0.25),
+              q75 = quantile(value, probs = 0.75),
+              q95 = quantile(value, probs = 0.95),
+              q97.5 = quantile(value, probs = 0.975),
+              p.greater0 = mean(value > 0),
+              p.less0 = mean(value < 0),
+              p.diff.not0 = ifelse(median > 0, p.greater0, p.less0))
+}
+
+
+# Ordered factor modeling setup -------------------------------------------
 
 # By default, R uses polynomial contrasts for ordered factors in linear models
 # options("contrasts") 
@@ -13,6 +53,9 @@ options(contrasts = rep("contr.treatment", 2))
 # contrasts(df$x) <- "contr.treatment"
 
 
+# Coefficient naming ------------------------------------------------------
+
+# Table of coefficients and their clean names
 clean_coefs <- tribble(
   ~term, ~term_clean,
   "(Intercept)", "Intercept",
@@ -38,6 +81,13 @@ clean_coefs <- tribble(
 ) %>% 
   mutate(term_clean_fct = fct_inorder(term_clean, ordered = TRUE))
 
[…]

### 2018-04-07 02_analysis.Rmd
Graph general likelihood and amount donated

@@
         panel.grid.major.y = element_blank())
+```
+
+## Likelihood of donation
+
+```{r fig-likelihood-bars, fig.width=9, fig.height=4}
+donate_summary <- results %>% 
+  count(donate_likely) %>% 
+  mutate(perc = n / sum(n)) %>% 
+  mutate(highlight = ifelse(donate_likely %in% c("Extremely likely", "Somewhat likely"), TRUE, FALSE))
+
+plot_donate_summary <- ggplot(donate_summary, aes(x = n, y = donate_likely, 
+                                                  fill = highlight)) +
+  geom_barh(stat = "identity") +
+  scale_x_continuous(sec.axis = sec_axis(~ . / sum(donate_summary$n),
+                                         labels = percent)) +
+  scale_fill_manual(values = c(ngo_green, ngo_blue), guide = FALSE) +
+  labs(x = NULL, y = NULL) +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_donate_summary %T>% 
+  print() %T>%
+  ggsave(., filename = file.path(here(), "output", "figures", "donate_summary.pdf"),
+         width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "donate_summary.png"),
+         width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
+```
+
+## Amount donated
+
+```{r fig-amount-bars, fig.width=9, fig.height=2.75}
+plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
+  geom_histogram(bins = 20, fill = ngo_blue) +
+  scale_x_continuous(labels = dollar) +
+  labs(x = NULL, y = NULL) +
+  theme_ngos(18) +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank())
+
+plot_amount_summary %T>% 
+  print() %T>%
+  ggsave(., filename = file.path(here(), "output", "figures", "amount_summary.pdf"),
+         width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount_summary.png"),
+         width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
 ```

### 2018-04-07 03_additional-analysis.Rmd
Move survey details to additional analysis

---
title: "Additional analysis"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(here)

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))
source(file.path(here(), "lib", "modeling.R"))

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))
```

# Miscellaneous survey details

## Average time to complete survey

```{r avg-time, results="asis"}
results %>% summarize(min = min(duration),
                      max = max(duration),
                      mean = mean(duration),
                      sd = sd(duration),
                      median = median(duration)) %>% 
  pandoc.table()
```

## Attention check #2

```{r attention-check-2, results="asis"}
results %>% count(attention2_correct) %>% pandoc.table()
```

### 2018-04-07 03_additional-analysis.Rmd
Simpler summary

@@
 ```{r avg-time, results="asis"}
-results %>% summarize(min = min(duration),
-                      max = max(duration),
-                      mean = mean(duration),
-                      sd = sd(duration),
-                      median = median(duration)) %>% 
+results %>% 
+  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
   pandoc.table()

### 2018-04-08 lib/modeling.R
Add simple model flag

@@ -57,27 +57,27 @@ options(contrasts = rep("contr.treatment", 2))
 
 # Table of coefficients and their clean names
 clean_coefs <- tribble(
-  ~term, ~term_clean,
-  "(Intercept)", "Intercept",
-  "crackdownCrackdown", "Crackdown (yes)",
-  "issueHumanitarian assistance", "Issue (humanitarian)",
-  "fundingPrivate", "Funding (private)",
-  "crackdownCrackdown:issueHumanitarian assistance", "Crackdown × Issue",
-  "crackdownCrackdown:fundingPrivate", "Crackdown × Funding",
-  "issueHumanitarian assistance:fundingPrivate", "Issue × Funding",
-  "crackdownCrackdown:issueHumanitarian assistance:fundingPrivate", "Crackdown × Issue × Funding",
-  "favor_humanitarian_binFavorable", "Prior favorability towards humanitarian NGOs",
-  "favor_human_rights_binFavorable", "Prior favorability towards human rights NGOs",
-  "favor_development_binFavorable", "Prior favorability towards development NGOs",
-  "give_charity_3Once a month-once a year", "Give to charity once a month–once a year",
-  "give_charity_3At least once a month", "Give to charity at least once a month",
-  "volunteerYes", "Volunteered in past year",
-  "political_knowledge_binOften", "Follow current political evens often",
-  "ideology_binLiberal", "Liberal political views",
-  "education_binBA and above", "Bachelor's degree or higher",
-  "religiosity_binAt least once a month", "Attend religious services at least once a month",
-  "income_binAt least $50,000 – $59,999", "Income $50,000 or higher",
-  "age_binAt least 35 – 44", "Age 35 or higher"
+  ~simple_model, ~term, ~term_clean,
+  TRUE, "(Intercept)", "Intercept",
+  TRUE, "crackdownCrackdown", "Crackdown (yes)",
+  TRUE, "issueHumanitarian assistance", "Issue (humanitarian)",
+  TRUE, "fundingPrivate", "Funding (private)",
+  TRUE, "crackdownCrackdown:issueHumanitarian assistance", "Crackdown × Issue",
+  TRUE, "crackdownCrackdown:fundingPrivate", "Crackdown × Funding",
+  TRUE, "issueHumanitarian assistance:fundingPrivate", "Issue × Funding",
+  TRUE, "crackdownCrackdown:issueHumanitarian assistance:fundingPrivate", "Crackdown × Issue × Funding",
[…]

### 2018-04-08 02_analysis.Rmd
Move survey details to additional analysis
Move full models out; compare all single conditions

@@
 }
-```
-
-## Attention check #2
-
-```{r attention-check-2}
-results %>% count(attention2_correct)
 ```
@@
   labs(x = NULL, y = NULL) +
-  theme_ngos(18) +
+  theme_ngos() +
   theme(panel.grid.major.x = element_blank(),
@@
 
-# Interaction models with extra controls
-m_amount_c_full <- update(m_amount_c, . ~ . + 
-                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
-                            give_charity_3 + volunteer + political_knowledge_bin +
-                            ideology_bin + education_bin + religiosity_bin +
-                            income_bin + age_bin)
-
-m_amount_ci_full <- update(m_amount_ci, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
-
-m_amount_cif_full <-update(m_amount_cif, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
+# Models with just issue and just funding
+m_amount_i <- update(m_amount_c, . ~ issue)
+m_amount_f <- update(m_amount_c, . ~ funding)
 ```
@@
 ```{r tbl-models-amount, warning=FALSE, results="asis"}
+# Get subset of coefficients
+coefs_to_include <- list(m_amount_c, m_amount_ci, m_amount_cif) %>% 
+  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)
+
 huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
-       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
-       coefs = clean_coefs_named,
+       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
        statistics = model_stats_bayes,
@@
   cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
-```
-
-## Coefficient plot
-
-```{r models-plot}
-coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
-                           model = list(m_amount_cif,
-                                        m_amount_cif_full)) %>% 
-  mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
-                                         conf.method = "HPDinterval"))) %>% 
-  unnest(tidy) %>% 
-  left_join(clean_coefs, by = "term") %>% 
-  filter(term_clean != "Intercept")
-
-ggplot(coefs_amount, aes(x = estimate, y = fct_rev(term_clean_fct), 
-                         color = fct_rev(model_name))) +
-  geom_pointrangeh(aes(xmin = conf.high, xmax = conf.low), 
-                   position = position_dodgev(height = 0.5)) +
-  geom_vline(xintercept = 0) + 
-  scale_color_manual(values = c(ngo_red, ngo_blue), 
-                     guide = guide_legend(title = NULL, reverse = TRUE)) +
-  labs(x = "Posterior median estimate + 90% credible interval", y = NULL) +
-  theme_ngos() +
-  theme(panel.grid.major.y = element_blank())
 ```
@@
   theme(panel.grid.major.x = element_blank())
+```
+
+```{r amount-median-i}
+newdata_conditions_i <- results %>% expand(nesting(issue))
+
+chains_fitted_i <- posterior_linpred(m_amount_i, 
+                                     newdata = newdata_conditions_i)
+
+coef_summary_i <- newdata_conditions_i %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_i), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+```
+
+```{r amount-median-f}
+newdata_conditions_f <- results %>% expand(nesting(funding))
+
+chains_fitted_f <- posterior_linpred(m_amount_f, 
+                                     newdata = newdata_conditions_f)
+
+coef_summary_f <- newdata_conditions_f %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_f), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
 ```
@@
   facet_wrap(~ issue + funding)
+```
+
+```{r plot-single-amount-medians, warning=FALSE, fig.width=7, fig.height=2.5}
+coef_summary_singles <- bind_rows(coef_summary_c, coef_summary_i, coef_summary_f) %>% 
+  gather(condition, value, crackdown, issue, funding) %>% 
+  filter(!is.na(value)) %>% 
+  mutate(value = fct_inorder(value, ordered = TRUE),
+         condition = fct_inorder(str_to_title(condition), ordered = TRUE))
+
+plot_amount_singles <- ggplot(coef_summary_singles, aes(y = estimate, x = value)) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = condition)) +
+  scale_y_continuous(labels = dollar) +
+  scale_color_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
+  labs(x = NULL, y = "Median amount donated") +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank(),
+        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
+  facet_wrap(~ condition, scales = "free_x")
+
+plot_amount_singles %T>%
+  print() %T>%
+  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.pdf"),
+         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.png"),
+         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
+```{r amount-diffs-i}
+diffs_coef_pairs_i <- chains_fitted_i %>% 
+  as_data_frame() %>% 
+  magrittr::set_colnames(levels(newdata_conditions_i$issue)) %>% 
+  mcmc_pairwise_diffs()
+
+diffs_coef_pairs_detail_i <- tidy_diffs(diffs_coef_pairs_i)
+
+pairs_plot_data_i <- diffs_coef_pairs_i %>%
+  gather(pair, value) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+```
+
+```{r amount-diffs-f}
+diffs_coef_pairs_f <- chains_fitted_f %>% 
+  as_data_frame() %>% 
+  magrittr::set_colnames(levels(newdata_conditions_f$funding)) %>% 
+  mcmc_pairwise_diffs()
+
+diffs_coef_pairs_detail_f <- tidy_diffs(diffs_coef_pairs_f)
+
+pairs_plot_data_f <- diffs_coef_pairs_f %>%
+  gather(pair, value) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+```
+
 ```{r amount-diffs-ci}
@@
 
+**Compare only individual conditions:**
+
+```{r plot-single-amount-diffs, fig.width=7, fig.height=2.5}
+diffs_plot_data_singles <- bind_rows(pairs_plot_data_c,
+                                     pairs_plot_data_i,
+                                     pairs_plot_data_f) %>% 
+  mutate(pair = fct_inorder(pair, ordered = TRUE))
+
+diffs_coef_pairs_detail_singles <- bind_rows(diffs_coef_pairs_detail_c,
+                                             diffs_coef_pairs_detail_i,
+                                             diffs_coef_pairs_detail_f) %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair),
+         pair = fct_inorder(pair, ordered = TRUE))
+
+plot_diffs_singles <- ggplot() +
+  geom_density(data = diffs_plot_data_singles, 
+               aes(x = value, fill = pair),
+               colour = NA, alpha = 0.4) +
+  geom_segment(data = diffs_coef_pairs_detail_singles, 
+               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
+               size = 3) +
+  geom_vline(data = diffs_coef_pairs_detail_singles, 
+             aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  scale_x_continuous(labels = dollar) +
+  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ pair)
+
+plot_diffs_singles %T>%
+  print() %T>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.pdf"),
+         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.png"),
+         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
+```
+
+```{r tbl-single-amount-diffs, results="asis"}
+bind_rows(diffs_coef_pairs_detail_c,
+          diffs_coef_pairs_detail_i,
+          diffs_coef_pairs_detail_f) %>% 
+  select(`Frame` = pair, `∆~median~` = median, 
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(missing = "—", 
+                      caption = "Median difference between likelihood to donate across single conditions") %T>%
+  cat() %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
+```
+
+\
+
+**Compare nested conditions (what we're really most concerned about):**
+
 ```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
@@
   select(Issue = issue, Funding = funding, 
-         `No crackdown − crackdown (median)` = median, 
+         `No crackdown − crackdown~median~` = median, 
          `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
@@
 
-# Interaction models with extra controls
-m_likely_c_full <- update(m_likely_c, . ~ . + 
-                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
-                            give_charity_3 + volunteer + political_knowledge_bin +
-                            ideology_bin + education_bin + religiosity_bin +
-                            income_bin + age_bin)
-
-m_likely_ci_full <- update(m_likely_ci, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
-
-m_likely_cif_full <-update(m_likely_cif, . ~ . + 
-                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
+# Models with just issue and just funding
+m_likely_i <- update(m_likely_c, . ~ issue)
+m_likely_f <- update(m_likely_c, . ~ funding)
 ```
@@
 ```{r tbl-models-likely, warning=FALSE, results="asis"}
+# Get subset of coefficients
+coefs_to_include <- list(m_likely_c, m_likely_ci, m_likely_cif) %>% 
+  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)
+
 huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
-       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
-       coefs = clean_coefs_named,
+       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
        statistics = model_stats_bayes,
@@
 ```
-
-## Coefficient plot
 
@@
   # coord_cartesian(ylim = c(0, 100)) +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank())
+```
+
+```{r likely-median-i}
+newdata_conditions_i <- results %>% expand(nesting(issue))
+
+chains_fitted_likely_i <- posterior_linpred(m_likely_i, 
+                                            newdata = newdata_conditions_i, 
+                                            transform = TRUE)
+
+coef_summary_likely_i <- newdata_conditions_i %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_i), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_likely_i <- ggplot(coef_summary_likely_i, aes(y = estimate, x = issue)) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  scale_y_continuous(labels = percent) +
+  labs(x = NULL, y = "Probability of donating") +
+  theme_ngos() +
+  theme(panel.grid.major.x = element_blank())
+```
+
+```{r likely-median-f}
+newdata_conditions_f <- results %>% expand(nesting(funding))
+
+chains_fitted_likely_f <- posterior_linpred(m_likely_f, 
+                                            newdata = newdata_conditions_f, 
+                                            transform = TRUE)
+
+coef_summary_likely_f <- newdata_conditions_f %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_f), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
+
+plot_likely_f <- ggplot(coef_summary_likely_f, aes(y = estimate, x = funding)) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  scale_y_continuous(labels = percent) +
+  labs(x = NULL, y = "Probability of donating") +
   theme_ngos() +
@@
 
+```{r likely-diffs-i}
+diffs_coef_likely_pairs_i <- chains_fitted_likely_i %>% 
+  as_data_frame() %>% 
+  magrittr::set_colnames(levels(newdata_conditions_i$issue)) %>% 
+  mcmc_pairwise_diffs()
+
+diffs_coef_likely_pairs_detail_i <- tidy_diffs(diffs_coef_likely_pairs_i)
+
+pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i %>%
+  gather(pair, value) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+```
+
+```{r likely-diffs-f}
+diffs_coef_likely_pairs_f <- chains_fitted_likely_f %>% 
+  as_data_frame() %>% 
+  magrittr::set_colnames(levels(newdata_conditions_f$funding)) %>% 
+  mcmc_pairwise_diffs()
+
+diffs_coef_likely_pairs_detail_f <- tidy_diffs(diffs_coef_likely_pairs_f)
+
+pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f %>%
+  gather(pair, value) %>%
+  mutate(pair1 = pair) %>%
+  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair))
+```
+
 ```{r likely-diffs-ci}
@@
 
+**Compare only individual conditions:**
+
+```{r plot-single-likely-diffs, fig.width=7, fig.height=2.5}
+diffs_likely_plot_data_singles <- bind_rows(pairs_likely_plot_data_c,
+                                            pairs_likely_plot_data_i,
+                                            pairs_likely_plot_data_f) %>% 
+  mutate(pair = fct_inorder(pair, ordered = TRUE))
+
+diffs_coef_likely_pairs_detail_singles <- bind_rows(diffs_coef_likely_pairs_detail_c,
+                                                    diffs_coef_likely_pairs_detail_i,
+                                                    diffs_coef_likely_pairs_detail_f) %>%
+  mutate(pair = ifelse(nchar(pair) > 25,
+                       str_replace(pair, "−", "−\n"),
+                       pair),
+         pair = fct_inorder(pair, ordered = TRUE))
+
+plot_diffs_likely_singles <- ggplot() +
+  geom_density(data = diffs_likely_plot_data_singles, 
+               aes(x = value, fill = pair),
+               colour = NA, alpha = 0.4) +
+  geom_segment(data = diffs_coef_likely_pairs_detail_singles, 
+               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
+               size = 3) +
+  geom_vline(data = diffs_coef_likely_pairs_detail_singles, 
+             aes(xintercept = median), size = 0.25) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  scale_x_continuous(labels = percent) +
+  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
+  labs(x = "Difference in medians") +
+  theme_ngos(density = TRUE) +
+  facet_wrap(~ pair)
+
+plot_diffs_likely_singles %T>%
+  print() %T>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.pdf"),
+         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.png"),
+         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
+```
+
+```{r tbl-single-likely-diffs, results="asis"}
+bind_rows(diffs_coef_likely_pairs_detail_c,
+          diffs_coef_likely_pairs_detail_i,
+          diffs_coef_likely_pairs_detail_f) %>% 
+  select(`Frame` = pair, `∆~median~` = median, 
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(missing = "—", 
+                      caption = "Median difference between likelihood to donate across single conditions") %T>%
+  cat() %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
+```
+
+\
+
+**Compare nested conditions (what we're really most concerned about):**
+
 ```{r plot-all-likely-diffs, fig.width=8, fig.height=6}

### 2018-04-08 03_additional-analysis.Rmd
Coefficient plots for full models

@@
 library(ggstance)
+library(ggridges)
 library(patchwork)
@@
 library(huxtable)
+library(modelr)
 library(here)
@@
 ```
+
+\
+
+# Amount donated (full)
+
+## Models
+
+```{r build-models-amount-full, warning=FALSE, message=FALSE, cache=TRUE}
+# Basic model
+m_amount_c <- stan_glm(amount_donate ~ crackdown,
+                       data = results, family = gaussian(),
+                       prior = cauchy(location = 0, scale = 2.5),
+                       prior_intercept = cauchy(location = 0, scale = 10),
+                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)
+
+m_amount_cif <- update(m_amount_c, . ~ . + 
+                         issue + funding + crackdown * issue + crackdown * funding + 
+                         issue * funding + crackdown * issue * funding)
+
+# Interaction models with extra controls
+m_amount_c_full <- update(m_amount_c, . ~ . + 
+                            favor_humanitarian_bin + 
+                            give_charity_3 + volunteer + political_knowledge_bin +
+                            ideology_bin + education_bin + religiosity_bin +
+                            income_bin + age_bin)
+
+m_amount_ci_full <- update(m_amount_ci, . ~ . + 
+                             favor_humanitarian_bin + 
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
+
+m_amount_cif_full <-update(m_amount_cif, . ~ . + 
+                             favor_humanitarian_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
+```
+
+```{r tbl-models-amount-full, warning=FALSE, results="asis"}
+huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
+       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
+       coefs = clean_coefs_named,
+       statistics = model_stats_bayes,
+       stars = NULL) %T>% 
+  print_hux() %>% 
+  to_md(max_width = 100) %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-models-amount-full.md"))
+```
+
+## Coefficient plot
+
+```{r models-coefs-plot-amount, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
+posterior_details <- data_frame(model_name = c("Basic model", "Full model"),
+                                model = list(m_amount_cif,
+                                             m_amount_cif_full)) %>% 
+  mutate(posterior = model %>% map(~ as_data_frame(.)),
+         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
+                                                 conf.method = "HPDinterval")))
+
+coefs_posterior <- posterior_details %>%
+  unnest(posterior) %>% 
+  gather(term, value, -model_name) %>% 
+  left_join(clean_coefs, by = "term") %>% 
+  filter(term_clean != "Intercept") %>% 
+  mutate(full_model = !simple_model)
+
+coefs_summary <- posterior_details %>% 
+  unnest(tidy_summary) %>% 
+  left_join(clean_coefs, by = "term") %>% 
+  filter(term_clean != "Intercept") %>% 
+  mutate(full_model = !simple_model)
+
+ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
+  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
+                      rel_min_height = 0.01, scale = 1.5, 
+                      quantile_lines = TRUE, quantiles = 2) +
+  geom_segment(data = coefs_summary, 
+               aes(x = conf.low, xend = conf.high, 
+                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
+               size = 1) +
+  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
+  scale_fill_manual(values = c(ngo_red, ngo_blue), name = NULL) +
+  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
+       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
+  facet_wrap(~ full_model, scales = "free") + 
+  theme_ngos() +
+  theme(legend.position = "bottom",
+        strip.text = element_blank())
+```
+
+## Predicted medians across different variables
+
+**Charitable giving**
+
+```{r plot-charity-amounts, fig.width=5, fig.height=4}
+newdata_means <- results %>% 
+  select(favor_humanitarian_bin, favor_human_rights_bin, favor_development_bin,
+         give_charity_3, volunteer, political_knowledge_bin,
+         ideology_bin, education_bin, religiosity_bin, income_bin, age_bin) %>% 
+  summarize_all(typical) %>% 
+  mutate(id = 1)
+
+newdata_conditions_c <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
+  mutate(id = 1) %>% 
+  left_join(select(newdata_means, -give_charity_3), by = "id") %>% 
+  select(-id)
+
+chains_fitted_c <- posterior_linpred(m_amount_c_full, 
+                                     newdata = newdata_conditions_c)
+
+coef_summary_c <- newdata_conditions_c %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
+  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))
+
+ggplot(coef_summary_c, aes(x = fct_rev(give_charity_3), y = estimate)) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
+                  position = position_dodge(width = 0.5)) +
+  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
+  scale_y_continuous(labels = dollar) +
+  labs(x = "How often do you give to charity?", y = "Median amount donated") +
+  theme_ngos() +
+  theme(legend.position = "bottom",
+        panel.grid.major.x = element_blank())
+```
+
+\
+
+# Likelihood of donation (full)
+
+## Models
+
+```{r build-models-likely-full, warning=FALSE, message=FALSE, cache=TRUE}
+# Basic models
+m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
+                       data = results, family = binomial(link = "logit"),
+                       prior = student_t(3, 0, 2.5),
+                       prior_intercept = student_t(3, 0, 10),
+                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)
+
+m_likely_cif <- update(m_likely_c, . ~ . + 
+                         issue + funding + crackdown * issue + crackdown * funding + 
+                         issue * funding + crackdown * issue * funding)
+
+# Interaction models with extra controls
+m_likely_c_full <- update(m_likely_c, . ~ . + 
+                            favor_humanitarian_bin +
+                            give_charity_3 + volunteer + political_knowledge_bin +
+                            ideology_bin + education_bin + religiosity_bin +
+                            income_bin + age_bin)
+
+m_likely_ci_full <- update(m_likely_ci, . ~ . + 
+                             favor_humanitarian_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
+
+m_likely_cif_full <-update(m_likely_cif, . ~ . + 
+                             favor_humanitarian_bin +
+                             give_charity_3 + volunteer + political_knowledge_bin +
+                             ideology_bin + education_bin + religiosity_bin +
+                             income_bin + age_bin)
+```
+
+```{r tbl-models-likely-full, warning=FALSE, results="asis"}
+huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
+       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
+       coefs = clean_coefs_named,
+       statistics = model_stats_bayes,
+       stars = NULL) %T>% 
+  print_hux() %>% 
+  to_md(max_width = 100) %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood-full.md"))
+```
+
+## Coefficient plot
+
+```{r models-coefs-plot-likely, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
+posterior_details_likely <- data_frame(model_name = c("Basic model", "Full model"),
+                                       model = list(m_likely_cif,
+                                                    m_likely_cif_full)) %>% 
+  mutate(posterior = model %>% map(~ as_data_frame(.)),
+         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
+                                                 conf.method = "HPDinterval")))
+
+coefs_posterior_likely <- posterior_details_likely %>%
+  unnest(posterior) %>% 
+  gather(term, value, -model_name) %>% 
+  left_join(clean_coefs, by = "term") %>% 
+  filter(term_clean != "Intercept") %>% 
+  mutate(full_model = !simple_model)
+
+coefs_summary_likely <- posterior_details_likely %>% 
+  unnest(tidy_summary) %>% 
+  left_join(clean_coefs, by = "term") %>% 
+  filter(term_clean != "Intercept") %>% 
+  mutate(full_model = !simple_model)
+
+ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
+  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
+                      rel_min_height = 0.01, scale = 1.5, 
+                      quantile_lines = TRUE, quantiles = 2) +
+  geom_segment(data = coefs_summary_likely, 
+               aes(x = conf.low, xend = conf.high, 
+                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
+               size = 1) +
+  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
+  scale_fill_manual(values = c(ngo_red, ngo_blue), name = NULL) +
+  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
+       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
+  facet_wrap(~ full_model, scales = "free") + 
+  theme_ngos() +
+  theme(legend.position = "bottom",
+        strip.text = element_blank())
+```

### 2018-04-08 03_additional-analysis.Rmd
Nicer misc tables

@@
 library(huxtable)
+library(lubridate)
 library(modelr)
@@
   summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
+  gather(Statistic, value) %>% 
+  mutate(value = seconds_to_period(value)) %>% 
+  mutate(Minutes = sprintf("%02d:%02d", minute(value), second(value))) %>% 
+  select(-value) %>% 
   pandoc.table()
@@
 ```{r attention-check-2, results="asis"}
-results %>% count(attention2_correct) %>% pandoc.table()
+results %>% count(attention2_correct) %>% 
+  rename(`Attention check 2 correct` = attention2_correct, Count = n) %>% 
+  pandoc.table()
 ```

### 2018-04-20 03_additional-analysis.Rmd
Show voluntarism and religiosity

@@
 
-newdata_conditions_c <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
+newdata_conditions_charity <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
   mutate(id = 1) %>% 
@@
 
-chains_fitted_c <- posterior_linpred(m_amount_c_full, 
-                                     newdata = newdata_conditions_c)
+chains_fitted_charity <- posterior_linpred(m_amount_c_full, 
+                                           newdata = newdata_conditions_charity)
 
-coef_summary_c <- newdata_conditions_c %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
+coef_summary_charity <- newdata_conditions_charity %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_charity), estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
@@
 
-ggplot(coef_summary_c, aes(x = fct_rev(give_charity_3), y = estimate)) +
+ggplot(coef_summary_charity, aes(x = fct_rev(give_charity_3), y = estimate)) +
   geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
@@
   labs(x = "How often do you give to charity?", y = "Median amount donated") +
+  theme_ngos() +
+  theme(legend.position = "bottom",
+        panel.grid.major.x = element_blank())
+```
+
+**Voluntarism and religiosity**
+
+```{r plot-vol-relig-amounts}
+newdata_conditions_vol_relig <- results %>% 
+  expand(nesting(crackdown, volunteer, religiosity_bin)) %>% 
+  filter(!is.na(religiosity_bin)) %>% 
+  mutate(id = 1) %>% 
+  left_join(select(newdata_means, -volunteer, -religiosity_bin), by = "id") %>% 
+  select(-id)
+
+chains_fitted_vol_relig <- posterior_linpred(m_amount_c_full, 
+                                             newdata = newdata_conditions_vol_relig)
+
+coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
+  bind_cols(tidyMCMC(as.mcmc(chains_fitted_vol_relig), estimate.method = "median",
+                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
+  mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
+  mutate(religiosity_bin = fct_recode(religiosity_bin,
+                                      `Rarely attend religious services` = "Rarely",
+                                      `Attend religious services\nat least once a month` = 
+                                        "At least once a month"))
+
+ggplot(coef_summary_vol_relig, aes(x = fct_rev(volunteer), y = estimate)) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
+                  position = position_dodge(width = 0.5)) +
+  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
+  scale_y_continuous(labels = dollar) +
+  labs(x = "Have you volunteered in the last 12 months?", y = "Median amount donated") +
+  facet_wrap(~ religiosity_bin) +
   theme_ngos() +

### 2018-04-20 03_additional-analysis.Rmd
Nuke existing packages before loading them
grrrr

@@
 ```{r load-libraries-data, warning=FALSE, message=FALSE}
+# Unload all the already-loaded packages because R Markdown websites *don't* knit 
+# each Rmd in a separate environment: https://github.com/rstudio/rmarkdown/issues/1326
+#
+# This means that here::here() and lubridate::here() will conflict becuase **here**
+# has already been loaded in previous scripts
+if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
+  invisible(suppressWarnings(sapply(paste0("package:", names(sessionInfo()$otherPkgs)),
+                                    detach, character.only = TRUE, unload = TRUE)))
+}
+
+# Load libraries again
 library(tidyverse)

### 2018-04-20 preregistration.Rmd
Add IRB approval forms

@@
 
-We will preregister this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).
+We preregistered this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).
 
-<p><a href="#" class="btn btn-primary btn-md btn-success disabled" target="_blank">
+<p><a href="https://osf.io/dx973/register/565fb3678c5e4a66b5582f67" class="btn btn-primary btn-md btn-success" target="_blank">
 <i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
@@
 
-We will also participate in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:
+We are participating in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:
 
@@
 
-This project has received IRB approval from the human subjects research committees at both Duke and Dartmouth. We have included a generic version of our protocol below.
+This project has received IRB approval from the human subjects research committees at both BYU and Christopher Newport. We have included a generic version of our protocol below.
 
-<p><a href="files/duke-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
+<p><a href="files/byu-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
 <i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
-Duke IRB approval
+BYU IRB approval
 </a> 
 &nbsp;
-<a href="#" class="btn btn-primary btn-md btn-success disabled" target="_blank">
+<a href="files/cnu-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
 <i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
-Dartmouth IRB approval
+Christopher Newport IRB approval
 </a></p>
+
+\
 

### 2018-04-30 03_additional-analysis.Rmd
Minor changes from upgrading to R 3.5

--- 2018-04-20 03_additional-analysis.Rmd
@@
 ```{r load-libraries-data, warning=FALSE, message=FALSE}
+# Unload all the already-loaded packages because R Markdown websites *don't* knit 
+# each Rmd in a separate environment: https://github.com/rstudio/rmarkdown/issues/1326
+#
+# This means that here::here() and lubridate::here() will conflict becuase **here**
+# has already been loaded in previous scripts
+if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
+  invisible(suppressWarnings(sapply(paste0("package:", names(sessionInfo()$otherPkgs)),
+                                    detach, character.only = TRUE)))
+}
+
+# Load libraries again
 library(tidyverse)
@@
   mutate(value = seconds_to_period(value)) %>% 
-  mutate(Minutes = sprintf("%02d:%02d", minute(value), second(value))) %>% 
+  mutate(Minutes = sprintf("%02.0f:%02.0f", minute(value), second(value))) %>% 
   select(-value) %>% 

### 2018-06-25 02_analysis.Rmd
Cooler color system

@@
 ```{r fig-ngo-favorability, fig.width=7, fig.height=4}
+favorability_cols <- data_frame(value = c("Very unfavorable", "Unfavorable", "Neutral",
+                                          "Favorable", "Very favorable"),
+                                color = ngo_pal("ordered")(5))
+
 ngo_favorability_raw <- results %>%
@@
   left_join(vars_to_summarize, by = "variable") %>% 
-  left_join(favorability_cols_5, by = "value") %>% 
+  left_join(favorability_cols, by = "value") %>%
   mutate(clean_name = str_replace(clean_name, "towards", "towards\n")) %>% 
@@
                                          labels = percent)) +
-  scale_fill_manual(values = c(ngo_green, ngo_blue), guide = FALSE) +
+  scale_fill_manual(values = ngo_cols("green", "blue", name = FALSE), guide = FALSE) +
   labs(x = NULL, y = NULL) +
@@
   theme(panel.grid.major.y = element_blank())
+
+plot_donate_summary
 
@@
 plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
-  geom_histogram(bins = 20, fill = ngo_blue) +
+  geom_histogram(bins = 20, fill = ngo_cols("blue")) +
   scale_x_continuous(labels = dollar) +
@@
   #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
   scale_y_continuous(labels = dollar) +
@@
   #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
   scale_y_continuous(labels = dollar) +
@@
   #            color = "grey50", size = 0.5, alpha = 0.5) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
   scale_y_continuous(labels = dollar) +
@@
   scale_y_continuous(labels = dollar) +
-  scale_color_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
+  scale_color_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
   labs(x = NULL, y = "Median amount donated") +
@@
   geom_density(data = pairs_plot_data_c, aes(x = value),
-               fill = ngo_green, colour = NA, alpha = 0.4) + 
+               fill = ngo_cols("green"), colour = NA, alpha = 0.4) + 
   geom_segment(data = diffs_coef_pairs_detail_c, 
@@
   geom_density(data = pairs_plot_data_ci, aes(x = value),
-               fill = ngo_blue, colour = NA, alpha = 0.4) + 
+               fill = ngo_cols("blue"), colour = NA, alpha = 0.4) + 
   geom_segment(data = diffs_coef_pairs_detail_ci, 
@@
   geom_density(data = pairs_plot_data_cif, aes(x = value),
-               fill = ngo_red, colour = NA, alpha = 0.4) + 
+               fill = ngo_cols("red"), colour = NA, alpha = 0.4) + 
   geom_segment(data = diffs_coef_pairs_detail_cif, 
@@
   scale_x_continuous(labels = dollar) +
-  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
+  scale_fill_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
   labs(x = "Difference in medians") +
@@
   #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
   scale_y_continuous(labels = percent) +
@@
 plot_likely_i <- ggplot(coef_summary_likely_i, aes(y = estimate, x = issue)) + 
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
   scale_y_continuous(labels = percent) +
@@
 plot_likely_f <- ggplot(coef_summary_likely_f, aes(y = estimate, x = funding)) + 
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
   scale_y_continuous(labels = percent) +
@@
   #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
   scale_y_continuous(labels = percent) +
@@
   #            color = "grey50", size = 0.5, alpha = 0.5) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
+  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
   scale_y_continuous(labels = percent) +
@@
   geom_density(data = pairs_likely_plot_data_c, aes(x = value),
-               fill = ngo_green, colour = NA, alpha = 0.4) + 
+               fill = ngo_cols("green"), colour = NA, alpha = 0.4) + 
   geom_segment(data = diffs_coef_likely_pairs_detail_c, 
@@
   geom_density(data = pairs_likely_plot_data_ci, aes(x = value),
-               fill = ngo_blue, colour = NA, alpha = 0.4) + 
+               fill = ngo_cols("blue"), colour = NA, alpha = 0.4) + 
   geom_segment(data = diffs_coef_likely_pairs_detail_ci, 
@@
   geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
-               fill = ngo_red, colour = NA, alpha = 0.4) + 
+               fill = ngo_cols("red"), colour = NA, alpha = 0.4) + 
   geom_segment(data = diffs_coef_likely_pairs_detail_cif, 
@@
   scale_x_continuous(labels = percent) +
-  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
+  scale_fill_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
   labs(x = "Difference in medians") +

### 2018-06-25 lib/graphics.R

@@ -1,22 +1,3 @@
-# Colors ------------------------------------------------------------------
-
-# Color palette from ColorBrewer, diverging spectral, 5 categories
-# http://colorbrewer2.org/#type=diverging&scheme=Spectral&n=5
-#
-# library(RColorBrewer)
-# RColorBrewer::brewer.pal(5, "Spectral")
-ngo_red <- "#D7191C"
-ngo_orange <- "#FDAE61"
-ngo_yellow <- "#FFFFBF"
-ngo_green <- "#ABDDA4"
-ngo_blue <- "#2B83BA"
-
-favorability_cols_5 <- data_frame(value = c("Very unfavorable", "Unfavorable", "Neutral", 
-                                            "Favorable", "Very favorable"),
-                                  color = c(ngo_red, ngo_orange, ngo_yellow,
-                                            ngo_green, ngo_blue))
-
-
 # ggplot themes -----------------------------------------------------------
 
 theme_spark <- function() {
@@ -57,5 +38,104 @@ theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", de
             strip.text = element_text(margin = margin(5, 0, 2, 0, "pt")))
   } else {
     ret
+  }
+}
+
+
+# Colors ------------------------------------------------------------------
+
+# How to create custom palettes:
+# https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2
+#
+# Color palette adapted from ColorBrewer, diverging spectral, 5 categories
+# http://colorbrewer2.org/#type=diverging&scheme=Spectral&n=5
+#
+# library(RColorBrewer)
+# RColorBrewer::brewer.pal(5, "Spectral")
+
+ngo_colors <- c(
+  `red`         = "#D7191C",
+  `orange`      = "#FDAE61",
+  `yellow`      = "#FFFFBF",
+  `green`       = "#ABDDA4",
+  `blue`        = "#2B83BA",
+  `light grey`  = "grey80",
+  `dark grey`   = "grey10"
+)
+
+#' Function to extract NGO colors as hex codes
+#'
+#' @param ... Character names of ngo_colors 
+#'
+ngo_cols <- function(..., name = TRUE) {
+  cols <- c(...)
+  
+  if (is.null(cols)) {
+    return(ngo_colors)
+  }
+  
+  if (name) {
+    ngo_colors[cols]
+  } else {
+    unname(ngo_colors[cols])
+  }
+}
+
+# Palette definitions
+ngo_palettes <- list(
[…]

### 2018-06-25 experiment.Rmd
Move actual experiment to external file for reuse

@@
 
-## Consent
-
-***Q1.1***: You have been invited to participate in an academic research survey about international nongovernmental organizations.
-This study is being conducted by Suparna Chaudhry from Christopher Newport University and Andrew Heiss from Brigham Young University.
-The experiment should take about **5 minutes** to complete.
-You will be paid **$0.75** for your participation.
-
-Your participation in this study is entirely voluntary and you are free to skip any question or withdraw from the experiment at any time.
-You will not be asked to provide any personal information, and your answers will remain anonymous.
-There are no reasonably foreseeable risks or discomforts associated with participating in this study.
-There will be questions designed to check that you’re paying attention to the details of the experiment.
-If you answer these incorrectly, the survey will end early and you may not receive compensation.
-
-Beyond your payment, you will receive no direct benefits from participating in this research study, but your responses may reveal important and useful insights about international NGOs and philanthropy.
-
-If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (suparna.chaudhry@cnu.edu; Reiff Center for Human Rights and Conflict Resolution, Christopher Newport University, Newport News, VA 23606) or Andrew Heiss (andrew_heiss@byu.edu; Romney Institute of Public Management, Brigham Young University, Provo, UT 84602) at andrew_heiss@byu.edu.
-This research has been reviewed by the Institutional Review Board at Christopher Newport University (757-594-7461; IRB@cnu.edu) and the IRB administrator at Brigham Young University (801-422-1461; irb@byu.edu).
-
-By clicking "I agree" below you are indicating that you are at least 18 years old, have read and understood this consent form and agree to participate in this research study.
-Please print a copy of this page for your records.
-
-*Q1.2*: I have read the above information, and I consent to take part in the study.
-
-:   Single answer
-
-    - Yes
-    - No
-
----
-
-*Q1.3*: Please read the paragraph below carefully.
-
-What is your favorite color?
-While we are interested in learning about your preferences on a variety of topics, including colors, we also want to make sure that you are reading the questions we have written.
-To demonstrate that you’ve read this much, just go ahead and select both green and yellow from among the alternatives listed below, no matter what your favorite color is.
-Yes, ignore the first sentence and select both green and yellow.
-
-**(End survey without payment if this question is incorrect.)**
-
-: Multiple answers allowed (*must be green and yellow*)
-
-    - Pink
-    - Red
-    - Green
-    - White
-    - Yellow
-    - Blue
-
----
-
-## Crackdown and private giving
-
-*Q2.1*: How do you feel about the following types of organizations?
-
-:   Matrix table
-
-    |                                                                          | Very unfavorable | Unfavorable | Neutral | Favorable | Very favorable |
-    |--------------------------------------------------------------------------|:----------------:|:-----------:|:-------:|:---------:|:--------------:|
-    | Nonprofit organizations that provide humanitarian relief                 |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
-    | Nonprofit organizations that advocate for human rights                   |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
-    | Nonprofit organizations that help with development and alleviate poverty |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
-
----
-
-![](img/irc_logo.png "IRC logo"){.img-responsive .center}
-
-\
-
-*Q2.2*: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.
-
-A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.
-
-*Q2.3*: How likely would you be to donate to IRC?
-
-:   Single answer
-
-    - Extremely likely
-    - Somewhat likely
-    - Neither likely nor unlikely
-    - Somewhat unlikely
-    - Extremely unlikely
-
-*Q2.4*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)
-
-:   Numeric slider, options must sum to 100
-
-    - Donate to IRC (0–100)
-    - Keep for yourself (0–100)
-
-*Q2.5*: Why did you select that amount?
-
-:   Text field
-
----
-
-## Demographics
-
-*Q3.1*: Almost done! This is the last page of the study.
-
-*Q3.2*: How often do you donate to charity (either cash or in-kind)?
-
-:   Single answer
-
-    - Once a week
-    - Once a month
-    - Once every three months
-    - Once every six months
-    - Once a year
-    - Once every few years
-    - Never
-
-*Q3.3*: Have you volunteered in the past 12 months?
-
-:   Single answer
-
-    - Yes
-    - No
-
-*Q3.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not.
-Others aren't that interested.
-Would you say that you follow what's going on in government and public affairs…
-
-:   Single answer
-
-    - Most of the time
-    - Some of the time
-    - Only now and then
-    - Hardly at all
-
-*Q3.5*: How would you describe your political views?
-
-:   Single answer
-
-    - Strong liberal
-    - Liberal
-    - Independent, leaning liberal
-    - Independent
-    - Independent, leaning conservative
-    - Conservative
-    - Very conservative
-
-*Q3.6*: What is the highest degree or level of school you have completed?
-
-:   Single answer
-
-    - Less than high school
-    - High school graduate
-    - Some college
-    - 2 year degree
-    - 4 year degree
-    - Graduate or professional degree
-    - Doctorate
-
-*Q3.7*: Aside from weddings and funerals, how often do you attend religious services?
-
-:   Single answer
-
-    - More than once a week
-    - Once a week
-    - Once or twice a month
-    - A few times a year
-    - Seldom
-    - Never
-    - Don't know
-
-*Q3.8*: Please select blue from the following list:
-
-:   Single answer
-
-    - Red
-    - Yellow
-    - Blue
-    - Green
-
-*Q3.9*: What is your gender?
-
-:   Single answer
-
-    - Female
-    - Male
-    - Transgender
-    - Other:
-    - Prefer not to say
-
-*Q3.10*: What is your total household income?
-
-:   Single answer
-
-    - Less than $10,000
-    - $10,000 - $19,999
-    - $20,000 - $29,999
-    - $30,000 - $39,999
-    - $40,000 - $49,999
-    - $50,000 - $59,999
-    - $60,000 - $69,999
-    - $70,000 - $79,999
-    - $80,000 - $89,999
-    - $90,000 - $99,999
-    - $100,000 - $149,999
-    - More than $150,000
-
-*Q3.11*: How old are you?
-
-:   Single answer
-
-    - Under 18
-    - 18 - 24
-    - 25 - 34
-    - 35 - 44
-    - 45 - 54
-    - 55 - 64
-    - 65 - 74
-    - 75 - 84
-    - 85 or older
+```{r child = "text/experiment.md"}
+```

### 2018-06-25 03_additional-analysis.Rmd
Use new color system

@@
   geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
-  scale_fill_manual(values = c(ngo_red, ngo_blue), name = NULL) +
+  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
   labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
@@
                   position = position_dodge(width = 0.5)) +
-  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
+  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
   scale_y_continuous(labels = dollar) +

### 2018-06-25 01_clean-data.Rmd
Minor changes from upgrading to R 3.5
Better recording of excluded results

@@
 # line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
-results_raw <- read_csv(results_file, skip = 10,
+results_raw <- read_csv(results_file, skip = 16,
                         col_names = colnames(results_meta))
@@
 # IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
-codes_to_exclude <- readLines(file.path(here(), "data", "codes_to_exclude.txt")) %>% 
-  as.numeric()
+codes_to_exclude <- read_csv(file.path(here(), "data", "codes_to_exclude.csv"))
 
 # Clean everything
-results <- results_raw %>%
+results_check_attention <- results_raw %>%
   # Only select necessary columns
@@
   mutate(attention1_correct = ifelse(confirmation_code == 6518634,
-                                     TRUE, attention1_correct)) %>% 
-  filter(!(confirmation_code %in% codes_to_exclude)) %>%
+                                     TRUE, attention1_correct))
+
+results <- results_check_attention %>% 
+  filter(!(confirmation_code %in% codes_to_exclude$confirmation_code)) %>%
   # Factorize variables
@@
 
+# Save final clean data
 saveRDS(results, file.path(here(), "data", "results_clean.rds"))
@@
 ```
+
+```{r completed-summary}
+# Save information about completion rates
+completed_skeleton <- results_check_attention %>% 
+  left_join(codes_to_exclude, by = "confirmation_code") %>% 
+  replace_na(list(reason = "Approved")) %>% 
+  expand(reason, crackdown, issue, funding)
+
+completed_summary <- results_check_attention %>% 
+  left_join(codes_to_exclude, by = "confirmation_code") %>% 
+  replace_na(list(reason = "Approved")) %>% 
+  count(reason, crackdown, issue, funding) %>% 
+  right_join(completed_skeleton, by = c("reason", "crackdown", "issue", "funding")) %>% 
+  replace_na(list(n = 0))
+
+saveRDS(completed_summary, file.path(here(), "data", "completion_summary.rds"))
+write_csv(completed_summary, file.path(here(), "data", "completion_summary.csv"))
+```

### 2018-06-25 03_additional-analysis.Rmd
CONSORT diagram!

@@
 library(coda)
+library(glue)
 library(ggstance)
 library(ggridges)
+library(grid)
+library(Gmisc)
 library(patchwork)
@@
 results <- readRDS(file.path(here(), "data", "results_clean.rds"))
+```
+
+# CONSORT flow
+
+```{r build-consort, results="hide", fig.width=10, fig.height=6}
+consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
+  spread(reason, n) %>% 
+  mutate(group = 1:n(),
+         assigned = Approved + `Failed first attention check`,
+         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
+  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
+         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))
+
+assessed_eligibility_n <- sum(consort$Approved, consort$`Failed first attention check`, 
+                              consort$`Took survey outisde of MTurk`)
+ineligible_n <- sum(consort$`Took survey outisde of MTurk`)
+randomized_n <- sum(consort$Approved, consort$`Failed first attention check`)
+
+# https://aghaynes.wordpress.com/2018/05/09/flow-charts-in-r/
+# set some parameters to use repeatedly
+width <- 0.1
+xs <- seq(0.1, 0.9, length.out = 8)
+allocated_y <- 0.375
+completed_y <- 0.125
+
+box_gp_grey <- gpar(fill = ngo_cols("light grey"))
+box_gp_blue_dk <- gpar(fill = ngo_cols("blue"), alpha = 0.75)
+box_gp_blue_lt <- gpar(fill = ngo_cols("blue"), alpha = 0.35)
+box_gp_green <- gpar(fill = ngo_cols("green"), alpha = 0.65)
+box_gp_yellow <- gpar(fill = ngo_cols("yellow"))
+box_gp_orange <- gpar(fill = ngo_cols("orange"), alpha = 0.65)
+
+txt_gp <- gpar(fontfamily = "Encode Sans Condensed Medium", 
+               fontface = "plain", fontsize = 8)
+
+# Create boxes
+total <- boxGrob(glue("Assessed for eligibility\n N = {assessed_eligibility_n}"), 
+                 x = 0.5, y = 0.9, width = 2 * width,
+                 box_gp = box_gp_blue_lt, txt_gp = txt_gp)
+randomized <- boxGrob(glue("Randomized\n N = {randomized_n}"), 
+                      x = 0.5, y = 0.65, width = 2 * width,
+                      box_gp = box_gp_blue_dk, txt_gp = txt_gp)
+ineligible <- boxGrob(glue("Participants excluded for\ncompleting Qualtrics survey\noutside of MTurk\n N = {ineligible_n}"), 
+                      x = xs[7], y = 0.775, #width = 0.25,
+                      box_gp = box_gp_yellow, txt_gp = txt_gp)
+
+group1 <- boxGrob(filter(consort, group == 1)$assigned_label,
+                  x = xs[1], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group2 <- boxGrob(filter(consort, group == 2)$assigned_label,
+                  x = xs[2], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group3 <- boxGrob(filter(consort, group == 3)$assigned_label,
+                  x = xs[3], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group4 <- boxGrob(filter(consort, group == 4)$assigned_label,
+                  x = xs[4], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group5 <- boxGrob(filter(consort, group == 5)$assigned_label,
+                  x = xs[5], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group6 <- boxGrob(filter(consort, group == 6)$assigned_label,
+                  x = xs[6], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group7 <- boxGrob(filter(consort, group == 7)$assigned_label,
+                  x = xs[7], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+group8 <- boxGrob(filter(consort, group == 8)$assigned_label,
+                  x = xs[8], y = allocated_y, width = width, 
+                  box_gp = box_gp_orange, txt_gp = txt_gp)
+
+group1_completed <- boxGrob(filter(consort, group == 1)$completed_label, 
+                            x = xs[1], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group2_completed <- boxGrob(filter(consort, group == 2)$completed_label, 
+                            x = xs[2], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group3_completed <- boxGrob(filter(consort, group == 3)$completed_label, 
+                            x = xs[3], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group4_completed <- boxGrob(filter(consort, group == 4)$completed_label, 
+                            x = xs[4], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group5_completed <- boxGrob(filter(consort, group == 5)$completed_label, 
+                            x = xs[5], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group6_completed <- boxGrob(filter(consort, group == 6)$completed_label, 
+                            x = xs[6], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group7_completed <- boxGrob(filter(consort, group == 7)$completed_label, 
+                            x = xs[7], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+group8_completed <- boxGrob(filter(consort, group == 8)$completed_label, 
+                            x = xs[8], y = completed_y, width = width,
+                            box_gp = box_gp_green, txt_gp = txt_gp)
+
+# Connect boxes
+grid.newpage()
+total; randomized; ineligible
+connectGrob(total, randomized, "v")
+connectGrob(total, ineligible, "-")
+
+group1; group2; group3; group4; group5; group6; group7; group8
+connectGrob(randomized, group1, "N")
+connectGrob(randomized, group2, "N")
+connectGrob(randomized, group3, "N")
+connectGrob(randomized, group4, "N")
+connectGrob(randomized, group5, "N")
+connectGrob(randomized, group6, "N")
+connectGrob(randomized, group7, "N")
+connectGrob(randomized, group8, "N")
+
+group1_completed; group2_completed; group3_completed; group4_completed; 
+group5_completed; group6_completed; group7_completed; group8_completed
+connectGrob(group1, group1_completed, "N")
+connectGrob(group2, group2_completed, "N")
+connectGrob(group3, group3_completed, "N")
+connectGrob(group4, group4_completed, "N")
+connectGrob(group5, group5_completed, "N")
+connectGrob(group6, group6_completed, "N")
+connectGrob(group7, group7_completed, "N")
+connectGrob(group8, group8_completed, "N")
+
+# Use a global plot device temporarily because each chunk starts a new viewport
+# and I want to use grid.grab() on this chunk, but I also want to hide the
+# output from grid.grab() since knitr/grid inexplicably insist on plotting a
+# second figure even when wrapping grid.grab() in invisible() or enabling
+# results="hide" in the chunk options. So, the hacky solution here is to use a
+# global device, capture the grid output in a new chunk that isn't included, and
+# turn off the global plot device later. I also include code that isn't run for
+# the sake of readability (i.e. fig_consort would come out of nowhere otherwise)
+#
+# See https://stackoverflow.com/a/17509770/120898
+knitr::opts_knit$set(global.device = TRUE)
+```
+
+```{r grab-figure-actual, include=FALSE}
+fig_consort <- grid.grab()
+```
+
+```{r grab-figure-fake, eval=FALSE}
+fig_consort <- grid.grab()
+```
+
+```{r show-save-consort, fig.width=10, fig.height=6}
+# Turn off global device
+knitr::opts_knit$set(global.device = FALSE)
+
+fig_consort %T>%
+  ggsave(., filename = file.path(here(), "output", "figures", "consort.pdf"),
+         width = 10, height = 6, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "consort.png"),
+         width = 10, height = 6, units = "in", type = "cairo", dpi = 300)
 ```

### 2018-06-25 03_additional-analysis.Rmd
Ha, load magrittr

@@
 library(tidyverse)
+library(magrittr)
 library(rstanarm)

### 2018-06-25 02_analysis.Rmd
Don't hardcode pdf + remove ..

@@
     code_folding: hide
+    pandoc_args: [
+      "--default-image-extension=png"
+    ]
 editor_options: 
@@
   file_name <- gsub("\\.| ", "_", tolower(variable))
-  md_img <- paste0("![](../output/figures/summary-table/", file_name, ".pdf)")
+  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")
 
@@
   output <- data_frame(spark = md_img, summary = inline_summary)
+  return(output)
 }
@@
   rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
-  janitor::adorn_totals(where = "row") %T>% 
+  janitor::adorn_totals(., where = "row") %T>% 
   pandoc.table() %>% 

### 2018-06-25 03_additional-analysis.Rmd
Better CONSORT saving

@@
 
-```{r build-consort, results="hide", fig.width=10, fig.height=6}
+```{r build-consort}
 consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
@@
 
-# Connect boxes
-grid.newpage()
-total; randomized; ineligible
-connectGrob(total, randomized, "v")
-connectGrob(total, ineligible, "-")
+total_random_connect <- connectGrob(total, randomized, "v")
+total_ineligible_connect <- connectGrob(total, ineligible, "-")
 
-group1; group2; group3; group4; group5; group6; group7; group8
-connectGrob(randomized, group1, "N")
-connectGrob(randomized, group2, "N")
-connectGrob(randomized, group3, "N")
-connectGrob(randomized, group4, "N")
-connectGrob(randomized, group5, "N")
-connectGrob(randomized, group6, "N")
-connectGrob(randomized, group7, "N")
-connectGrob(randomized, group8, "N")
+rand_connect1 <- connectGrob(randomized, group1, "N")
+rand_connect2 <- connectGrob(randomized, group2, "N")
+rand_connect3 <- connectGrob(randomized, group3, "N")
+rand_connect4 <- connectGrob(randomized, group4, "N")
+rand_connect5 <- connectGrob(randomized, group5, "N")
+rand_connect6 <- connectGrob(randomized, group6, "N")
+rand_connect7 <- connectGrob(randomized, group7, "N")
+rand_connect8 <- connectGrob(randomized, group8, "N")
 
-group1_completed; group2_completed; group3_completed; group4_completed; 
-group5_completed; group6_completed; group7_completed; group8_completed
-connectGrob(group1, group1_completed, "N")
-connectGrob(group2, group2_completed, "N")
-connectGrob(group3, group3_completed, "N")
-connectGrob(group4, group4_completed, "N")
-connectGrob(group5, group5_completed, "N")
-connectGrob(group6, group6_completed, "N")
-connectGrob(group7, group7_completed, "N")
-connectGrob(group8, group8_completed, "N")
+complete_connect1 <- connectGrob(group1, group1_completed, "N")
+complete_connect2 <- connectGrob(group2, group2_completed, "N")
+complete_connect3 <- connectGrob(group3, group3_completed, "N")
+complete_connect4 <- connectGrob(group4, group4_completed, "N")
+complete_connect5 <- connectGrob(group5, group5_completed, "N")
+complete_connect6 <- connectGrob(group6, group6_completed, "N")
+complete_connect7 <- connectGrob(group7, group7_completed, "N")
+complete_connect8 <- connectGrob(group8, group8_completed, "N")
 
-# Use a global plot device temporarily because each chunk starts a new viewport
-# and I want to use grid.grab() on this chunk, but I also want to hide the
-# output from grid.grab() since knitr/grid inexplicably insist on plotting a
-# second figure even when wrapping grid.grab() in invisible() or enabling
-# results="hide" in the chunk options. So, the hacky solution here is to use a
-# global device, capture the grid output in a new chunk that isn't included, and
-# turn off the global plot device later. I also include code that isn't run for
-# the sake of readability (i.e. fig_consort would come out of nowhere otherwise)
-#
-# See https://stackoverflow.com/a/17509770/120898
-knitr::opts_knit$set(global.device = TRUE)
-```
-
-```{r grab-figure-actual, include=FALSE}
-fig_consort <- grid.grab()
-```
-
-```{r grab-figure-fake, eval=FALSE}
-fig_consort <- grid.grab()
+full_chart <- list(total, randomized, ineligible, total_random_connect, total_ineligible_connect,
+                   group1, group2, group3, group4, group5, group6, group7, group8,
+                   rand_connect1, rand_connect2, rand_connect3, rand_connect4, 
+                   rand_connect5, rand_connect6, rand_connect7, rand_connect8,
+                   group1_completed, group2_completed, group3_completed, group4_completed, 
+                   group5_completed, group6_completed, group7_completed, group8_completed,
+                   complete_connect1, complete_connect2, complete_connect3, complete_connect4, 
+                   complete_connect5, complete_connect6, complete_connect7, complete_connect8) 
 ```
@@
 ```{r show-save-consort, fig.width=10, fig.height=6}
-# Turn off global device
-knitr::opts_knit$set(global.device = FALSE)
+# Ordinarily, you can use grid.grab() to save the output of a grid figure into
+# an object and then use that in ggsave(). However, when knitting, this creates
+# a duplicate plot, which is frustrating. So instead, we use walk() to reprint
+# all the grobs within specific pdf and png devices
+#
+# See https://stackoverflow.com/a/17509770/120898 for a similar issue
 
-fig_consort %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "consort.pdf"),
-         width = 10, height = 6, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "consort.png"),
-         width = 10, height = 6, units = "in", type = "cairo", dpi = 300)
+# Save as PDF
+cairo_pdf(filename = file.path(here(), "output", "figures", "consort.pdf"),
+          width = 10, height = 6)
+grid.newpage()
+walk(full_chart, ~ print(.))
+invisible(dev.off())
+
+# Save as PNG
+png(filename = file.path(here(), "output", "figures", "consort.png"), 
+    width = 10, height = 6, units = "in",
+    bg = "white", res = 300, type = "cairo")
+grid.newpage()
+walk(full_chart, ~ print(.))
+invisible(dev.off())
+
+# Show in knitted document
+grid.newpage()
+walk(full_chart, ~ print(.))
 ```

### 2018-06-25 03_additional-analysis.Rmd
Plot average time

@@
 library(grid)
+library(gridExtra)
 library(Gmisc)
@@
 ```{r avg-time, results="asis"}
-results %>% 
-  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
+fmt_ms <- function(x) {
+  n_seconds <- seconds_to_period(x)
+  sprintf("%02.0f:%02.0f", minute(n_seconds), second(n_seconds))
+}
+
+theme_ngos_table <- ttheme_minimal(
+  core = 
+    list(fg_params = 
+           list(hjust = 0, x = 0.1,
+                fontsize = 7, fontface = "plain",
+                fontfamily = "Encode Sans Condensed Light"),
+         bg_params = list(fill = "white")),
+  colhead = 
+    list(fg_params = 
+           list(hjust = 0, x = 0.1, col = "white",
+                fontsize = 7, fontface = "plain",
+                fontfamily = "Encode Sans Condensed SemiBold"),
+         bg_params = list(fill = ngo_cols("blue"))),
+  padding = unit(c(4, 2), "mm"))
+
+time_summary <- results %>% 
+  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
+                                    `Standard deviation` = sd, Median = median)) %>% 
   gather(Statistic, value) %>% 
-  mutate(value = seconds_to_period(value)) %>% 
-  mutate(Minutes = sprintf("%02.0f:%02.0f", minute(value), second(value))) %>% 
-  select(-value) %>% 
-  pandoc.table()
+  mutate(Minutes = fmt_ms(value)) %>% 
+  select(-value)
+
+pandoc.table(time_summary)
 ```
 
-## Attention check #2
+```{r avg-time-plot, fig.height=2.5, fig.width=4}
+summary_stats <- tableGrob(time_summary, rows = NULL, theme = theme_ngos_table) %>% 
+  gtable::gtable_add_grob(., grobs = rectGrob(gp = gpar(fill = NA, lwd = 1)),
+                          t = 1, b = nrow(.), l = 1, r = ncol(.))
 
-```{r attention-check-2, results="asis"}
-results %>% count(attention2_correct) %>% 
-  rename(`Attention check 2 correct` = attention2_correct, Count = n) %>% 
-  pandoc.table()
+plot_avg_time <- ggplot(results, aes(x = duration)) +
+  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
+  scale_x_time(labels = fmt_ms) +
+  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
+  labs(x = "Minutes spent on experiment", y = "Count") +
+  theme_ngos() +
+  theme(panel.grid.minor = element_blank())
+
+plot_avg_time %T>% 
+  print() %T>%
+  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.pdf"),
+         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.png"),
+         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
 ```
-
-\
 

### 2018-07-09 02_analysis.Rmd
Better patchwork annotations + facet titles

@@
 ```{r plot-all-amount-medians, fig.width=8, fig.height=6}
-((plot_amount_c + 
-   labs(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
-        subtitle = "90% credible intervals shown around each point")) / 
-   plot_amount_ci) | plot_amount_cif
-
-((plot_amount_c / plot_amount_ci) | 
-    plot_amount_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
+plot_amount_all <- 
+  (plot_amount_c / plot_amount_ci) | 
+  plot_amount_cif
+
+plot_amount_all +
+  plot_annotation(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
+                  subtitle = "90% credible intervals shown around each point",
+                  tag_levels = "A", theme = theme_ngos())
+
+(plot_amount_all + 
+    plot_annotation(caption = "90% credible intervals shown around each point",
+                    tag_levels = "A", theme = theme_ngos())) %T>% 
   ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
-         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
+         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
   ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
-         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
+         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
 ```
@@
 ```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
-((plot_diffs_c + 
-   labs(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
-        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
-   plot_diffs_ci) | plot_diffs_cif
-
-((plot_diffs_c / plot_diffs_ci) | 
-    plot_diffs_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
+plot_diffs_all <- 
+  (plot_diffs_c / plot_diffs_ci) | 
+  plot_diffs_cif
+
+plot_diffs_all +
+  plot_annotation(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
+                  subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
+                  tag_levels = "A", theme = theme_ngos())
+
+(plot_diffs_all +
+  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
+                  tag_levels = "A", theme = theme_ngos())) %T>% 
   ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
@@
 ```{r plot-all-likely-medians, fig.width=8, fig.height=6}
-((plot_likely_c + 
-   labs(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
-        subtitle = "90% credible intervals shown around each point")) / 
-   plot_likely_ci) | plot_likely_cif
-
-((plot_likely_c / plot_likely_ci) | 
-    plot_likely_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
+plot_likely_all <- 
+  (plot_likely_c / plot_likely_ci) | 
+  plot_likely_cif
+
+plot_likely_all +
+  plot_annotation(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
+                  subtitle = "90% credible intervals shown around each point",
+                  tag_levels = "A", theme = theme_ngos())
+
+(plot_likely_all +
+  plot_annotation(caption = "90% credible intervals shown around each point",
+                  tag_levels = "A", theme = theme_ngos())) %T>% 
   ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
-         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
+         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
   ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
-         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
+         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
 ```
@@
 ```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
-((plot_diffs_likely_c + 
-   labs(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
-        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
-   plot_diffs_likely_ci) | plot_diffs_likely_cif
-
-((plot_diffs_likely_c / plot_diffs_likely_ci) | 
-    plot_diffs_likely_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
+plot_diffs_likely_all <- 
+  (plot_diffs_likely_c / plot_diffs_likely_ci) | 
+  plot_diffs_likely_cif
+
+plot_diffs_likely_all +
+  plot_annotation(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
+                  subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
+                  tag_levels = "A", theme = theme_ngos())
+
+(plot_diffs_likely_all +
+  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
+                  tag_levels = "A", theme = theme_ngos())) %T>% 
   ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),

### 2018-07-09 lib/graphics.R

@@ -20,8 +20,11 @@ theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", de
           plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
                                       family = "Encode Sans Condensed Light",
                                       margin = margin(t = 10)),
-          strip.text = element_text(size = rel(1), face = "plain",
-                                    family = "Encode Sans Condensed SemiBold"),
+          plot.tag = element_text(size = rel(1), face = "plain", color = "grey50",
+                                  family = "Encode Sans Condensed SemiBold"),
+          strip.text = element_text(size = rel(0.8), face = "plain",
+                                    family = "Encode Sans Condensed Medium"),
+          strip.text.x = element_text(margin = margin(t = 1, b = 1)),
           panel.border = element_blank(), 
           strip.background = element_rect(fill = "#ffffff", colour = NA),
           axis.ticks = element_blank(),

### 2018-07-14 01_clean-data.Rmd
Add two-level versions of gender and charity

@@
                                      Rarely = "Once every few years",
-                                     Rarely = "Never") %>% fct_rev()) %>% 
+                                     Rarely = "Never") %>% fct_rev(),
+         give_charity_2 = fct_recode(give_charity,
+                                     `At least once a year` = "Once a week",
+                                     `At least once a year` = "Once a month",
+                                     `At least once a year` = "Once every three months",
+                                     `At least once a year` = "Once every six months",
+                                     `At least once a year` = "Once a year",
+                                     Rarely = "Once every few years",
+                                     Rarely = "Never")) %>% 
   mutate(political_knowledge_bin = fct_recode(political_knowledge,
@@
   mutate(age_bin = factor(age >= median(.$age), levels = c(FALSE, TRUE),
-                          labels = paste(c("Less than", "At least"), median(.$age))))
+                          labels = paste(c("Less than", "At least"), median(.$age))),
+         gender_bin = fct_collapse(gender,
+                                   Female = "Female",
+                                   `Not Female` = c("Male", "Transgender", 
+                                                    "Other", "Prefer not to say")))
 

### 2018-07-14 03_additional-analysis.Rmd
Use Bayesian inference for sample vs. population comparisons
THIS IS SO COOL.

@@
 library(magrittr)
+library(rstan)
 library(rstanarm)
 library(broom)
-library(coda)
 library(glue)
@@
 library(modelr)
+library(ipumsr)
 library(here)
@@
 walk(full_chart, ~ print(.))
+```
+
+# Characteristics of experiment samples
+
+We compare our sample with demographic characteristics of the general population.
+Since there is no nationally representative sample for each of our demographic variables, we look at multiple data sources.
+
+- Age:
+- Volunteering
+- Donating to charity:
+
+Extract data from Current Population Survey, housed at the Minnesota Population Center’s Integrated Public Use Microdata Series
+
+```{r load-clean-cps, warning=FALSE, message=FALSE}
+cps_2015_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.xml")
+cps_2015_data_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.dat.gz")
+
+cps_2015_ddi <- read_ipums_ddi(cps_2015_ddi_file)
+cps_2015_data <- read_ipums_micro(cps_2015_ddi_file, data_file = cps_2015_data_file, verbose = FALSE)
+
+cps_2017_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_2017.xml")
+cps_2017_data_file <- file.path(here(), "data", "ipums-cps", "cps_2017.dat.gz")
+
+cps_2017_ddi <- read_ipums_ddi(cps_2017_ddi_file)
+cps_2017_data <- read_ipums_micro(cps_2017_ddi_file, data_file = cps_2017_data_file, verbose = FALSE)
+
+# Volunteering data from September 2015 only
+df_volunteering <- cps_2015_data %>% 
+  # Remove values not in the universe
+  mutate_at(vars(VLSTATUS, VLDONATE), funs(ifelse(. == 99, NA, .)))
+
+# All other data from annual March 2017 survey
+df_demographics <- cps_2017_data %>% 
+  # Remove values not in the universe
+  mutate(SEX = ifelse(SEX == 9, NA, SEX),
+         EDUC = ifelse(EDUC <= 1 | EDUC == 999, NA, EDUC),
+         INCTOT = ifelse(INCTOT == 99999999, NA, INCTOT))
+```
+
+```{r population-values}
+global_demographics <- df_demographics %>% 
+  summarize(age = weighted.mean(AGE >= 35, ASECWT), 
+            female = weighted.mean(SEX == 2, ASECWT),
+            college = weighted.mean(EDUC >= 111, ASECWT, na.rm = TRUE),
+            income = weighted.mean(INCTOT >= 50000, ASECWT, na.rm = TRUE)) %>% 
+  c()
+
+global_vol <- df_volunteering %>% 
+  summarize(volunteering = weighted.mean(VLSTATUS == 2, VLSUPPWT, na.rm = TRUE),
+            donating = weighted.mean(VLDONATE == 2, VLSUPPWT, na.rm = TRUE)) %>% 
+  c()
+
+global_stats <- c(global_vol, global_demographics)
+```
+
+```{r sample-population-characteristics-freq, include=FALSE, eval=FALSE}
+# Demographic variables
+table(results$gender_bin) %>% prop.test(., p = global_stats$female)
+table(results$education_bin) %>% prop.test(., p = global_stats$college)
+table(results$income_bin) %>% prop.test(., p = global_stats$income)
+table(results$age_bin) %>% prop.test(., p = global_stats$age)
+
+# Volunteering
+table(results$volunteer) %>% prop.test(., p = global_stats$volunteering)
+table(results$give_charity_2) %>% prop.test(., p = global_stats$donating)
+```
+
+```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
+prop_test_bayes_saved <- file.path(here(), "lib", "bayes_prop_test.rds")
+
+if (file.exists(prop_test_bayes_saved)) {
+  prop_test_bayes <- readRDS(prop_test_bayes_saved)
+} else {
+  prop_test_bayes <- stan_model(file.path(here(), "lib", "bayes_prop_test.stan"))
+  saveRDS(prop_test_bayes, prop_test_bayes_saved)
+}
+```
+
+```{r sample-population-characteristics, cache=TRUE}
+compare_sample_to_pop_bayes <- function(sample_value, population_value) {
+  mcmc_samples <- sampling(prop_test_bayes, list(x = table(sample_value)[1],
+                                                 total_n = length(sample_value),
+                                                 pop_prop = population_value),
+                           chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.9, 
+                     estimate.method = "median", conf.method = "HPDinterval") %>%
+    mutate(in_hpdi = (population_value >= conf.low & population_value <= conf.high))
+
+  thetas <- unlist(extract(mcmc_samples, "theta"))
+  pop_quantile_in_sample <- ecdf(thetas)(population_value)
+
+  in_hpdi <- (population_value >= tidied[1,]$conf.low & 
+                population_value <= tidied[1,]$conf.high)
+
+  return(list(mcmc_samples = mcmc_samples, tidied = tidied, theta_in_hpdi = in_hpdi,
+              pop_quantile_in_sample = pop_quantile_in_sample))
+}
+
+calc_sample_pop <- tribble(
+  ~Variable, ~sample_value, ~National,
+  "Female (%)", results$gender_bin, global_stats$female,
+  "Age (% 35+)", results$age_bin, global_stats$age,
+  "Income (% $50,000+)", results$income_bin, global_stats$income,
+  "Education (% BA+)", results$education_bin, global_stats$college,
+  "Donated in past year (%)", results$give_charity_2, global_stats$donating,
+  "Volunteered in past year (%)", results$volunteer, global_stats$volunteering
+) %>% 
+  mutate(Sample = sample_value %>% map_dbl(~ prop.table(table(.))[1]),
+         prop_test_bayes = map2(.x = sample_value, .y = National, 
+                                .f = ~ compare_sample_to_pop_bayes(.x, .y))) 
+```
+
+```{r tbl-sample-characteristics, results="asis"}
+format_hpdi <- function(post_lower, post_upper, star, digits = 1) {
+  glue("({lower}%, {upper}%){star}",
+       lower = round(100 * post_lower, digits),
+       upper = round(100 * post_upper, digits))
+}
+
+tbl_sample_pop <- calc_sample_pop %>% 
+  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
+         not_hpdi_symbol = ifelse(in_hpdi, "", "†"),
+         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
+         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
+         diffs_hpdi_fancy = diffs_tidy %>%
+           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
+                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
+  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
+  select(Variable, Sample, National, 
+         `Sample − National~posterior\\ median~` = diffs_median,
+         `90% HPDI` = diffs_hpdi_fancy)
+
+tbl_sample_pop %>% 
+  pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 
+                      caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-exp-sample.md")) %>% 
+  cat()
 ```
@@
 coef_summary_charity <- newdata_conditions_charity %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_charity), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_charity, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
@@
 coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_vol_relig), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_vol_relig, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
@@
 
-m_likely_cif_full <-update(m_likely_cif, . ~ . + 
+m_likely_cif_full <- update(m_likely_cif, . ~ . + 
                               favor_humanitarian_bin +

### 2018-07-15 03_additional-analysis.Rmd
Stop using file.path(here())

@@
 
-source(file.path(here(), "lib", "graphics.R"))
-source(file.path(here(), "lib", "pander_options.R"))
-source(file.path(here(), "lib", "modeling.R"))
+source(here("lib", "graphics.R"))
+source(here("lib", "pander_options.R"))
+source(here("lib", "modeling.R"))
 
 # Load data
-results <- readRDS(file.path(here(), "data", "results_clean.rds"))
+results <- readRDS(here("data", "results_clean.rds"))
 ```
@@
 ```{r build-consort}
-consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
+consort <- readRDS(here("data", "completion_summary.rds")) %>% 
   spread(reason, n) %>% 
@@
 # Save as PDF
-cairo_pdf(filename = file.path(here(), "output", "figures", "consort.pdf"),
+cairo_pdf(filename = here("output", "figures", "consort.pdf"),
           width = 10, height = 6)
@@
 # Save as PNG
-png(filename = file.path(here(), "output", "figures", "consort.png"), 
+png(filename = here("output", "figures", "consort.png"), 
     width = 10, height = 6, units = "in",
@@
 ```{r load-clean-cps, warning=FALSE, message=FALSE}
-cps_2015_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.xml")
-cps_2015_data_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.dat.gz")
+cps_2015_ddi_file <- here("data", "ipums-cps", "cps_09_2015.xml")
+cps_2015_data_file <- here("data", "ipums-cps", "cps_09_2015.dat.gz")
 
@@
 
-cps_2017_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_2017.xml")
-cps_2017_data_file <- file.path(here(), "data", "ipums-cps", "cps_2017.dat.gz")
+cps_2017_ddi_file <- here("data", "ipums-cps", "cps_2017.xml")
+cps_2017_data_file <- here("data", "ipums-cps", "cps_2017.dat.gz")
 
@@
 ```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
-prop_test_bayes_saved <- file.path(here(), "lib", "bayes_prop_test.rds")
+prop_test_bayes_saved <- here("lib", "bayes_prop_test.rds")
 
@@
 } else {
-  prop_test_bayes <- stan_model(file.path(here(), "lib", "bayes_prop_test.stan"))
+  prop_test_bayes <- stan_model(here("lib", "bayes_prop_test.stan"))
   saveRDS(prop_test_bayes, prop_test_bayes_saved)
@@
                       caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-exp-sample.md")) %>% 
+  cat(file = here("output", "tables", "tbl-exp-sample.md")) %>% 
   cat()
@@
   print() %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.pdf"),
+  ggsave(., filename = here("output", "figures", "avg-time.pdf"),
          width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.png"),
+  ggsave(., filename = here("output", "figures", "avg-time.png"),
          width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
@@
   to_md(max_width = 100) %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-models-amount-full.md"))
+  cat(file = here("output", "tables", "tbl-models-amount-full.md"))
 ```
@@
   to_md(max_width = 100) %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood-full.md"))
+  cat(file = here("output", "tables", "tbl-models-likelihood-full.md"))
 ```

### 2018-07-15 03_additional-analysis.Rmd
Descript IPUMS and CPS stuff

@@
 We compare our sample with demographic characteristics of the general population.
-Since there is no nationally representative sample for each of our demographic variables, we look at multiple data sources.
+Since there is no nationally representative sample for each of our demographic variables, we use two waves of the US Census's Current Population Survey (CPS), with data from the [Minnesota Population Center's Integrated Public Use Microdata Series (IPUMS)](https://cps.ipums.org/cps/).
 
-- Age:
-- Volunteering
-- Donating to charity:
+For general demographic information, we use data from the 2017 [Annual Social and Economic Supplement (ASEC)](https://cps.ipums.org/cps/asec_sample_notes.shtml) for the CPS.
+From 2002–2015, the CPS included a [Volunteer Supplement](https://cps.ipums.org/cps/volunteer_sample_notes.shtml) every September, so we use 2015 data for data on volunteering and donating to charity.
 
-Extract data from Current Population Survey, housed at the Minnesota Population Center’s Integrated Public Use Microdata Series
+IPUMS requires that you manually generate a data extract through their website, so downloading data from them is not entirely automated or reproducible.
+We created two extracts (though this could have been combined into one), with the following variables
+
+-  `"data/ipums-cps/cps_2017.dat.gz"`: 2017 ASEC, with the following variables selected (in addition to whatever IPUMS preselects by default) (and weighted by `ASECWT`):
+    - `AGE`
+    - `SEX`
+    - `EDUC`
+    - `INCTOT`
+-  `"data/ipums-cps/cps_09_2015.dat.gz"`: September 2015 basic monthly CPS (which includes the Volunteer Supplement), with the following variables selected (and weighted by `VLSUPPWT`):
+    - `VLSTATUS`
+    - `VLDONATE`
+
+We do not show other respondent demographic details because we don't have good population-level data to compare our sample with.
+We could theoretically use Pew data for political preferences, but they collect data on party affiliation, while we collected data about respondent positions along a conservative–liberal spectrum, so the two variables aren't comparable.
 
@@
   ~Variable, ~sample_value, ~National,
-  "Female (%)", results$gender_bin, global_stats$female,
-  "Age (% 35+)", results$age_bin, global_stats$age,
-  "Income (% $50,000+)", results$income_bin, global_stats$income,
-  "Education (% BA+)", results$education_bin, global_stats$college,
-  "Donated in past year (%)", results$give_charity_2, global_stats$donating,
-  "Volunteered in past year (%)", results$volunteer, global_stats$volunteering
+  "Female (%)^a^", results$gender_bin, global_stats$female,
+  "Age (% 35+)^a^", results$age_bin, global_stats$age,
+  "Income (% $50,000+)^a^", results$income_bin, global_stats$income,
+  "Education (% BA+)^a^", results$education_bin, global_stats$college,
+  "Donated in past year (%)^b^", results$give_charity_2, global_stats$donating,
+  "Volunteered in past year (%)^b^", results$volunteer, global_stats$volunteering
 ) %>% 
@@
   mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
-         not_hpdi_symbol = ifelse(in_hpdi, "", "†"),
+         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
          diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
@@
 
-tbl_sample_pop %>% 
+note_row <- data_frame(Variable = c("*^a^Annual CPS, March 2017*",
+                                    "*^b^Monthly CPS, September 2015*",
+                                    "*^†^National value is outside the sample highest posterior density interval (HPDI)*"))
+
+bind_rows(tbl_sample_pop, note_row) %>% 
   pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 

### 2018-07-15 03_additional-analysis.Rmd
Make it so this can be built as part of a site

@@
 # has already been loaded in previous scripts
+# 
+# Stupid bleeding environments
+# https://github.com/andrewheiss/rmarkdown-website-envs-orig
 if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
@@
                                     detach, character.only = TRUE)))
+
+  # THIS IS SO EVIL AND AWFUL BUT NECESSARY BECAUSE STUFF HAPPENS IN PREVIOUS
+  # FILES THAT BREAK THIS FILE WHEN IT IS KNIT AS PART OF AN RMARKDOWN WEBSITE
+  #
+  # DON'T TELL JENNY BRYAN
+  rm(list = ls())
+  # AHHH THE HORROR
 }

### 2018-07-15 02_analysis.Rmd
Add session info
Add caption labels

@@
   pandoc.table.return(missing = "—", 
-                      caption = "Median difference between likelihood to donate across single conditions") %T>%
+                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
   cat() %>% 
@@
   pandoc.table.return(missing = "—", 
-                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions') %T>%
+                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions {#tbl:amount-diffs}') %T>%
   cat() %>% 
@@
   pandoc.table.return(missing = "—", 
-                      caption = "Median difference between likelihood to donate across single conditions") %T>%
+                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
   cat() %>% 
@@
   pandoc.table.return(missing = "—", 
-                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions') %T>%
+                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions {#tbl:likelihood-diffs}') %T>%
   cat() %>% 
@@
 ```
+
+# Session info
+
+<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>
+
+<div id="sessioninfo" class="collapse">
+
+```{r show-session-info}
+sessionInfo()
+```
+
+</div>

### 2018-07-15 03_additional-analysis.Rmd
Add session info
Shrink time figure

@@
   labs(x = "Minutes spent on experiment", y = "Count") +
-  theme_ngos() +
+  theme_ngos(base_size = 9.5) +
   theme(panel.grid.minor = element_blank())
@@
   ggsave(., filename = here("output", "figures", "avg-time.pdf"),
-         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
+         width = 4, height = 2.25, units = "in", device = cairo_pdf) %>% 
   ggsave(., filename = here("output", "figures", "avg-time.png"),
-         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
+         width = 4, height = 2.25, units = "in", type = "cairo", dpi = 300)
 ```

### 2018-07-15 preregistration.Rmd
Move IRB text to separate file

@@
 
-## Project title
-
-Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy
-
-## Purpose of the study
-
-State repression of civil society organizations, in particular NGOs, has become ubiquitous over the last few decades.
-Besides undertaking violence towards costly organizations, states have also increasingly used legislation to crack down on NGOs.
-By creating barriers to their entry, funding, and operations, these laws restrict the space available for NGOs to engage in advocacy and provide services.
-How do such legal restrictions on NGOs impact private donors?
-With states increasingly providing funding for NGOs working in non-contentious issue areas, and a lack of philanthropic culture in many developing countries, numerous NGO rely on funds from private donors in Western countries.
-We use a survey experiment to examine the impact of state repression of NGOs on the preferences of private donors, as well as their actual behavior donating to besieged NGOs.
-In particular, we explore how state crackdown against NGOs changes private donors’ preferences and behavior based on the issue area of the organization, and the main source of its funds.
-Our results have important implications for understanding donor behavior, as well as for the sustainability of civil society organizations in developing countries.
-
-## Participant activities
-
-Participants will fill out a survey experiment that (1) describes a prominent international NGO—the International Rescue Committee (IRC)—and (2) requests participants how much money they would hypothetically donate to the organization.
-We manipulate the vignette describing IRC’s work in three different ways to isolate the effect of civil society legal crackdowns on private philanthropy:
-
-> The International Rescue Committee (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.
-> 
-> A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.
-
-The survey also offers a vignette related to corporate philanthropy, describing Google’s partnership with IRC in late 2016.
-We manipulate the vignette using the same scenarios (presence or absence of a legal crackdown, issue area, and funding source) to isolate the effect of legal crackdowns on corporate social responsibility campaigns and perceptions of companies engaging in corporate philanthropy.
-
-Finally, the survey asks participants a series of general questions related to their views of philanthropy, political knowledge, and general demographic features.
-
-## Subject selection and recruitment
-
-Participants of the survey experiment will be recruited via Amazon Mechanical Turk (MTurk), an online crowdsourcing platform that has been extensively used in social science research in recent years.
-MTurk allows researchers to recruit participants to perform tasks such as filling out surveys and opinion polls, participating in experiments, or coding the content of documents.
-Researchers advertise their studies as a human intelligence task (HIT) on MTurk, and participants choose only those HITs that interest them, given the promised price and estimated duration of the task.
-Participants are paid for completing HITs, and payment is transferred directly to participants’ credit cards immediately after the completion of a study.
-
-Our study will be listed as “Survey on international nonprofit organizations” and will take approximately 5 minutes to complete.
-Participants will be paid \$0.75 for completing the experiment, commensurate with a \$9/hour wage.
-After selecting our HIT, participants will be taken directly to the survey experiment, which will be hosted on Qualtrics.
-MTurk rules state that participants can terminate the study by returning the HIT at any time, without penalty.
-
-## Data security and participant privacy
-
-We will not collect personally identifiable data.
-MTurk workers are assigned a semi-random alphanumeric worker ID, which is the only information exposed to us as researchers.
-We collect MTurk worker IDs to distribute compensation after completion of the experiment and to exclude workers from future iterations of the study.
-Worker IDs will not be shared with anyone outside of the research team, will be removed from the data set, and will not be associated with any survey responses.
-Both Amazon and Qualtrics use SSL encryption (HTTPS) when collecting data from workers and transferring data to servers, so responses will remain confidential during the administration of the survey.
-
-After collecting data and paying participants, we plan on creating a clean, anonymous, non-identifiable dataset to use for our analysis and for public distribution following the publication of the results of the study.
-This data will not contain any worker-identifiable information and will be safe to store and use without extra security measures.
-
-Suparna Chaudhry and Andrew Heiss are co-investigators and will both have access to the clean, anonymized. Both have independently submitted IRB applications to their respective institutions.
-
-## Compensation
-
-Participants will be paid \$0.75 for successfully completing the experiment, commensurate with a \$9/hour wage.
-
-Previous studies have found that including simple questions to screen for attention can improve the results of MTurk experiments and filter out workers who try to get through the HIT as quickly as possible without reading the questions [@BerinskyMargolisSances:2014].
-To ensure that participants only receive compensation for completing the full experiment, we include two attention check questions.
-The first (Q1.3) involves reading several sentences and following instructions to select specific responses.
-The second (Q4.8) is simpler and asks the respondent to select a single color from a list.
-
-Each attention check question serves a different purpose.
-The longer question (Q1.3) is designed to filter out respondents who are not paying attention at all and are trying to get a quick payout.
-Respondents who fail this question will exit the experiment and will not receive compensation.
-In an effort to not waste worker time, this is the first question after the consent form, so little participant time will have been wasted.
-
-The shorter question (Q4.8) is designed to quickly check if the respondent is still paying attention near the end.
-Participants who fail this question will still be compensated, but we will account for their lack of attention in our statistical analysis and may omit their response.
-
-## Risks and benefits
-
-The study poses minimal risks to participants.
-The experiment does not include false information—the manipulations we make in the vignettes (shown between curly braces (`{}`)) only serve to make each fact about the International Rescue Committee (IRC) and Google more salient:
-
-- “providing humanitarian assistance for refugees | advocating human rights for refugees”: IRC provides humanitarian assistance and engages in human rights advocacy for refugees
-- “in countries where nonprofit organizations are harshly restricted”: IRC works in some countries that have passed anti-NGO laws, such as Egypt and Turkey, as well as countries with no such laws
-- “A substantial proportion of IRC’s funding comes from government | private donors”: According to IRC’s most recent annual report, >25% of their income came from each of these sources
-- Google has hosted several events to raise money for IRC, including initiatives in 2015 and 2016. We do not manipulate the amount of money raised.
+```{r child = "text/irb.md"}
+```
 

### 2018-07-15 03_additional-analysis.Rmd
Add additional analysis to supplement

@@
 
-m_amount_cif_full <-update(m_amount_cif, . ~ . + 
+m_amount_cif_full <- update(m_amount_cif, . ~ . + 
                              favor_humanitarian_bin +
@@
 
-ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
+amount_coefs_full <- ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
   stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
@@
         strip.text = element_blank())
+
+amount_coefs_full %T>%
+  print() %T>% 
+  ggsave(., filename = here("output", "figures", "amount-coefs-full.pdf"),
+         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = here("output", "figures", "amount-coefs-full.png"),
+         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
+likely_coefs_full <- ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
   stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
@@
         strip.text = element_blank())
+
+likely_coefs_full %T>%
+  print() %T>% 
+  ggsave(., filename = here("output", "figures", "likely-coefs-full.pdf"),
+         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = here("output", "figures", "likely-coefs-full.png"),
+         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
 ```

### 2018-07-16 02_analysis.Rmd
Minor edits + summary of hypotheses

@@
 # Session info
+# Summary of hypotheses
+
+```{r hypotheses-summary, warning=FALSE, message=FALSE, results="asis"}
+# TODO: Make this more dynamic so I don't have to type all the values manually
+hypotheses <- read_csv(here("text", "hypotheses-summary.csv"))
+
+hypotheses %>% 
+  pandoc.table.return(justify = "ll", style = "grid", keep.line.breaks = TRUE,
+                      caption = "Summary of all hypotheses {#tbl:hypotheses}") %T>%
+  cat() %>% 
+  cat(file = file.path(here(), "output", "tables", "tbl-hypotheses.md"))
+```
 

### 2018-07-16 03_additional-analysis.Rmd
Use safesite

@@
 ```{r load-libraries-data, warning=FALSE, message=FALSE}
-# Unload all the already-loaded packages because R Markdown websites *don't* knit 
-# each Rmd in a separate environment: https://github.com/rstudio/rmarkdown/issues/1326
-#
-# This means that here::here() and lubridate::here() will conflict becuase **here**
-# has already been loaded in previous scripts
-# 
-# Stupid bleeding environments
-# https://github.com/andrewheiss/rmarkdown-website-envs-orig
-if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
-  invisible(suppressWarnings(sapply(paste0("package:", names(sessionInfo()$otherPkgs)),
-                                    detach, character.only = TRUE)))
-
-  # THIS IS SO EVIL AND AWFUL BUT NECESSARY BECAUSE STUFF HAPPENS IN PREVIOUS
-  # FILES THAT BREAK THIS FILE WHEN IT IS KNIT AS PART OF AN RMARKDOWN WEBSITE
-  #
-  # DON'T TELL JENNY BRYAN
-  rm(list = ls())
-  # AHHH THE HORROR
-}
-
-# Load libraries again
+# Load libraries
 library(tidyverse)

### 2018-07-16 index.Rmd
Use safesite

@@
 date: "Last run: `r format(Sys.time(), '%F')`"
+site: safesite::safesite
 ---

### 2018-07-16 lib/modeling.R
Flip crackdown diffs so it's easier to interpret

@@ -14,7 +14,7 @@ options(mc.cores = parallel::detectCores())
 mcmc_pairwise_diffs <- function(chains) {
   pair_names <- outer(colnames(chains), colnames(chains),
                       paste, sep = " − ")
-  pairs_to_omit <- which(lower.tri(pair_names, diag = TRUE))
+  pairs_to_omit <- which(upper.tri(pair_names, diag = TRUE))
   
   mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
                       function(x, y) chains[,x] - chains[,y]) %>% 

### 2018-07-16 02_analysis.Rmd
Better session info
Nicer session info
Stop using coda

@@
 library(broom)
-library(coda)
 library(ggstance)
@@
 coef_summary_c <- newdata_conditions_c %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_c, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 # newdata <- newdata_conditions %>% 
-#   bind_cols(tidyMCMC(as.mcmc(posterior_fit), estimate.method = "median",
+#   bind_cols(tidyMCMC(posterior_fit, estimate.method = "median",
 #                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_i <- newdata_conditions_i %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_i), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_i, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_f <- newdata_conditions_f %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_f), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_f, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_ci <- newdata_conditions_ci %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_ci), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_ci, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_cif <- newdata_conditions_cif %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_cif), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_cif, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_likely_c <- newdata_conditions_c %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_c), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_likely_c, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_likely_i <- newdata_conditions_i %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_i), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_likely_i, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_likely_f <- newdata_conditions_f %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_f), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_likely_f, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_likely_ci <- newdata_conditions_ci %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_ci), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_likely_ci, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 coef_summary_likely_cif <- newdata_conditions_cif %>% 
-  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_cif), estimate.method = "median",
+  bind_cols(tidyMCMC(chains_fitted_likely_cif, estimate.method = "median",
                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
@@
 
-# Session info
 # Summary of hypotheses
@@
 
+# Original computing environment
+
 <button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>
@@
 
-```{r show-session-info}
-sessionInfo()
+```{r show-session-info, echo=TRUE}
+writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
+
+devtools::session_info()
 ```

### 2018-07-16 02_analysis.Rmd
Calculate percent change!

@@
 results <- readRDS(file.path(here(), "data", "results_clean.rds"))
+# qwraps2::lazyload_cache_dir("02_analysis_cache/html")
 
@@
 
-plot_donate_summary
-
 plot_donate_summary %T>% 
@@
 
-pairs_plot_data_c <- diffs_coef_pairs_c %>%
+pairs_plot_data_c <- diffs_coef_pairs_c$mcmc_diffs %>%
   gather(pair, value) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
 
-pairs_plot_data_i <- diffs_coef_pairs_i %>%
+pairs_plot_data_i <- diffs_coef_pairs_i$mcmc_diffs %>%
   gather(pair, value) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
 
-pairs_plot_data_f <- diffs_coef_pairs_f %>%
+pairs_plot_data_f <- diffs_coef_pairs_f$mcmc_diffs %>%
   gather(pair, value) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
   mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
-         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))
+         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
+         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))
 
@@
   unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs)
+  select(-data, -diffs_coef_pairs, -diffs_coefs) #%>% 
+  #mutate(pair = "Hey")
 
 pairs_plot_data_ci <- pairs_conditions_ci %>% 
-  select(issue, diffs_coef_pairs) %>% 
-  unnest(diffs_coef_pairs) %>%
+  select(issue, diffs_coefs) %>% 
+  unnest(diffs_coefs) %>%
   gather(pair, value, -issue) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
   unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs)
+  select(-data, -diffs_coef_pairs, -diffs_coefs)
 
 pairs_plot_data_cif <- pairs_conditions_cif %>% 
-  select(issue, funding, diffs_coef_pairs) %>% 
-  unnest(diffs_coef_pairs) %>%
+  select(issue, funding, diffs_coefs) %>% 
+  unnest(diffs_coefs) %>%
   gather(pair, value, -issue, -funding) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair),
@@
   select(`Frame` = pair, `∆~median~` = median, 
+         `% change~median~` = median_pct_change,
          `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
@@
   select(Issue = issue, Funding = funding, 
-         `No crackdown − crackdown~median~` = median, 
+         `Crackdown - No crackdown~median~` = median, 
+         `% change~median~` = median_pct_change,
          `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(missing = "—", 
-                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions {#tbl:amount-diffs}') %T>%
+                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
   cat() %>% 
@@
 
-pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c %>%
+pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c$mcmc_diffs %>%
   gather(pair, value) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
 
-pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i %>%
+pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i$mcmc_diffs %>%
   gather(pair, value) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
 
-pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f %>%
+pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f$mcmc_diffs %>%
   gather(pair, value) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
 pairs_likely_plot_data_ci <- pairs_likely_conditions_ci %>% 
-  select(issue, diffs_coef_pairs) %>% 
-  unnest(diffs_coef_pairs) %>%
+  select(issue, diffs_coefs) %>% 
+  unnest(diffs_coefs) %>%
   gather(pair, value, -issue) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
   unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs)
+  select(-data, -diffs_coef_pairs, -diffs_coefs)
 
 pairs_likely_plot_data_cif <- pairs_likely_conditions_cif %>% 
-  select(issue, funding, diffs_coef_pairs) %>% 
-  unnest(diffs_coef_pairs) %>%
+  select(issue, funding, diffs_coefs) %>% 
+  unnest(diffs_coefs) %>%
   gather(pair, value, -issue, -funding) %>%
   mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
+  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
   mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "−", "−\n"),
+                       str_replace(pair, "-", "-\n"),
                        pair))
@@
   geom_vline(data = diffs_coef_likely_pairs_detail_cif,
-             aes(xintercept = median), size = 0.25) +
+             aes(xintercept = `median`), size = 0.25) +
   geom_vline(xintercept = 0, linetype = "dotted") +
@@
   select(Issue = issue, Funding = funding, 
-         `No crackdown − crackdown~median~` = median, 
+         `Crackdown - No crackdown~median~` = median, 
+         `% change~median~` = median_pct_change,
          `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(missing = "—", 
-                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions {#tbl:likelihood-diffs}') %T>%
+                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
   cat() %>% 

### 2018-07-16 lib/modeling.R

@@ -13,20 +13,33 @@ options(mc.cores = parallel::detectCores())
 # Adapted from http://stackoverflow.com/a/28187446/120898
 mcmc_pairwise_diffs <- function(chains) {
   pair_names <- outer(colnames(chains), colnames(chains),
-                      paste, sep = " − ")
+                      paste, sep = " - ")
   pairs_to_omit <- which(upper.tri(pair_names, diag = TRUE))
   
   mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
                       function(x, y) chains[,x] - chains[,y]) %>% 
-    magrittr::set_colnames(pair_names) %>% 
-    select(-pairs_to_omit)
+    magrittr::set_colnames(., pair_names) %>% 
+    select(-pairs_to_omit) %>% 
+    as_data_frame()
   
-  return(mcmc_diffs)
+  mcmc_pct_change <- outer(1:ncol(chains), 1:ncol(chains),
+                      function(x, y) (chains[,x] - chains[,y]) / chains[,y]) %>% 
+    magrittr::set_colnames(., pair_names) %>% 
+    select(-pairs_to_omit) %>% 
+    as_data_frame()
+  
+  return(list(mcmc_diffs = mcmc_diffs, mcmc_pct_change = mcmc_pct_change))
 }
 
 # Summarize the differences between MCMC pairs
 tidy_diffs <- function(diffs_pairs) {
-  diffs_pairs %>% 
+  pct_change_pairs <- diffs_pairs$mcmc_pct_change %>% 
+    gather(pair, value) %>% 
+    group_by(pair) %>% 
+    summarise(mean_pct_change = mean(value),
+              median_pct_change = median(value))
+  
+  mcmc_diffs_pairs <- diffs_pairs$mcmc_diffs %>% 
     gather(pair, value) %>% 
     group_by(pair) %>% 
     summarise(mean = mean(value),
@@ -40,6 +53,9 @@ tidy_diffs <- function(diffs_pairs) {
               p.greater0 = mean(value > 0),
               p.less0 = mean(value < 0),
               p.diff.not0 = ifelse(median > 0, p.greater0, p.less0))
+  
+  diffs_summary <- left_join(mcmc_diffs_pairs, pct_change_pairs, by = "pair")
+  return(diffs_summary)
 }
 
 

### 2018-07-17 01_clean-data.Rmd
Add session info
Nicer session info
Stop using file.path(here(.))

@@
 ---
+
+# Load and clean data
 
@@
 # results_file <- file.path(here(), "data", "test_data.csv")
-results_file <- file.path(here(), "private", 
+results_file <- here("private", 
                      "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")
@@
 # IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
-codes_to_exclude <- read_csv(file.path(here(), "data", "codes_to_exclude.csv"))
+codes_to_exclude <- read_csv(here("data", "codes_to_exclude.csv"))
 
@@
 # Save final clean data
-saveRDS(results, file.path(here(), "data", "results_clean.rds"))
-write_csvy(results, file = file.path(here(), "data", "results_clean.csv"),
-           metadata = file.path(here(), "data", "results_clean.yaml"), na = "NA")
+saveRDS(results, here("data", "results_clean.rds"))
+write_csvy(results, file = here("data", "results_clean.csv"),
+           metadata = here("data", "results_clean.yaml"), na = "NA")
 ```
@@
 
-saveRDS(completed_summary, file.path(here(), "data", "completion_summary.rds"))
-write_csv(completed_summary, file.path(here(), "data", "completion_summary.csv"))
+saveRDS(completed_summary, here("data", "completion_summary.rds"))
+write_csv(completed_summary, here("data", "completion_summary.csv"))
 ```
+
+# Original computing environment
+
+<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>
+
+<div id="sessioninfo" class="collapse">
+
+```{r show-session-info, echo=TRUE}
+writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
+
+devtools::session_info()
+```
+
+</div>

### 2018-07-17 02_analysis.Rmd
Stop using file.path(here(.))

@@
 
-source(file.path(here(), "lib", "graphics.R"))
-source(file.path(here(), "lib", "pander_options.R"))
-source(file.path(here(), "lib", "modeling.R"))
+source(here("lib", "graphics.R"))
+source(here("lib", "pander_options.R"))
+source(here("lib", "modeling.R"))
 
 # Load data
-results <- readRDS(file.path(here(), "data", "results_clean.rds"))
+results <- readRDS(here("data", "results_clean.rds"))
 # qwraps2::lazyload_cache_dir("02_analysis_cache/html")
@@
 
-  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
+  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
                                   paste0(file_name, ".pdf")), 
          width = 1, height = 0.2, device = cairo_pdf)
-  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
+  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
                                   paste0(file_name, ".png")), 
@@
 
-  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
+  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
                                    paste0(file_name, ".pdf")), 
          width = 1, height = 0.2, device = cairo_pdf)
-  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
+  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
                                    paste0(file_name, ".png")), 
@@
   pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-experimental-conditions.md"))
+  cat(file = here("output", "tables", "tbl-experimental-conditions.md"))
 ```
@@
                       split.cell = 80, split.table = Inf) %T>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-descriptive-stats.md")) %>% 
+  cat(file = here("output", "tables", "tbl-descriptive-stats.md")) %>%
   cat()
@@
   pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-avg-results.md"))
+  cat(file = here("output", "tables", "tbl-avg-results.md"))
 ```
@@
   print() %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "donate_summary.pdf"),
+  ggsave(., filename = here("output", "figures", "donate_summary.pdf"),
          width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "donate_summary.png"),
+  ggsave(., filename = here("output", "figures", "donate_summary.png"),
          width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
@@
   print() %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "amount_summary.pdf"),
+  ggsave(., filename = here("output", "figures", "amount_summary.pdf"),
          width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "amount_summary.png"),
+  ggsave(., filename = here("output", "figures", "amount_summary.png"),
          width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
@@
   pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-coefficients-to-add.md"))
+  cat(file = here("output", "tables", "tbl-coefficients-to-add.md"))
 ```
@@
   to_md(max_width = 100) %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
+  cat(file = here("output", "tables", "tbl-models-amount.md"))
 ```
@@
   print() %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.pdf"),
+  ggsave(., filename = here("output", "figures", "amount_single_summary.pdf"),
          width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.png"),
+  ggsave(., filename = here("output", "figures", "amount_single_summary.png"),
          width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
@@
                     tag_levels = "A", theme = theme_ngos())) %T>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
+  ggsave(., filename = here("output", "figures", "amount-medians.pdf"),
          width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
+  ggsave(., filename = here("output", "figures", "amount-medians.png"),
          width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
@@
   print() %T>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.pdf"),
+  ggsave(., filename = here("output", "figures", "amount-singles-diffs.pdf"),
          width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.png"),
+  ggsave(., filename = here("output", "figures", "amount-singles-diffs.png"),
          width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
@@
   cat() %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
+  cat(file = here("output", "tables", "tbl-amount-single-diffs.md"))
 ```
@@
                   tag_levels = "A", theme = theme_ngos())) %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
+  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
          width = 8, height = 5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.png"),
+  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
          width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
@@
   cat() %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
+  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
 ```
@@
   to_md(max_width = 100) %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood.md"))
+  cat(file = here("output", "tables", "tbl-models-likelihood.md"))
 ```
@@
                   tag_levels = "A", theme = theme_ngos())) %T>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
+  ggsave(., filename = here("output", "figures", "likelihood-medians.pdf"),
          width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
+  ggsave(., filename = here("output", "figures", "likelihood-medians.png"),
          width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
@@
   print() %T>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.pdf"),
+  ggsave(., filename = here("output", "figures", "likelihood-singles-diffs.pdf"),
          width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.png"),
+  ggsave(., filename = here("output", "figures", "likelihood-singles-diffs.png"),
          width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
@@
   cat() %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
+  cat(file = here("output", "tables", "tbl-likelihood-single-diffs.md"))
 ```
@@
                     tag_levels = "A", theme = theme_ngos())) %T>%
-  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),
+  ggsave(., filename = here("output", "figures", "likelihood-diffs.pdf"),
          width = 8, height = 5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.png"),
+  ggsave(., filename = here("output", "figures", "likelihood-diffs.png"),
          width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
@@
   cat() %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
+  cat(file = here("output", "tables", "tbl-likelihood-diffs.md"))
 ```
@@
   cat() %>% 
-  cat(file = file.path(here(), "output", "tables", "tbl-hypotheses.md"))
+  cat(file = here("output", "tables", "tbl-hypotheses.md"))
 ```

### 2018-07-17 02_analysis.Rmd
Figure of treatment effects

@@
 
-```{r hypotheses-summary, warning=FALSE, message=FALSE, results="asis"}
-# TODO: Make this more dynamic so I don't have to type all the values manually
-hypotheses <- read_csv(here("text", "hypotheses-summary.csv"))
-
-hypotheses %>% 
-  pandoc.table.return(justify = "ll", style = "grid", keep.line.breaks = TRUE,
-                      caption = "Summary of all hypotheses {#tbl:hypotheses}") %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-hypotheses.md"))
+```{r hypotheses-summary-figure, fig.width=8, fig.height=6.5}
+hypotheses <- tribble(
+  ~dv, ~hypothesis, ~summary,
+  "Likelihood", "H1a: Donors more likely\nto give to NGOs\nfacing crackdown", diffs_coef_likely_pairs_detail_c,
+  "Likelihood", "H2a: Donors more likely\nto give to humanitarian\nNGOs facing crackdown", diffs_coef_likely_pairs_detail_ci,
+  "Likelihood", "H3a: Donors more likely\nto give to privately funded\nNGOs facing crackdown", diffs_coef_likely_pairs_detail_cif,
+  "Amount", "H1b: Donors give more \nto NGOs facing crackdown", diffs_coef_pairs_detail_c,
+  "Amount", "H2b: Donors give more \nto humanitarian NGOs\nfacing crackdown", diffs_coef_pairs_detail_ci,
+  "Amount", "H3b: Donors give more \nto privately funded NGOs\nfacing crackdown", diffs_coef_pairs_detail_cif
+)
+
+plot_hypotheses <- hypotheses %>% 
+  unnest(summary) %>% 
+  select(-diffs_coefs) %>% 
+  mutate(condition = paste0(issue, " + ", funding),
+         condition = recode(condition, 
+                            `Human rights + NA` = "Human rights",
+                            `Humanitarian assistance + NA` = "Humanitarian assistance",
+                            `NA + NA` = "Crackdown only")) %>% 
+  mutate(hypothesis_custom = case_when(
+    .$condition == "Human rights + Government" ~ paste(hypothesis, "\n(government funding condition)"),
+    .$condition == "Humanitarian assistance + Government" ~ paste(hypothesis, "\n(government funding condition)"),
+    .$condition == "Human rights + Private" ~ paste(hypothesis, "\n(private funding condition)"),
+    .$condition == "Humanitarian assistance + Private" ~ paste(hypothesis, "\n(private funding condition)"),
+    TRUE ~ hypothesis
+  )) %>% 
+  mutate(issue = fct_rev(fct_explicit_na(issue, na_level = "Crackdown only")),
+         hypothesis_facet = ifelse(str_detect(hypothesis, "H3"), 2, 1),
+         p_lab = case_when(
+           .$dv == "Likelihood" ~ sprintf("∆ = %.2f; p(∆ ≠ 0) = %.2f", .$median, .$p.diff.not0),
+           .$dv == "Amount" ~ sprintf("∆ = $%.2f; p(∆ ≠ 0) = %.2f", .$median, .$p.diff.not0)
+         ))
+
+plot_hypotheses_likely <- filter(plot_hypotheses, dv == "Likelihood")
+plot_hypotheses_amount <- filter(plot_hypotheses, dv == "Amount")
+
+plot_summary_likely <- ggplot(plot_hypotheses_likely, 
+                              aes(x = median, y = fct_rev(hypothesis_custom))) +
+  geom_pointrangeh(aes(xmin = q5, xmax = q95, color = issue),
+                   position = position_dodgev(height = 0.5)) +
+  geom_vline(xintercept = 0, size = 0.25, linetype = "dashed") +
+  geom_label(data = filter(plot_hypotheses_likely, issue == "Human rights"), 
+             aes(label = p_lab, color = issue), size = 3, nudge_y = 0.35, show.legend = FALSE) +
+  geom_label(data = filter(plot_hypotheses_likely, issue == "Humanitarian assistance"), 
+             aes(label = p_lab, color = issue), size = 3, nudge_y = -0.35, show.legend = FALSE) +
+  geom_label(data = filter(plot_hypotheses_likely, issue == "Crackdown only"), 
+             aes(label = p_lab, color = issue), size = 3, nudge_y = 0.2, show.legend = FALSE) +
+  labs(x = expression(paste("Effect of crackdown: (Crackdown - No crackdown)"["median"])),
+       y = NULL, subtitle = "Likelihood of donation") +
+  scale_x_continuous(labels = percent_format(accuracy = 1)) +
+  scale_color_manual(values = ngo_cols("dark grey", "blue", "red", name = FALSE), name = NULL) +
+  coord_cartesian(clip = "off") +
+  theme_ngos() + 
+  theme(strip.text = element_blank(),
+        panel.grid.minor = element_blank(),
+        plot.subtitle = element_text(size = rel(1.2), face = "plain", #hjust = 0.5,
+                                    family = "Encode Sans Condensed Medium")) +
+  facet_wrap(~ hypothesis_facet, nrow = 1, scales = "free")
+
+plot_summary_amount <- ggplot(plot_hypotheses_amount, 
+                              aes(x = median, y = fct_rev(hypothesis_custom))) +
+  geom_pointrangeh(aes(xmin = q5, xmax = q95, color = issue),
+                   position = position_dodgev(height = 0.5)) +
+  geom_vline(xintercept = 0, size = 0.25, linetype = "dashed") +
+  geom_label(data = filter(plot_hypotheses_amount, issue == "Human rights"), 
+             aes(label = p_lab, color = issue), size = 3, nudge_y = 0.35, show.legend = FALSE) +
+  geom_label(data = filter(plot_hypotheses_amount, issue == "Humanitarian assistance"), 
+             aes(label = p_lab, color = issue), size = 3, nudge_y = -0.35, show.legend = FALSE) +
+  geom_label(data = filter(plot_hypotheses_amount, issue == "Crackdown only"), 
+             aes(label = p_lab, color = issue), size = 3, nudge_y = 0.2, show.legend = FALSE) +
+  labs(x = expression(paste("Effect of crackdown: (Crackdown - No crackdown)"["median"])),
+       y = NULL, subtitle = "Amount donated",
+       caption = "90% credible intervals shown around each point") +
+  scale_x_continuous(labels = dollar_format()) +
+  scale_color_manual(values = ngo_cols("dark grey", "blue", "red", name = FALSE), guide = FALSE) +
+  coord_cartesian(clip = "off") +
+  theme_ngos() + 
+  theme(strip.text = element_blank(),
+        panel.grid.minor = element_blank(),
+        plot.subtitle = element_text(size = rel(1.2), face = "plain", #hjust = 0.5,
+                                    family = "Encode Sans Condensed Medium")) +
+  facet_wrap(~ hypothesis_facet, nrow = 1, scales = "free")
+
+plot_summary_diffs <- plot_summary_likely + plot_summary_amount +
+  plot_layout(ncol = 1)
+
+plot_summary_diffs
+
+plot_summary_diffs %T>%
+  ggsave(., filename = here("output", "figures", "summary-diffs.pdf"),
+         width = 8, height = 6.5, units = "in", device = cairo_pdf) %>%
+  ggsave(., filename = here("output", "figures", "summary-diffs.png"),
+         width = 8, height = 6.5, units = "in", type = "cairo", dpi = 300)
 ```

### 2018-07-17 lib/graphics.R

@@ -9,8 +9,8 @@ theme_spark <- function() {
 }
 
 theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", density = FALSE) {
-  update_geom_defaults("label", list(family = "Encode Sans Condensed Medium"))
-  update_geom_defaults("text", list(family = "Encode Sans Condensed Medium"))
+  update_geom_defaults("label", list(family = "Encode Sans Condensed Light", face = "plain"))
+  update_geom_defaults("text", list(family = "Encode Sans Condensed Light", face = "plain"))
   
   ret <- theme_bw(base_size, base_family) +
     theme(plot.title = element_text(size = rel(1.4), face = "plain",

### 2018-07-19 02_analysis.Rmd
Shrink column titles

@@
   select(`Frame` = pair, `∆~median~` = median, 
-         `% change~median~` = median_pct_change,
+         `%∆~median~` = median_pct_change,
          `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
@@
   select(Issue = issue, Funding = funding, 
-         `Crackdown - No crackdown~median~` = median, 
-         `% change~median~` = median_pct_change,
+         `∆~median~` = median, 
+         `%∆~median~` = median_pct_change,
          `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 

### 2018-07-19 03_additional-analysis.Rmd
Nicer session info
Shrink column titles

@@
   select(Variable, Sample, National, 
-         `Sample − National~posterior\\ median~` = diffs_median,
+         `∆~median~` = diffs_median,
          `90% HPDI` = diffs_hpdi_fancy)
@@
 
-# Session info
+# Original computing environment
 

### 2018-07-19 index.Rmd
Add abstract and fix GitHub links

@@
 
-\\(•◡•)/
+## Abstract
+
+State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common.
+How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
+With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries.
+Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO.
+We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs.
+Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues.
+We conclude by discussing the implications for the sustainability of NGOs working abroad.

### 2019-02-26 lib/graphics.R
Add pts() for converting mm to pts

@@ -45,6 +45,12 @@ theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", de
 }
 
 
+# Point size --------------------------------------------------------------
+# Convert mms to pts 
+pts <- function(x) {
+  as.numeric(grid::convertUnit(grid::unit(x, "pt"), "mm"))
+}
+
 # Colors ------------------------------------------------------------------
 
 # How to create custom palettes:

### 2019-02-26 lib/modeling.R
Boost iterations and warmups

@@ -1,8 +1,8 @@
 # Stan details ------------------------------------------------------------
 
 CHAINS <- 4
-ITER <-2000
-WARMUP <- 1000
+ITER <- 4000
+WARMUP <- 2000
 BAYES_SEED <- 1234
 options(mc.cores = parallel::detectCores())
 

### 2019-02-26 02_analysis.Rmd
Use RAW STAN for better analysis
No more triple interaction terms!

--- 2018-07-17 02_analysis.Rmd
@@
 author: "Andrew Heiss and Suparna Chaudhry"
-date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
+date: "Last run: `r format(Sys.time(), '%F')`"
 output: 
@@
     code_folding: hide
-    pandoc_args: [
-      "--default-image-extension=png"
-    ]
 editor_options: 
@@
 library(tidyverse)
-library(rstanarm)
+library(rstan)
+library(tidybayes)
 library(broom)
@@
 
-  factor_summary <- data_frame(x) %>% 
+  factor_summary <- tibble(x) %>% 
     count(x) %>%
@@
 
-  output <- data_frame(spark = md_img, summary = inline_summary)
+  output <- tibble(spark = md_img, summary = inline_summary)
   return(output)
@@
 
-## Prior favorability towards NGOs
-
-```{r fig-ngo-favorability, fig.width=7, fig.height=4}
-favorability_cols <- data_frame(value = c("Very unfavorable", "Unfavorable", "Neutral",
-                                          "Favorable", "Very favorable"),
-                                color = ngo_pal("ordered")(5))
-
-ngo_favorability_raw <- results %>%
-  select(favor_humanitarian, favor_human_rights, favor_development) %>% 
-  gather(variable, value) %>% 
-  count(variable, value) %>% 
-  left_join(vars_to_summarize, by = "variable") %>% 
-  left_join(favorability_cols, by = "value") %>%
-  mutate(clean_name = str_replace(clean_name, "towards", "towards\n")) %>% 
-  mutate(value = factor(value, levels = levels(results$favor_humanitarian), ordered = TRUE),
-         clean_name = fct_inorder(clean_name, ordered = TRUE)) %>%
-  arrange(value) %>% 
-  mutate(color = fct_inorder(color, ordered = TRUE))
-
-ngo_favorability_high <- ngo_favorability_raw %>% 
-  filter(!str_detect(value, "nfav")) %>% 
-  mutate(n = ifelse(value == "Neutral", n / 2, n),
-         n_plot = n,
-         value = fct_rev(value), color = fct_rev(color))
-
-ngo_favorability_low <- ngo_favorability_raw %>% 
-  filter(str_detect(value, "nfav") | value == "Neutral") %>% 
-  mutate(n = ifelse(value == "Neutral", n / 2, n),
-         n_plot = -n)
-
-ggplot(mapping = aes(x = n_plot, y = clean_name, fill = color)) +
-  geom_barh(data = ngo_favorability_high, stat = "identity") +
-  geom_barh(data = ngo_favorability_low, stat = "identity") +
-  geom_vline(xintercept = 0, color = "black") +
-  scale_x_continuous(labels = abs) +
-  scale_fill_identity(labels = levels(ngo_favorability_raw$value),
-                      breaks = levels(ngo_favorability_raw$color),
-                      guide = "legend", name = NULL) +
-  labs(x = NULL, y = NULL) +
-  theme_ngos() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major.y = element_blank())
-```
-
 ## Likelihood of donation
@@
   scale_x_continuous(sec.axis = sec_axis(~ . / sum(donate_summary$n),
-                                         labels = percent)) +
+                                         labels = percent_format(accuracy = 1))) +
   scale_fill_manual(values = ngo_cols("green", "blue", name = FALSE), guide = FALSE) +
@@
 
-# Interpreting interactions in models
-
-Ordinarily, people use ANOVA to analyze 3-way, 2 × 2 × 2 factorial designs, [like this](https://mypages.valdosta.edu/mwhatley/3600/2x2x2.htm).
-A more flexible ([yet identical!](https://www.theanalysisfactor.com/why-anova-and-linear-regression-are-the-same-analysis/)) way to do this is to use a regular regression model with interaction terms for each of the conditions, like so (here we use three, since we can use simper models to get averages for the larger umbrella groups, like just crackdowns and crackdown + issue):
-
-- Model 1:
-
-    $$
-    y = \beta_0 + \beta_1 \text{Crackdown}
-    $$
-
-- Model 2:
+```{r all-datasets-nested}
+all_models <- tribble(
+  ~title, ~df,
+  "Crackdown", results,
+  # Ha, cheat here by renaming the issue and funding columns to crackdown. 
+  # All other tests are based on the crackdown column except these two, so
+  # rather than build all sorts of convoluted arguments and functions, we just
+  # rename these as issue and funding
+  "Issue", mutate(results, crackdown = issue),
+  "Funding", mutate(results, crackdown = funding),
+  # Create all the nested conditions
+  "Human rights | Crackdown", filter(results, issue == "Human rights"),
+  "Humanitarian assistance | Crackdown", filter(results, issue != "Human rights"),
+  "Government | Crackdown", filter(results, funding == "Government"),
+  "Private | Crackdown", filter(results, funding == "Private"),
+  "Human rights | Government | Crackdown", filter(results, issue == "Human rights", funding == "Government"),
+  "Human rights | Private | Crackdown", filter(results, issue == "Human rights", funding == "Private"),
+  "Humanitarian assistance | Government | Crackdown", filter(results, issue != "Human rights", funding == "Government"),
+  "Humanitarian assistance | Private | Crackdown", filter(results, issue != "Human rights", funding == "Private")
+) 
+```
+
+# Treatment effects: Likelihood of donation
+
+This time around, we're not using interactionful regression models to calculate all these differences in groups.
+Instead we use real live Stan code to estimate the differences in group means and proportions!
+
+## Priors and models
+
+We estimate the proportion of people responding that they'd be likely to donate to the organization with a binomial distribution, with a prior $\theta$ distribution of $\text{Beta}(5, 5)$.
+We build the following model in Stan:
 
@@
 \begin{aligned}
-    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue } + \\
-    & \beta_3 \text{Crackdown} \times \text{Issue}
+n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{total in group}}, \theta_{\text{group}}) &\text{[likelihood]}\\
+\text{Difference} &= n_{\text{group 2}} - n_{\text{group 1}} &\text{[difference in proportions]} \\
+n &: \text{Number likely to donate} \\
+\\
+\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of being likely to donate]}
 \end{aligned}
@@
 
-- Model 3:
+```{r priors-likely, fig.width=2.75, fig.height=1.5, fig.align="center"}
+likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
+  geom_area(stat = "function", fun = dbeta, args = list(shape1 = 5, shape2 = 5), 
+            fill = "grey80", color = "black") +
+  labs(x = expression(Probability ~ of ~ being ~ likely ~ to ~ donate ~ (theta)), y = "Density") +
+  annotate(geom = "label", x = 0.5, y = 1, label = "Beta(5, 5)", size = pts(9)) +
+  theme_ngos(base_size = 9, density = TRUE)
+likely_theta
+```
+
+## Differences
+
+```{r run-likely-models, results="hide", cache=TRUE}
+# This takes forever because of C++ compiling and actual MCMC sampling, so this
+# chunk is cached
+
+# Compile model
+donate_likely <- stan_model(here("lib", "donate_likely.stan"))
+
+# Sample from the compiled model
+all_models_likely_run <- all_models %>% 
+  # Simplify data for sending to Stan
+  mutate(stan_data_counts = df %>% map(~ {
+    df_counts <- .x %>% 
+      count(crackdown, donate_likely_bin) %>% 
+      group_by(crackdown) %>% 
+      mutate(total = sum(n)) %>% 
+      filter(donate_likely_bin == "Likely")
+
+    return(list(
+      n_total_1 = df_counts$total[1],
+      n_total_2 = df_counts$total[2],
+      n_likely_1 = df_counts$n[1],
+      n_likely_2 = df_counts$n[2]
+    ))
+  })) %>% 
+  # Run the actual model on the simplified data
+  mutate(model = stan_data_counts %>% map(~ {
+    sampling(donate_likely, data = .x, control = list(max_treedepth = 15),
+             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+  }))
+
+# Extract stuff
+all_models_likely <- all_models_likely_run %>% 
+  # Extract posterior chains
+  mutate(posterior_chains_long = map(model, ~ {
+      .x %>% gather_draws(theta_1, theta_2, theta_diff, pct_change)
+  })) %>% 
+  mutate(posterior_chains_wide = map(model, ~ {
+      .x %>% spread_draws(theta_1, theta_2, theta_diff, pct_change)
+  })) %>% 
+  # Get HDI medians in tidy form
+  mutate(tidy = posterior_chains_long %>% map(~ {
+    .x %>% median_hdci() %>% to_broom_names()
+  }))
+```
+
+```{r plot-likely-diffs, warning=FALSE, fig.width=6, fig.height=8}
+tidied_diffs_likely <- all_models_likely %>% 
+  unnest(posterior_chains_long) %>% 
+  filter(.variable == "theta_diff") %>% 
+  mutate(category = case_when(
+    str_count(title, "\\|") == 0 ~ "Level 1",
+    str_count(title, "\\|") == 1 ~ "Level 2",
+    str_count(title, "\\|") == 2 ~ "Level 3"
+  )) %>% 
+  mutate(title = str_remove(title, " \\| Crackdown"))
+
+level1_likely <- tidied_diffs_likely %>% 
+  filter(category == "Level 1") %>%
+  mutate(title = recode(title, 
+                        Crackdown = "Crackdown −\nNo crackdown",
+                        Issue = "Humanitarian\nassistance −\nHuman rights",
+                        Funding = "Private −\nGovernment\nfunding")) %>% 
+  mutate(title = fct_inorder(title))
+
+plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
+  geom_halfeyeh(.width = c(0.8, 0.95)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
+  labs(x = "Median difference in donation likelihood", y = NULL, tag = "A") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+level2_likely <- tidied_diffs_likely %>% 
+  filter(category == "Level 2") %>%
+  mutate(condition = case_when(
+    title %in% c("Human rights", "Humanitarian assistance") ~ "Issue",
+    title %in% c("Government", "Private") ~ "Funding"
+  )) %>% 
+  mutate(facet_title = case_when(
+    title %in% c("Human rights", "Humanitarian assistance") ~ paste(title, "issues"),
+    title %in% c("Government", "Private") ~ paste(title, "funding")
+  )) %>% 
+  mutate(title = case_when(
+    title %in% c("Humanitarian assistance", "Private") ~ "",
+    TRUE ~ "Crackdown −\nNo crackdown")
+  )
+
+plot_diff_likely_b <- ggplot(filter(level2_likely, condition == "Issue"), 
+                             aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = NULL, y = NULL, tag = "B") +
+  facet_wrap(~ facet_title, scales = "free_y") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
+                             aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "Median difference in donation likelihood", y = NULL, tag = "C") +
+  facet_wrap(~ facet_title, scales = "free_y") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+level3_likely <- tidied_diffs_likely %>% 
+  filter(category == "Level 3") %>%
+  separate(title, c("issue", "funding"), sep = " \\| ") %>%
+  mutate(issue = paste(issue, "issues"),
+         funding = paste(funding, "funding")) %>% 
+  mutate(facet_title = paste0(issue, "\n", funding)) %>% 
+  mutate(title = case_when(
+    funding == "Private funding" ~ "",
+    TRUE ~ "Crackdown −\nNo crackdown")
+  )
+
+plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "Median difference in donation likelihood", y = NULL, tag = "D") +
+  facet_wrap(~ facet_title, scales = "free_y") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_diffs_likely_all <- plot_diff_likely_a / 
+  (plot_diff_likely_b / plot_diff_likely_c) / 
+  plot_diff_likely_d
+
+plot_diffs_likely_all
+
+plot_diffs_likely_all %T>% 
+  ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
+         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
+  ggsave(., filename = here("output", "figures", "likely-diffs.png"),
+         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
+```
+
+```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
+tbl_likely_tidy <- all_models_likely %>% 
+  unnest(tidy) %>% 
+  filter(term %in% c("theta_diff", "pct_change")) %>% 
+  select(title, term, estimate) %>% 
+  spread(term, estimate) %>% 
+  mutate(category = case_when(
+    str_count(title, "\\|") == 0 ~ "Level 1",
+    str_count(title, "\\|") == 1 ~ "Level 2",
+    str_count(title, "\\|") == 2 ~ "Level 3"
+  ))
+
+tbl_likely_probs <- all_models_likely %>% 
+  unnest(posterior_chains_long) %>% 
+  filter(.variable == "theta_diff") %>% 
+  group_by(title) %>% 
+  summarize(p.greater0 = mean(.value > 0),
+            p.less0 = mean(.value < 0),
+            p.diff.not0 = ifelse(median(.value) > 0, p.greater0, p.less0)) %>% 
+  ungroup()
+
+tbl_likely_tidy %>% 
+  left_join(tbl_likely_probs, by = "title") %>% 
+  filter(category == "Level 1") %>%
+  mutate(title = recode(title, 
+                        Crackdown = "Crackdown −\nNo crackdown",
+                        Issue = "Humanitarian\nassistance −\nHuman rights",
+                        Funding = "Private −\nGovernment\nfunding")) %>% 
+  mutate(title = fct_inorder(title)) %>% 
+  select(`Frame` = title, `∆` = theta_diff, `%∆` = pct_change,
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
+  cat() %>% 
+  cat(file = here("output", "tables", "tbl-likely-diffs-1.md"))
+```
+
+```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
+tbl_likely_tidy %>% 
+  left_join(tbl_likely_probs, by = "title") %>% 
+  filter(category == "Level 2") %>%
+  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
+  mutate(title_clean = case_when(
+    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
+    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
+  )) %>% 
+  mutate(title_clean = factor(title_clean, 
+                              levels = c("Human rights issues", 
+                                         "Humanitarian assistance issues", 
+                                         "Government funding", "Private funding"))) %>% 
+  arrange(title_clean) %>% 
+  select(Frame = title_clean, `∆` = theta_diff, `%∆` = pct_change,
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
+  cat() %>% 
+  cat(file = here("output", "tables", "tbl-likely-diffs-2.md"))
+```
+
+```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
+tbl_likely_tidy %>% 
+  left_join(tbl_likely_probs, by = "title") %>% 
+  filter(category == "Level 3") %>%
+  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
+  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
+  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
+         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
+  arrange(Issue, Funding) %>% 
+  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = theta_diff, `%∆` = pct_change,
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
+  cat() %>% 
+  cat(file = here("output", "tables", "tbl-likely-diffs-3.md"))
+```
+
+\
+
+# Treatment effects: Amount donated
+
+## Priors and models
+
+Following [John Kruschke's "Bayesian Estimation Supersedes the t-test (BEST)" procedure](http://www.indiana.edu/~kruschke/BEST/BEST.pdf), we estimate means for each group with a t-distribution.
+We use the following priors for the distribution parameters:
 
@@
 \begin{aligned}
-    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue} + \beta_3 \text{Funding } + \\
-    & \beta_4 \text{Crackdown} \times \text{Issue } + \\
-    & \beta_5 \text{Crackdown} \times \text{Funding } + \\
-    & \beta_6 \text{Issue} \times \text{Funding } + \\
-    & \beta_7 \text{Crackdown} \times \text{Issue} \times \text{Funding}
+x_{\text{group 1, group 2}} &\sim \text{Student } t(\nu, \mu, \sigma) &\text{[likelihood]}\\
+\text{Difference} &= x_{\text{group 2}} - x_{\text{group 1}} &\text{[difference in means]} \\
+x &: \text{Mean amount donated} \\
+\\
+\nu &\sim \text{Exponential}(1 / 29) &\text{[prior normality]} \\
+\mu_{\text{group 1, group 2}} &\sim \mathcal{N}(\bar{x}_{\text{group 1, group 2}}, 10) &\text{[prior donation mean per group]}\\
+\sigma_{\text{group 1, group 2}} &\sim \text{Cauchy}(0, 1)&\text{[prior donation sd per group]}
 \end{aligned}
@@
 
-Adding different combinations of the coefficients provides the average values for each combination of factors, which corresponds to the average likelihood and amount donated table above.
-
-```{r interaction-interpretation, results="asis"}
-model1 <- "1"
-model2 <- "2"
-model3 <- "3"
-
-interpretation <- tribble(
-  ~Model, ~`Coefficients to add together`,
-  model3, "Intercept",
-  model3, "Intercept + Funding",
-  model2, "Intercept",
-  model3, "Intercept + Issue",
-  model3, "Intercept + Issue + Funding + (Issue × Funding)",
-  model2, "Intercept + Issue",
-  model1, "Intercept",
-  model3, "Intercept + Crackdown",
-  model3, "Intercept + Crackdown + Funding + (Crackdown × Funding)",
-  model2, "Intercept + Crackdown",
-  model3, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
-  model3, "Intercept + Crackdown + Issue + Funding + (Crackdown × Issue) + (Crackdown × Funding) + (Issue × Funding) + (Crackdown × Issue × Funding)",
-  model2, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
-  model1, "Intercept + Crackdown"
+```{r priors-amounts, fig.width=8, fig.height=1.5}
+amount_nu <- ggplot(data = tibble(x = c(0, 200)), aes(x = x)) +
+  geom_area(stat = "function", fun = dexp, args = list(rate = 1/29), 
+            fill = "grey80", color = "black") +
+  labs(x = expression(Normality ~ parameter ~ (nu)), y = "Density") +
+  annotate(geom = "label", x = 100, y = 0.009, 
+           label = "Exponential(1/29)", size = pts(9)) +
+  theme_ngos(base_size = 9, density = TRUE)
+
+amount_mu <- ggplot(data = tibble(x = c(0, 100)), aes(x = x)) +
+  geom_area(stat = "function", fun = dnorm, args = list(mean = 50, sd = 10),
+            fill = "grey80", color = "black") +
+  scale_x_continuous(breaks = c(seq(0, 100, 25)),
+                     labels = c("−$50", "−$25", "Group average", "+$25", "+$50")) +
+  annotate(geom = "label", x = 50, y = 0.01, label = "N(bar(x), 10)", 
+           parse = TRUE, size = pts(9)) +
+  labs(x = expression(Average ~ donated ~ (mu)), y = NULL) +
+  theme_ngos(base_size = 9, density = TRUE)
+
+amount_sigma <- ggplot(data = tibble(x = c(0, 10)), aes(x = x)) +
+  geom_area(stat = "function", fun = dcauchy, args = list(location = 0, scale = 1),
+            fill = "grey80", color = "black") +
+  scale_x_continuous(labels = dollar) +
+  annotate(geom = "label", x = 5, y = 0.08, label = "Cauchy(0, 1)", size = pts(9)) +
+  labs(x = expression(SD ~ donated ~ (sigma)), y = NULL) +
+  theme_ngos(base_size = 9, density = TRUE)
+
+amount_nu + amount_mu + amount_sigma
+```
+
+## Differences
+
+```{r run-amount-models, results="hide", cache=TRUE}
+# This takes forever because of C++ compiling and actual MCMC sampling, so this
+# chunk is cached
+
+# Compile model
+amount_donated_best <- stan_model(here("lib", "amount_donated_best.stan"))
+
+# Sample from the compiled model
+all_models_amount_run <- all_models %>% 
+  # Simplify data for sending to Stan
+  mutate(stan_data = df %>% map(~ {
+    select(.x, amount = amount_donate, group = crackdown)
+  })) %>% 
+  # Run the actual model on the simplified data
+  mutate(model = stan_data %>% map(~ {
+    sampling(amount_donated_best, data = compose_data(.x),
+             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+  }))
+
+# Extract stuff
+all_models_amount <- all_models_amount_run %>% 
+  # Extract posterior chains
+  mutate(posterior_chains_long = map2(model, stan_data, ~ {
+    .x %>% 
+      recover_types(.y) %>% 
+      gather_draws(mu[group], sigma[group], mu_diff, pct_change, cohen_d, cles, nu, log10nu)
+  })) %>% 
+  mutate(posterior_chains_wide = map2(model, stan_data, ~ {
+    .x %>% 
+      recover_types(.y) %>% 
+      spread_draws(mu[group], sigma[group], mu_diff, pct_change, cohen_d, cles, nu, log10nu)
+  })) %>% 
+  # Get HDI medians in tidy form
+  mutate(tidy = posterior_chains_long %>% map(~ {
+    .x %>% median_hdci() %>% to_broom_names()
+  }))
+```
+
+```{r plot-amount-diffs, warning=FALSE, fig.width=6, fig.height=8}
+# This will generate a warning because unnest() puts the crackdown values into
+# one column and we cheated by renaming issue and funding as crackdown, so it
+# gets mad when combining the factors in crackdown with those in issue and
+# funding. But because we only care about the diffs, we don't actually need the
+# category labels here, so it's all good.
+tidied_diffs_amount <- all_models_amount %>% 
+  unnest(posterior_chains_long) %>% 
+  filter(.variable == "mu_diff") %>% 
+  mutate(category = case_when(
+    str_count(title, "\\|") == 0 ~ "Level 1",
+    str_count(title, "\\|") == 1 ~ "Level 2",
+    str_count(title, "\\|") == 2 ~ "Level 3"
+  )) %>% 
+  mutate(title = str_remove(title, " \\| Crackdown"))
+
+level1_amount <- tidied_diffs_amount %>% 
+  filter(category == "Level 1") %>%
+  mutate(title = recode(title, 
+                        Crackdown = "Crackdown −\nNo crackdown",
+                        Issue = "Humanitarian\nassistance −\nHuman rights",
+                        Funding = "Private −\nGovernment\nfunding")) %>% 
+  mutate(title = fct_inorder(title))
+
+plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
+  geom_vline(xintercept = 0) +
+  geom_halfeyeh(.width = c(0.8, 0.95)) +
+  scale_x_continuous(labels = dollar) +
+  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
+  labs(x = "Median difference in amount donated", y = NULL, tag = "A") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+level2_amount <- tidied_diffs_amount %>% 
+  filter(category == "Level 2") %>%
+  mutate(condition = case_when(
+    title %in% c("Human rights", "Humanitarian assistance") ~ "Issue",
+    title %in% c("Government", "Private") ~ "Funding"
+  )) %>% 
+  mutate(facet_title = case_when(
+    title %in% c("Human rights", "Humanitarian assistance") ~ paste(title, "issues"),
+    title %in% c("Government", "Private") ~ paste(title, "funding")
+  )) %>% 
+  mutate(title = case_when(
+    title %in% c("Humanitarian assistance", "Private") ~ "",
+    TRUE ~ "Crackdown −\nNo crackdown")
   )
 
-conditions_summary_clean %>% 
-  select(1:3) %>% 
-  slice(-n()) %>% 
-  bind_cols(interpretation) %T>% 
-  pandoc.table() %>% 
-  pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
-  cat(file = here("output", "tables", "tbl-coefficients-to-add.md"))
+plot_diff_amount_b <- ggplot(filter(level2_amount, condition == "Issue"), 
+                             aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = dollar) +
+  labs(x = NULL, y = NULL, tag = "B") +
+  facet_wrap(~ facet_title, scales = "free_y") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
+                             aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = dollar) +
+  labs(x = "Median difference in amount donated", y = NULL, tag = "C") +
+  facet_wrap(~ facet_title, scales = "free_y") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+level3_amount <- tidied_diffs_amount %>% 
+  filter(category == "Level 3") %>%
+  separate(title, c("issue", "funding"), sep = " \\| ") %>%
+  mutate(issue = paste(issue, "issues"),
+         funding = paste(funding, "funding")) %>% 
+  mutate(facet_title = paste0(issue, "\n", funding)) %>% 
+  mutate(title = case_when(
+    funding == "Private funding" ~ "",
+    TRUE ~ "Crackdown −\nNo crackdown")
+  )
+
+plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
+  geom_vline(xintercept = 0) +
+  scale_x_continuous(labels = dollar) +
+  labs(x = "Median difference in amount donated", y = NULL, tag = "D",
+       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
+  facet_wrap(~ facet_title, scales = "free_y") +
+  theme_ngos() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_diffs_amounts_all <- plot_diff_amount_a / 
+  (plot_diff_amount_b / plot_diff_amount_c) / 
+  plot_diff_amount_d
+
+plot_diffs_amounts_all
+
+plot_diffs_amounts_all %T>% 
+  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
+         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
+  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
+         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
+```
+
+```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
+tbl_amounts_tidy <- all_models_amount %>% 
+  unnest(tidy) %>% 
+  filter(term %in% c("mu_diff", "pct_change")) %>% 
+  select(title, term, estimate) %>% 
+  spread(term, estimate) %>% 
+  mutate(category = case_when(
+    str_count(title, "\\|") == 0 ~ "Level 1",
+    str_count(title, "\\|") == 1 ~ "Level 2",
+    str_count(title, "\\|") == 2 ~ "Level 3"
+  ))
+
+tbl_amounts_probs <- all_models_amount %>% 
+  unnest(posterior_chains_long) %>% 
+  filter(.variable == "mu_diff") %>% 
+  group_by(title) %>% 
+  summarize(p.greater0 = mean(.value > 0),
+            p.less0 = mean(.value < 0),
+            p.diff.not0 = ifelse(median(.value) > 0, p.greater0, p.less0)) %>% 
+  ungroup()
+
+tbl_amounts_tidy %>% 
+  left_join(tbl_amounts_probs, by = "title") %>% 
+  filter(category == "Level 1") %>%
+  mutate(title = recode(title, 
+                        Crackdown = "Crackdown −\nNo crackdown",
+                        Issue = "Humanitarian\nassistance −\nHuman rights",
+                        Funding = "Private −\nGovernment\nfunding")) %>% 
+  mutate(title = fct_inorder(title)) %>% 
+  select(`Frame` = title, `∆` = mu_diff, `%∆` = pct_change,
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(caption = 'Difference between amount donated across single conditions; values represent posterior medians {#tbl:amount-diffs-1}') %T>%
+  cat() %>% 
+  cat(file = here("output", "tables", "tbl-amount-diffs-1.md"))
+```
+
+```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
+tbl_amounts_tidy %>% 
+  left_join(tbl_amounts_probs, by = "title") %>% 
+  filter(category == "Level 2") %>%
+  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
+  mutate(title_clean = case_when(
+    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
+    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
+  )) %>% 
+  mutate(title_clean = factor(title_clean, 
+                              levels = c("Human rights issues", 
+                                         "Humanitarian assistance issues", 
+                                         "Government funding", "Private funding"))) %>% 
+  arrange(title_clean) %>% 
+  select(Frame = title_clean, `∆` = mu_diff, `%∆` = pct_change,
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-2}') %T>%
+  cat() %>% 
+  cat(file = here("output", "tables", "tbl-amount-diffs-2.md"))
+```
+
+```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
+tbl_amounts_tidy %>% 
+  left_join(tbl_amounts_probs, by = "title") %>% 
+  filter(category == "Level 3") %>%
+  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
+  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
+  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
+         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
+  arrange(Issue, Funding) %>% 
+  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = mu_diff, `%∆` = pct_change,
+         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-3}') %T>%
+  cat() %>% 
+  cat(file = here("output", "tables", "tbl-amount-diffs-3.md"))
+```
+
+## Effect size
+
+```{r amount-effect-size, warning=FALSE}
+# Effect size
+# (μ₁ - μ₂) / sqrt( (σ₁² + σ₂²) / 2)
+tidied_eff_size_amount <- all_models_amount %>% 
+  unnest(posterior_chains_long) %>% 
+  filter(.variable == "cohen_d") %>% 
+  mutate(category = case_when(
+    str_count(title, "\\|") == 0 ~ "Level 1",
+    str_count(title, "\\|") == 1 ~ "Level 2",
+    str_count(title, "\\|") == 2 ~ "Level 3"
+  )) %>% 
+  mutate(title = str_remove(title, " \\| Crackdown")) %>% 
+  mutate(title = fct_inorder(title))
+
+effect_sizes <- tribble(
+  ~size, ~x_end,
+  "Small", 0.2,
+  "Medium", 0.5,
+  "Large", 0.8
+) %>% 
+  mutate(x_start = -x_end)
+
+ggplot(tidied_eff_size_amount, aes(x = .value, y = fct_rev(title))) +
+  geom_halfeyeh(.width = c(0.8, 0.95)) +
+  geom_vline(xintercept = 0, size = 1) +
+  geom_vline(xintercept = c(0.2, -0.2), linetype = "dotted", size = 0.5) +
+  geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
+  geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
+  coord_cartesian(xlim = c(-0.6, 0.6)) +
+  labs(x = "Cohen's d (effect size)", y = NULL) +
+  theme_ngos()
 ```
@@
 \
-
-# Amount donated
-
-## Models
-
-```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
-# Basic interaction models
-m_amount_c <- stan_glm(amount_donate ~ crackdown,
-                       data = results, family = gaussian(),
-                       prior = cauchy(location = 0, scale = 2.5),
-                       prior_intercept = cauchy(location = 0, scale = 10),
-                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
-
-m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)
-
-m_amount_cif <- update(m_amount_c, . ~ . + 
-                         issue + funding + crackdown * issue + crackdown * funding + 
-                         issue * funding + crackdown * issue * funding)
-
-# Models with just issue and just funding
-m_amount_i <- update(m_amount_c, . ~ issue)
-m_amount_f <- update(m_amount_c, . ~ funding)
-```
-
-```{r tbl-models-amount, warning=FALSE, results="asis"}
-# Get subset of coefficients
-coefs_to_include <- list(m_amount_c, m_amount_ci, m_amount_cif) %>% 
-  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)
-
-huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
-       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
-       statistics = model_stats_bayes,
-       stars = NULL) %T>% 
-  print_hux() %>% 
-  to_md(max_width = 100) %>% 
-  cat(file = here("output", "tables", "tbl-models-amount.md"))
-```
-
-## Predicted medians
-
-The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution (like, [they didn't even want to invent it, and then when they did they wanted to hide it](https://github.com/stan-dev/rstanarm/issues/85), and it has a big warning in the documentation).
-But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates.
-If I use the full force of `posterior_predict()`, I add more uncertainty with each added coefficient (so in a 2×2×2 version, the 8th condition is actually the sum of all 8 coefficients, which means it gets 8 levels of uncertainity, which is probably excessive).
-But we do it both ways too, just to be on the safe side.
-
-```{r amount-median-c}
-newdata_conditions_c <- results %>% expand(nesting(crackdown))
-
-chains_fitted_c <- posterior_linpred(m_amount_c, 
-                                     newdata = newdata_conditions_c)
-
-# posterior_fit <- posterior_predict(m_amount_c, 
-#                                    newdata = newdata_conditions_c,
-#                                    draws = 50, seed = BAYES_SEED)
-
-coef_summary_c <- newdata_conditions_c %>% 
-  bind_cols(tidyMCMC(chains_fitted_c, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-# newdata <- newdata_conditions %>% 
-#   bind_cols(tidyMCMC(posterior_fit, estimate.method = "median",
-#                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_amount_c <- ggplot(coef_summary_c, aes(y = estimate, x = crackdown)) + 
-  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
-  #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
-  scale_y_continuous(labels = dollar) +
-  labs(x = NULL, y = "Median amount donated") +
-  # coord_cartesian(ylim = c(0, 100)) +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-```{r amount-median-i}
-newdata_conditions_i <- results %>% expand(nesting(issue))
-
-chains_fitted_i <- posterior_linpred(m_amount_i, 
-                                     newdata = newdata_conditions_i)
-
-coef_summary_i <- newdata_conditions_i %>% 
-  bind_cols(tidyMCMC(chains_fitted_i, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-```
-
-```{r amount-median-f}
-newdata_conditions_f <- results %>% expand(nesting(funding))
-
-chains_fitted_f <- posterior_linpred(m_amount_f, 
-                                     newdata = newdata_conditions_f)
-
-coef_summary_f <- newdata_conditions_f %>% 
-  bind_cols(tidyMCMC(chains_fitted_f, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-```
-
-```{r amount-median-ci}
-newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))
-
-chains_fitted_ci <- posterior_linpred(m_amount_ci, 
-                                      newdata = newdata_conditions_ci)
-
-coef_summary_ci <- newdata_conditions_ci %>% 
-  bind_cols(tidyMCMC(chains_fitted_ci, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_amount_ci <- ggplot(coef_summary_ci, aes(y = estimate, x = crackdown)) + 
-  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
-  #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
-  scale_y_continuous(labels = dollar) +
-  labs(x = NULL, y = "Median amount donated") +
-  # coord_cartesian(ylim = c(0, 100)) +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank(),
-        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
-  facet_wrap(~ issue)
-```
-
-```{r amount-median-cif}
-newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))
-
-chains_fitted_cif <- posterior_linpred(m_amount_cif, 
-                                       newdata = newdata_conditions_cif)
-
-coef_summary_cif <- newdata_conditions_cif %>% 
-  bind_cols(tidyMCMC(chains_fitted_cif, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_amount_cif <- ggplot(coef_summary_cif, aes(y = estimate, x = crackdown)) + 
-  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
-  #            color = "grey50", size = 0.5, alpha = 0.5) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
-  scale_y_continuous(labels = dollar) +
-  labs(x = NULL, y = "Median amount donated") +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank(),
-        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
-  facet_wrap(~ issue + funding)
-```
-
-```{r plot-single-amount-medians, warning=FALSE, fig.width=7, fig.height=2.5}
-coef_summary_singles <- bind_rows(coef_summary_c, coef_summary_i, coef_summary_f) %>% 
-  gather(condition, value, crackdown, issue, funding) %>% 
-  filter(!is.na(value)) %>% 
-  mutate(value = fct_inorder(value, ordered = TRUE),
-         condition = fct_inorder(str_to_title(condition), ordered = TRUE))
-
-plot_amount_singles <- ggplot(coef_summary_singles, aes(y = estimate, x = value)) + 
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = condition)) +
-  scale_y_continuous(labels = dollar) +
-  scale_color_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
-  labs(x = NULL, y = "Median amount donated") +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank(),
-        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
-  facet_wrap(~ condition, scales = "free_x")
-
-plot_amount_singles %T>%
-  print() %T>%
-  ggsave(., filename = here("output", "figures", "amount_single_summary.pdf"),
-         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "amount_single_summary.png"),
-         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
-```
-
-```{r plot-all-amount-medians, fig.width=8, fig.height=6}
-plot_amount_all <- 
-  (plot_amount_c / plot_amount_ci) | 
-  plot_amount_cif
-
-plot_amount_all +
-  plot_annotation(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
-                  subtitle = "90% credible intervals shown around each point",
-                  tag_levels = "A", theme = theme_ngos())
-
-(plot_amount_all + 
-    plot_annotation(caption = "90% credible intervals shown around each point",
-                    tag_levels = "A", theme = theme_ngos())) %T>% 
-  ggsave(., filename = here("output", "figures", "amount-medians.pdf"),
-         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "amount-medians.png"),
-         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
-```
-
-## Differences in medians
-
-```{r amount-diffs-c}
-diffs_coef_pairs_c <- chains_fitted_c %>% 
-  as_data_frame() %>% 
-  magrittr::set_colnames(levels(newdata_conditions_c$crackdown)) %>% 
-  mcmc_pairwise_diffs()
-
-diffs_coef_pairs_detail_c <- tidy_diffs(diffs_coef_pairs_c)
-
-pairs_plot_data_c <- diffs_coef_pairs_c$mcmc_diffs %>%
-  gather(pair, value) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-
-plot_diffs_c <- ggplot() + 
-  geom_density(data = pairs_plot_data_c, aes(x = value),
-               fill = ngo_cols("green"), colour = NA, alpha = 0.4) + 
-  geom_segment(data = diffs_coef_pairs_detail_c, 
-               aes(x = q5, xend = q95, y = 0, yend = 0),
-               size = 3) +
-  geom_vline(data = diffs_coef_pairs_detail_c, aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  guides(fill = FALSE, color = FALSE) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ pair)
-```
-
-```{r amount-diffs-i}
-diffs_coef_pairs_i <- chains_fitted_i %>% 
-  as_data_frame() %>% 
-  magrittr::set_colnames(levels(newdata_conditions_i$issue)) %>% 
-  mcmc_pairwise_diffs()
-
-diffs_coef_pairs_detail_i <- tidy_diffs(diffs_coef_pairs_i)
-
-pairs_plot_data_i <- diffs_coef_pairs_i$mcmc_diffs %>%
-  gather(pair, value) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-```
-
-```{r amount-diffs-f}
-diffs_coef_pairs_f <- chains_fitted_f %>% 
-  as_data_frame() %>% 
-  magrittr::set_colnames(levels(newdata_conditions_f$funding)) %>% 
-  mcmc_pairwise_diffs()
-
-diffs_coef_pairs_detail_f <- tidy_diffs(diffs_coef_pairs_f)
-
-pairs_plot_data_f <- diffs_coef_pairs_f$mcmc_diffs %>%
-  gather(pair, value) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-```
-
-```{r amount-diffs-ci}
-# Nest each fitted chain into a single row that corresponds to each newdata_condition
-chains_nested_ci <- chains_fitted_ci %>% 
-  as_data_frame() %>% 
-  mutate(id = 1:n()) %>% 
-  gather(condition, value, -id) %>% 
-  group_by(condition) %>% 
-  nest()
-
-# Add the fitted chains to the conditions, spread the main crackdown condition
-# into two columns, then nest everything by issue
-all_chains_ci <- bind_cols(newdata_conditions_ci, chains_nested_ci) %>% 
-  unnest(data) %>% 
-  select(-condition) %>% 
-  group_by(issue) %>% 
-  spread(crackdown, value) %>% 
-  select(-id) %>% 
-  nest()
-
-# All the pairwise differences in a single data frame, grouped by issue
-pairs_conditions_ci <- all_chains_ci %>% 
-  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
-         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
-         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))
-
-# Extract coefficient details and plot data
-diffs_coef_pairs_detail_ci <- pairs_conditions_ci %>% 
-  unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs, -diffs_coefs) #%>% 
-  #mutate(pair = "Hey")
-
-pairs_plot_data_ci <- pairs_conditions_ci %>% 
-  select(issue, diffs_coefs) %>% 
-  unnest(diffs_coefs) %>%
-  gather(pair, value, -issue) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-
-plot_diffs_ci <- ggplot() + 
-  geom_density(data = pairs_plot_data_ci, aes(x = value),
-               fill = ngo_cols("blue"), colour = NA, alpha = 0.4) + 
-  geom_segment(data = diffs_coef_pairs_detail_ci,
-               aes(x = q5, xend = q95, y = 0, yend = 0),
-               size = 3) +
-  geom_vline(data = diffs_coef_pairs_detail_ci, aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  guides(fill = FALSE, color = FALSE) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ issue + pair)
-```
-
-```{r amount-diffs-cif}
-# Nest each fitted chain into a single row that corresponds to each newdata_condition
-chains_nested_cif <- chains_fitted_cif %>% 
-  as_data_frame() %>% 
-  mutate(id = 1:n()) %>% 
-  gather(condition, value, -id) %>% 
-  group_by(condition) %>% 
-  nest()
-
-# Add the fitted chains to the conditions, spread the main crackdown condition
-# into two columns, then nest everything by issue
-all_chains_cif <- bind_cols(newdata_conditions_cif, chains_nested_cif) %>% 
-  unnest(data) %>% 
-  select(-condition) %>% 
-  group_by(issue, funding) %>% 
-  spread(crackdown, value) %>% 
-  select(-id) %>% 
-  nest()
-
-# All the pairwise differences in a single data frame, grouped by issue
-pairs_conditions_cif <- all_chains_cif %>% 
-  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
-         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
-         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))
-
-# Extract coefficient details and plot data
-diffs_coef_pairs_detail_cif <- pairs_conditions_cif %>% 
-  unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs, -diffs_coefs)
-
-pairs_plot_data_cif <- pairs_conditions_cif %>% 
-  select(issue, funding, diffs_coefs) %>% 
-  unnest(diffs_coefs) %>%
-  gather(pair, value, -issue, -funding) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-
-plot_diffs_cif <- ggplot() + 
-  geom_density(data = pairs_plot_data_cif, aes(x = value),
-               fill = ngo_cols("red"), colour = NA, alpha = 0.4) + 
-  geom_segment(data = diffs_coef_pairs_detail_cif, 
-               aes(x = q5, xend = q95, y = 0, yend = 0),
-               size = 3) +
-  geom_vline(data = diffs_coef_pairs_detail_cif, aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  guides(fill = FALSE, color = FALSE) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ issue + funding + pair)
-```
-
-**Compare only individual conditions:**
-
-```{r plot-single-amount-diffs, fig.width=7, fig.height=2.5}
-diffs_plot_data_singles <- bind_rows(pairs_plot_data_c,
-                                     pairs_plot_data_i,
-                                     pairs_plot_data_f) %>% 
-  mutate(pair = fct_inorder(pair, ordered = TRUE))
-
-diffs_coef_pairs_detail_singles <- bind_rows(diffs_coef_pairs_detail_c,
-                                             diffs_coef_pairs_detail_i,
-                                             diffs_coef_pairs_detail_f) %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair),
-         pair = fct_inorder(pair, ordered = TRUE))
-
-plot_diffs_singles <- ggplot() +
-  geom_density(data = diffs_plot_data_singles, 
-               aes(x = value, fill = pair),
-               colour = NA, alpha = 0.4) +
-  geom_segment(data = diffs_coef_pairs_detail_singles, 
-               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
-               size = 3) +
-  geom_vline(data = diffs_coef_pairs_detail_singles, 
-             aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  scale_x_continuous(labels = dollar) +
-  scale_fill_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ pair)
-
-plot_diffs_singles %T>%
-  print() %T>% 
-  ggsave(., filename = here("output", "figures", "amount-singles-diffs.pdf"),
-         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "amount-singles-diffs.png"),
-         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
-```
-
-```{r tbl-single-amount-diffs, results="asis"}
-bind_rows(diffs_coef_pairs_detail_c,
-          diffs_coef_pairs_detail_i,
-          diffs_coef_pairs_detail_f) %>% 
-  select(`Frame` = pair, `∆~median~` = median, 
-         `% change~median~` = median_pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(missing = "—", 
-                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-amount-single-diffs.md"))
-```
-
-\
-
-**Compare nested conditions (what we're really most concerned about):**
-
-```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
-plot_diffs_all <- 
-  (plot_diffs_c / plot_diffs_ci) | 
-  plot_diffs_cif
-
-plot_diffs_all +
-  plot_annotation(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
-                  subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
-                  tag_levels = "A", theme = theme_ngos())
-
-(plot_diffs_all +
-  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
-                  tag_levels = "A", theme = theme_ngos())) %T>%
-  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
-         width = 8, height = 5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
-         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
-```
-
-```{r tbl-all-amount-diffs, results="asis"}
-bind_rows(diffs_coef_pairs_detail_c,
-          diffs_coef_pairs_detail_ci,
-          diffs_coef_pairs_detail_cif) %>% 
-  select(Issue = issue, Funding = funding, 
-         `Crackdown - No crackdown~median~` = median, 
-         `% change~median~` = median_pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(missing = "—", 
-                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
-```
-
-\
-
-# Likelihood of donation
-
-## Models
-
-```{r build-models-likely, warning=FALSE, message=FALSE, cache=TRUE}
-# Basic interaction models
-# Weakly informative student t priors, since these coefficients are log-odds
-# See https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations#prior-for-the-regression-coefficients-in-logistic-regression-non-sparse-case and https://arxiv.org/abs/1507.07170
-m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
-                       data = results, family = binomial(link = "logit"),
-                       prior = student_t(3, 0, 2.5),
-                       prior_intercept = student_t(3, 0, 10),
-                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
-
-m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)
-
-m_likely_cif <- update(m_likely_c, . ~ . + 
-                         issue + funding + crackdown * issue + crackdown * funding + 
-                         issue * funding + crackdown * issue * funding)
-
-# Models with just issue and just funding
-m_likely_i <- update(m_likely_c, . ~ issue)
-m_likely_f <- update(m_likely_c, . ~ funding)
-```
-
-```{r tbl-models-likely, warning=FALSE, results="asis"}
-# Get subset of coefficients
-coefs_to_include <- list(m_likely_c, m_likely_ci, m_likely_cif) %>% 
-  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)
-
-huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
-       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
-       statistics = model_stats_bayes,
-       stars = NULL) %T>% 
-  print_hux() %>% 
-  to_md(max_width = 100) %>% 
-  cat(file = here("output", "tables", "tbl-models-likelihood.md"))
-```
-
-## Predicted medians
-
-```{r likely-median-c}
-newdata_conditions_c <- results %>% expand(nesting(crackdown))
-
-# transform = TRUE does the same thing as plogis(as.matrix(m_likely_c))
-chains_fitted_likely_c <- posterior_linpred(m_likely_c, 
-                                            newdata = newdata_conditions_c, 
-                                            transform = TRUE)
-
-coef_summary_likely_c <- newdata_conditions_c %>% 
-  bind_cols(tidyMCMC(chains_fitted_likely_c, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_likely_c <- ggplot(coef_summary_likely_c, aes(y = estimate, x = crackdown)) + 
-  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
-  #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
-  scale_y_continuous(labels = percent) +
-  labs(x = NULL, y = "Probability of donating") +
-  # coord_cartesian(ylim = c(0, 100)) +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-```{r likely-median-i}
-newdata_conditions_i <- results %>% expand(nesting(issue))
-
-chains_fitted_likely_i <- posterior_linpred(m_likely_i, 
-                                            newdata = newdata_conditions_i, 
-                                            transform = TRUE)
-
-coef_summary_likely_i <- newdata_conditions_i %>% 
-  bind_cols(tidyMCMC(chains_fitted_likely_i, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_likely_i <- ggplot(coef_summary_likely_i, aes(y = estimate, x = issue)) + 
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
-  scale_y_continuous(labels = percent) +
-  labs(x = NULL, y = "Probability of donating") +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-```{r likely-median-f}
-newdata_conditions_f <- results %>% expand(nesting(funding))
-
-chains_fitted_likely_f <- posterior_linpred(m_likely_f, 
-                                            newdata = newdata_conditions_f, 
-                                            transform = TRUE)
-
-coef_summary_likely_f <- newdata_conditions_f %>% 
-  bind_cols(tidyMCMC(chains_fitted_likely_f, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_likely_f <- ggplot(coef_summary_likely_f, aes(y = estimate, x = funding)) + 
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("green")) + 
-  scale_y_continuous(labels = percent) +
-  labs(x = NULL, y = "Probability of donating") +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-```{r likely-median-ci}
-newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))
-
-chains_fitted_likely_ci <- posterior_linpred(m_likely_ci, 
-                                             newdata = newdata_conditions_ci,
-                                             transform = TRUE)
-
-coef_summary_likely_ci <- newdata_conditions_ci %>% 
-  bind_cols(tidyMCMC(chains_fitted_likely_ci, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_likely_ci <- ggplot(coef_summary_likely_ci, aes(y = estimate, x = crackdown)) + 
-  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
-  #            color = "grey50", size = 0.5, alpha = 0.25) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("blue")) + 
-  scale_y_continuous(labels = percent) +
-  labs(x = NULL, y = "Probability of donating") +
-  # coord_cartesian(ylim = c(0, 100)) +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank(),
-        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
-  facet_wrap(~ issue)
-```
-
-```{r likely-median-cif}
-newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))
-
-chains_fitted_likely_cif <- posterior_linpred(m_likely_cif, 
-                                              newdata = newdata_conditions_cif,
-                                              transform = TRUE)
-
-coef_summary_likely_cif <- newdata_conditions_cif %>% 
-  bind_cols(tidyMCMC(chains_fitted_likely_cif, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
-
-plot_likely_cif <- ggplot(coef_summary_likely_cif, aes(y = estimate, x = crackdown)) + 
-  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
-  #            color = "grey50", size = 0.5, alpha = 0.5) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_cols("red")) +
-  scale_y_continuous(labels = percent) +
-  labs(x = NULL, y = "Probability of donating") +
-  theme_ngos() +
-  theme(panel.grid.major.x = element_blank(),
-        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
-  facet_wrap(~ issue + funding)
-```
-
-```{r plot-all-likely-medians, fig.width=8, fig.height=6}
-plot_likely_all <- 
-  (plot_likely_c / plot_likely_ci) | 
-  plot_likely_cif
-
-plot_likely_all +
-  plot_annotation(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
-                  subtitle = "90% credible intervals shown around each point",
-                  tag_levels = "A", theme = theme_ngos())
-
-(plot_likely_all +
-  plot_annotation(caption = "90% credible intervals shown around each point",
-                  tag_levels = "A", theme = theme_ngos())) %T>% 
-  ggsave(., filename = here("output", "figures", "likelihood-medians.pdf"),
-         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "likelihood-medians.png"),
-         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
-```
-
-## Differences in medians
-
-```{r likely-diffs-c}
-diffs_coef_likely_pairs_c <- chains_fitted_likely_c %>% 
-  as_data_frame() %>% 
-  magrittr::set_colnames(levels(newdata_conditions_c$crackdown)) %>% 
-  mcmc_pairwise_diffs()
-
-diffs_coef_likely_pairs_detail_c <- tidy_diffs(diffs_coef_likely_pairs_c)
-
-pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c$mcmc_diffs %>%
-  gather(pair, value) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-
-plot_diffs_likely_c <- ggplot() + 
-  geom_density(data = pairs_likely_plot_data_c, aes(x = value),
-               fill = ngo_cols("green"), colour = NA, alpha = 0.4) + 
-  geom_segment(data = diffs_coef_likely_pairs_detail_c, 
-               aes(x = q5, xend = q95, y = 0, yend = 0),
-               size = 3) +
-  geom_vline(data = diffs_coef_likely_pairs_detail_c, 
-             aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  guides(fill = FALSE, color = FALSE) +
-  scale_x_continuous(labels = percent) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ pair)
-```
-
-```{r likely-diffs-i}
-diffs_coef_likely_pairs_i <- chains_fitted_likely_i %>% 
-  as_data_frame() %>% 
-  magrittr::set_colnames(levels(newdata_conditions_i$issue)) %>% 
-  mcmc_pairwise_diffs()
-
-diffs_coef_likely_pairs_detail_i <- tidy_diffs(diffs_coef_likely_pairs_i)
-
-pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i$mcmc_diffs %>%
-  gather(pair, value) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-```
-
-```{r likely-diffs-f}
-diffs_coef_likely_pairs_f <- chains_fitted_likely_f %>% 
-  as_data_frame() %>% 
-  magrittr::set_colnames(levels(newdata_conditions_f$funding)) %>% 
-  mcmc_pairwise_diffs()
-
-diffs_coef_likely_pairs_detail_f <- tidy_diffs(diffs_coef_likely_pairs_f)
-
-pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f$mcmc_diffs %>%
-  gather(pair, value) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-```
-
-```{r likely-diffs-ci}
-# Nest each fitted chain into a single row that corresponds to each newdata_condition
-chains_nested_likely_ci <- chains_fitted_likely_ci %>% 
-  as_data_frame() %>% 
-  mutate(id = 1:n()) %>% 
-  gather(condition, value, -id) %>% 
-  group_by(condition) %>% 
-  nest()
-
-# Add the fitted chains to the conditions, spread the main crackdown condition
-# into two columns, then nest everything by issue
-all_chains_likely_ci <- bind_cols(newdata_conditions_ci, 
-                                  chains_nested_likely_ci) %>% 
-  unnest(data) %>% 
-  select(-condition) %>% 
-  group_by(issue) %>% 
-  spread(crackdown, value) %>% 
-  select(-id) %>% 
-  nest()
-
-# All the pairwise differences in a single data frame, grouped by issue
-pairs_likely_conditions_ci <- all_chains_likely_ci %>% 
-  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
-         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
-         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))
-
-# Extract coefficient details and plot data
-diffs_coef_likely_pairs_detail_ci <- pairs_likely_conditions_ci %>% 
-  unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs)
-
-pairs_likely_plot_data_ci <- pairs_likely_conditions_ci %>% 
-  select(issue, diffs_coefs) %>% 
-  unnest(diffs_coefs) %>%
-  gather(pair, value, -issue) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-
-plot_diffs_likely_ci <- ggplot() + 
-  geom_density(data = pairs_likely_plot_data_ci, aes(x = value),
-               fill = ngo_cols("blue"), colour = NA, alpha = 0.4) + 
-  geom_segment(data = diffs_coef_likely_pairs_detail_ci, 
-               aes(x = q5, xend = q95, y = 0, yend = 0),
-               size = 3) +
-  geom_vline(data = diffs_coef_likely_pairs_detail_ci, 
-             aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  guides(fill = FALSE, color = FALSE) +
-  scale_x_continuous(labels = percent) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ issue + pair)
-```
-
-```{r likely-diffs-cif}
-# Nest each fitted chain into a single row that corresponds to each newdata_condition
-chains_nested_likely_cif <- chains_fitted_likely_cif %>% 
-  as_data_frame() %>% 
-  mutate(id = 1:n()) %>% 
-  gather(condition, value, -id) %>% 
-  group_by(condition) %>% 
-  nest()
-
-# Add the fitted chains to the conditions, spread the main crackdown condition
-# into two columns, then nest everything by issue
-all_chains_likely_cif <- bind_cols(newdata_conditions_cif, 
-                                   chains_nested_likely_cif) %>% 
-  unnest(data) %>% 
-  select(-condition) %>% 
-  group_by(issue, funding) %>% 
-  spread(crackdown, value) %>% 
-  select(-id) %>% 
-  nest()
-
-# All the pairwise differences in a single data frame, grouped by issue
-pairs_likely_conditions_cif <- all_chains_likely_cif %>% 
-  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
-         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
-         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))
-
-# Extract coefficient details and plot data
-diffs_coef_likely_pairs_detail_cif <- pairs_likely_conditions_cif %>% 
-  unnest(diffs_coef_pairs_detail) %>% 
-  select(-data, -diffs_coef_pairs, -diffs_coefs)
-
-pairs_likely_plot_data_cif <- pairs_likely_conditions_cif %>% 
-  select(issue, funding, diffs_coefs) %>% 
-  unnest(diffs_coefs) %>%
-  gather(pair, value, -issue, -funding) %>%
-  mutate(pair1 = pair) %>%
-  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair))
-
-plot_diffs_likely_cif <- ggplot() +
-  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
-               fill = ngo_cols("red"), colour = NA, alpha = 0.4) +
-  geom_segment(data = diffs_coef_likely_pairs_detail_cif,
-               aes(x = q5, xend = q95, y = 0, yend = 0),
-               size = 3) +
-  geom_vline(data = diffs_coef_likely_pairs_detail_cif,
-             aes(xintercept = `median`), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  guides(fill = FALSE, color = FALSE) +
-  scale_x_continuous(labels = percent) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ issue + funding + pair)
-```
-
-**Compare only individual conditions:**
-
-```{r plot-single-likely-diffs, fig.width=7, fig.height=2.5}
-diffs_likely_plot_data_singles <- bind_rows(pairs_likely_plot_data_c,
-                                            pairs_likely_plot_data_i,
-                                            pairs_likely_plot_data_f) %>% 
-  mutate(pair = fct_inorder(pair, ordered = TRUE))
-
-diffs_coef_likely_pairs_detail_singles <- bind_rows(diffs_coef_likely_pairs_detail_c,
-                                                    diffs_coef_likely_pairs_detail_i,
-                                                    diffs_coef_likely_pairs_detail_f) %>%
-  mutate(pair = ifelse(nchar(pair) > 25,
-                       str_replace(pair, "-", "-\n"),
-                       pair),
-         pair = fct_inorder(pair, ordered = TRUE))
-
-plot_diffs_likely_singles <- ggplot() +
-  geom_density(data = diffs_likely_plot_data_singles, 
-               aes(x = value, fill = pair),
-               colour = NA, alpha = 0.4) +
-  geom_segment(data = diffs_coef_likely_pairs_detail_singles, 
-               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
-               size = 3) +
-  geom_vline(data = diffs_coef_likely_pairs_detail_singles, 
-             aes(xintercept = median), size = 0.25) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  scale_x_continuous(labels = percent) +
-  scale_fill_manual(values = ngo_cols("green", "blue", "red", name = FALSE), guide = FALSE) +
-  labs(x = "Difference in medians") +
-  theme_ngos(density = TRUE) +
-  facet_wrap(~ pair)
-
-plot_diffs_likely_singles %T>%
-  print() %T>% 
-  ggsave(., filename = here("output", "figures", "likelihood-singles-diffs.pdf"),
-         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "likelihood-singles-diffs.png"),
-         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
-```
-
-```{r tbl-single-likely-diffs, results="asis"}
-bind_rows(diffs_coef_likely_pairs_detail_c,
-          diffs_coef_likely_pairs_detail_i,
-          diffs_coef_likely_pairs_detail_f) %>% 
-  select(`Frame` = pair, `∆~median~` = median, 
-         `% change~median~` = median_pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(missing = "—", 
-                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-likelihood-single-diffs.md"))
-```
-
-\
-
-**Compare nested conditions (what we're really most concerned about):**
-
-```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
-plot_diffs_likely_all <- 
-  (plot_diffs_likely_c / plot_diffs_likely_ci) | 
-  plot_diffs_likely_cif
-
-plot_diffs_likely_all +
-  plot_annotation(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
-                  subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
-                  tag_levels = "A", theme = theme_ngos())
-
-(plot_diffs_likely_all +
-    plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
-                    tag_levels = "A", theme = theme_ngos())) %T>%
-  ggsave(., filename = here("output", "figures", "likelihood-diffs.pdf"),
-         width = 8, height = 5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = here("output", "figures", "likelihood-diffs.png"),
-         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
-```
-
-```{r tbl-all-likely-diffs, results="asis"}
-bind_rows(diffs_coef_likely_pairs_detail_c,
-          diffs_coef_likely_pairs_detail_ci,
-          diffs_coef_likely_pairs_detail_cif) %>% 
-  select(Issue = issue, Funding = funding, 
-         `Crackdown - No crackdown~median~` = median, 
-         `% change~median~` = median_pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(missing = "—", 
-                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-likelihood-diffs.md"))
-```
-
-# Summary of hypotheses
-
-```{r hypotheses-summary, warning=FALSE, message=FALSE, results="asis"}
-# TODO: Make this more dynamic so I don't have to type all the values manually
-hypotheses <- read_csv(here("text", "hypotheses-summary.csv"))
-
-hypotheses %>% 
-  pandoc.table.return(justify = "ll", style = "grid", keep.line.breaks = TRUE,
-                      caption = "Summary of all hypotheses {#tbl:hypotheses}") %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-hypotheses.md"))
-```
 

### 2019-02-26 03_additional-analysis.Rmd
95% everywhere + tibble()

@@
 
-  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.9, 
+  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.95, 
                      estimate.method = "median", conf.method = "HPDinterval") %>%
@@
          `∆~median~` = diffs_median,
-         `90% HPDI` = diffs_hpdi_fancy)
+         `95% HPDI` = diffs_hpdi_fancy)
 
-note_row <- data_frame(Variable = c("*^a^Annual CPS, March 2017*",
+note_row <- tibble(Variable = c("*^a^Annual CPS, March 2017*",
                                 "*^b^Monthly CPS, September 2015*",
@@
 ```{r models-coefs-plot-amount, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
-posterior_details <- data_frame(model_name = c("Basic model", "Full model"),
+posterior_details <- tibble(model_name = c("Basic model", "Full model"),
                             model = list(m_amount_cif,
                                          m_amount_cif_full)) %>% 
-  mutate(posterior = model %>% map(~ as_data_frame(.)),
-         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
+  mutate(posterior = model %>% map(~ as_tibble(.)),
+         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.95,
                                                  conf.method = "HPDinterval")))
@@
   scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
-  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
-       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
+  labs(x = "Posterior median estimate + 95% credible interval", y = NULL,
+       caption = "95% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
   facet_wrap(~ full_model, scales = "free") + 
@@
   bind_cols(tidyMCMC(chains_fitted_charity, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
+                     conf.int = TRUE, conf.level = 0.95, conf.method = "HPDinterval")) %>% 
   mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))
@@
   bind_cols(tidyMCMC(chains_fitted_vol_relig, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
+                     conf.int = TRUE, conf.level = 0.95, conf.method = "HPDinterval")) %>% 
   mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
@@
 ```{r models-coefs-plot-likely, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
-posterior_details_likely <- data_frame(model_name = c("Basic model", "Full model"),
+posterior_details_likely <- tibble(model_name = c("Basic model", "Full model"),
                                    model = list(m_likely_cif,
                                                 m_likely_cif_full)) %>% 
-  mutate(posterior = model %>% map(~ as_data_frame(.)),
-         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
+  mutate(posterior = model %>% map(~ as_tibble(.)),
+         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.95,
                                                  conf.method = "HPDinterval")))

### 2019-02-27 02_analysis.Rmd
Save prior images

@@
 likely_theta
+
+likely_theta %T>% 
+  ggsave(., filename = here("output", "figures", "prior-likely.pdf"),
+         width = 2.75, height = 1.5, units = "in", device = cairo_pdf) %>%
+  ggsave(., filename = here("output", "figures", "prior-likely.png"),
+         width = 2.75, height = 1.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-amount_nu + amount_mu + amount_sigma
+amount_priors <- amount_nu + amount_mu + amount_sigma
+amount_priors
+
+amount_priors %T>% 
+  ggsave(., filename = here("output", "figures", "prior-amount.pdf"),
+         width = 8, height = 1.5, units = "in", device = cairo_pdf) %>%
+  ggsave(., filename = here("output", "figures", "prior-amount.png"),
+         width = 8, height = 1.5, units = "in", type = "cairo", dpi = 300)
 ```

### 2019-02-27 02_analysis.Rmd
Include point estimates in tables

@@
   scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
-  labs(x = "Median difference in donation likelihood", y = NULL, tag = "A") +
+  labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
   theme_ngos() +
@@
   scale_x_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "Median difference in donation likelihood", y = NULL, tag = "C") +
+  labs(x = "Difference in donation likelihood", y = NULL, tag = "C") +
   facet_wrap(~ facet_title, scales = "free_y") +
@@
   scale_x_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "Median difference in donation likelihood", y = NULL, tag = "D") +
+  labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
+       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
   facet_wrap(~ facet_title, scales = "free_y") +
@@
   unnest(tidy) %>% 
-  filter(term %in% c("theta_diff", "pct_change")) %>% 
+  filter(term %in% c("theta_1", "theta_2", "theta_diff", "pct_change")) %>% 
   select(title, term, estimate) %>% 
@@
   mutate(title = fct_inorder(title)) %>% 
-  select(`Frame` = title, `∆` = theta_diff, `%∆` = pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  select(`Frame` = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
+         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
@@
   arrange(title_clean) %>% 
-  select(Frame = title_clean, `∆` = theta_diff, `%∆` = pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  select(Frame = title_clean, `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
+         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
@@
   arrange(Issue, Funding) %>% 
-  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = theta_diff, `%∆` = pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  select(`Issue frame` = Issue, `Funding frame` = Funding, 
+         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
+         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
@@
   scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
-  labs(x = "Median difference in amount donated", y = NULL, tag = "A") +
+  labs(x = "Difference in amount donated", y = NULL, tag = "A") +
   theme_ngos() +
@@
   scale_x_continuous(labels = dollar) +
-  labs(x = "Median difference in amount donated", y = NULL, tag = "C") +
+  labs(x = "Difference in amount donated", y = NULL, tag = "C") +
   facet_wrap(~ facet_title, scales = "free_y") +
@@
   scale_x_continuous(labels = dollar) +
-  labs(x = "Median difference in amount donated", y = NULL, tag = "D",
+  labs(x = "Difference in amount donated", y = NULL, tag = "D",
        caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
@@
   unnest(tidy) %>% 
-  filter(term %in% c("mu_diff", "pct_change")) %>% 
+  filter(term %in% c("mu", "mu_diff", "pct_change")) %>% 
+  group_by(title) %>% 
+  mutate(group_id = 1:n()) %>% 
+  mutate(term = case_when(
+    term == "mu" ~ paste0(term, "_", group_id),
+    TRUE ~ term
+  )) %>% 
   select(title, term, estimate) %>% 
@@
     str_count(title, "\\|") == 2 ~ "Level 3"
-  ))
+  )) %>% 
+  ungroup()
 
@@
   mutate(title = fct_inorder(title)) %>% 
-  select(`Frame` = title, `∆` = mu_diff, `%∆` = pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  select(`Frame` = title, `Amount~treatment~` = mu_2, `Amount~control~` = mu_1,
+         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(caption = 'Difference between amount donated across single conditions; values represent posterior medians {#tbl:amount-diffs-1}') %T>%
@@
   arrange(title_clean) %>% 
-  select(Frame = title_clean, `∆` = mu_diff, `%∆` = pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  select(Frame = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
+         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-2}') %T>%
@@
   arrange(Issue, Funding) %>% 
-  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = mu_diff, `%∆` = pct_change,
-         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
+  select(`Issue frame` = Issue, `Funding frame` = Funding, 
+         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
+         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
   pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-3}') %T>%

### 2019-02-27 02_analysis.Rmd
Default png!
Use a YAML list, following https://github.com/rstudio/rmarkdown/issues/1474

@@
     code_folding: hide
+    pandoc_args:
+      - "--default-image-extension=png"
 editor_options: 

### 2019-02-27 02_analysis.Rmd
Fancy tables!

@@
 
-```{r plot-likely-diffs, warning=FALSE, fig.width=6, fig.height=8}
+```{r plot-likely-diffs, warning=FALSE, fig.width=4.5, fig.height=6.5}
 tidied_diffs_likely <- all_models_likely %>% 
@@
   labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
-  theme_ngos() +
+  theme_ngos(base_size = 9) +
   theme(panel.grid.major.y = element_blank())
@@
   facet_wrap(~ facet_title, scales = "free_y") +
-  theme_ngos() +
+  theme_ngos(base_size = 9) +
   theme(panel.grid.major.y = element_blank())
@@
   labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
-       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
+       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
   facet_wrap(~ facet_title, scales = "free_y") +
-  theme_ngos() +
+  theme_ngos(base_size = 9) +
   theme(panel.grid.major.y = element_blank())
@@
   ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
-         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
+         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
   ggsave(., filename = here("output", "figures", "likely-diffs.png"),
-         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
+         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
 ```
 
-```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
+```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE}
 tbl_likely_tidy <- all_models_likely %>% 
@@
 
-tbl_likely_tidy %>% 
+tbl_likely_1 <- tbl_likely_tidy %>% 
   left_join(tbl_likely_probs, by = "title") %>% 
@@
   mutate(title = recode(title, 
-                        Crackdown = "Crackdown −\nNo crackdown",
-                        Issue = "Humanitarian\nassistance −\nHuman rights",
-                        Funding = "Private −\nGovernment\nfunding")) %>% 
-  mutate(title = fct_inorder(title)) %>% 
-  select(`Frame` = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
-         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-likely-diffs-1.md"))
+                        Crackdown = "Crackdown − No crackdown",
+                        Issue = "*Humanitarian assistance − Human rights*",
+                        Funding = "*Private − Government funding*")) %>% 
+  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
+            funs(percent_format(accuracy = 0.1)(.))) %>% 
+  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
+  select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
+         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
 ```
 
-```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
-tbl_likely_tidy %>% 
+```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE}
+tbl_likely_2 <- tbl_likely_tidy %>% 
   left_join(tbl_likely_probs, by = "title") %>% 
@@
   arrange(title_clean) %>% 
-  select(Frame = title_clean, `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
-         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-likely-diffs-2.md"))
+  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
+            funs(percent_format(accuracy = 0.1)(.))) %>% 
+  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
+  mutate(title_clean = as.character(title_clean)) %>% 
+  select(`H~2a~ and H~3a~` = title_clean, 
+         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
+         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
 ```
 
-```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
-tbl_likely_tidy %>% 
+```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE}
+tbl_likely_3 <- tbl_likely_tidy %>% 
   left_join(tbl_likely_probs, by = "title") %>% 
@@
   arrange(Issue, Funding) %>% 
-  select(`Issue frame` = Issue, `Funding frame` = Funding, 
+  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
+            funs(percent_format(accuracy = 0.1)(.))) %>% 
+  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
+  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
+  select(`H~2a~ and H~3a~ (nested)` = Frame,
          `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
-         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
+         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+```
+
+```{r combine-likely-tables, results="asis"}
+tbl_likely_2_header <- enframe(colnames(tbl_likely_2)) %>% 
+  mutate(value = pandoc.strong.return(value)) %>% 
+  spread(name, value) %>% 
+  set_names(colnames(tbl_likely_1))
+
+tbl_likely_3_header <- enframe(colnames(tbl_likely_3)) %>% 
+  mutate(value = pandoc.strong.return(value)) %>% 
+  spread(name, value) %>% 
+  set_names(colnames(tbl_likely_1))
+
+bind_rows(tbl_likely_1, 
+          tbl_likely_2_header, 
+          set_names(tbl_likely_2, colnames(tbl_likely_1)),
+          tbl_likely_3_header,
+          set_names(tbl_likely_3, colnames(tbl_likely_1))) %>% 
+  rename(`H~1a~` = Frame) %>% 
+  pandoc.table.return(caption = 'Likelihood of donation and differences in proportions in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs}',
+                      justify = "lccccc") %T>%
   cat() %>%
-  cat(file = here("output", "tables", "tbl-likely-diffs-3.md"))
+  cat(file = here("output", "tables", "tbl-likely-diffs.md"))
 ```
@@
 
-```{r plot-amount-diffs, warning=FALSE, fig.width=6, fig.height=8}
+```{r plot-amount-diffs, warning=FALSE, fig.width=4.5, fig.height=6.5}
 # This will generate a warning because unnest() puts the crackdown values into
@@
   labs(x = "Difference in amount donated", y = NULL, tag = "A") +
-  theme_ngos() +
+  theme_ngos(base_size = 9) +
   theme(panel.grid.major.y = element_blank())
@@
   labs(x = "Difference in amount donated", y = NULL, tag = "D",
-       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
+       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
   facet_wrap(~ facet_title, scales = "free_y") +
-  theme_ngos() +
+  theme_ngos(base_size = 9) +
   theme(panel.grid.major.y = element_blank())
@@
   ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
-         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
+         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
   ggsave(., filename = here("output", "figures", "amount-diffs.png"),
-         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
+         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
 ```
 
-```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
+```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE}
 tbl_amounts_tidy <- all_models_amount %>% 
@@
 
-tbl_amounts_tidy %>% 
+tbl_amount_1 <- tbl_amounts_tidy %>% 
   left_join(tbl_amounts_probs, by = "title") %>% 
@@
   mutate(title = recode(title, 
-                        Crackdown = "Crackdown −\nNo crackdown",
-                        Issue = "Humanitarian\nassistance −\nHuman rights",
-                        Funding = "Private −\nGovernment\nfunding")) %>% 
-  mutate(title = fct_inorder(title)) %>% 
-  select(`Frame` = title, `Amount~treatment~` = mu_2, `Amount~control~` = mu_1,
-         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(caption = 'Difference between amount donated across single conditions; values represent posterior medians {#tbl:amount-diffs-1}') %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-amount-diffs-1.md"))
+                        Crackdown = "Crackdown − No crackdown",
+                        Issue = "*Humanitarian assistance − Human rights*",
+                        Funding = "*Private − Government funding*")) %>% 
+  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
+  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
+  select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
+         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
 ```
 
-```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
-tbl_amounts_tidy %>% 
+```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE}
+tbl_amount_2 <- tbl_amounts_tidy %>% 
   left_join(tbl_amounts_probs, by = "title") %>% 
@@
   arrange(title_clean) %>% 
-  select(Frame = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
-         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-2}') %T>%
-  cat() %>% 
-  cat(file = here("output", "tables", "tbl-amount-diffs-2.md"))
+  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
+  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
+  mutate(title_clean = as.character(title_clean)) %>% 
+  select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
+         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
 ```
 
-```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
-tbl_amounts_tidy %>% 
+```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE}
+tbl_amount_3 <- tbl_amounts_tidy %>% 
   left_join(tbl_amounts_probs, by = "title") %>% 
@@
   arrange(Issue, Funding) %>% 
-  select(`Issue frame` = Issue, `Funding frame` = Funding, 
+  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
+  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
+  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
+  select(`H~2b~ and H~3b~ (nested)` = Frame,
          `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
-         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
-  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-3}') %T>%
+         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+```
+
+```{r combine-amount-tables, results="asis"}
+tbl_amount_2_header <- enframe(colnames(tbl_amount_2)) %>% 
+  mutate(value = pandoc.strong.return(value)) %>% 
+  spread(name, value) %>% 
+  set_names(colnames(tbl_amount_1))
+
+tbl_amount_3_header <- enframe(colnames(tbl_amount_3)) %>% 
+  mutate(value = pandoc.strong.return(value)) %>% 
+  spread(name, value) %>% 
+  set_names(colnames(tbl_amount_1))
+
+bind_rows(tbl_amount_1, 
+          tbl_amount_2_header, 
+          set_names(tbl_amount_2, colnames(tbl_amount_1)),
+          tbl_amount_3_header,
+          set_names(tbl_amount_3, colnames(tbl_amount_1))) %>% 
+  rename(`H~1b~` = Frame) %>% 
+  pandoc.table.return(caption = 'Mean values and differences in means for amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs}',
+                      justify = "lccccc") %T>%
   cat() %>%
-  cat(file = here("output", "tables", "tbl-amount-diffs-3.md"))
+  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
 ```

### 2019-03-01 02_analysis.Rmd
Wider session info
Add causal pathway diagram

@@
 library(ggstance)
+library(ggdag)
 library(patchwork)
@@
 }
+```
+
+# Causal pathway
+
+Our theory and hypotheses are laid out in the causal pathway below.
+Our outcomes (Y: % likely to donate and amount donated) "listen to" or respond to C (crackdown), which is our main treatment or exposure.
+Funding (F) and issue (I) serve as heuristics for donation and influence a government's decision to crack down on NGOs, hence the dual arrows to C and Y.
+
+```{r causal-dag, fig.width=4.5, fig.height=2.5}
+theory_dag <- dagify(Y ~ I + C + F,
+                     C ~ I + F,
+                     outcome = "F",
+                     exposure = "C") %>% 
+  tidy_dagitty(layout = "sugiyama")
+
+plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
+  geom_dag_node(size = 12) +
+  geom_dag_edges() +
+  geom_dag_text(size = pts(9), family = "Encode Sans Condensed SemiBold") +
+  scale_dag() +
+  theme_ngos() +
+  theme(panel.grid = element_blank(),
+        axis.title = element_blank(),
+        axis.text = element_blank())
+
+plot_dag %T>% 
+  print() %T>%
+  ggsave(., filename = here("output", "figures", "causal-path.pdf"),
+         width = 4.5, height = 2.5, units = "in", device = cairo_pdf) %>% 
+  ggsave(., filename = here("output", "figures", "causal-path.png"),
+         width = 4.5, height = 2.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r show-session-info, echo=TRUE}
+```{r show-session-info, echo=TRUE, width=100}
 writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

### 2019-03-01 02_analysis.Rmd
Use Roboto instead of Encode

@@
   geom_dag_edges() +
-  geom_dag_text(size = pts(9), family = "Encode Sans Condensed SemiBold") +
+  geom_dag_text(size = pts(9), family = "Roboto Condensed Bold") +
   scale_dag() +

### 2019-03-01 03_additional-analysis.Rmd
Wider session info
Use Roboto instead of Encode

@@
 
-txt_gp <- gpar(fontfamily = "Encode Sans Condensed Medium", 
+txt_gp <- gpar(fontfamily = "Roboto Condensed", 
                fontface = "plain", fontsize = 8)
@@
                 fontsize = 7, fontface = "plain",
-                fontfamily = "Encode Sans Condensed Light"),
+                fontfamily = "Roboto Condensed Light"),
          bg_params = list(fill = "white")),
@@
                 fontsize = 7, fontface = "plain",
-                fontfamily = "Encode Sans Condensed SemiBold"),
+                fontfamily = "Roboto Condensed Bold"),
          bg_params = list(fill = ngo_cols("blue"))),

### 2019-03-01 lib/graphics.R

@@ -8,22 +8,22 @@ theme_spark <- function() {
         plot.margin = unit(c(0, 0, -0.25, -0.25), "lines"))
 }
 
-theme_ngos <- function(base_size = 11, base_family = "Encode Sans Condensed", density = FALSE) {
-  update_geom_defaults("label", list(family = "Encode Sans Condensed Light", face = "plain"))
-  update_geom_defaults("text", list(family = "Encode Sans Condensed Light", face = "plain"))
+theme_ngos <- function(base_size = 11, base_family = "Roboto Condensed Light", density = FALSE) {
+  update_geom_defaults("label", list(family = "Roboto Condensed Light", face = "plain"))
+  update_geom_defaults("text", list(family = "Roboto Condensed Light", face = "plain"))
   
   ret <- theme_bw(base_size, base_family) +
     theme(plot.title = element_text(size = rel(1.4), face = "plain",
-                                    family = "Encode Sans Condensed SemiBold"),
+                                    family = "Roboto Condensed Bold"),
           plot.subtitle = element_text(size = rel(1), face = "plain",
-                                       family = "Encode Sans Condensed Light"),
+                                       family = "Roboto Condensed Light"),
           plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
-                                      family = "Encode Sans Condensed Light",
+                                      family = "Roboto Condensed Light",
                                       margin = margin(t = 10)),
           plot.tag = element_text(size = rel(1), face = "plain", color = "grey50",
-                                  family = "Encode Sans Condensed SemiBold"),
+                                  family = "Roboto Condensed Bold"),
           strip.text = element_text(size = rel(0.8), face = "plain",
-                                    family = "Encode Sans Condensed Medium"),
+                                    family = "Roboto Condensed Medium"),
           strip.text.x = element_text(margin = margin(t = 1, b = 1)),
           panel.border = element_blank(), 
           strip.background = element_rect(fill = "#ffffff", colour = NA),

### 2019-03-01 03_additional-analysis.Rmd
Remove old model-based analysis

@@
 
-# Amount donated (full)
-
-## Models
-
-```{r build-models-amount-full, warning=FALSE, message=FALSE, cache=TRUE}
-# Basic model
-m_amount_c <- stan_glm(amount_donate ~ crackdown,
-                       data = results, family = gaussian(),
-                       prior = cauchy(location = 0, scale = 2.5),
-                       prior_intercept = cauchy(location = 0, scale = 10),
-                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
-
-m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)
-
-m_amount_cif <- update(m_amount_c, . ~ . + 
-                         issue + funding + crackdown * issue + crackdown * funding + 
-                         issue * funding + crackdown * issue * funding)
-
-# Interaction models with extra controls
-m_amount_c_full <- update(m_amount_c, . ~ . + 
-                            favor_humanitarian_bin + 
-                            give_charity_3 + volunteer + political_knowledge_bin +
-                            ideology_bin + education_bin + religiosity_bin +
-                            income_bin + age_bin)
-
-m_amount_ci_full <- update(m_amount_ci, . ~ . + 
-                             favor_humanitarian_bin + 
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
-
-m_amount_cif_full <- update(m_amount_cif, . ~ . + 
-                             favor_humanitarian_bin +
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
-```
-
-```{r tbl-models-amount-full, warning=FALSE, results="asis"}
-huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
-       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
-       coefs = clean_coefs_named,
-       statistics = model_stats_bayes,
-       stars = NULL) %T>% 
-  print_hux() %>% 
-  to_md(max_width = 100) %>% 
-  cat(file = here("output", "tables", "tbl-models-amount-full.md"))
-```
-
-## Coefficient plot
-
-```{r models-coefs-plot-amount, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
-posterior_details <- tibble(model_name = c("Basic model", "Full model"),
-                            model = list(m_amount_cif,
-                                         m_amount_cif_full)) %>% 
-  mutate(posterior = model %>% map(~ as_tibble(.)),
-         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.95,
-                                                 conf.method = "HPDinterval")))
-
-coefs_posterior <- posterior_details %>%
-  unnest(posterior) %>% 
-  gather(term, value, -model_name) %>% 
-  left_join(clean_coefs, by = "term") %>% 
-  filter(term_clean != "Intercept") %>% 
-  mutate(full_model = !simple_model)
-
-coefs_summary <- posterior_details %>% 
-  unnest(tidy_summary) %>% 
-  left_join(clean_coefs, by = "term") %>% 
-  filter(term_clean != "Intercept") %>% 
-  mutate(full_model = !simple_model)
-
-amount_coefs_full <- ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
-  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
-                      rel_min_height = 0.01, scale = 1.5, 
-                      quantile_lines = TRUE, quantiles = 2) +
-  geom_segment(data = coefs_summary, 
-               aes(x = conf.low, xend = conf.high, 
-                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
-               size = 1) +
-  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
-  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
-  labs(x = "Posterior median estimate + 95% credible interval", y = NULL,
-       caption = "95% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
-  facet_wrap(~ full_model, scales = "free") + 
-  theme_ngos() +
-  theme(legend.position = "bottom",
-        strip.text = element_blank())
-
-amount_coefs_full %T>%
-  print() %T>% 
-  ggsave(., filename = here("output", "figures", "amount-coefs-full.pdf"),
-         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "amount-coefs-full.png"),
-         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
-```
-
-## Predicted medians across different variables
-
-**Charitable giving**
-
-```{r plot-charity-amounts, fig.width=5, fig.height=4}
-newdata_means <- results %>% 
-  select(favor_humanitarian_bin, favor_human_rights_bin, favor_development_bin,
-         give_charity_3, volunteer, political_knowledge_bin,
-         ideology_bin, education_bin, religiosity_bin, income_bin, age_bin) %>% 
-  summarize_all(typical) %>% 
-  mutate(id = 1)
-
-newdata_conditions_charity <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
-  mutate(id = 1) %>% 
-  left_join(select(newdata_means, -give_charity_3), by = "id") %>% 
-  select(-id)
-
-chains_fitted_charity <- posterior_linpred(m_amount_c_full, 
-                                           newdata = newdata_conditions_charity)
-
-coef_summary_charity <- newdata_conditions_charity %>% 
-  bind_cols(tidyMCMC(chains_fitted_charity, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.95, conf.method = "HPDinterval")) %>% 
-  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))
-
-ggplot(coef_summary_charity, aes(x = fct_rev(give_charity_3), y = estimate)) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
-                  position = position_dodge(width = 0.5)) +
-  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
-  scale_y_continuous(labels = dollar) +
-  labs(x = "How often do you give to charity?", y = "Median amount donated") +
-  theme_ngos() +
-  theme(legend.position = "bottom",
-        panel.grid.major.x = element_blank())
-```
-
-**Voluntarism and religiosity**
-
-```{r plot-vol-relig-amounts}
-newdata_conditions_vol_relig <- results %>% 
-  expand(nesting(crackdown, volunteer, religiosity_bin)) %>% 
-  filter(!is.na(religiosity_bin)) %>% 
-  mutate(id = 1) %>% 
-  left_join(select(newdata_means, -volunteer, -religiosity_bin), by = "id") %>% 
-  select(-id)
-
-chains_fitted_vol_relig <- posterior_linpred(m_amount_c_full, 
-                                             newdata = newdata_conditions_vol_relig)
-
-coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
-  bind_cols(tidyMCMC(chains_fitted_vol_relig, estimate.method = "median",
-                     conf.int = TRUE, conf.level = 0.95, conf.method = "HPDinterval")) %>% 
-  mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
-  mutate(religiosity_bin = fct_recode(religiosity_bin,
-                                      `Rarely attend religious services` = "Rarely",
-                                      `Attend religious services\nat least once a month` = 
-                                        "At least once a month"))
-
-ggplot(coef_summary_vol_relig, aes(x = fct_rev(volunteer), y = estimate)) +
-  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
-                  position = position_dodge(width = 0.5)) +
-  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
-  scale_y_continuous(labels = dollar) +
-  labs(x = "Have you volunteered in the last 12 months?", y = "Median amount donated") +
-  facet_wrap(~ religiosity_bin) +
-  theme_ngos() +
-  theme(legend.position = "bottom",
-        panel.grid.major.x = element_blank())
-```
-
-\
-
-# Likelihood of donation (full)
-
-## Models
-
-```{r build-models-likely-full, warning=FALSE, message=FALSE, cache=TRUE}
-# Basic models
-m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
-                       data = results, family = binomial(link = "logit"),
-                       prior = student_t(3, 0, 2.5),
-                       prior_intercept = student_t(3, 0, 10),
-                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
-
-m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)
-
-m_likely_cif <- update(m_likely_c, . ~ . + 
-                         issue + funding + crackdown * issue + crackdown * funding + 
-                         issue * funding + crackdown * issue * funding)
-
-# Interaction models with extra controls
-m_likely_c_full <- update(m_likely_c, . ~ . + 
-                            favor_humanitarian_bin +
-                            give_charity_3 + volunteer + political_knowledge_bin +
-                            ideology_bin + education_bin + religiosity_bin +
-                            income_bin + age_bin)
-
-m_likely_ci_full <- update(m_likely_ci, . ~ . + 
-                             favor_humanitarian_bin +
-                             give_charity_3 + volunteer + political_knowledge_bin +
-                             ideology_bin + education_bin + religiosity_bin +
-                             income_bin + age_bin)
-
-m_likely_cif_full <- update(m_likely_cif, . ~ . + 
-                              favor_humanitarian_bin +
-                              give_charity_3 + volunteer + political_knowledge_bin +
-                              ideology_bin + education_bin + religiosity_bin +
-                              income_bin + age_bin)
-```
-
-```{r tbl-models-likely-full, warning=FALSE, results="asis"}
-huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
-       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
-       coefs = clean_coefs_named,
-       statistics = model_stats_bayes,
-       stars = NULL) %T>% 
-  print_hux() %>% 
-  to_md(max_width = 100) %>% 
-  cat(file = here("output", "tables", "tbl-models-likelihood-full.md"))
-```
-
-## Coefficient plot
-
-```{r models-coefs-plot-likely, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
-posterior_details_likely <- tibble(model_name = c("Basic model", "Full model"),
-                                   model = list(m_likely_cif,
-                                                m_likely_cif_full)) %>% 
-  mutate(posterior = model %>% map(~ as_tibble(.)),
-         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.95,
-                                                 conf.method = "HPDinterval")))
-
-coefs_posterior_likely <- posterior_details_likely %>%
-  unnest(posterior) %>% 
-  gather(term, value, -model_name) %>% 
-  left_join(clean_coefs, by = "term") %>% 
-  filter(term_clean != "Intercept") %>% 
-  mutate(full_model = !simple_model)
-
-coefs_summary_likely <- posterior_details_likely %>% 
-  unnest(tidy_summary) %>% 
-  left_join(clean_coefs, by = "term") %>% 
-  filter(term_clean != "Intercept") %>% 
-  mutate(full_model = !simple_model)
-
-likely_coefs_full <- ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
-  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
-                      rel_min_height = 0.01, scale = 1.5, 
-                      quantile_lines = TRUE, quantiles = 2) +
-  geom_segment(data = coefs_summary_likely, 
-               aes(x = conf.low, xend = conf.high, 
-                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
-               size = 1) +
-  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
-  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
-  labs(x = "Posterior median estimate + 95% credible interval", y = NULL,
-       caption = "95% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
-  facet_wrap(~ full_model, scales = "free") + 
-  theme_ngos() +
-  theme(legend.position = "bottom",
-        strip.text = element_blank())
-
-likely_coefs_full %T>%
-  print() %T>% 
-  ggsave(., filename = here("output", "figures", "likely-coefs-full.pdf"),
-         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "likely-coefs-full.png"),
-         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
-```
-
 # Original computing environment

### 2019-03-08 README.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "The effect of NGO crackdowns on individual philanthropy"
```

# The effect of NGO crackdowns on individual philanthropy

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
[Andrew Heiss](https://www.andrewheiss.com/) • Romney Institute of Public Service and Ethics • Brigham Young University

---

### Abstract

State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries. Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO. We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs. Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues. We conclude by discussing the implications for the sustainability of NGOs working abroad.

---

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, testingthing, from GitHub with:

```r
pkgbuild::compile_dll()
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2019-03-08 analysis/01_clean-data.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

--- 2018-07-17 01_clean-data.Rmd
@@
 library(tidyverse)
+library(crackdownsphilanthropy)
+library(csvy)
 library(here)
-library(csvy)
-
-# Calculate the quantile (and median) of an ordered factor
-# Borrowed from @jrnold: https://gist.github.com/jrnold/6759254
-#
-# In the case of ties, the first in order will win. For instance, 
-# bloop <- factor(c("A", "A", "B", "B"), ordered = TRUE)
-# median(bloop)  # "A"
-quantile.ordered <- function(x, probs = seq(0, 1, 0.25)) {
-  tab <- table(x)
-  cdf <- cumsum(tab / sum(tab))
-  idx <- sapply(probs, function(p) min(which(cdf >= p)))
-  levels(x)[idx] 
-}
-
-quantile.factor <- quantile.ordered
-median.ordered <- function(x) quantile(x, 0.5)
-median.factor <- median.ordered
 
@@
 # results_file <- file.path(here(), "data", "test_data.csv")
-results_file <- here("private", 
+results_file <- here("data", "private_data", 
                      "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")
@@
 # repository because of privacy issues (it deals directly with MTurk worker
-# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
-codes_to_exclude <- read_csv(here("data", "codes_to_exclude.csv"))
+# IDs), called "data/private_data/approve_mturkers.R". It outputs this text list
+# of codes.
+codes_to_exclude <- read_csv(here("data", "derived_data", "codes_to_exclude.csv"))
 
@@
   filter(!(confirmation_code %in% codes_to_exclude$confirmation_code)) %>% 
+  filter(attention2_correct) %>%
   # Factorize variables
@@
 # Save final clean data
-saveRDS(results, here("data", "results_clean.rds"))
-write_csvy(results, file = here("data", "results_clean.csv"),
-           metadata = here("data", "results_clean.yaml"), na = "NA")
+saveRDS(results, here("data", "derived_data", "results_clean.rds"))
+write_csvy(results, file = here("data", "derived_data", "results_clean.csv"),
+           metadata = here("data", "derived_data", "results_clean.yaml"), na = "NA")
 ```
@@
 
-saveRDS(completed_summary, here("data", "completion_summary.rds"))
-write_csv(completed_summary, here("data", "completion_summary.csv"))
+saveRDS(completed_summary, here("data", "derived_data", "completion_summary.rds"))
+write_csv(completed_summary, here("data", "derived_data", "completion_summary.csv"))
 ```
@@
 
-```{r show-session-info, echo=TRUE}
+```{r show-session-info, echo=TRUE, width=90}
 writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

### 2019-03-08 analysis/02_analysis.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

--- 2019-03-01 02_analysis.Rmd
@@
 library(tidyverse)
+library(crackdownsphilanthropy)
 library(rstan)
@@
 library(janitor)
-library(huxtable)
 library(here)
 
-source(here("lib", "graphics.R"))
-source(here("lib", "pander_options.R"))
-source(here("lib", "modeling.R"))
+source(here("analysis", "options.R"))
 
 # Load data
-results <- readRDS(here("data", "results_clean.rds"))
+results <- readRDS(here("data", "derived_data", "results_clean.rds"))
 # qwraps2::lazyload_cache_dir("02_analysis_cache/html")
-
-# Helpful functions
-safe_mean <- function(x, ...) suppressWarnings(mean(as.numeric(x), ...))
-safe_sd <- function(x, ...) suppressWarnings(sd(as.numeric(x), ...))
-
-my_as_numeric <- function(x) {
-  is_num <- suppressWarnings(!any(is.na(as.numeric(x))))
-
-  if (is_num) {
-    as.numeric(x)
-  } else {
-    x
-  }
-}
-
-level_summary <- function(x, variable, df = results) {
-  variable <- as.character(variable)
-  if (is.factor(df[[variable]])) {
-    x_levels <- levels(df[[variable]])
-  } else {
-    x_levels <- unique(df[[variable]])
-  }
-
-  factor_summary <- tibble(x) %>% 
-    count(x) %>%
-    mutate(pct = n / sum(n),
-           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
-           x = factor(x, levels = x_levels, ordered = TRUE))
-
-  inline_summary <- factor_summary %>% arrange(x) %>% 
-    pull(fancy) %>% paste(collapse = " | ")
-
-  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
-    geom_bar(stat = "identity", fill = "grey50") +
-    theme_spark()
-
-  file_name <- gsub("\\.| ", "_", tolower(variable))
-  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")
-
-  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
-                                  paste0(file_name, ".pdf")), 
-         width = 1, height = 0.2, device = cairo_pdf)
-  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
-                                  paste0(file_name, ".png")), 
-         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)
-
-  output <- tibble(spark = md_img, summary = inline_summary)
-  return(output)
-}
-
-numeric_summary <- function(x, variable) {
-  inline_summary <- paste0("Median: ", round(median(x, na.rm = TRUE), 2),
-                           " | Mean: ", round(mean(x, na.rm = TRUE), 2), 
-                           " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2))
-
-  fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
-    geom_histogram(fill = "grey50", binwidth = 10) +
-    theme_spark()
-
-  file_name <- gsub("\\.| ", "_", tolower(variable))
-  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")
-
-  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
-                                   paste0(file_name, ".pdf")), 
-         width = 1, height = 0.2, device = cairo_pdf)
-  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
-                                   paste0(file_name, ".png")), 
-         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)
-
-  output <- tibble(spark = md_img, summary = inline_summary)
-  return(output)
-}
-
-my_summary <- function(x, variable, df) {
-  x <- my_as_numeric(x)
-
-  if (is.numeric(x)) {
-    numeric_summary(x, variable)
-  } else {
-    level_summary(x, variable, df)
-  }
-}
 ```
@@
   print() %T>%
-  ggsave(., filename = here("output", "figures", "causal-path.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "causal-path.pdf"),
          width = 4.5, height = 2.5, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "causal-path.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "causal-path.png"),
          width = 4.5, height = 2.5, units = "in", type = "cairo", dpi = 300)
@@
   pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
-  cat(file = here("output", "tables", "tbl-experimental-conditions.md"))
+  cat(file = here("analysis", "output", "tables", "tbl-experimental-conditions.md"))
 ```
@@
   mutate(N = data %>% map_int(~ nrow(.)),
-         summary = map2(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
+         summary = map2(.x = data, .y = variable, ~ md_summary_row(.x$value, .y, results))) %>% 
   left_join(vars_to_summarize, by = "variable") %>% 
@@
                       split.cell = 80, split.table = Inf) %T>% 
-  cat(file = here("output", "tables", "tbl-descriptive-stats.md")) %>%
+  cat(file = here("analysis", "output", "tables", "tbl-descriptive-stats.md")) %>%
   cat()
@@
   pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
-  cat(file = here("output", "tables", "tbl-avg-results.md"))
+  cat(file = here("analysis", "output", "tables", "tbl-avg-results.md"))
 ```
@@
   print() %T>%
-  ggsave(., filename = here("output", "figures", "donate_summary.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "donate_summary.pdf"),
          width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "donate_summary.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "donate_summary.png"),
          width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
@@
   print() %T>%
-  ggsave(., filename = here("output", "figures", "amount_summary.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "amount_summary.pdf"),
          width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "amount_summary.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "amount_summary.png"),
          width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
@@
 likely_theta %T>% 
-  ggsave(., filename = here("output", "figures", "prior-likely.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "prior-likely.pdf"),
          width = 2.75, height = 1.5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = here("output", "figures", "prior-likely.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "prior-likely.png"),
          width = 2.75, height = 1.5, units = "in", type = "cairo", dpi = 300)
@@
 ```{r run-likely-models, results="hide", cache=TRUE}
-# This takes forever because of C++ compiling and actual MCMC sampling, so this
-# chunk is cached
-
-# Compile model
-donate_likely <- stan_model(here("lib", "donate_likely.stan"))
+# This takes forever because of MCMC sampling, so this chunk is cached
 
@@
   mutate(model = stan_data_counts %>% map(~ {
-    sampling(donate_likely, data = .x, control = list(max_treedepth = 15),
+    sampling(donate_likely(), data = .x, control = list(max_treedepth = 15),
              chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
@@
 plot_diffs_likely_all %T>% 
-  ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.pdf"),
          width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = here("output", "figures", "likely-diffs.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.png"),
          width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
@@
   cat() %>%
-  cat(file = here("output", "tables", "tbl-likely-diffs.md"))
+  cat(file = here("analysis", "output", "tables", "tbl-likely-diffs.md"))
 ```
@@
 amount_priors %T>% 
-  ggsave(., filename = here("output", "figures", "prior-amount.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "prior-amount.pdf"),
          width = 8, height = 1.5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = here("output", "figures", "prior-amount.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "prior-amount.png"),
          width = 8, height = 1.5, units = "in", type = "cairo", dpi = 300)
@@
 ```{r run-amount-models, results="hide", cache=TRUE}
-# This takes forever because of C++ compiling and actual MCMC sampling, so this
-# chunk is cached
-
-# Compile model
-amount_donated_best <- stan_model(here("lib", "amount_donated_best.stan"))
-
 # Sample from the compiled model
@@
   mutate(model = stan_data %>% map(~ {
-    sampling(amount_donated_best, data = compose_data(.x),
+    sampling(amount_donated_best(), data = compose_data(.x),
              chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
@@
 plot_diffs_amounts_all %T>% 
-  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.pdf"),
          width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
-  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.png"),
          width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
@@
   cat() %>%
-  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
+  cat(file = here("analysis", "output", "tables", "tbl-amount-diffs.md"))
 ```

### 2019-03-08 analysis/03_additional-analysis.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

--- 2019-03-01 03_additional-analysis.Rmd
@@
 library(tidyverse)
+library(crackdownsphilanthropy)
 library(magrittr)
 library(rstan)
-library(rstanarm)
 library(broom)
 library(glue)
-library(ggstance)
-library(ggridges)
 library(grid)
@@
 library(Gmisc)
-library(patchwork)
 library(pander)
 library(scales)
-library(huxtable)
-library(lubridate)
-library(modelr)
 library(ipumsr)
@@
 
-source(here("lib", "graphics.R"))
-source(here("lib", "pander_options.R"))
-source(here("lib", "modeling.R"))
+source(here("analysis", "options.R"))
 
 # Load data
-results <- readRDS(here("data", "results_clean.rds"))
+results <- readRDS(here("data", "derived_data", "results_clean.rds"))
 ```
@@
 ```{r build-consort}
-consort <- readRDS(here("data", "completion_summary.rds")) %>% 
+consort <- readRDS(here("data", "derived_data", "completion_summary.rds")) %>% 
   spread(reason, n) %>% 
@@
 # Save as PDF
-cairo_pdf(filename = here("output", "figures", "consort.pdf"),
+cairo_pdf(filename = here("analysis", "output", "figures", "consort.pdf"),
           width = 10, height = 6)
@@
 # Save as PNG
-png(filename = here("output", "figures", "consort.png"), 
+png(filename = here("analysis", "output", "figures", "consort.png"), 
     width = 10, height = 6, units = "in",
@@
 ```{r load-clean-cps, warning=FALSE, message=FALSE}
-cps_2015_ddi_file <- here("data", "ipums-cps", "cps_09_2015.xml")
-cps_2015_data_file <- here("data", "ipums-cps", "cps_09_2015.dat.gz")
+cps_2015_ddi_file <- here("data", "raw_data", "ipums-cps", "cps_09_2015.xml")
+cps_2015_data_file <- here("data", "raw_data", "ipums-cps", "cps_09_2015.dat.gz")
 
@@
 
-cps_2017_ddi_file <- here("data", "ipums-cps", "cps_2017.xml")
-cps_2017_data_file <- here("data", "ipums-cps", "cps_2017.dat.gz")
+cps_2017_ddi_file <- here("data", "raw_data", "ipums-cps", "cps_2017.xml")
+cps_2017_data_file <- here("data", "raw_data", "ipums-cps", "cps_2017.dat.gz")
 
@@
 
-```{r sample-population-characteristics-freq, include=FALSE, eval=FALSE}
-# Demographic variables
-table(results$gender_bin) %>% prop.test(., p = global_stats$female)
-table(results$education_bin) %>% prop.test(., p = global_stats$college)
-table(results$income_bin) %>% prop.test(., p = global_stats$income)
-table(results$age_bin) %>% prop.test(., p = global_stats$age)
-
-# Volunteering
-table(results$volunteer) %>% prop.test(., p = global_stats$volunteering)
-table(results$give_charity_2) %>% prop.test(., p = global_stats$donating)
-```
-
-```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
-prop_test_bayes_saved <- here("lib", "bayes_prop_test.rds")
-
-if (file.exists(prop_test_bayes_saved)) {
-  prop_test_bayes <- readRDS(prop_test_bayes_saved)
-} else {
-  prop_test_bayes <- stan_model(here("lib", "bayes_prop_test.stan"))
-  saveRDS(prop_test_bayes, prop_test_bayes_saved)
-}
-```
-
 ```{r sample-population-characteristics, cache=TRUE}
-compare_sample_to_pop_bayes <- function(sample_value, population_value) {
-  mcmc_samples <- sampling(prop_test_bayes, list(x = table(sample_value)[1],
-                                                 total_n = length(sample_value),
-                                                 pop_prop = population_value),
+compare_sample_to_pop <- function(sample_value, population_value) {
+  mcmc_samples <- pop_prop_stan(
+    x = table(sample_value)[1],
+    n_total = length(sample_value),
+    pop_prop = population_value,
     chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
@@
          prop_test_bayes = map2(.x = sample_value, .y = National, 
-                                .f = ~ compare_sample_to_pop_bayes(.x, .y))) 
+                                .f = ~ compare_sample_to_pop(.x, .y))) 
 ```
@@
                       caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
-  cat(file = here("output", "tables", "tbl-exp-sample.md")) %>% 
+  cat(file = here("analysis", "output", "tables", "tbl-exp-sample.md")) %>% 
   cat()
@@
 ```{r avg-time, results="asis"}
-fmt_ms <- function(x) {
-  n_seconds <- seconds_to_period(x)
-  sprintf("%02.0f:%02.0f", minute(n_seconds), second(n_seconds))
-}
-
-theme_ngos_table <- ttheme_minimal(
-  core = 
-    list(fg_params = 
-           list(hjust = 0, x = 0.1,
-                fontsize = 7, fontface = "plain",
-                fontfamily = "Roboto Condensed Light"),
-         bg_params = list(fill = "white")),
-  colhead = 
-    list(fg_params = 
-           list(hjust = 0, x = 0.1, col = "white",
-                fontsize = 7, fontface = "plain",
-                fontfamily = "Roboto Condensed Bold"),
-         bg_params = list(fill = ngo_cols("blue"))),
-  padding = unit(c(4, 2), "mm"))
-
 time_summary <- results %>% 
@@
   gather(Statistic, value) %>% 
-  mutate(Minutes = fmt_ms(value)) %>% 
+  mutate(Minutes = fmt_seconds(value)) %>% 
   select(-value)
@@
   geom_histogram(bins = 50, fill = ngo_cols("blue")) +
-  scale_x_time(labels = fmt_ms) +
+  scale_x_time(labels = fmt_seconds) +
   annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
@@
   print() %T>%
-  ggsave(., filename = here("output", "figures", "avg-time.pdf"),
+  ggsave(., filename = here("analysis", "output", "figures", "avg-time.pdf"),
          width = 4, height = 2.25, units = "in", device = cairo_pdf) %>% 
-  ggsave(., filename = here("output", "figures", "avg-time.png"),
+  ggsave(., filename = here("analysis", "output", "figures", "avg-time.png"),
          width = 4, height = 2.25, units = "in", type = "cairo", dpi = 300)

### 2019-03-08 analysis/index.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

--- 2018-07-19 index.Rmd
@@
 date: "Last run: `r format(Sys.time(), '%F')`"
-site: safesite::safesite
 ---

### 2019-03-08 R/compiled_models.R

@@ -1,0 +1,25 @@
+#' Stan models
+#' 
+#' Precompiled Stan models ready to be used with `rstan::sampling`
+#' 
+#' Instead of writing wrapper functions for these two models, we just provide them as precompiled models that we can then use on their own
+#' 
+#' @name compiled_models
+#' @md
+NULL
+
+#' @rdname compiled_models
+#'
+#' @export
+# This has to be wrapped in a function for some reason; just doing
+# stanmodels$donate_likely breaks and idk why
+donate_likely <- function() {
+  return(stanmodels$donate_likely)
+}
+
+#' @rdname compiled_models
+#'
+#' @export
+amount_donated_best <- function() {
+  return(stanmodels$amount_donated_best)
+}

### 2019-03-08 R/crackdownsphilanthropy-package.R

@@ -1,0 +1,17 @@
+#' The 'crackdownsphilanthropy' package.
+#' 
+#' @description A DESCRIPTION OF THE PACKAGE
+#' 
+#' @docType package
+#' @name crackdownsphilanthropy-package
+#' @aliases crackdownsphilanthropy
+#' @useDynLib crackdownsphilanthropy, .registration = TRUE
+#' @import methods
+#' @import Rcpp
+#' @import rstantools
+#' @importFrom rstan sampling
+#' 
+#' @references 
+#' Stan Development Team (2018). RStan: the R interface to Stan. R package version 2.18.2. http://mc-stan.org
+#' 
+NULL

### 2019-03-08 R/factor_quantiles.R

@@ -1,0 +1,48 @@
+#' Factor quantiles
+#' 
+#' Calculate the quantiles of factor variables.
+#' 
+#' @param x factor to calculate quantiles for
+#' @param probs numeric vector of probabilities
+#' 
+#' @source Borrowed from Jeffrey Arnold: \url{https://gist.github.com/jrnold/6759254}
+#' 
+#' @name factor_quantiles
+#' 
+#' @examples
+#' # Normal factors
+#' responses <- factor(c("Agree", "Agree", "Agree", "Disagree", "Disagree"))
+#' median(responses)
+#' quantile(responses, probs = c(0.25, 0.75))
+#' 
+#' # Ordered factors
+#' responses_ordered <- factor(c("Agree", "Agree", "Agree", "Disagree", "Disagree"),
+#'                             ordered = TRUE)
+#' median(responses_ordered)
+#' quantile(responses_ordered, probs = c(0.25, 0.75))
+#' 
+#' # In the case of ties, the first in order will win.
+#' with_ties <- factor(c("A", "A", "B", "B"), ordered = TRUE)
+#' median(with_ties)  # "A"
+NULL
+
+#' @rdname factor_quantiles
+#' @export
+quantile.ordered <- function(x, probs = seq(0, 1, 0.25)) {
+  tab <- table(x)
+  cdf <- cumsum(tab / sum(tab))
+  idx <- sapply(probs, function(p) min(which(cdf >= p)))
+  levels(x)[idx] 
+}
+
+#' @rdname factor_quantiles
+#' @export
+quantile.factor <- quantile.ordered
+
+#' @rdname factor_quantiles
+#' @export
+median.ordered <- function(x) quantile(x, 0.5)
+
+#' @rdname factor_quantiles
+#' @export
+median.factor <- median.ordered

### 2019-03-08 R/graphics.R

@@ -1,0 +1,258 @@
+# Colors ------------------------------------------------------------------
+
+# How to create custom palettes:
+# https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2
+#
+# Color palette adapted from ColorBrewer, diverging spectral, 5 categories
+# http://colorbrewer2.org/#type=diverging&scheme=Spectral&n=5
+#
+# library(RColorBrewer)
+# RColorBrewer::brewer.pal(5, "Spectral")
+
+#' Hex codes for colors used in project
+#' 
+#' @export
+ngo_colors <- c(
+  `red`         = "#D7191C",
+  `orange`      = "#FDAE61",
+  `yellow`      = "#FFFFBF",
+  `green`       = "#ABDDA4",
+  `blue`        = "#2B83BA",
+  `light grey`  = "grey80",
+  `dark grey`   = "grey10"
+)
+
+#' Function to extract NGO colors as hex codes
+#'
+#' @param ... Character names of ngo_colors 
+#'
+#' @export
+ngo_cols <- function(..., name = TRUE) {
+  cols <- c(...)
+  
+  if (is.null(cols)) {
+    return(ngo_colors)
+  }
+  
+  if (name) {
+    ngo_colors[cols]
+  } else {
+    unname(ngo_colors[cols])
+  }
+}
+
+#' Palette definitions
+#'
+#' @export
+ngo_palettes <- list(
+  `main`    = ngo_cols("green", "blue", "red", "orange", "yellow"),
+  `ordered` = ngo_cols("red", "orange", "yellow", "green", "blue"),
+  `cool`    = ngo_cols("blue", "green", "yellow"),
+  `hot`     = ngo_cols("red", "orange", "yellow"),
+  `grey`    = ngo_cols("light grey", "dark grey")
+)
+
+#' Return function to interpolate a NGO color palette
+#'
+#' @param palette Character name of palette in ngo_palettes
+#' @param reverse Boolean indicating whether the palette should be reversed
+#' @param ... Additional arguments to pass to colorRampPalette()
+#'
+#' @export
+ngo_pal <- function(palette = "main", reverse = FALSE, ...) {
+  pal <- ngo_palettes[[palette]]
+  
+  if (reverse) pal <- rev(pal)
+  
+  colorRampPalette(pal, ...)
+}
+
+#' Color scale constructor for NGO colors
+#'
+#' @param palette Character name of palette in ngo_palettes
[…]

### 2019-03-08 R/pop_prop_stan.R

@@ -1,0 +1,18 @@
+#' pop_prop_stan
+#' 
+#' Compare the proportion of a characteristic in a sample with a population-level proportion.
+#' 
+#' @param x Number of observations in sample with characteristic
+#' @param n_total Number of observations in sample
+#' @param pop_prop Population proportion to compare with (x / n_total)
+#' @param ... Arguments passed to `rstan::sampling` (e.g. iter, chains).
+#' 
+#' @export
+#' 
+#' @return An object of class `stanfit` returned by `rstan::sampling`
+#'
+pop_prop_stan <- function(x, n_total, pop_prop, ...) {
+  standata <- list(x = x, n_total = n_total, pop_prop = pop_prop)
+  out <- rstan::sampling(stanmodels$compare_pop_prop, data = standata, ...)
+  return(out)
+}

### 2019-03-08 R/stanmodels.R

@@ -1,0 +1,37 @@
+# Part of the crackdownsphilanthropy package for estimating model parameters
+# Copyright (C) 2015, 2016, 2017 Trustees of Columbia University
+# 
+# This program is free software; you can redistribute it and/or
+# modify it under the terms of the GNU General Public License
+# as published by the Free Software Foundation; either version 3
+# of the License, or (at your option) any later version.
+# 
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+# 
+# You should have received a copy of the GNU General Public License
+# along with this program; if not, write to the Free Software
+# Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301, USA.
+
+# This file is only intended to be used during the installation process
+# nocov start
+MODELS_HOME <- "src"
+if (!file.exists(MODELS_HOME)) MODELS_HOME <- sub("R$", "src", getwd())
+
+stan_files <- dir(file.path(MODELS_HOME, "stan_files"),
+                  pattern = "stan$", full.names = TRUE)
+stanmodels <- lapply(stan_files, function(f) {
+  model_cppname <- sub("\\.stan$", "", basename(f))
+  stanfit <- rstan::stanc(f, allow_undefined = TRUE, 
+                          obfuscate_model_name = FALSE)
+  stanfit$model_cpp <- list(model_cppname = stanfit$model_name, 
+                            model_cppcode = stanfit$cppcode)
+  return(do.call(methods::new, args = c(stanfit[-(1:3)], Class = "stanmodel", 
+                 mk_cppmodule = function(x) get(paste0("model_", model_cppname)))))
+  }
+)
+names(stanmodels) <- sub("\\.stan$", "", basename(stan_files))
+rm(MODELS_HOME)
+# nocov end

### 2019-03-08 R/summary_table.R

@@ -1,0 +1,120 @@
+#' Generate a summary table with sparkgraphs
+#' 
+#' Create a fancy summary Markdown table for numeric and factor variables with tiny ggplot sparkgraphs
+#' 
+#' @name summary_table
+NULL
+
+my_as_numeric <- function(x) {
+  is_num <- suppressWarnings(!any(is.na(as.numeric(x))))
+  
+  if (is_num) {
+    as.numeric(x)
+  } else {
+    x
+  }
+}
+
+level_summary <- function(x, variable, df) {
+  variable <- as.character(variable)
+  if (is.factor(df[[variable]])) {
+    x_levels <- levels(df[[variable]])
+  } else {
+    x_levels <- unique(df[[variable]])
+  }
+  
+  factor_summary <- tibble(x) %>% 
+    count(x) %>%
+    mutate(pct = n / sum(n),
+           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
+           x = factor(x, levels = x_levels, ordered = TRUE)) 
+  
+  inline_summary <- factor_summary %>% arrange(x) %>% 
+    pull(fancy) %>% paste(collapse = " | ")
+  
+  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
+    geom_bar(stat = "identity", fill = "grey50") +
+    theme_spark()
+  
+  file_name <- gsub("\\.| ", "_", tolower(variable))
+  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")
+  
+  ggsave(fig_bar, filename = here("analysis", "output", "figures", "summary-table",
+                                  paste0(file_name, ".pdf")), 
+         width = 1, height = 0.2, device = cairo_pdf)
+  ggsave(fig_bar, filename = here("analysis", "output", "figures", "summary-table",
+                                  paste0(file_name, ".png")), 
+         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)
+  
+  output <- tibble(spark = md_img, summary = inline_summary)
+  return(output)
+}
+
+numeric_summary <- function(x, variable) {
+  inline_summary <- paste0("Median: ", round(median(x, na.rm = TRUE), 2),
+                           " | Mean: ", round(mean(x, na.rm = TRUE), 2), 
+                           " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2))
+  
[…]

### 2019-03-08 lib/graphics.R

@@ -1,150 +1,0 @@
-# ggplot themes -----------------------------------------------------------
-
-theme_spark <- function() {
-  theme(line = element_blank(), rect = element_blank(), text = element_blank(), 
-        panel.border = element_blank(),
-        panel.background = element_rect(fill = "transparent", color = NA),
-        plot.background = element_rect(fill = "transparent", color = NA),
-        plot.margin = unit(c(0, 0, -0.25, -0.25), "lines"))
-}
-
-theme_ngos <- function(base_size = 11, base_family = "Roboto Condensed Light", density = FALSE) {
-  update_geom_defaults("label", list(family = "Roboto Condensed Light", face = "plain"))
-  update_geom_defaults("text", list(family = "Roboto Condensed Light", face = "plain"))
-  
-  ret <- theme_bw(base_size, base_family) +
-    theme(plot.title = element_text(size = rel(1.4), face = "plain",
-                                    family = "Roboto Condensed Bold"),
-          plot.subtitle = element_text(size = rel(1), face = "plain",
-                                       family = "Roboto Condensed Light"),
-          plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
-                                      family = "Roboto Condensed Light",
-                                      margin = margin(t = 10)),
-          plot.tag = element_text(size = rel(1), face = "plain", color = "grey50",
-                                  family = "Roboto Condensed Bold"),
-          strip.text = element_text(size = rel(0.8), face = "plain",
-                                    family = "Roboto Condensed Medium"),
-          strip.text.x = element_text(margin = margin(t = 1, b = 1)),
-          panel.border = element_blank(), 
-          strip.background = element_rect(fill = "#ffffff", colour = NA),
-          axis.ticks = element_blank(),
-          axis.title.x = element_text(margin = margin(t = 10)),
-          legend.margin = margin(t = 0),
-          legend.title = element_text(size = rel(0.8)),
-          legend.position = "bottom")
-  
-  if (density) {
-    ret <- ret +
-      theme(panel.grid = element_blank(),
-            axis.title.y = element_blank(),
-            axis.text.y = element_blank(),
[…]

### 2019-03-08 lib/modeling.R

@@ -1,141 +1,0 @@
-# Stan details ------------------------------------------------------------
-
-CHAINS <- 4
-ITER <- 4000
-WARMUP <- 2000
-BAYES_SEED <- 1234
-options(mc.cores = parallel::detectCores())
-
-
-# Helper functions for comparing models -----------------------------------
-
-# Calculate the pairwise differences between columns
-# Adapted from http://stackoverflow.com/a/28187446/120898
-mcmc_pairwise_diffs <- function(chains) {
-  pair_names <- outer(colnames(chains), colnames(chains),
-                      paste, sep = " - ")
-  pairs_to_omit <- which(upper.tri(pair_names, diag = TRUE))
-  
-  mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
-                      function(x, y) chains[,x] - chains[,y]) %>% 
-    magrittr::set_colnames(., pair_names) %>% 
-    select(-pairs_to_omit) %>% 
-    as_data_frame()
-  
-  mcmc_pct_change <- outer(1:ncol(chains), 1:ncol(chains),
-                      function(x, y) (chains[,x] - chains[,y]) / chains[,y]) %>% 
-    magrittr::set_colnames(., pair_names) %>% 
-    select(-pairs_to_omit) %>% 
-    as_data_frame()
-  
-  return(list(mcmc_diffs = mcmc_diffs, mcmc_pct_change = mcmc_pct_change))
-}
-
-# Summarize the differences between MCMC pairs
-tidy_diffs <- function(diffs_pairs) {
-  pct_change_pairs <- diffs_pairs$mcmc_pct_change %>% 
-    gather(pair, value) %>% 
-    group_by(pair) %>% 
-    summarise(mean_pct_change = mean(value),
-              median_pct_change = median(value))
-  
-  mcmc_diffs_pairs <- diffs_pairs$mcmc_diffs %>% 
-    gather(pair, value) %>% 
-    group_by(pair) %>% 
-    summarise(mean = mean(value),
-              median = median(value),
-              q2.5 = quantile(value, probs = 0.025),
-              q5 = quantile(value, probs = 0.05),
-              q25 = quantile(value, probs = 0.25),
-              q75 = quantile(value, probs = 0.75),
-              q95 = quantile(value, probs = 0.95),
-              q97.5 = quantile(value, probs = 0.975),
-              p.greater0 = mean(value > 0),
-              p.less0 = mean(value < 0),
[…]

### 2019-03-08 lib/pander_options.R

@@ -1,9 +1,0 @@
-# Universal pandoc options ------------------------------------------------
-
-panderOptions("table.split.table", Inf)
-panderOptions("table.split.cells", Inf)
-panderOptions("missing", "")
-panderOptions("big.mark", ",")
-panderOptions("digits", 3)
-panderOptions("round", 3)
-panderOptions("table.alignment.default", "left")

### 2019-03-08 src/init.cpp

@@ -1,0 +1,20 @@
+// Generated by the rstantools package
+
+
+#include <R.h>
+#include <Rinternals.h>
+#include <R_ext/Rdynload.h>
+#include <R_ext/Visibility.h>
+#include <Rversion.h>
+
+
+static const R_CallMethodDef CallEntries[] = {
+  {NULL, NULL, 0}
+};
+
+
+void attribute_visible R_init_crackdownsphilanthropy(DllInfo *dll) {
+  // next line is necessary to avoid a NOTE from R CMD check
+  R_registerRoutines(dll, NULL, CallEntries, NULL, NULL);
+  R_useDynamicSymbols(dll, TRUE); // necessary for .onLoad() to work
+}

### 2019-03-08 README.Rmd
Add dual licensing details

@@
 
-**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))
 
-**Code :** See the [DESCRIPTION](DESCRIPTION) file
+**Code:** With only two exceptions, all the code is dual-licensed under the [MIT License](LICENSE.md) and [GPL 3](https://www.gnu.org/licenses/gpl-3.0.en.html).
+Two dependencies related to Stan compilation—[`R/stanmodels.R`](R/stanmodels.R) and [`tools/make_cc.R`](tools/make_cc.R)—are licensed as GPL 3 only, and we can't backwards-license them as only MIT.
+Additionally, any binary files generated by those files (i.e.
+the compiled Stan code) is inherently GPL-licensed, which also makes this entire project GPL-licensed in the end.
+But since we've dual-licensed pretty much everything else, you treat everything as MIT unless a file is explicitly GPL-only.
 
-**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+*(Here are a bunch of resources about the vagaries of mixing MIT and GPL licenses: [link](https://github.com/ropensci/unconf17/issues/32); [link](https://github.com/stan-dev/rstantools/issues/17); [link](https://opensource.stackexchange.com/questions/1640/if-im-using-a-gpl-3-library-in-my-project-can-i-license-my-project-under-mit-l))*
 

### 2019-03-09 manuscript/supplement.Rmd
Rmd-ify the manuscript and supplement
It's still not really actually running any R code yet, but it's all self contained now and doesn't require my messy network of dependencies to convert to HTML/docx/TeX

---
title: "Supplement to Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Supplement to Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Brigham Young University
  email: andrew_heiss@byu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---

<!-- supplement.md is generated from supplement.Rmd. Only edit the .Rmd file, *not* the .md file. -->

# Sample

## Recruitment

Experiment participants were recruited via Amazon Mechanical Turk (MTurk), an online crowdsourcing platform that has been extensively used in social science research in recent years. MTurk allows researchers to recruit participants to perform tasks such as filling out surveys and opinion polls, participating in experiments, or coding the content of documents. Researchers advertise their studies as a human intelligence task (HIT) on MTurk, and participants choose only those HITs that interest them, given the promised price and estimated duration of the task. We listed a link to our survey on MTurk on March 22–23, 2018, and offered participants \$0.75 for successfully completing the study. We estimated that the survey would take 5 minutes to complete and paid participants the equivalent of a \$9/hour wage. On average, participants completed the survey in 3 minutes and 20 seconds (see @fig:avg-time).

![Time spent on experiment](output/figures/avg-time.pdf){#fig:avg-time}

## Sample size

We used power analysis to determine our sample size: with the anticipation of finding a small effect size ($f^2 = 0.02$) at a 0.05 significance level with a power of 0.9, our target sample size was 527, which we then rounded up to 540 in case of error or noncompliance with the survey.

## Demographics and representativeness

MTurk has become an increasingly popular method for fielding survey experiments on cheap semi-representative national samples, though drawing definitive causal inference from convenience samples is not without issues. Previous research has found that MTurk workers tend to be more liberal, younger, and less racially diverse than the general US population [@CliffordJewellWaggoner:2015; @BerniskyHuberLenz:2012]. The results from our experiment generally mirror these findings. @tbl:exp-sample compares demographic characteristics of our sample with national averages from the US Census's Current Population Survey (CPS) [@IPUMS-CPS:2017]. For general demographic information, we use the 2017 Annual Social and Economic Supplement (ASEC) to the CPS. From 2002–2015, the CPS included a Volunteer Supplement every September, so we use 2015 data for data on volunteering and donating to charity. We do not show other respondent demographic details because we do not have good population-level data to compare our sample with. We could theoretically use Pew data to compare political preferences, but Pew collects data on party affiliation, while we collected data about respondents' ideological positions along a conservative–liberal spectrum, which makes the two variables incomparable.

```{r child = "output/tables/tbl-exp-sample.md"}
```

\newpage

As seen in @tbl:exp-sample, our sample is younger, wealthier, and more educated than national averages. This is to be expected, given previous findings about the characteristics of MTurk workers and given that our target population is the portion of Americans willing to give money to charities online, which implies access to technology and disposable income. Our sample self-reports high levels of charitable giving: 82% said they donate at least once a year, while only 49% donate to charity in the previous year nationally. There are several possible explanations for this discrepancy. First, there are differences in the wording of our question and CPS's question—we ask how often respondents typically donate, while CPS asks if respondents have donated (or not) in the past 12 months. Second, respondents were primed and knew that the survey was related to NGOs, and thus might be displaying social desirability bias. Finally, some charitably-oriented respondents may have self-selected into the survey, given that the title listed on MTurk mentioned international nonprofit organizations. We are not overly concerned with these discrepancies, since we aimed our study at those who would be more inclined to donate online.

@tbl:descriptive-stats provides summary statistics for all the variables we collected in our survey.

\stgroup

\renewcommand*{\arraystretch}{1.75}

```{r child = "output/tables/tbl-descriptive-stats.md"}
```

\fingroup

# Experiment

## Preregistration

Prior to launching the survey, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/). We made two minor deviations from the original preregistration. First, in the *text* of our preregistration, we only specified the non-nested versions of our hypotheses:

1. Donors will give more/be more likely to give to NGOs that face legal crackdowns abroad
2. Donors will give more/be more likely to give to NGOs working on humanitarian issues
3. Donors will give more/be more likely to give to NGOs that do not receive substantial funding from government sources

In our preregistered data analysis *plan*, however, we explained that we will test the interacted versions of the hypotheses (i.e. donors will give more to humanitarian NGOs facing legal crackdowns, etc.). This was an oversight—we inadvertently used overly simple (and incorrect) textual hypotheses, but correctly described the full analysis plan (using the correct, unstated, unstated hypotheses).

Second, in our preregistration plan, we declared that we would analyze our data with a series of three Bayesian linear regression models with increasing numbers of interaction terms. To find the effect of crackdown within issue area, for instance, we used a $\text{crackdown} × \text{issue}$ term, and to find the effect of crackdown conditioned on issue and funding we used a three-way $\text{crackdown} \times \text{issue} \times \text{funding}$ term. We then planned on reassembling the different coefficient and intercept terms to approximate the mean values in each combination of conditions. To simplify our analyses in this version of the paper, we estimated group means directly with Stan [@stan; @rstan; @r-project]. This approach provides the same results as the regression models with 2- and 3-way interaction terms, but is far simpler to interpret.

## Treatment assignments and CONSORT diagram

To help ensure the quality of the responses we received and filter out workers who try to get through the HIT as quickly as possible without reading the questions [@BerinskyMargolisSances:2014], we included two attention check questions in the experiment. The first check was the second question in the survey (Q1.3) and involved reading several sentences and following instructions to select specific responses. We designed this question to filter out shirking respondents. We included a second, simpler check later in the survey, to ensure that participants were still engaged (Q3.8). Only two participants did not pass this check.

@fig:consort uses a CONSORT diagram to show the assignment of participants to the eight different experimental conditions. We excluded participants that (1) did not participate in the experiment through MTurk and (2) failed either attention check.

\blandscape

![CONSORT diagram for experiment](output/figures/consort.pdf){#fig:consort}

\elandscape

\newpage

# Priors and models

We use two statistical models for measuring the effect of the crackdown condition on the likelihood of donating and the amount hypothetically donated. Because we measure likelihood of donation with a binary "Likely to donate" vs. "Not likely to donate" variable, we model the proportion of people responding that they would be likely to donate with a binomial distribution. We use a prior distribution of $\text{Beta}(5, 5)$ for $\theta$ to center the probability of responding positively at 50%. In more formal terms, we model this distribution as follows:

$$
\begin{aligned}
n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{total in group}}, \theta_{\text{group}}) &\text{[likelihood]}\\
\text{Difference} &= n_{\text{group 2}} - n_{\text{group 1}} &\text{[difference in proportions]} \\
n &: \text{Number likely to donate} \\
\\
\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of being likely to donate]}
\end{aligned}
$$

![Prior $\theta$ for binomial models](output/figures/prior-likely.pdf){#fig:prior-likely}

We estimate the mean amount donated in each condition (crackdown vs. no crackdown, humanitarian assistance vs. human rights issues, private vs. government funding) using a *t* distribution. Following @Kruschke:2013, we use an exponential distribution with a rate of 1/29 for the $\nu$ parameter; a normal distribution with the group mean and standard deviation of 10 to capture wider variability in how much respondents might donate for the $\mu$ parameter; and a $\text{Cauchy}(0, 1)$ distribution for the $\sigma$ parameter. In more formal terms, we use the following model and priors:

$$
\begin{aligned}
x_{\text{group 1, group 2}} &\sim \text{Student } t(\nu, \mu, \sigma) &\text{[likelihood]}\\
\text{Difference} &= x_{\text{group 2}} - x_{\text{group 1}} &\text{[difference in means]} \\
x &: \text{Mean amount donated} \\
\\
\nu &\sim \text{Exponential}(1 / 29) &\text{[prior normality]} \\
\mu_{\text{group 1, group 2}} &\sim \mathcal{N}(\bar{x}_{\text{group 1, group 2}}, 10) &\text{[prior donation mean per group]}\\
\sigma_{\text{group 1, group 2}} &\sim \text{Cauchy}(0, 1)&\text{[prior donation sd per group]}
\end{aligned}
$$

![Prior $\nu$, $\mu$, and $\sigma$ for amount models](output/figures/prior-amount.pdf){#fig:prior-amount}

We obtain the posterior distribution of each dependent variable with Markov Chain Monte Carlo (MCMC) sampling and simulate values from the joint posterior distribution of the coefficient parameters. We use Stan [@stan; @rstan; @r-project] to generate 4 MCMC chains with 4,000 iterations in each chain, 2,000 of which are used for warmup. We use the median values from the posterior distributions as point estimates and calculate credible intervals using the 95% highest posterior density.

\newpage

# Survey experiment

## Recruitment and payment

Title of Mechanical Turk HIT

:   "Survey on international nonprofit organizations (~ 5 minutes)"

HIT description

:   "We are conducting an academic survey about international nonprofit organizations and want to know your opinion about them. This survey will take roughly five minutes to complete."

Payment

:   Participants were paid \$0.75 for successfully completing the experiment, commensurate with a \$9/hour wage.

```{r child = "../analysis/text/experiment_blind.md"}
```

\newpage

### 2019-03-10 analysis/02_analysis.Rmd
Dynamically include all reported values!
\(•◡•)/ R Markdown! \(•◡•)/

@@
 
+# Save combined table for later use in manuscript
+tbl_likely_tidy %>% 
+  left_join(tbl_likely_probs, by = "title") %>% 
+  saveRDS(here("data", "derived_data", "results_models_likely.rds"))
+
 tbl_likely_1 <- tbl_likely_tidy %>% 
@@
 
+# Save combined table for later use in manuscript
+tbl_amounts_tidy %>% 
+  left_join(tbl_amounts_probs, by = "title") %>% 
+  saveRDS(here("data", "derived_data", "results_models_amount.rds"))
+
 tbl_amount_1 <- tbl_amounts_tidy %>% 

### 2019-03-10 manuscript/manuscript.Rmd
Dynamically include all reported values!
\(•◡•)/ R Markdown! \(•◡•)/

---
title: "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
  twitter: SuparnaChaudhry
- name: Andrew Heiss
  affiliation: Brigham Young University
  email: andrew_heiss@byu.edu
  url: https://www.andrewheiss.com/
  twitter: andrewheiss
date: "`r format(Sys.time(), '%B %e, %Y')`"
published: Please do not cite without permission.
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: false
title-page: true
abstract: >-
  State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries. Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO. We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs. Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues. We conclude by discussing the implications for the sustainability of NGOs working abroad. 
thanks: >-
  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input. We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance. This experiment received approval by the human subjects research committees at both Christopher Newport University (018.042) and Brigham Young University (E18104). We preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/dx973/>.
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Visiting Assistant Professor, Romney Institute of Public Service and Ethics, Brigham Young University. 
additional-info: Figures should appear in color online only, not in print.
correspondence: >-
  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of Political Science, Christopher Newport University, Newport News, VA 23606, 757-594-7821. Contact: suparna.chaudhry@cnu.edu
word-count: "3,998"
---

<!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->

```{r setup, include=FALSE}
library(tidyverse)
library(scales)
library(glue)
library(here)

# Formatting functions
tex_percent <- percent_format(accuracy = 0.1, suffix = "\\%")  # Escape for TeX
percent_0 <- percent_format(accuracy = 1)  # 5%
percent_1 <- percent_format(accuracy = 0.1)  # 5.5%
md_dollar <- dollar_format(prefix = "\\$")  # Escape for Markdown/TeX

# Load and clean data
likely <- readRDS(here("data", "derived_data", "results_models_likely.rds")) %>% 
  # Make LaTeXy versions of numbers
  mutate(delta = glue("$\\Delta = {x}$", x = tex_percent(theta_diff)),
         p_neq0 = glue("$p(\\Delta \\neq 0) = {x}$", x = round(p.diff.not0, 2))) %>% 
  # Simplify title
  mutate(title = str_replace_all(title, " \\| Crackdown", "")) %>% 
  # Add subscripts to funding and issue numbers
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Funding",
                        str_replace(., "Delta", "Delta_\\\\text{funding}"), .))) %>% 
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Issue",
                        str_replace(., "Delta", "Delta_\\\\text{issue}"), .)))

amount <- readRDS(here("data", "derived_data", "results_models_amount.rds")) %>% 
  # Make LaTeXy versions of numbers
  mutate(delta = glue("$\\Delta = {x}$", x = round(mu_diff, 2)),
         p_neq0 = glue("$p(\\Delta \\neq 0) = {x}$", x = round(p.diff.not0, 2))) %>% 
  # Simplify title
  mutate(title = str_replace_all(title, " \\| Crackdown", "")) %>% 
  # Add subscripts to funding and issue numbers
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Funding",
                        str_replace(., "Delta", "Delta_\\\\text{funding}"), .))) %>% 
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Issue",
                        str_replace(., "Delta", "Delta_\\\\text{issue}"), .)))

results <- readRDS(here("data", "derived_data", "results_clean.rds"))
```

In January 2011, the Egyptian uprisings presented an opportunity for domestic non-governmental organizations (NGOs) to leverage their knowledge and expertise to transform Egypt into a democratic state. However, just as NGOs began to take advantage of new levels of public engagement and civic freedoms, successive Egyptian governments passed laws restricting funding and advocacy by civil society. Subsequently, international donor agencies cut support for Egyptian NGOs out of concern that they would be accused of offering them illegal support [@Brechenmacher:2017]. Egypt is not alone in its non-violent crackdown on NGOs. India, Bolivia, Hungary, China, Russia, and others have required that funds to NGOs be routed through state-owned banks, mandated that funds cannot be used for political purposes, or prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].

These restrictive laws have had tangible consequences for NGOs worldwide. Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in restrictive countries [@Brechenmacher:2017]. In response to this dramatic shift in the NGO funding landscape, organizations have increasingly turned to individual private donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015]. In 2016, U.S. private philanthropy for international NGOs amounted to \$22.06 billion [@givingusa:2017].

Donor location poses a challenge for NGOs, however. Donations from local host-country *domestic* donors in repressive countries are unreliable and inconsistent. Citizens in many countries in the Global South often cannot effort to support local NGOs, may lack a culture of philanthropic giving, or may prefer to channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017]. Even when donors in repressive countries wish to donate to NGOs working in contentious areas, they are often deterred by dismal tax incentives, threats to take away business permits, or have a general fear of retribution [@HudsonInstitute:2015]. In some authoritarian contexts, legal or structural changes make it impossible or counter-productive to donate [@Baoumi:2016]. Accordingly, NGOs working abroad have increasingly sought out funds from *foreign* individual donors in countries with institutions and regulations better suited for philanthropy. Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing a large amount of resources and manpower to raise similar sums locally [@RonKairePandya:2018]. Given increased crackdown on NGOs across the world, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors' decision to donate?

**NEED TO MAKE THIS PUNCHIER**: Our results show that the domestic political and legal environments of NGO host countries can influence the preferences of foreign private donors. In general, crackdowns do not have a strong effect on the preferences of foreign private donors: donors are only substantially more likely to donate to privately funded human rights NGOs facing legal trouble. However, we find that already-likely donors tend to give more to legally restricted NGOs, on average donating `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more when NGOs face crackdown, `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs, and `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)` more to government-funded humanitarian NGOs.

# Theory and hypotheses

We investigate these questions by exploring the structural determinants of private philanthropy. Substantial research has looked at the private motivations of donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011]. The decision to donate to an NGO is rarely rational, however [@Tremblay-BoirePrakash:2017]. In theory, perfectly rational donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation. Instead, research has shown that donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs. These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009]. In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness we argue that deeper structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@Rajan:2009; @CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].

We propose that nature of the legal and regulatory relationship between international NGOs and their host governments can also serve as a structural signal to donors of NGO trustworthiness and deservingness. NGO-related legislation is not inherently restrictive. Governments frequently use regulations to routinize the behavior of NGOs—regulations produce convergent practices [@BloodgoodTB, 145], prevent malfeasance that threatens to undermine confidence in the entire NGO community [@GibelmanGelman; @ONeill2009], and help improve NGO access to the policy-making process [@Teets:2014]. Here, however, we focus on the impact of restrictive regulations or anti-NGO laws. Unlike regulations aimed at standardizing state–NGO relations, these laws are designed to limit the NGO community by creating deliberate barriers to their entry, funding, and advocacy. These laws can even limit organizations who comply with regulations regarding registration, auditing, and transparency.

The legal threats that NGOs face in their host countries serve as yet another donor heuristic. Heavy legal restrictions could convey to donors that NGOs undertake important work, which is why governments perceive them as threatening. Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:

> **H~1a~**:  If NGOs face legal crackdowns abroad, individual donors will be more likely to donate to them.
> 
> **H~1b~**:  If NGOs face legal crackdowns abroad, individual donors will donate more to them.

@fig:causal-path represents this relationship more formally [@Pearl:2019]. Legal crackdowns (**C**) have a direct effect on donor outcomes (**Y**; likelihood and amount of donation) because of their heuristic function. Legal crackdowns do not occur in isolation, however. Countries are more likely to legally restrict NGOs when organizational missions are in tension in with government preferences and when organizations receive substantial money from abroad [@Chaudhry:2016; @DPR:2015; @Heiss:2017]. These effects are represented in the figure as **F** (funding), and **I** (issue and programs). Each of these organizational characteristics increase the likelihood of crackdown, but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.

![Causal diagram showing causes of donor behavior. Y = likelihood of donation and amount donated; C = anti-NGO legal crackdown, I = NGO issue area, F = NGO funding source.](output/figures/causal-path.pdf){#fig:causal-path}

The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences—can influence donor behavior. Donors commonly support programs that have easily measurable goals and successes [@Bush:2015; @Kiai:2017]. NGOs working on regime-compatible issues such as service provision, health, education, and humanitarian relief rarely challenge the government. As such, their programmatic output is easily quantifiable and donors can see the results of their charity more readily.

In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes and are less compatible with their host governments. Accordingly, these NGOs are often viewed as politically motivated outsiders, due to their advocacy against state-sanctioned abuses and efforts to changing discriminatory policies and attitudes that threaten the rights of marginalized and unpopular groups [@Crowther:2015]. Thus, they run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted. Their programmatic effectiveness is also harder to measure and quantify. Further, donors may believe that it is more difficult to propagate human rights in the target country's society, which limits NGOs' ability to achieve their goals.

We thus hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, and directed towards the most deserving of need, and are more capable of producing short-term quantifiable results. As shorthand, we use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues:

> **H~2a~**:  If legally besieged NGOs work on humanitarian issues, individual donors will be more likely to donate to them.
> 
> **H~2b~**:  If legally besieged NGOs work on humanitarian issues, individual donors will donate more to them.

The *source of NGO funding* can also influence donor behavior. Government grants to NGOs can crowd out private funding and significant reductions in fundraising from private donors [@AndreoniPayne:2003]. In addition, donors may feel less inclined to contribute since the NGO does not need (or might not even typically accept) their donation, and since donors might perceive that their tax money already funds the organization. Further, government funding for NGOs can also potentially signal a lack of independence from the government. Organizations that receive substantial government funding frequently avoid programming that would question the government even if it is in line with their mission [@Stroup:2012]. In contrast, donors who see that organizations are privately funded will feel that they can also contribute and help.

Funding sources also have an effect on anti-legal crackdowns on NGOs (see @fig:causal-path), given that funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015]. As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness. Donors could punish government-funded NGOs that face restrictions, since legal trouble could further fuel donor mistrust, and since anti-NGO crackdowns are commonly based on fears of foreign intervention in domestic politics. Donors thus are more likely to donate more to NGOs that rely on private funding:

> **H~3a~**:  If legally besieged NGOs do not receive substantial funding from government sources, individual donors will be more likely to donate to them.
>
> **H~3b~**: If legally besieged NGOs do not receive substantial funding from government sources, individual donors will donate more to them.

# Methods

## Sample

We test these hypotheses with a between-subjects vignette-based survey experiment with participants recruited from Amazon's Mechanical Turk. Our target population is the portion of Americans hypothetically willing to donate money for human rights and humanitarian work abroad. Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples (see Tables S1 and S2 in the supplement).[^supp]

## Experimental treatments and outcomes

We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy. The vignette thus results in three manipulated variables: (1) crackdown vs. no crackdown, (2) humanitarian assistance vs. human rights, and (3) government funding vs. private funding. We used the International Rescue Committee (IRC) as our example international NGO because its work easily applies to each possible frame. IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donation, and IRC works in some countries that have passed anti-NGO laws, such as Egypt and Turkey, as well as countries with no such laws. We use a 2×2×2 between-subject factorial design, with participants randomly assigned to one of eight versions of the following vignette.

> The International Rescue Committee (IRC) focuses on *{humanitarian assistance for refugees | human rights for refugees}* *{and works in countries that have recently passed laws that harshly restrict nonprofit organizations | NOTHING}*. A substantial proportion of IRC's funding comes from *{government | private}* donors.

We collected two outcome measures, which we use as our main dependent variables: (1) how likely participants would be to donate to IRC (measured with a 5-point Likert scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100. For the ease of analysis, we collapse the likelihood question into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate. We also included a free response question for exploratory purposes, asking respondents to explain why they chose to donate the amount they indicated.

## Estimation

We test our first hypothesis by calculating the differences in the average likelihood to donate and the average amount donated across the crackdown vs. no crackdown condition. For our second and third hypotheses, in which we posit that this crackdown effect is mediated by issue and funding, we measure the same difference in means spread across both issue and funding conditions. For additional exploration of the effect of issue and funding, we also measure the effect of crackdown within all combinations of issue and funding conditions.

We use two Bayesian models to measure the effect of crackdown on the likelihood of donating and the amount hypothetically donated.[^priors] We model the proportion of respondents indicating they would likely donate as a binomial distribution:

$$
\begin{aligned}
n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{total in group}}, \theta_{\text{group}}) &\text{[likelihood]}\\
\Delta_n &= n_{\text{group 2}} - n_{\text{group 1}} &\text{[difference in proportions]} \\
n &: \text{Number likely to donate} \\
\\
\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of being likely to donate]}
\end{aligned}
$$

We estimate the mean amount donated in each condition using a *t* distribution [@Kruschke:2013]:

$$
\begin{aligned}
x_{\text{group 1, group 2}} &\sim \text{Student } t(\nu, \mu, \sigma) &\text{[likelihood]}\\
\Delta_x &= x_{\text{group 2}} - x_{\text{group 1}} &\text{[difference in means]} \\
x &: \text{Mean amount donated} \\
\\
\nu &\sim \text{Exponential}(1 / 29) &\text{[prior normality]} \\
\mu_{\text{group 1, group 2}} &\sim \mathcal{N}(\bar{x}_{\text{group 1, group 2}}, 10) &\text{[prior donation mean per group]}\\
\sigma_{\text{group 1, group 2}} &\sim \text{Cauchy}(0, 1)&\text{[prior donation sd per group]}
\end{aligned}
$$

To account for uncertainty in the aggregated estimates from these models, we base our inference on the posterior distributions of the modeled estimates. We use the median values from the posterior distributions as point estimates and calculate credible intervals using the 95% highest posterior density. We declare an effect statistically significant if the posterior probability of being different from zero is larger than 0.95 [@KruschkeLiddell:2018]. Because differences can be either positive or negative (i.e. in some frames, the crackdown condition causes greater donations; in others it causes fewer donations), we report the probability that the difference is not equal to zero. When the median value is negative, we report the proportion of predicted values that are negative, and when the median value is positive, we report the proportion of values that are positive.

# Results

## Likelihood of donation

Without looking within issue or funding conditions, we find that respondents are not significantly more likely to donate to legally besieged international NGOs (H~1a~). As seen in @fig:likely-diffs(A), those exposed to the crackdown condition tend to have a slightly higher probability of donating (`r percent_1(filter(likely, title == "Crackdown")$theta_2)`) than those in the control condition (`r percent_1(filter(likely, title == "Crackdown")$theta_1)`), but the difference is not significant (`r filter(likely, title == "Crackdown")$delta`; `r filter(likely, title == "Crackdown")$p_neq0`). We find similar results when looking at the isolated effects of issue area and funding. Both differences are positive, but the posterior probability of being larger than zero is low (`r filter(likely, title == "Issue")$delta`; `r filter(likely, title == "Issue")$p_neq0`; `r filter(likely, title == "Funding")$delta`; `r filter(likely, title == "Funding")$p_neq0`). We thus do not initially find evidence to support our hypothesis that crackdowns (or issue or funding) alone increase the likelihood of donating.

![Difference in likelihood of donation across crackdown and no crackdown groups, conditioned by other experimental frames](output/figures/likely-diffs.pdf){#fig:likely-diffs}

```{r child = "output/tables/tbl-likely-diffs.md"}
```

@fig:likely-diffs(B–C) shows the difference in donation likelihood for both crackdown conditions across NGO issue areas (H~2a~) and funding sources (H~3a~). Crackdown has almost no effect on the likelihood of donating to human rights NGOs (`r filter(likely, title == "Human rights")$p_neq0`). We hypothesized that the positive crackdown effect would be stronger for humanitarian NGOs, and while crackdown does have a positive effect on under the humanitarian frame, the probability this difference is greater than zero is below our 95% threshold (`r filter(likely, title == "Humanitarian assistance")$p_neq0`). We do find some evidence for H~3a~, however. Crackdown has little effect on the likelihood of donating to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).

While the crackdown frame had no effect on the probability of donating to human rights NGOs alone, conditioning this finding on the source of NGO funding uncovers competing trends. @fig:likely-diffs(D) shows difference in donation likelihood across all three experimental conditions. When individual donors know that a human rights organization receives the majority of its funding from the government, they are more likely (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`) to donate in the *absence* of crackdowns than when the NGO faces legal difficulties. In contrast, when donors know that an organization receives most of its funding from private sources, they are more likely (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`) to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles. For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting funding and issue frames.

These results give partial support to H~3a~. The source of funding has little influence on the propensity to donate to humanitarian NGOs, but on average, donors are substantially more likely to give to privately-funded human rights NGOs than government-funded organizations. However, the effect of crackdowns reverses across conditions, as donors appear to both punish government-funded human rights NGOs that face legal difficulties and rally behind privately-funded NGOs facing those same hurdles. Many of the respondents described their reasoning for removing support for besieged government-funded organizations, explaining that "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others,"[^3154467] and that accordingly, they would be less likely to contribute. Others explained that they would decrease their donations to government-backed organizations because of the bad optics of legal crackdown, with one stating outright that "I'm not exactly sure what they did was right or wrong, I think it just seems bad, so I'm less likely to want to donate to them."[^8425616]

While donors on average appear to punish government-funded human rights organizations, they increase their support to privately funded NGOs. Many respondents explained their motivation for being more likely to donate in moralistic, normative terms, reasoning that "[s]ince I was small child my parents thought [sic] me to help others,"[^6009603] or "I would want to do the right thing."[^9526638] Another explained "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.

## Amount donated

Crackdowns do not substantially influence donors' *likelihood* to donate, but they do increase the *amount* of money that respondents are willing to contribute (see @fig:amount-diffs(A)). Informing participants that IRC faces legal hurdles abroad increased donations by `r md_dollar(filter(amount, title == "Crackdown")$mu_diff)` on average, a `r percent_0(filter(amount, title == "Crackdown")$pct_change)` increase from the no crackdown condition (`r filter(amount, title == "Crackdown")$p_neq0`). This provides good evidence for H~1b~—donors appear to give more money to besieged international NGOs. In contrast, neither issue area nor funding have an effect on the amount donated (`r filter(amount, title == "Issue")$delta`; `r filter(amount, title == "Issue")$p_neq0`; `r filter(amount, title == "Funding")$delta`; `r filter(amount, title == "Funding")$p_neq0`), indicating that crackdown is a more powerful heuristic for determining private donations.

![Difference in amount donated across crackdown and no crackdown groups, conditioned by other experimental frames](output/figures/amount-diffs.pdf){#fig:amount-diffs}

```{r child = "output/tables/tbl-amount-diffs.md"}
```

This trend also holds true when accounting for the issue area of the NGO. As seen in @fig:amount-diffs(B–C), the crackdown condition elicits higher donations for both the human rights and humanitarian assistance conditions, though with varying levels of significance. Emphasizing legal crackdown increased donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)` above the no crackdown condition, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`). In contrast, crackdowns significantly boosted donations to humanitarian assistance NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`). We thus find support for H~2b~: donors give more to besieged humanitarian NGOs. In general, informing donors about crackdowns causes them to give more to humanitarian NGOs facing legal difficulties abroad. We also find evidence for H~3b~. Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`).

Finally, combining issue and funding sources adds more texture to these results. We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they run into legal issues. This finding also applies somewhat to the amount donors give. Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`. Anecdotally, many of the respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).

Emphasizing legal difficulties increased donations to government-funded humanitarian assistance NGOs by `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)`, or `r md_dollar(abs(filter(amount, title == "Humanitarian assistance | Government")$mu_diff))` (`r filter(amount, title == "Humanitarian assistance | Government")$p_neq0`). The crackdown condition caused this increase despite some notable hesitation from respondents, many of whom felt that government-backed NGOs do not need or deserve private donations. Respondents reasoned since IRC "is already receiving funding from governments, so funding from private individuals doesn't seem as necessary. I'd prefer to give my money to an organization that is primarily run by private donations"[^6486084] or because "[m]y tax paying dollars go to the government and if the government is helping to fund it then they are in turn getting some of my money."[^9509936] This hesitation was not universal, however, and in aggregate most respondents chose to give substantially more. Many echoed this respondent, who identified the crackdown condition as one of the reasons for giving the full hypothetical \$100: "I believe the work of such organizations has an urgency that affects many refugees and their families. If they can function without being affected by the harsh laws against non-profits, I would want them to have as much help as possible to do their humanitarian work."[^1097165]

In contrast, crackdowns had no substantial effect on the amount donated to privately-funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`). None of the respondents in these conditions mentioned funding sources when justifying their giving, and many explained that they would not give solely on the basis of the legal crackdown, including one who stated that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations. For instance, donors might assume that an international NGO that receives substantial money from USAID would ostensibly have the backing and support of the U.S. government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges. Further research is needed to probe this trend.

# Conclusion

Over the last three decades, dozens of countries have used legal restrictions to limit international NGO funding and programming. Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors for their funding. But how do these donors respond to anti-NGO legal restrictions, and how do an organization's issue area and funding sources interact with these restrictions? In this study, propose that legal crackdowns on NGOs can serve as a heuristic or signal to donors of the deservingness and efficiency of NGO programming. We find that crackdowns, funding, and issue area do not directly influence the *likelihood* of donation on their own. Donors are more likely to give to privately funded NGOs facing legal crackdown, however, and are more likely to do so when those organizations focus on human rights issues. Donors appear to punish government-funded human rights organizations that face crackdown and are less likely to support them. Crackdowns do, however, influence the *amount* that donors give. Respondents indicated a willingness to donate substantially more to NGOs facing legal restrictions, and this effect persists when mediated by issue area and funding—respondents give more to restricted humanitarian NGOs and privately funded NGOs. For human rights NGOs, those funded through private donations see increased donations under legal crackdown, while donors again appear to punish those that rely on government funding.

This study makes two important contributions. While recent work has looked at how state repression of NGOs affects official aid flows [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how such repression affects private aid flows. Further, prior literature on the determinants of donation to NGOs predominantly focuses on individual-level factors. Our study measures important structural determinants that influence giving and shows how these factors interact with organizational attributes to signal NGO deservingness. Additional research should determine the extent to which these preferences translate into action—here, we have only asked respondents to make a hypothetical donation—as well as test the generalizability of our findings to other issue areas.

Our results have several implications for policy and future research. NGOs may actually benefit from publicizing when they are targets of government crackdown. While this may not be enough to sway the average U.S. citizen, our results show that communicating this information can convince already-likely donors to donate more to besieged groups. Our study also highlights the importance of framing issue areas. {{TODO: Donors are likely to view legally besieged human rights NGOs with suspicion. This framing is critical, as previous research on human rights micromobilization has shown that the way people process information can affect their increased willingness to help others in need [@SmallLoewensteinSlovic:2007; @Slovic:2007]. However, human rights groups undertake a variety of programs and missions, and communicating the nature of their work and specifying the main target of the organization's efforts can allay the public's fears.}} Finally, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown. Moreover, since private funders tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.

With increasing government repression of NGOs, these groups can no longer rely on a single funding source. However, these new and challenging scenarios create an opportunity for NGOs to rethink how to address different audiences and create a robust market for philanthropy towards besieged NGOs abroad.

[^supp]: Figures and tables in the supplement are prefixed with "S." Complete details about our sample (Table SX), our power analysis, and treatment assignment balance (Figure S2) are included in the supplement.

[^priors]: The "Priors" section in the supplement provides complete details about our prior choices and computational choices.

[^3154467]: Response 3154467.

[^8425616]: Response 8425616.

[^6009603]: Response 6009603.

[^9526638]: Response 9526638.

[^13685]: Response 13685.

[^3025921]: Response 3025921.

[^6486084]: Response 6486084.

[^9509936]: Response 9509936.

[^1097165]: Response 1097165.

[^8995923]: Response 8995923.

### 2019-03-10 README.Rmd
Add correct instructions

@@
 Title <- "The effect of NGO crackdowns on individual philanthropy"
+Authors <- "Suparna Chaudhry and Andrew Heiss"
+Year <- "2019"
 ```
@@
 
-### Abstract
+## Abstract
 
@@
 
-This repository contains the data and code for our paper:
+This repository contains the data and code for our paper. Our pre-print is online here:
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>
+> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>
 
-Our pre-print is online here:
-
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-
-### How to cite
+## How to cite
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>
 
-### How to download or install
+## How to download and install
 
-You can download the compendium as a zip from from this URL: </archive/master.zip>
+You can either [download the compendium as a ZIP file](/archive/master.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).
 
-Or you can install this compendium as an R package, testingthing, from GitHub with:
+In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:
 
-```r
-pkgbuild::compile_dll()
-```
+1. Open the compendium as a project in RStudio (double click on `crackdownsphilanthropy.proj`).
+2.
+Install the **pkgbuild**, **devtools**, **rstan**, and **rstantools** packages, either with RStudio's "Packages" panel or by running `install.packages(c("pkgbuild", "devtools", "rstan", "rstantools"))`
+3.
+Due to [strange](https://github.com/stan-dev/rstantools/issues/52) [incompatibilties](https://github.com/klutometis/roxygen/issues/822#issuecomment-441425591) with **roxygen2** and **rstantools**, you need to compile the Stan C++ binary DLLs before building the actual **crackdownsphilanthropy** compendium package.
+Run `pkgbuild::compile_dll()` and wait a few minutes while the Stan models are built.
+4. Finally, build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.
 
-### Licenses
+You should now be able to run `library(crackdownsphilanthropy)` and reproduce all the findings in the paper (as well as the paper itself).
+
+To reproduce the analysis, run `make build` from RStudio's "Terminal" panel. Open `analysis/_site/` to see the results. Run `make serve` to serve the site at <http://localhost:7000>.
+
+To repdocuce the paper, run `make html` or `make tex` or `make docx` or `make paper` (for all three output formats) from the terminal.
+Open `manuscript/` (or `manuscript/tex_out/` for PDFs) to see the results.
+
+## Licenses
 
@@
 
-### Contributions
+## Contributions
 

### 2019-03-10 README.Rmd
Add OSF DOI

@@
 )
-# Please put your title here to include it in the file below. 
+
 Title <- "The effect of NGO crackdowns on individual philanthropy"
@@
 
-# The effect of NGO crackdowns on individual philanthropy
+# `r Title`
 
@@
 
-> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>
+> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org/10.17605/OSF.IO/FG53W>
 
@@
 
-> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>
+> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org/10.17605/OSF.IO/FG53W>
 

### 2019-03-12 manuscript/manuscript.Rmd
More shrinking

@@
 
-In January 2011, the Egyptian uprisings presented an opportunity for domestic non-governmental organizations (NGOs) to leverage their knowledge and expertise to transform Egypt into a democratic state.
-However, just as NGOs began to take advantage of new levels of public engagement and civic freedoms, successive Egyptian governments passed laws restricting funding and advocacy by civil society.
-Subsequently, international donor agencies cut support for Egyptian NGOs out of concern that they would be accused of offering them illegal support [@Brechenmacher:2017].
+In January 2011, the Egyptian uprisings presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state.
+However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
 Egypt is not alone in its non-violent crackdown on NGOs.
-India, Bolivia, Hungary, China, Russia, and others have required that funds to NGOs be routed through state-owned banks, mandated that funds cannot be used for political purposes, or prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].
+India, Bolivia, Hungary, China, Russia, and others have mandated that funds cannot be used for political purposes, or prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].
 
-These restrictive laws have had tangible consequences for NGOs worldwide.
+These restrictive laws have tangible consequences for NGOs worldwide.
 Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in restrictive countries [@Brechenmacher:2017].
@@
 Donor location poses a challenge for NGOs, however.
-Donations from local host-country *domestic* donors in repressive countries are unreliable and inconsistent.
-Citizens in many countries in the Global South often cannot effort to support local NGOs, may lack a culture of philanthropic giving, or may prefer to channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
-Even when donors in repressive countries wish to donate to NGOs working in contentious areas, they are often deterred by dismal tax incentives, threats to take away business permits, or have a general fear of retribution [@HudsonInstitute:2015].
+Donations from *domestic* donors in repressive countries are unreliable and inconsistent.
+Citizens in many countries in the Global South often cannot support local NGOs, may lack a culture of philanthropic giving, or may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
+Even when donors in repressive countries prefer to donate to NGOs working in contentious areas, they may be deterred by dismal tax incentives, threats to take away business permits, or have a general fear of retribution [@HudsonInstitute:2015].
 In some authoritarian contexts, legal or structural changes make it impossible or counter-productive to donate [@Baoumi:2016].
-Accordingly, NGOs working abroad have increasingly sought out funds from *foreign* individual donors in countries with institutions and regulations better suited for philanthropy.
+Accordingly, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions and regulations better suited for philanthropy.
 Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing a large amount of resources and manpower to raise similar sums locally [@RonKairePandya:2018].
@@
 We investigate these questions by exploring the structural determinants of private philanthropy.
-Substantial research has looked at the private motivations of donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
+Substantial research has looked at the private motivations of donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @BekkersWiepking:2011].
 The decision to donate to an NGO is rarely rational, however [@Tremblay-BoirePrakash:2017].
@@
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
-In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness we argue that deeper structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@Rajan:2009; @CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
+In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness we argue that structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
 
-We propose that nature of the legal and regulatory relationship between international NGOs and their host governments can also serve as a structural signal to donors of NGO trustworthiness and deservingness.
+We propose that nature of the legal and regulatory relationship between international NGOs and their host governments can serve as a signal of NGO trustworthiness and deservingness.
 NGO-related legislation is not inherently restrictive.
-Governments frequently use regulations to routinize the behavior of NGOs—regulations produce convergent practices [@BloodgoodTB, 145], prevent malfeasance that threatens to undermine confidence in the entire NGO community [@GibelmanGelman; @ONeill2009], and help improve NGO access to the policy-making process [@Teets:2014].
+Governments frequently use regulations to routinize the behavior of NGOs—regulations produce convergent practices [@BloodgoodTB, 145] and help improve NGO access to the policy-making process [@Teets:2014].
 Here, however, we focus on the impact of restrictive regulations or anti-NGO laws.
@@
 
-> **H~1a~**:  If NGOs face legal crackdowns abroad, individual donors will be more likely to donate to them.
+> **H~1a~**:  If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
 > 
-> **H~1b~**:  If NGOs face legal crackdowns abroad, individual donors will donate more to them.
+> **H~1b~**:  If NGOs face legal crackdowns abroad, then individual donors will donate more to them.
 
@@
 
-In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes and are less compatible with their host governments.
-Accordingly, these NGOs are often viewed as politically motivated outsiders, due to their advocacy against state-sanctioned abuses and efforts to changing discriminatory policies and attitudes that threaten the rights of marginalized and unpopular groups [@Crowther:2015].
-Thus, they run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted.
-Their programmatic effectiveness is also harder to measure and quantify.
-Further, donors may believe that it is more difficult to propagate human rights in the target country's society, which limits NGOs' ability to achieve their goals.
+In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes.
+Therefore, these INGOs are often viewed as politically motivated outsiders and they run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted.
+Due to the nature of the political and social issues they work on, their programmatic effectiveness is also harder to measure and quantify [@Bush:2015].
+Thus, donors may believe that it is more difficult to improve respect for human rights in the target country, which limits NGOs' ability to achieve their goals.
 
@@
 
-> **H~2a~**:  If legally besieged NGOs work on humanitarian issues, individual donors will be more likely to donate to them.
+> **H~2a~**:  If legally besieged NGOs work on humanitarian issues, then individual donors will be more likely to donate to them.
 > 
-> **H~2b~**:  If legally besieged NGOs work on humanitarian issues, individual donors will donate more to them.
+> **H~2b~**:  If legally besieged NGOs work on humanitarian issues, then individual donors will donate more to them.
 
 The *source of NGO funding* can also influence donor behavior.
-Government grants to NGOs can crowd out private funding and significant reductions in fundraising from private donors [@AndreoniPayne:2003].
+Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003].
 In addition, donors may feel less inclined to contribute since the NGO does not need (or might not even typically accept) their donation, and since donors might perceive that their tax money already funds the organization.
@@
 As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
-Donors could punish government-funded NGOs that face restrictions, since legal trouble could further fuel donor mistrust, and since anti-NGO crackdowns are commonly based on fears of foreign intervention in domestic politics.
+Donors could punish government-funded NGOs that face restrictions, since legal trouble could further fuel private donor mistrust.
 Donors thus are more likely to donate more to NGOs that rely on private funding:
 
-> **H~3a~**:  If legally besieged NGOs do not receive substantial funding from government sources, individual donors will be more likely to donate to them.
+> **H~3a~**:  If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will be more likely to donate to them.
 >
-> **H~3b~**: If legally besieged NGOs do not receive substantial funding from government sources, individual donors will donate more to them.
+> **H~3b~**: If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will donate more to them.
 
@@
 However, the effect of crackdowns reverses across conditions, as donors appear to both punish government-funded human rights NGOs that face legal difficulties and rally behind privately-funded NGOs facing those same hurdles.
-Many of the respondents described their reasoning for removing support for besieged government-funded organizations, explaining that "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others,"[^3154467] and that accordingly, they would be less likely to contribute.
-Others explained that they would decrease their donations to government-backed organizations because of the bad optics of legal crackdown, with one stating outright that "I'm not exactly sure what they did was right or wrong, I think it just seems bad, so I'm less likely to want to donate to them."[^8425616]
-
-While donors on average appear to punish government-funded human rights organizations, they increase their support to privately funded NGOs.
-Many respondents explained their motivation for being more likely to donate in moralistic, normative terms, reasoning that "[s]ince I was small child my parents thought [sic] me to help others,"[^6009603] or "I would want to do the right thing."[^9526638] Another explained "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.
+Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.
 
@@
 
-This trend also holds true when accounting for the issue area of the NGO.
-As seen in @fig:amount-diffs(B–C), the crackdown condition elicits higher donations for both the human rights and humanitarian assistance conditions, though with varying levels of significance.
+This trend also holds true when accounting for NGO issue area.
+As seen in @fig:amount-diffs(B–C), the crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance.
 Emphasizing legal crackdown increased donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)` above the no crackdown condition, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`).
-In contrast, crackdowns significantly boosted donations to humanitarian assistance NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`).
+In contrast, crackdowns significantly boosted donations to humanitarian NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`).
 We thus find support for H~2b~: donors give more to besieged humanitarian NGOs.
-In general, informing donors about crackdowns causes them to give more to humanitarian NGOs facing legal difficulties abroad.
 We also find evidence for H~3b~.
@@
 
-Finally, combining issue and funding sources adds more texture to these results.
+Finally, combining issue areas and funding sources adds more texture to these results.
 We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they run into legal issues.
-This finding also applies somewhat to the amount donors give.
+This finding also applies to the amount donors give.
 Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`.
-Anecdotally, many of the respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).
+Respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).
 
-Emphasizing legal difficulties increased donations to government-funded humanitarian assistance NGOs by `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)`, or `r md_dollar(abs(filter(amount, title == "Humanitarian assistance | Government")$mu_diff))` (`r filter(amount, title == "Humanitarian assistance | Government")$p_neq0`).
+Emphasizing legal difficulties increased donations to government-funded humanitarian NGOs by `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)`, or `r md_dollar(abs(filter(amount, title == "Humanitarian assistance | Government")$mu_diff))` (`r filter(amount, title == "Humanitarian assistance | Government")$p_neq0`).
 The crackdown condition caused this increase despite some notable hesitation from respondents, many of whom felt that government-backed NGOs do not need or deserve private donations.
@@
 In contrast, crackdowns had no substantial effect on the amount donated to privately-funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`).
-None of the respondents in these conditions mentioned funding sources when justifying their giving, and many explained that they would not give solely on the basis of the legal crackdown, including one who stated that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations.
-For instance, donors might assume that an international NGO that receives substantial money from USAID would ostensibly have the backing and support of the U.S.
+No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations.
+For instance, donors might assume that an international NGO that receives substantial money from USAID would ostensibly have the support of the U.S.
 government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
@@
 
-Over the last three decades, dozens of countries have used legal restrictions to limit international NGO funding and programming.
+Over the last three decades, several countries have used legal restrictions to limit international NGO funding and programming.
 Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors for their funding.
-But how do these donors respond to anti-NGO legal restrictions, and how do an organization's issue area and funding sources interact with these restrictions?
-In this study, propose that legal crackdowns on NGOs can serve as a heuristic or signal to donors of the deservingness and efficiency of NGO programming.
+How do these donors respond to anti-NGO legal restrictions, and how do an organization's issue area and funding sources interact with these restrictions?
+In this study, we propose that legal crackdowns on NGOs can serve as a heuristic or signal to donors of the deservingness and efficiency of NGO programming.
 We find that crackdowns, funding, and issue area do not directly influence the *likelihood* of donation on their own.
 Donors are more likely to give to privately funded NGOs facing legal crackdown, however, and are more likely to do so when those organizations focus on human rights issues.
-Donors appear to punish government-funded human rights organizations that face crackdown and are less likely to support them.
 Crackdowns do, however, influence the *amount* that donors give.
@@
 Our study measures important structural determinants that influence giving and shows how these factors interact with organizational attributes to signal NGO deservingness.
-Additional research should determine the extent to which these preferences translate into action—here, we have only asked respondents to make a hypothetical donation—as well as test the generalizability of our findings to other issue areas.
+Additional research should determine the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation—as well as test the generalizability of our findings to other issue areas.
 
 Our results have several implications for policy and future research.
-NGOs may actually benefit from publicizing when they are targets of government crackdown.
+NGOs may benefit from publicizing when they are targets of government crackdown.
 While this may not be enough to sway the average U.S.
 citizen, our results show that communicating this information can convince already-likely donors to donate more to besieged groups.
-Our study also highlights the importance of framing issue areas.
-{{TODO: Donors are likely to view legally besieged human rights NGOs with suspicion.
-This framing is critical, as previous research on human rights micromobilization has shown that the way people process information can affect their increased willingness to help others in need [@SmallLoewensteinSlovic:2007; @Slovic:2007].
-However, human rights groups undertake a variety of programs and missions, and communicating the nature of their work and specifying the main target of the organization's efforts can allay the public's fears.}} Finally, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
-Moreover, since private funders tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.
-
-With increasing government repression of NGOs, these groups can no longer rely on a single funding source.
-However, these new and challenging scenarios create an opportunity for NGOs to rethink how to address different audiences and create a robust market for philanthropy towards besieged NGOs abroad.
+Our study also highlights the importance of framing NGO operations.
+Previous research on human rights micromobilization has shown that the way people process information can affect their increased willingness to help others in need [@Slovic:2007].
+Our results show that donors are likely to view legally besieged human rights NGOs with suspicion.
+However, human rights groups undertake a variety of programs, and communicating the nature of their work and specifying the main target of the organization's efforts can allay the public's fears.
+Finally, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
+Moreover, since private funders typically tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.
 

### 2019-03-12 manuscript/manuscript.Rmd
Minor edits

@@
 
-In January 2011, the Egyptian uprisings presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state.
+In January 2011, the Egyptian uprising presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state.
 However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
 Egypt is not alone in its non-violent crackdown on NGOs.
-India, Bolivia, Hungary, China, Russia, and others have mandated that funds cannot be used for political purposes, or prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].
+India, Bolivia, Hungary, China, Russia, and others have mandated that funds cannot be used for political purposes and prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].
 
@@
 In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes.
-Therefore, these INGOs are often viewed as politically motivated outsiders and they run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted.
+Therefore, these NGOs are often viewed as politically motivated outsiders and run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted.
 Due to the nature of the political and social issues they work on, their programmatic effectiveness is also harder to measure and quantify [@Bush:2015].
@@
 ```{r child = "output/tables/tbl-likely-diffs.md"}
+
 ```
@@
 ```{r child = "output/tables/tbl-amount-diffs.md"}
+
 ```
@@
 
-[^8425616]: Response 8425616.
-
-[^6009603]: Response 6009603.
-
-[^9526638]: Response 9526638.
-
 [^13685]: Response 13685.

### 2019-03-12 manuscript/manuscript.Rmd
MAJOR shrinkage

@@
 
-In January 2011, the Egyptian uprising presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state.
+The 2011 Egyptian uprising presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state.
 However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
 Egypt is not alone in its non-violent crackdown on NGOs.
-India, Bolivia, Hungary, China, Russia, and others have mandated that funds cannot be used for political purposes and prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].
-
-These restrictive laws have tangible consequences for NGOs worldwide.
+India, Bolivia, Hungary, China, Russia, and others have imposed funding and programmatic restrictions on NGOs  [@Carothers:2015; @DPR:2015].
+These laws have tangible consequences for NGOs worldwide.
 Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in restrictive countries [@Brechenmacher:2017].
 In response to this dramatic shift in the NGO funding landscape, organizations have increasingly turned to individual private donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015].
-In 2016, U.S.
-private philanthropy for international NGOs amounted to \$22.06 billion [@givingusa:2017].
 
-Donor location poses a challenge for NGOs, however.
 Donations from *domestic* donors in repressive countries are unreliable and inconsistent.
-Citizens in many countries in the Global South often cannot support local NGOs, may lack a culture of philanthropic giving, or may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
-Even when donors in repressive countries prefer to donate to NGOs working in contentious areas, they may be deterred by dismal tax incentives, threats to take away business permits, or have a general fear of retribution [@HudsonInstitute:2015].
-In some authoritarian contexts, legal or structural changes make it impossible or counter-productive to donate [@Baoumi:2016].
-Accordingly, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions and regulations better suited for philanthropy.
-Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing a large amount of resources and manpower to raise similar sums locally [@RonKairePandya:2018].
+Citizens in the Global South often cannot support local NGOs, may lack a culture of philanthropic giving, or may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
+Even when donors in repressive countries prefer to donate to NGOs working in contentious areas, they may be deterred by dismal tax incentives, threats to take away business permits, or a general fear of retribution [@HudsonInstitute:2015].
+NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
+Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing resources to raise similar sums locally [@RonKairePandya:2018].
+
 Given increased crackdown on NGOs across the world, how do individual donors in the U.S.
@@
 Do legal restrictions on NGOs influence donors' decision to donate?
-
-**NEED TO MAKE THIS PUNCHIER**: Our results show that the domestic political and legal environments of NGO host countries can influence the preferences of foreign private donors.
-In general, crackdowns do not have a strong effect on the preferences of foreign private donors: donors are only substantially more likely to donate to privately funded human rights NGOs facing legal trouble.
-However, we find that already-likely donors tend to give more to legally restricted NGOs, on average donating `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more when NGOs face crackdown, `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs, and `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)` more to government-funded humanitarian NGOs.
+We argue that domestic political environments of NGO host countries can influence preferences of foreign private donors and that legal crackdowns on NGOs serve as a heuristic to donors of organizational deservingness.
+We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
+This effect persists when mediated by other structural heuristics like NGO issue area and funding sources.
 
@@
 
-We investigate these questions by exploring the structural determinants of private philanthropy.
-Substantial research has looked at the private motivations of donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @BekkersWiepking:2011].
-The decision to donate to an NGO is rarely rational, however [@Tremblay-BoirePrakash:2017].
+The decision to donate to an NGO is rarely rational.
 In theory, perfectly rational donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation.
@@
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
-In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness we argue that structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
+In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness, structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
 
-We propose that nature of the legal and regulatory relationship between international NGOs and their host governments can serve as a signal of NGO trustworthiness and deservingness.
-NGO-related legislation is not inherently restrictive.
-Governments frequently use regulations to routinize the behavior of NGOs—regulations produce convergent practices [@BloodgoodTB, 145] and help improve NGO access to the policy-making process [@Teets:2014].
-Here, however, we focus on the impact of restrictive regulations or anti-NGO laws.
-Unlike regulations aimed at standardizing state–NGO relations, these laws are designed to limit the NGO community by creating deliberate barriers to their entry, funding, and advocacy.
-These laws can even limit organizations who comply with regulations regarding registration, auditing, and transparency.
-
-The legal threats that NGOs face in their host countries serve as yet another donor heuristic.
-Heavy legal restrictions could convey to donors that NGOs undertake important work, which is why governments perceive them as threatening.
+We propose that the regulatory relationship between international NGOs and their host governments serves as a signal of NGO trustworthiness and deservingness.
+NGO legislation is not inherently restrictive, and governments frequently use regulations to benignly routinize the behavior of NGOs [@BloodgoodTB].
+Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
+These stricter anti-NGO laws can signal to donors that NGOs undertake crucial work abroad, precipitating government crackdown.
 Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:
@@
 
-@fig:causal-path represents this relationship more formally [@Pearl:2019].
-Legal crackdowns (**C**) have a direct effect on donor outcomes (**Y**; likelihood and amount of donation) because of their heuristic function.
+@fig:causal-path represents this relationship more formally.
+Legal crackdowns (**C**) have a direct effect on donor outcomes (**Y**; donation likelihood and amount) because of their heuristic function.
 Legal crackdowns do not occur in isolation, however.
-Countries are more likely to legally restrict NGOs when organizational missions are in tension in with government preferences and when organizations receive substantial money from abroad [@Chaudhry:2016; @DPR:2015; @Heiss:2017].
-These effects are represented in the figure as **F** (funding), and **I** (issue and programs).
-Each of these organizational characteristics increase the likelihood of crackdown, but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.
+Countries are more likely to legally restrict NGOs when organizational missions (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
+Each of these organizational characteristics increase the likelihood of crackdown but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.
 
@@
 The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences—can influence donor behavior.
-Donors commonly support programs that have easily measurable goals and successes [@Bush:2015; @Kiai:2017].
-NGOs working on regime-compatible issues such as service provision, health, education, and humanitarian relief rarely challenge the government.
+Donors commonly support programs that have easily measurable goals and successes, and NGOs working on regime-compatible issues like health, education, and humanitarian relief rarely challenge the government [@Bush:2015; @Kiai:2017].
 As such, their programmatic output is easily quantifiable and donors can see the results of their charity more readily.
+In contrast, NGOs working on more contentious human rights issues can pose political challenges to regimes.
+These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources.
+Due to the nature of the political and social issues they work on, programmatic effectiveness is also harder to measure and quantify [@Bush:2015].
+Thus, donors may believe that it is more difficult to improve human rights in the target country and reduce their donations.
 
-In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes.
-Therefore, these NGOs are often viewed as politically motivated outsiders and run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted.
-Due to the nature of the political and social issues they work on, their programmatic effectiveness is also harder to measure and quantify [@Bush:2015].
-Thus, donors may believe that it is more difficult to improve respect for human rights in the target country, which limits NGOs' ability to achieve their goals.
-
-We thus hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, and directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
-As shorthand, we use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues:
+We hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, and directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
+We use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues:
 
@@
 Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003].
-In addition, donors may feel less inclined to contribute since the NGO does not need (or might not even typically accept) their donation, and since donors might perceive that their tax money already funds the organization.
-Further, government funding for NGOs can also potentially signal a lack of independence from the government.
+Donors may feel less inclined to contribute to NGOs receiving government funding as they might perceive that their tax money already funds the organization.
+Government funding can also signal a lack of independence from the government.
 Organizations that receive substantial government funding frequently avoid programming that would question the government even if it is in line with their mission [@Stroup:2012].
-In contrast, donors who see that organizations are privately funded will feel that they can also contribute and help.
+In contrast, donors who see that organizations are privately funded may feel that they can also contribute and help.
 
-Funding sources also have an effect on anti-legal crackdowns on NGOs (see @fig:causal-path), given that funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015].
+As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding influences anti-NGO crackdowns (see @fig:causal-path).
 As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
@@
 
-We test these hypotheses with a between-subjects vignette-based survey experiment with participants recruited from Amazon's Mechanical Turk.
+We test these hypotheses with a vignette-based survey experiment fielded through Amazon's Mechanical Turk.
 Our target population is the portion of Americans hypothetically willing to donate money for human rights and humanitarian work abroad.
-Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples (see Tables S1 and S2 in the supplement).[^supp]
+Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples.[^supp]
 
@@
 
-We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy.
-The vignette thus results in three manipulated variables: (1) crackdown vs.
-no crackdown, (2) humanitarian assistance vs.
-human rights, and (3) government funding vs.
-private funding.
-We used the International Rescue Committee (IRC) as our example international NGO because its work easily applies to each possible frame.
-IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donation, and IRC works in some countries that have passed anti-NGO laws, such as Egypt and Turkey, as well as countries with no such laws.
-We use a 2×2×2 between-subject factorial design, with participants randomly assigned to one of eight versions of the following vignette.
+We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy: (1) crackdown/no crackdown, (2) humanitarian assistance/human rights, and (3) government/private funding.
+We used the International Rescue Committee (IRC) as our example NGO because its work easily applies to each possible frame.
+IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donation, and it works in countries with and without anti-NGO laws.
+We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:
 
@@
 
-We collected two outcome measures, which we use as our main dependent variables: (1) how likely participants would be to donate to IRC (measured with a 5-point Likert scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100.
-For the ease of analysis, we collapse the likelihood question into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate.
-We also included a free response question for exploratory purposes, asking respondents to explain why they chose to donate the amount they indicated.
+We collected two outcome measures: (1) how likely participants would be to donate to IRC (measured with a 5-point scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100.
+We collapsed the likelihood scale into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate.
+We also included an exploratory free response question asking respondents to justify their choice.
 
@@
 
-We test our first hypothesis by calculating the differences in the average likelihood to donate and the average amount donated across the crackdown vs.
-no crackdown condition.
-For our second and third hypotheses, in which we posit that this crackdown effect is mediated by issue and funding, we measure the same difference in means spread across both issue and funding conditions.
+We test our first hypothesis by calculating the differences in the average likelihood to donate and the average amount donated across the crackdown conditions.
+For our second and third hypotheses we measure the difference in means spread across both issue and funding conditions.
 For additional exploration of the effect of issue and funding, we also measure the effect of crackdown within all combinations of issue and funding conditions.
 
-We use two Bayesian models to measure the effect of crackdown on the likelihood of donating and the amount hypothetically donated.[^priors] We model the proportion of respondents indicating they would likely donate as a binomial distribution:
+We use two Bayesian models to estimate the effect of crackdown on the likelihood of donating and the amount hypothetically donated.[^priors] We model the proportion of respondents indicating they would likely donate as a binomial distribution:
 
@@
 
-To account for uncertainty in the aggregated estimates from these models, we base our inference on the posterior distributions of the modeled estimates.
-We use the median values from the posterior distributions as point estimates and calculate credible intervals using the 95% highest posterior density.
-We declare an effect statistically significant if the posterior probability of being different from zero is larger than 0.95 [@KruschkeLiddell:2018].
+We use median values from the posterior distributions as point estimates and calculate credible intervals using the 95% highest posterior density.
+We declare an effect statistically significant if the posterior probability of being different from zero exceeds 0.95.
 Because differences can be either positive or negative (i.e.
-in some frames, the crackdown condition causes greater donations; in others it causes fewer donations), we report the probability that the difference is not equal to zero.
-When the median value is negative, we report the proportion of predicted values that are negative, and when the median value is positive, we report the proportion of values that are positive.
+in some frames, the crackdown condition causes larger donations; in others it causes smaller donations), we report the probability that the difference is not equal to zero: when the median value is negative we report the proportion of predicted values that are negative, and vice versa.
 
@@
 
-Without looking within issue or funding conditions, we find that respondents are not significantly more likely to donate to legally besieged international NGOs (H~1a~).
+Without considering issue or funding, we find that respondents are not more likely to donate to legally besieged international NGOs (H~1a~).
 As seen in @fig:likely-diffs(A), those exposed to the crackdown condition tend to have a slightly higher probability of donating (`r percent_1(filter(likely, title == "Crackdown")$theta_2)`) than those in the control condition (`r percent_1(filter(likely, title == "Crackdown")$theta_1)`), but the difference is not significant (`r filter(likely, title == "Crackdown")$delta`; `r filter(likely, title == "Crackdown")$p_neq0`).
@@
 
-While the crackdown frame had no effect on the probability of donating to human rights NGOs alone, conditioning this finding on the source of NGO funding uncovers competing trends.
-@fig:likely-diffs(D) shows difference in donation likelihood across all three experimental conditions.
-When individual donors know that a human rights organization receives the majority of its funding from the government, they are more likely (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`) to donate in the *absence* of crackdowns than when the NGO faces legal difficulties.
-In contrast, when donors know that an organization receives most of its funding from private sources, they are more likely (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`) to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles.
+While the crackdown frame has no effect on the probability of donating to human rights NGOs alone, conditioning this finding on the source of NGO funding reveals competing trends.
+@fig:likely-diffs(D) shows the difference in donation likelihood across all experimental conditions.
+When donors know that a human rights organization is primarily government funded, they are more likely to donate in the *absence* of crackdowns than when the NGO faces legal difficulties (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`).
+In contrast, when donors know that an organization is privately funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
 For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting funding and issue frames.
@@
 This trend also holds true when accounting for NGO issue area.
-As seen in @fig:amount-diffs(B–C), the crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance.
-Emphasizing legal crackdown increased donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)` above the no crackdown condition, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`).
-In contrast, crackdowns significantly boosted donations to humanitarian NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`).
+The crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance (see @fig:amount-diffs(B–C)).
+Emphasizing legal crackdown increases donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)`, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`).
+In contrast, crackdowns boost donations to humanitarian NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`).
 We thus find support for H~2b~: donors give more to besieged humanitarian NGOs.
@@
 
-Finally, combining issue areas and funding sources adds more texture to these results.
-We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they run into legal issues.
+Combining issue areas and funding sources adds more texture to these results.
+We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues.
 This finding also applies to the amount donors give.
@@
 Emphasizing legal difficulties increased donations to government-funded humanitarian NGOs by `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)`, or `r md_dollar(abs(filter(amount, title == "Humanitarian assistance | Government")$mu_diff))` (`r filter(amount, title == "Humanitarian assistance | Government")$p_neq0`).
-The crackdown condition caused this increase despite some notable hesitation from respondents, many of whom felt that government-backed NGOs do not need or deserve private donations.
+The crackdown condition causes this increase despite some hesitation from respondents who often indicated that government-funded NGOs do not deserve private donations.
 Respondents reasoned since IRC "is already receiving funding from governments, so funding from private individuals doesn't seem as necessary.
-I'd prefer to give my money to an organization that is primarily run by private donations"[^6486084] or because "[m]y tax paying dollars go to the government and if the government is helping to fund it then they are in turn getting some of my money."[^9509936] This hesitation was not universal, however, and in aggregate most respondents chose to give substantially more.
+I'd prefer to give my money to an organization that is primarily run by private donations"[^6486084] or because "[m]y tax paying dollars go to the government and if the government is helping to fund it then they are in turn getting some of my money."[^9509936] This hesitation is not universal, however, and in aggregate most respondents chose to give substantially more.
 Many echoed this respondent, who identified the crackdown condition as one of the reasons for giving the full hypothetical \$100: "I believe the work of such organizations has an urgency that affects many refugees and their families.
@@
 
-In contrast, crackdowns had no substantial effect on the amount donated to privately-funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`).
+In contrast, crackdowns have no substantial effect on the amount donated to privately-funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`).
 No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations.
-For instance, donors might assume that an international NGO that receives substantial money from USAID would ostensibly have the support of the U.S.
+Donors might assume that an international NGO that receives substantial money from USAID would have the support of the U.S.
 government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
@@
 
-Over the last three decades, several countries have used legal restrictions to limit international NGO funding and programming.
-Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors for their funding.
-How do these donors respond to anti-NGO legal restrictions, and how do an organization's issue area and funding sources interact with these restrictions?
-In this study, we propose that legal crackdowns on NGOs can serve as a heuristic or signal to donors of the deservingness and efficiency of NGO programming.
-We find that crackdowns, funding, and issue area do not directly influence the *likelihood* of donation on their own.
-Donors are more likely to give to privately funded NGOs facing legal crackdown, however, and are more likely to do so when those organizations focus on human rights issues.
-Crackdowns do, however, influence the *amount* that donors give.
-Respondents indicated a willingness to donate substantially more to NGOs facing legal restrictions, and this effect persists when mediated by issue area and funding—respondents give more to restricted humanitarian NGOs and privately funded NGOs.
-For human rights NGOs, those funded through private donations see increased donations under legal crackdown, while donors again appear to punish those that rely on government funding.
+Dozens of countries have legally restricted NGO funding and programming.
+Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors as an additional funding source.
+Do ongoing legal crackdowns influence these donors' decision to donate?
+Our results show that legal restrictions provide donors with an additional signal of NGO deservingness and efficiency and can change both the likelihood that donors will give and the amount they will give.
+While crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
+This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs, and `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)` more to government-funded humanitarian NGOs.
+Anti-NGO crackdowns can thus serve as a signal of NGO effectiveness.
 
 This study makes two important contributions.
-While recent work has looked at how state repression of NGOs affects official aid flows [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how such repression affects private aid flows.
+While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid.
 Further, prior literature on the determinants of donation to NGOs predominantly focuses on individual-level factors.
@@
 
-Our results have several implications for policy and future research.
+This has several implications for policy and future research.
 NGOs may benefit from publicizing when they are targets of government crackdown.
@@
 
-[^supp]: Figures and tables in the supplement are prefixed with "S." Complete details about our sample (Table SX), our power analysis, and treatment assignment balance (Figure S2) are included in the supplement.
+[^supp]: See the supplement for details about our sample demographics and treatment assignment balance.
 
-[^priors]: The "Priors" section in the supplement provides complete details about our prior choices and computational choices.
+[^priors]: See the supplement for details about our prior choices and computational environment.
 

### 2019-03-13 manuscript/manuscript.Rmd
Suparna edits

@@
 abstract: >-
-  State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common.
+  State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding and advocacy, has become increasingly pervasive across the globe.
 How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries.
+With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in various developing countries, many NGOs rely on funds from private donors in Western countries.
+Existing research has predominantly focused on individual-level determinants of philanthropy.
+However, we argue that domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness.
 Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO.
-We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs.
-Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues.
-We conclude by discussing the implications for the sustainability of NGOs working abroad.
+We find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
+We conclude by discussing the implications of our results on the sustainability of civil society organizations working in repressive countries.
 thanks: >-
@@
 Contact: suparna.chaudhry@cnu.edu
-word-count: "3,998"
+word-count: "4,081"
 ---
@@
 These laws have tangible consequences for NGOs worldwide.
-Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in restrictive countries [@Brechenmacher:2017].
-In response to this dramatic shift in the NGO funding landscape, organizations have increasingly turned to individual private donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015].
+Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in repressive countries [@Brechenmacher:2017].
 
-Donations from *domestic* donors in repressive countries are unreliable and inconsistent.
+In response to this dramatic shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015].
+This is because donations from *domestic* donors in repressive countries are unreliable and inconsistent.
 Citizens in the Global South often cannot support local NGOs, may lack a culture of philanthropic giving, or may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
 Even when donors in repressive countries prefer to donate to NGOs working in contentious areas, they may be deterred by dismal tax incentives, threats to take away business permits, or a general fear of retribution [@HudsonInstitute:2015].
-NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
+Therefore, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
 Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing resources to raise similar sums locally [@RonKairePandya:2018].
@@
 We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
-This effect persists when mediated by other structural heuristics like NGO issue area and funding sources.
+This effect persists when mediated by other structural heuristics like NGO issue area and its main funding sources.
 
-# Theory and hypotheses
+# Theorizing the effects of crackdown on philanthropy
 
@@
 Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
-These stricter anti-NGO laws can signal to donors that NGOs undertake crucial work abroad, precipitating government crackdown.
+These stricter anti-NGO laws can signal to donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
 Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:
@@
 Legal crackdowns do not occur in isolation, however.
-Countries are more likely to legally restrict NGOs when organizational missions (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
+Countries are more likely to repress NGOs when organizational missions (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
 Each of these organizational characteristics increase the likelihood of crackdown but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.
@@
 Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003].
-Donors may feel less inclined to contribute to NGOs receiving government funding as they might perceive that their tax money already funds the organization.
+Donors may feel less inclined to contribute to NGOs receiving government funding, as they might perceive that their tax money already funds the organization.
 Government funding can also signal a lack of independence from the government.
-Organizations that receive substantial government funding frequently avoid programming that would question the government even if it is in line with their mission [@Stroup:2012].
+Organizations that receive substantial government funding frequently avoid programming that would question the government even if it were in line with their mission [@Stroup:2012].
 In contrast, donors who see that organizations are privately funded may feel that they can also contribute and help.
 
-As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding influences anti-NGO crackdowns (see @fig:causal-path).
+As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding can influence anti-NGO crackdowns (see @fig:causal-path).
 As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
-Donors could punish government-funded NGOs that face restrictions, since legal trouble could further fuel private donor mistrust.
-Donors thus are more likely to donate more to NGOs that rely on private funding:
+Private donors may be more likely to punish government-funded NGOs that face restrictions.
+This is because legal trouble with the group's main funder could fuel private donor mistrust.
+Donors thus may be more likely to donate more to NGOs that rely on private funding:
 
@@
 
-# Methods
+# Research Design
 
@@
 Both differences are positive, but the posterior probability of being larger than zero is low (`r filter(likely, title == "Issue")$delta`; `r filter(likely, title == "Issue")$p_neq0`; `r filter(likely, title == "Funding")$delta`; `r filter(likely, title == "Funding")$p_neq0`).
-We thus do not initially find evidence to support our hypothesis that crackdowns (or issue or funding) alone increase the likelihood of donating.
+We thus do not initially find evidence that crackdowns (or issue or funding) alone increase the likelihood of donating.
 
@@
 Crackdown has almost no effect on the likelihood of donating to human rights NGOs (`r filter(likely, title == "Human rights")$p_neq0`).
-We hypothesized that the positive crackdown effect would be stronger for humanitarian NGOs, and while crackdown does have a positive effect on under the humanitarian frame, the probability this difference is greater than zero is below our 95% threshold (`r filter(likely, title == "Humanitarian assistance")$p_neq0`).
+We hypothesized that the positive crackdown effect would be stronger for humanitarian NGOs, and while crackdown does have a positive effect under the humanitarian frame, the probability this difference is greater than zero is below our 95% threshold (`r filter(likely, title == "Humanitarian assistance")$p_neq0`).
 We do find some evidence for H~3a~, however.
@@
 While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid.
-Further, prior literature on the determinants of donation to NGOs predominantly focuses on individual-level factors.
-Our study measures important structural determinants that influence giving and shows how these factors interact with organizational attributes to signal NGO deservingness.
+Further, prior literature on the determinants of donation to NGOs focuses predominantly on individual-level factors.
+Our study measures important structural determinants that influence philanthropy and shows how these factors interact with organizational attributes to signal NGO deservingness.
 Additional research should determine the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation—as well as test the generalizability of our findings to other issue areas.
@@
 Our study also highlights the importance of framing NGO operations.
-Previous research on human rights micromobilization has shown that the way people process information can affect their increased willingness to help others in need [@Slovic:2007].
+Previous research on human rights micro-mobilization has shown that the way people process information can affect their increased willingness to help others in need [@Slovic:2007].
 Our results show that donors are likely to view legally besieged human rights NGOs with suspicion.

### 2019-03-13 R/graphics.R
Stop using light face

@@ -133,7 +133,7 @@ theme_spark <- function() {
 #' A custom ggplot2 theme used throughout this project
 #'
 #' @param base_size base font size
-#' @param base_family base font family (default is Roboto Condensed Light)
+#' @param base_family base font family (default is Roboto Condensed)
 #' @param density Binary indicator to remove the panel grid and make a few other adjustments
 #'
 #' @export
@@ -150,27 +150,27 @@ theme_spark <- function() {
 #' ggplot(mtcars, aes(x = mpg)) +
 #'   geom_density(fill = "grey80") +
 #'   theme_ngos(density = TRUE)
-theme_ngos <- function(base_size = 11, base_family = "Roboto Condensed Light", density = FALSE) {
-  update_geom_defaults("label", list(family = "Roboto Condensed Light", face = "plain"))
-  update_geom_defaults("text", list(family = "Roboto Condensed Light", face = "plain"))
+theme_ngos <- function(base_size = 11, base_family = "Roboto Condensed", density = FALSE) {
+  update_geom_defaults("label", list(family = "Roboto Condensed", face = "plain"))
+  update_geom_defaults("text", list(family = "Roboto Condensed", face = "plain"))
   
   ret <- theme_bw(base_size, base_family) +
     theme(plot.title = element_text(size = rel(1.4), face = "plain",
-                                    family = "Roboto Condensed Bold"),
+                                    family = "Roboto Condensed"),
           plot.subtitle = element_text(size = rel(1), face = "plain",
-                                       family = "Roboto Condensed Light"),
+                                       family = "Roboto Condensed"),
           plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
-                                      family = "Roboto Condensed Light",
+                                      family = "Roboto Condensed",
                                       margin = margin(t = 10)),
           plot.tag = element_text(size = rel(1), face = "plain", color = "grey50",
-                                  family = "Roboto Condensed Bold"),
+                                  family = "Roboto Condensed"),
           strip.text = element_text(size = rel(0.8), face = "plain",
-                                    family = "Roboto Condensed Bold"),
+                                    family = "Roboto Condensed"),
           strip.text.x = element_text(margin = margin(t = 1, b = 1)),
           panel.border = element_blank(), 
           strip.background = element_rect(fill = "#ffffff", colour = NA),
[…]

### 2019-03-13 analysis/02_analysis.Rmd
Shrink figures for R&P columns

@@
 library(ggdag)
+library(ggraph)
 library(patchwork)
@@
 
-```{r causal-dag, fig.width=4.5, fig.height=2.5}
+```{r causal-dag, fig.width=10/3, fig.height=2}
 theory_dag <- dagify(Y ~ I + C + F,
                      C ~ I + F,
-                     outcome = "F",
+                     outcome = "Y",
                      exposure = "C") %>% 
@@
 plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
-  geom_dag_node(size = 12) +
-  geom_dag_edges() +
-  geom_dag_text(size = pts(9), family = "Roboto Condensed Bold") +
+  geom_dag_point(size = 6) +
+  geom_dag_edges(start_cap = circle(4, "mm"),
+                 end_cap = circle(4, "mm")) +
+  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
   scale_dag() +
@@
   ggsave(., filename = here("analysis", "output", "figures", "causal-path.pdf"),
-         width = 4.5, height = 2.5, units = "in", device = cairo_pdf) %>% 
+         width = 10/3, height = 2, units = "in", device = cairo_pdf) %>% 
   ggsave(., filename = here("analysis", "output", "figures", "causal-path.png"),
-         width = 4.5, height = 2.5, units = "in", type = "cairo", dpi = 300)
+         width = 10/3, height = 2, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r plot-likely-diffs, warning=FALSE, fig.width=4.5, fig.height=6.5}
+```{r plot-likely-diffs, warning=FALSE, fig.width=10/3, fig.height=5.5}
 tidied_diffs_likely <- all_models_likely %>% 
@@
   labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
-  theme_ngos(base_size = 9) +
+  theme_ngos(base_size = 8) +
   theme(panel.grid.major.y = element_blank())
@@
   facet_wrap(~ facet_title, scales = "free_y") +
-  theme_ngos(base_size = 9) +
+  theme_ngos(base_size = 8) +
   theme(panel.grid.major.y = element_blank())
@@
   ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.pdf"),
-         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
+         width = 10/3, height = 5.5, units = "in", device = cairo_pdf) %>%
   ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.png"),
-         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
+         width = 10/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r plot-amount-diffs, warning=FALSE, fig.width=4.5, fig.height=6.5}
+```{r plot-amount-diffs, warning=FALSE, fig.width=10/3, fig.height=5.5}
 # This will generate a warning because unnest() puts the crackdown values into
@@
   labs(x = "Difference in amount donated", y = NULL, tag = "A") +
-  theme_ngos(base_size = 9) +
+  theme_ngos(base_size = 8) +
   theme(panel.grid.major.y = element_blank())
@@
   ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.pdf"),
-         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
+         width = 10/3, height = 5.5, units = "in", device = cairo_pdf) %>%
   ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.png"),
-         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
+         width = 10/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
 ```

### 2019-03-13 analysis/02_analysis.Rmd
Use LaTeX in table headers since R&P doesn't use xelatex

@@
   select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
-         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
+         `$p(\\Delta \\neq 0)$` = p.diff.not0)
 ```
@@
          `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
-         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
+         `$p(\\Delta \\neq 0)$` = p.diff.not0)
 ```
@@
   select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
-         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
+         `$p(\\Delta \\neq 0)$` = p.diff.not0)
 ```
@@
   select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
-         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
+         `$p(\\Delta \\neq 0)$` = p.diff.not0)
 ```
@@
          `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
-         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
+         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
+         `$p(\\Delta \\neq 0)$` = p.diff.not0)
 ```

### 2019-03-13 manuscript/pandoc/bin/clean.py
Process and build Sage TeX file

@@ -1,0 +1,49 @@
+#!/usr/bin/env python3
+
+# Clean up text for using in vanilla non-xelatex LaTeX.
+#
+# usage: clean.py [-h] [input_file] [output]
+#
+# Recommended usage: Send the Markdown output to stdout (default) and pipe
+# into pandoc for instant preprocessing:
+#
+#   clean.py document.md | pandoc -f markdown -t tex -o document.tex
+
+# Load libraries
+import argparse
+import sys
+import re
+
+# Get command line arguments
+parser = argparse.ArgumentParser(description='Clean up text for vanilla LaTeX.')
+parser.add_argument('input_file', type=argparse.FileType('r'),
+                    nargs='?', default=sys.stdin,
+                    help='file to clean')
+parser.add_argument('output', type=argparse.FileType('w'),
+                    nargs='?', default=sys.stdout,
+                    help='the name of the output file (defaults to stdout)')
+args = parser.parse_args()
+
+# Clean up the text
+def clean(text):
+    # Unicode stuff
+    text = re.sub("×", r"\\(\\times\\)", text)
+    text = re.sub("−", r"\\(-\\)", text)
+
+    # Footnotes to endnotes
+    text = re.sub(r"\\footnote\{", r"\\endnote{", text)
+
+    # Add midrules to pseudo table headers!!
+    text = re.sub(r"(\\\\)\nH\\textsubscript", "\\1\\\\midrule\nH\\\\textsubscript", text)
+    text = re.sub(r"(\\\\)\nHuman rights issues &", "\\1\\\\midrule\nHuman rights issues &", text)
+    text = re.sub(r"(\\\\)\nHuman rights issues, Government", "\\1\\\\midrule\nHuman rights issues, Government", text)
+
+    # Simplify figure path
+    text = re.sub(r"\\includegraphics{output/figures/", "\\\includegraphics{figures/", text)
+    
+    return(text)
+
+
+# All done!
+with args.output as f:
+    f.write(clean(args.input_file.read()))

### 2019-03-13 manuscript/pandoc/bin/tabularize.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python3
+
+# Filter to convert pandoc-generated longtable elements to tabular elements.
+#
+# usage: pandoc document.md -o document.tex --filter tabularize.py
+#
+# I copied this from Wagner Macedo's original filter at:
+# https://groups.google.com/forum/#!msg/pandoc-discuss/RUC-tuu_qf0/h-H3RRVt1coJ
+# 
+# I made two adjustments to the original script:
+# - Use `table*` instead of `table` to span two columns in SAGE LaTeX template
+# - Surround table with \small and \normalize to shrink the text a little
+
+import pandocfilters as pf
+
+def latex(s):
+    return pf.RawBlock('latex', s)
+
+def inlatex(s):
+    return pf.RawInline('latex', s)
+
+def tbl_caption(s):
+    return pf.Para([inlatex(r'\caption{')] + s + [inlatex('}')])
+
+def tbl_alignment(s):
+    aligns = {
+        "AlignDefault": 'l',
+        "AlignLeft": 'l',
+        "AlignCenter": 'c',
+        "AlignRight": 'r',
+    }
+    return ''.join([aligns[e['t']] for e in s])
+
+def tbl_headers(s):
+    result = s[0][0]['c'][:]
+    for i in range(1, len(s)):
+        result.append(inlatex(' & '))
+        result.extend(s[i][0]['c'])
+    result.append(inlatex(r' \\\midrule'))
+    return pf.Para(result)
+
+def tbl_contents(s):
+    result = []
+    for row in s:
+        para = []
+        for col in row:
+            para.extend(col[0]['c'])
+            para.append(inlatex(' & '))
+        result.extend(para)
+        result[-1] = inlatex(r' \\' '\n')
+    return pf.Para(result)
+
+def do_filter(k, v, f, m):
+    if k == "Table":
+        return [latex(r'\begin{table*}[ht]' '\n' r'\centering' '\n' r'\small' '\n'),
+                tbl_caption(v[0]),
+                latex(r'\begin{tabular}{@{}%s@{}}' % tbl_alignment(v[1]) +
+                      ('\n' r'\toprule')),
+                tbl_headers(v[3]),
+                tbl_contents(v[4]),
+                latex(r'\bottomrule' '\n' r'\end{tabular}'),
+                latex(r'\end{table*}')]
+
+
+if __name__ == "__main__":
+    pf.toJSONFilter(do_filter)

### 2019-03-13 README.Rmd
Update abstract and title

@@
 
-Title <- "The effect of NGO crackdowns on individual philanthropy"
+Title <- "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
 Authors <- "Suparna Chaudhry and Andrew Heiss"
@@
 
-State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common.
+State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding and advocacy, has become increasingly pervasive across the globe.
 How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries.
+With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in various developing countries, many NGOs rely on funds from private donors in Western countries.
+Existing research has predominantly focused on individual-level determinants of philanthropy.
+However, we argue that domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness.
 Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO.
-We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs.
-Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues.
-We conclude by discussing the implications for the sustainability of NGOs working abroad.
+We find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
+We conclude by discussing the implications of our results on the sustainability of civil society organizations working in repressive countries.
 

### 2019-03-13 manuscript/manuscript.Rmd
Use LaTeX in table headers since R&P doesn't use xelatex
Shrink tables
Add keywords

@@
 word-count: "4,081"
+keywords: international NGOs, donor behavior, philanthropy, human rights, repression
 ---
@@
 
+\footnotesize
+
 $$
 \begin{aligned}
-n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{total in group}}, \theta_{\text{group}}) &\text{[likelihood]}\\
+n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{group total}}, \theta_{\text{group}}) &\text{[likelihood]}\\
 \Delta_n &= n_{\text{group 2}} - n_{\text{group 1}} &\text{[difference in proportions]} \\
@@
 \\
-\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of being likely to donate]}
+\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of likelihood]}
 \end{aligned}
@@
 
+\normalsize
+
 We estimate the mean amount donated in each condition using a *t* distribution [@Kruschke:2013]:
+
+\footnotesize
 
@@
 $$
+
+\normalsize
 

### 2019-03-13 manuscript/pandoc/bin/clean.py
Use figures in root directory

@@ -39,7 +39,7 @@ def clean(text):
     text = re.sub(r"(\\\\)\nHuman rights issues, Government", "\\1\\\\midrule\nHuman rights issues, Government", text)
 
     # Simplify figure path
-    text = re.sub(r"\\includegraphics{output/figures/", "\\\includegraphics{figures/", text)
+    text = re.sub(r"\\includegraphics{output/figures/", "\\\includegraphics{", text)
     
     return(text)
 

### 2019-03-13 README.Rmd
Add data finally

@@
 
+## Data
+
+This project includes the following data files:
+
+- [`data/raw_data/crackdowns-philanthropy-raw.csv`](data/raw_data/crackdowns-philanthropy-raw.csv): Original results from the Qualtrics survey
+- [`data/derived_data/results_clean.csv`](data/derived_data/results_clean.csv): Final version of the data, cleaned with [`analysis/01_clean-data.Rmd`](analysis/01_clean-data.Rmd)
+- [`data/derived_data/results_clean.yaml`](data/derived_data/results_clean.yaml): [YAML metadata](https://csvy.org/) describing the syntax of the cleaned data
+- [`data/derived_data/results_clean.rds`](data/derived_data/results_clean.rds): `.rds` version of cleaned data
+- [`data/derived_data/codes_to_exclude.csv`](data/derived_data/codes_to_exclude.csv): Unique IDs of participants who failed the attention checks or took the survey outside of Mechanical Turk.
+These are excluded from the final data in [`analysis/01_clean-data.Rmd`](analysis/01_clean-data.Rmd)
+- [`raw_data/ipums-cps/`](raw_data/ipums-cps/): Data extracts from the US Census's Current Population Survey (CPS) via the [Minnesota Population Center's Integrated Public Use Microdata Series (IPUMS)](https://cps.ipums.org/cps/):
+    -  `cps_2017.dat.gz`: 2017 ASEC, with the following variables selected (in addition to whatever IPUMS preselects by default) (and weighted by `ASECWT`):
+        - `AGE`
+        - `SEX`
+        - `EDUC`
+        - `INCTOT`
+    -  `cps_09_2015.dat.gz`: September 2015 basic monthly CPS (which includes the Volunteer Supplement), with the following variables selected (and weighted by `VLSUPPWT`):
+        - `VLSTATUS`
+        - `VLDONATE`
+
 ## Licenses

### 2019-03-13 analysis/01_clean-data.Rmd
Add data finally

@@
 # results_file <- file.path(here(), "data", "test_data.csv")
-results_file <- here("data", "private_data", 
-                     "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")
+results_file <- here("data", "raw_data", "crackdowns_philanthropy_raw.csv")
 

### 2019-03-13 analysis/03_additional-analysis.Rmd
Add data finally

@@
 
--  `"data/ipums-cps/cps_2017.dat.gz"`: 2017 ASEC, with the following variables selected (in addition to whatever IPUMS preselects by default) (and weighted by `ASECWT`):
+-  `"data/raw_data/ipums-cps/cps_2017.dat.gz"`: 2017 ASEC, with the following variables selected (in addition to whatever IPUMS preselects by default) (and weighted by `ASECWT`):
     - `AGE`
@@
     - `INCTOT`
--  `"data/ipums-cps/cps_09_2015.dat.gz"`: September 2015 basic monthly CPS (which includes the Volunteer Supplement), with the following variables selected (and weighted by `VLSUPPWT`):
+-  `"data/raw_data/ipums-cps/cps_09_2015.dat.gz"`: September 2015 basic monthly CPS (which includes the Volunteer Supplement), with the following variables selected (and weighted by `VLSUPPWT`):
     - `VLSTATUS`

### 2019-03-13 R/crackdownsphilanthropy-package.R
Update description with actual details

@@ -1,6 +1,6 @@
 #' The 'crackdownsphilanthropy' package.
 #' 
-#' @description A DESCRIPTION OF THE PACKAGE
+#' @description Research on how anti-NGO crackdowns influence donor behavior
 #' 
 #' @docType package
 #' @name crackdownsphilanthropy-package

### 2019-03-14 README.Rmd
Oops, fix data URL

--- 2019-03-13 README.Rmd
@@
 
+## Data
+
+This project includes the following data files:
+
+- [`data/raw_data/crackdowns_philanthropy_raw.csv`](data/raw_data/crackdowns_philanthropy_raw.csv): Original results from the Qualtrics survey
+- [`data/derived_data/results_clean.csv`](data/derived_data/results_clean.csv): Final version of the data, cleaned with [`analysis/01_clean-data.Rmd`](analysis/01_clean-data.Rmd)
+- [`data/derived_data/results_clean.yaml`](data/derived_data/results_clean.yaml): [YAML metadata](https://csvy.org/) describing the syntax of the cleaned data
+- [`data/derived_data/results_clean.rds`](data/derived_data/results_clean.rds): `.rds` version of cleaned data
+- [`data/derived_data/codes_to_exclude.csv`](data/derived_data/codes_to_exclude.csv): Unique IDs of participants who failed the attention checks or took the survey outside of Mechanical Turk.
+These are excluded from the final data in [`analysis/01_clean-data.Rmd`](analysis/01_clean-data.Rmd)
+- [`raw_data/ipums-cps/`](raw_data/ipums-cps/): Data extracts from the US Census's Current Population Survey (CPS) via the [Minnesota Population Center's Integrated Public Use Microdata Series (IPUMS)](https://cps.ipums.org/cps/):
+    -  `cps_2017.dat.gz`: 2017 ASEC, with the following variables selected (in addition to whatever IPUMS preselects by default) (and weighted by `ASECWT`):
+        - `AGE`
+        - `SEX`
+        - `EDUC`
+        - `INCTOT`
+    -  `cps_09_2015.dat.gz`: September 2015 basic monthly CPS (which includes the Volunteer Supplement), with the following variables selected (and weighted by `VLSUPPWT`):
+        - `VLSTATUS`
+        - `VLDONATE`
+
 ## Licenses

### 2019-09-05 analysis/02_analysis.Rmd
Remove citation ban

@@
 tbl_likely_2_header <- enframe(colnames(tbl_likely_2)) %>% 
-  mutate(value = pandoc.strong.return(value)) %>% 
+  mutate(value = (value)) %>% 
   spread(name, value) %>% 
@@
 tbl_likely_3_header <- enframe(colnames(tbl_likely_3)) %>% 
-  mutate(value = pandoc.strong.return(value)) %>% 
+  mutate(value = (value)) %>% 
   spread(name, value) %>% 
@@
 tbl_amount_2_header <- enframe(colnames(tbl_amount_2)) %>% 
-  mutate(value = pandoc.strong.return(value)) %>% 
+  mutate(value = (value)) %>% 
   spread(name, value) %>% 
@@
 tbl_amount_3_header <- enframe(colnames(tbl_amount_3)) %>% 
-  mutate(value = pandoc.strong.return(value)) %>% 
+  mutate(value = (value)) %>% 
   spread(name, value) %>% 

### 2019-09-05 manuscript/manuscript.Rmd
Remove citation ban

@@
 date: "`r format(Sys.time(), '%B %e, %Y')`"
-published: Please do not cite without permission.
 git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy

### 2020-01-19 R/amount_donated_best_stan.R
Update to rstantools 2.0's structure
This works so much better and is far less fragile!

@@ -1,0 +1,18 @@
+#' amount_donated_best
+#'
+#' Stan implementation of John Kruschke's Bayesian Estimation Supersedes the
+#' t-test (BEST).
+#'
+#' @param df Data frame with two columns: amount (numeric) and group (factor)
+#' @param ... Arguments passed to `rstan::sampling` (e.g. iter, chains).
+#'
+#' @export
+#'
+#' @return An object of class `stanfit` returned by `rstan::sampling`
+#'   
+amount_donated_best <- function(df, ...) {
+  standata <- tidybayes::compose_data(df)
+  
+  out <- rstan::sampling(stanmodels$amount_donated_best, data = standata, ...)
+  return(out)
+}

### 2020-01-19 R/compiled_models.R

@@ -1,25 +1,0 @@
-#' Stan models
-#' 
-#' Precompiled Stan models ready to be used with `rstan::sampling`
-#' 
-#' Instead of writing wrapper functions for these two models, we just provide them as precompiled models that we can then use on their own
-#' 
-#' @name compiled_models
-#' @md
-NULL
-
-#' @rdname compiled_models
-#'
-#' @export
-# This has to be wrapped in a function for some reason; just doing
-# stanmodels$donate_likely breaks and idk why
-donate_likely <- function() {
-  return(stanmodels$donate_likely)
-}
-
-#' @rdname compiled_models
-#'
-#' @export
-amount_donated_best <- function() {
-  return(stanmodels$amount_donated_best)
-}

### 2020-01-19 R/crackdownsphilanthropy-package.R

@@ -8,10 +8,9 @@
 #' @useDynLib crackdownsphilanthropy, .registration = TRUE
 #' @import methods
 #' @import Rcpp
-#' @import rstantools
 #' @importFrom rstan sampling
 #' 
 #' @references 
 #' Stan Development Team (2018). RStan: the R interface to Stan. R package version 2.18.2. http://mc-stan.org
-#' 
+#' all
 NULL

### 2020-01-19 R/donate_likely_stan.R

@@ -1,0 +1,21 @@
+#' donate_likely_stan
+#'
+#' Model the difference between two proportions. Essentially a Bayesian version
+#' of Fisher's exact test.
+#'
+#' @param n_total_1 Total number in group 1
+#' @param n_total_2 Total number in group 2
+#' @param n_likely_1 Number of answers responding "Likely" in group 1
+#' @param n_likely_2 Number of answers responding "Likely" in group 1
+#' @param ... Arguments passed to `rstan::sampling` (e.g. iter, chains).
+#'
+#' @export
+#'
+#' @return An object of class `stanfit` returned by `rstan::sampling`
+#'   
+donate_likely <- function(n_total_1, n_total_2, n_likely_1, n_likely_2, ...) {
+  standata <- tidybayes::compose_data(n_total_1, n_total_2, n_likely_1, n_likely_2)
+
+  out <- rstan::sampling(stanmodels$donate_likely, data = standata, ...)
+  return(out)
+}

### 2020-01-19 R/stanmodels.R

@@ -1,37 +1,27 @@
-# Part of the crackdownsphilanthropy package for estimating model parameters
-# Copyright (C) 2015, 2016, 2017 Trustees of Columbia University
-# 
-# This program is free software; you can redistribute it and/or
-# modify it under the terms of the GNU General Public License
-# as published by the Free Software Foundation; either version 3
-# of the License, or (at your option) any later version.
-# 
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-# 
-# You should have received a copy of the GNU General Public License
-# along with this program; if not, write to the Free Software
-# Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301, USA.
+# Generated by rstantools.  Do not edit by hand.
 
-# This file is only intended to be used during the installation process
-# nocov start
-MODELS_HOME <- "src"
-if (!file.exists(MODELS_HOME)) MODELS_HOME <- sub("R$", "src", getwd())
+# names of stan models
+stanmodels <- c("amount_donated_best", "compare_pop_prop", "donate_likely")
 
-stan_files <- dir(file.path(MODELS_HOME, "stan_files"),
-                  pattern = "stan$", full.names = TRUE)
-stanmodels <- lapply(stan_files, function(f) {
-  model_cppname <- sub("\\.stan$", "", basename(f))
-  stanfit <- rstan::stanc(f, allow_undefined = TRUE, 
-                          obfuscate_model_name = FALSE)
-  stanfit$model_cpp <- list(model_cppname = stanfit$model_name, 
+# load each stan module
+Rcpp::loadModule("stan_fit4amount_donated_best_mod", what = TRUE)
+Rcpp::loadModule("stan_fit4compare_pop_prop_mod", what = TRUE)
+Rcpp::loadModule("stan_fit4donate_likely_mod", what = TRUE)
+
+# instantiate each stanmodel object
+stanmodels <- sapply(stanmodels, function(model_name) {
+  # create C++ code for stan model
+  stan_file <- if(dir.exists("stan")) "stan" else file.path("inst", "stan")
+  stan_file <- file.path(stan_file, paste0(model_name, ".stan"))
+  stanfit <- rstan::stanc_builder(stan_file,
+                                  allow_undefined = TRUE,
[…]

### 2020-01-19 src/init.cpp

@@ -1,20 +1,0 @@
-// Generated by the rstantools package
-
-
-#include <R.h>
-#include <Rinternals.h>
-#include <R_ext/Rdynload.h>
-#include <R_ext/Visibility.h>
-#include <Rversion.h>
-
-
-static const R_CallMethodDef CallEntries[] = {
-  {NULL, NULL, 0}
-};
-
-
-void attribute_visible R_init_crackdownsphilanthropy(DllInfo *dll) {
-  // next line is necessary to avoid a NOTE from R CMD check
-  R_registerRoutines(dll, NULL, CallEntries, NULL, NULL);
-  R_useDynamicSymbols(dll, TRUE); // necessary for .onLoad() to work
-}

### 2020-01-19 R/summary_table.R
Improve summary_table functions
They now get fed entire columns collapsed into a list instead of a bunch of character values that have to be reclassed here.

@@ -5,38 +5,20 @@
 #' @name summary_table
 NULL
 
-my_as_numeric <- function(x) {
-  is_num <- suppressWarnings(!any(is.na(as.numeric(x))))
-  
-  if (is_num) {
-    as.numeric(x)
-  } else {
-    x
-  }
-}
-
-level_summary <- function(x, variable, df) {
-  variable <- as.character(variable)
-  if (is.factor(df[[variable]])) {
-    x_levels <- levels(df[[variable]])
-  } else {
-    x_levels <- unique(df[[variable]])
-  }
-  
-  factor_summary <- tibble(x) %>% 
-    count(x) %>%
+level_summary <- function(value, variable_name) {
+  factor_summary <- tibble(value) %>% 
+    count(value) %>%
     mutate(pct = n / sum(n),
-           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
-           x = factor(x, levels = x_levels, ordered = TRUE)) 
+           fancy = paste0(value, " (", n, "; ", percent(pct), ")"))
   
-  inline_summary <- factor_summary %>% arrange(x) %>% 
+  inline_summary <- factor_summary %>% arrange(value) %>% 
     pull(fancy) %>% paste(collapse = " | ")
   
-  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
+  fig_bar <- ggplot(factor_summary, aes(x = value, y = n)) +
     geom_bar(stat = "identity", fill = "grey50") +
     theme_spark()
   
-  file_name <- gsub("\\.| ", "_", tolower(variable))
+  file_name <- gsub("\\.| ", "_", tolower(variable_name))
   md_img <- paste0("![](output/figures/summary-table/", file_name, ")")
   
   ggsave(fig_bar, filename = here("analysis", "output", "figures", "summary-table",
@@ -50,16 +32,16 @@ level_summary <- function(x, variable, df) {
   return(output)
 }
 
-numeric_summary <- function(x, variable) {
-  inline_summary <- paste0("Median: ", round(median(x, na.rm = TRUE), 2),
-                           " | Mean: ", round(mean(x, na.rm = TRUE), 2), 
-                           " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2))
+numeric_summary <- function(value, variable_name) {
+  inline_summary <- paste0("Median: ", round(median(value, na.rm = TRUE), 2),
[…]

### 2020-01-19 analysis/02_analysis.Rmd
Modernize tidyverse syntax and use newer stan functions

@@
   geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
-  scale_dag() +
   theme_ngos() +
@@
 
-```{r tbl-descriptive-statistics, results="asis", warning=FALSE}
+```{r tbl-descriptive-statistics, results="asis"}
 vars_to_summarize <- tribble(
-  ~variable, ~clean_name,
+  ~variable_name, ~clean_name,
   "donate_likely", "Likelihood of donation",
@@
 results_summary_stats <- results %>% 
-  select(one_of(vars_to_summarize$variable)) %>% 
-  gather(variable, value) %>% 
-  group_by(variable) %>% 
-  nest() %>% 
-  mutate(N = data %>% map_int(~ nrow(.)),
-         summary = map2(.x = data, .y = variable, ~ md_summary_row(.x$value, .y, results))) %>% 
-  left_join(vars_to_summarize, by = "variable") %>% 
-  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
-  arrange(variable) %>% 
-  select(-data, -variable) %>% 
+  select(one_of(vars_to_summarize$variable_name)) %>% 
+  summarise_all(~list(.)) %>% 
+  pivot_longer(everything(), names_to = "variable_name", values_to = "value") %>% 
+  mutate(N = value %>% map_int(~ length(na.omit(.))),
+         summary = map2(.x = value, .y = variable_name, ~ md_summary_row(.x, .y))) %>% 
+  left_join(vars_to_summarize, by = "variable_name") %>% 
+  mutate(variable_name = factor(variable_name, 
+                                levels = vars_to_summarize$variable_name, 
+                                ordered = TRUE)) %>% 
+  arrange(variable_name) %>% 
+  select(-value, -variable_name) %>% 
   unnest(summary) %>% 
@@
 
-```{r tbl-results-conditions, results="asis"}
+```{r tbl-results-conditions, warning=FALSE, results="asis"}
 conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
@@
                                 group_by(results, crackdown) %>% nest(),
-                                results %>% nest()) %>% 
+                                results %>% nest(data = everything())) %>% 
   arrange(crackdown, issue, funding) %>% 
@@
                            N = nrow(.)))) %>% 
-  unnest(summary) %>% select(-data)
+  unnest(summary) %>% select(-data) %>% ungroup()
 
@@
   mutate(model = stan_data_counts %>% map(~ {
-    sampling(donate_likely(), data = .x, control = list(max_treedepth = 15),
+    donate_likely(n_total_1 = .x$n_total_1, n_total_2 = .x$n_total_2,
+                  n_likely_1 = .x$n_likely_1, n_likely_2 = .x$n_likely_2,
+                  control = list(max_treedepth = 15),
                   chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
@@
   mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
-            funs(percent_format(accuracy = 0.1)(.))) %>% 
+            list(~percent_format(accuracy = 0.1)(.))) %>% 
   mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
@@
   mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
-            funs(percent_format(accuracy = 0.1)(.))) %>% 
+            list(~percent_format(accuracy = 0.1)(.))) %>% 
   mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
@@
 
-```{r run-amount-models, results="hide", cache=TRUE}
+```{r run-amount-models, results="hide", cache=TRUE, warning=FALSE}
 # Sample from the compiled model
@@
   mutate(model = stan_data %>% map(~ {
-    sampling(amount_donated_best(), data = compose_data(.x),
-             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+    amount_donated_best(df = .x, chains = CHAINS, iter = ITER, 
+                        warmup = WARMUP, seed = BAYES_SEED)
   }))
@@
                         Funding = "*Private − Government funding*")) %>% 
-  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
+  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), list(~as.character(round(., 2)))) %>% 
   mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
@@
   arrange(title_clean) %>% 
-  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
+  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), list(~as.character(round(., 2)))) %>% 
   mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
@@
   mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
-  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
+  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), list(~as.character(round(., 2)))) %>% 
   mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%

### 2020-01-20 analysis/02_analysis.Rmd
Update to use latest tidyverse conventions
list() instead of funs(); pivot_*() instead of gather() and spread()

@@
   select(title, term, estimate) %>% 
-  spread(term, estimate) %>% 
+  pivot_wider(names_from = term, values_from = estimate) %>%
   mutate(category = case_when(
@@
   mutate(value = (value)) %>% 
-  spread(name, value) %>% 
+  pivot_wider(names_from = name, values_from = value) %>% 
   set_names(colnames(tbl_likely_1))
@@
   select(title, term, estimate) %>% 
-  spread(term, estimate) %>% 
+  pivot_wider(names_from = term, values_from = estimate) %>% 
   mutate(category = case_when(
@@
   mutate(value = (value)) %>% 
-  spread(name, value) %>% 
+  pivot_wider(names_from = name, values_from = value) %>% 
   set_names(colnames(tbl_amount_1))

### 2020-01-20 analysis/03_additional-analysis.Rmd
Update to use latest tidyverse conventions
list() instead of funs(); pivot_*() instead of gather() and spread()

@@
 consort <- readRDS(here("data", "derived_data", "completion_summary.rds")) %>% 
-  spread(reason, n) %>% 
+  pivot_wider(names_from = reason, values_from = n) %>% 
   mutate(group = 1:n(),
@@
   # Remove values not in the universe
-  mutate_at(vars(VLSTATUS, VLDONATE), funs(ifelse(. == 99, NA, .)))
+  mutate_at(vars(VLSTATUS, VLDONATE), list(~ifelse(. == 99, NA, .)))
 
@@
                     .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
-  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
+  mutate_at(vars(National, Sample, diffs_median), list(percent)) %>% 
   select(Variable, Sample, National, 
@@
 time_summary <- results %>% 
-  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
+  summarize_at(vars(duration), list(Minimum = min, Maximum = max, Mean = mean, 
                                     `Standard deviation` = sd, Median = median)) %>% 
-  gather(Statistic, value) %>% 
+  pivot_longer(everything(), names_to = "Statistic", values_to = "value") %>% 
   mutate(Minutes = fmt_seconds(value)) %>% 

### 2020-01-20 README.Rmd
Add new installation instructions

@@
 Authors <- "Suparna Chaudhry and Andrew Heiss"
-Year <- "2019"
+Year <- "2020"
 ```
@@
 [Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
-[Andrew Heiss](https://www.andrewheiss.com/) • Romney Institute of Public Service and Ethics • Brigham Young University
+[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University
 
@@
 1. Open the compendium as a project in RStudio (double click on `crackdownsphilanthropy.proj`).
+
 2.
 Install the **pkgbuild**, **devtools**, **rstan**, and **rstantools** packages, either with RStudio's "Packages" panel or by running `install.packages(c("pkgbuild", "devtools", "rstan", "rstantools"))`
+
 3.
-Due to [strange](https://github.com/stan-dev/rstantools/issues/52) [incompatibilties](https://github.com/klutometis/roxygen/issues/822#issuecomment-441425591) with **roxygen2** and **rstantools**, you need to compile the Stan C++ binary DLLs before building the actual **crackdownsphilanthropy** compendium package.
-Run `pkgbuild::compile_dll()` and wait a few minutes while the Stan models are built.
-4. Finally, build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.
+You need to compile the Stan c++ binary DLLs before building and installing the actual  **crackdownsphilanthropy** compendium package ([see here for details about why](https://mc-stan.org/rstantools/articles/minimal-rstan-package.html#documentation)).
+Run these two lines in R:
+
+    ```r
+    pkgbuild::compile_dll()  # This will probably take a few minutes
+    roxygen2::roxygenize()
+    ```
+
+4. Finally, build the compendium package by running this in R:
+
+    ```r
+    devtools::install(".")
+    ```
 

### 2020-01-20 manuscript/manuscript.Rmd
Suparna edits

@@
 Existing research has predominantly focused on individual-level determinants of philanthropy.
-However, we argue that domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness.
+However, we argue that structural factors such as domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness.
 Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO.
@@
 
-The 2011 Egyptian uprising presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state.
-However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
-Egypt is not alone in its non-violent crackdown on NGOs.
-India, Bolivia, Hungary, China, Russia, and others have imposed funding and programmatic restrictions on NGOs  [@Carothers:2015; @DPR:2015].
-These laws have tangible consequences for NGOs worldwide.
-Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in repressive countries [@Brechenmacher:2017].
+Following the 2011 Egyptian uprising, just as domestic non-governmental organizations (NGOs) began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
+Egypt is not alone in its crackdown on NGOs.
+India, Bolivia, Hungary, Russia, and others have imposed funding restrictions on NGOs  [@Carothers:2015; @DPR:2015].
+Consequently, official aid flows as well as grants from large foundations have considerably decreased to NGOs in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 
@@
 This is because donations from *domestic* donors in repressive countries are unreliable and inconsistent.
-Citizens in the Global South often cannot support local NGOs, may lack a culture of philanthropic giving, or may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
-Even when donors in repressive countries prefer to donate to NGOs working in contentious areas, they may be deterred by dismal tax incentives, threats to take away business permits, or a general fear of retribution [@HudsonInstitute:2015].
+Citizens in the Global South often cannot support local NGOs, may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017], or may be deterred by dismal tax incentives, threats to take away business permits, or a general fear of retribution [@HudsonInstitute:2015].
 Therefore, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
-Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing resources to raise similar sums locally [@RonKairePandya:2018].
+By 2016, the amount directed towards civil society groups working in international affairs increased to \$22.03 billion [@givingusa:2017].
+As Daniel Runde pointed out in a statement before a U.S.
+Senate subcommittee on multilateral institutions, “U.S.
+philanthropy is significant [for global philanthropic efforts] but it is mainly Ms.
+Smith and Mr.
+Johnson, [n]ot Mr.
+and Mrs.
+Gates” [@Runde:2017].
 
@@
 Do legal restrictions on NGOs influence donors' decision to donate?
-We argue that domestic political environments of NGO host countries can influence preferences of foreign private donors and that legal crackdowns on NGOs serve as a heuristic to donors of organizational deservingness.
+Given information asymmetry and time constraints, individual donors often use heurestics to simply their decision-making [@TverskyKahneman:1974].
+While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note, we argue that domestic political environments of NGO host countries can also serve as one such structural heuristic that can influence individual donor decisions.
+In particular, legal crackdowns on NGOs serve as a heuristic to donors of organizational deservingness and when donors are provided salient information about crackdown on NGOs and its impact on NGO activities, it can influence donor preferences and behavior.
 We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
-This effect persists when mediated by other structural heuristics like NGO issue area and its main funding sources.
+This effect persists when mediated by other organizational-level heuristics like NGO issue area and its main funding sources.
+
+This research note two important contributions.
+While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid.
+Further, while there is a robust existing literature on the individual-level determinants of philanthropy, far less is known about structural determinants that influence philanthropy, particularly towards international causes, and how these factors interact with organizational attributes to signal NGO deservingness.
+
+Below, we first summarize existing research on the determinants of philanthropic-giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect charitable-giving.
+We then describe our survey and present the results.
+We conclude with implications for NGOs working in repressive countries and lay out questions ripe for future research.
 
@@
 
+Substantial research on charitable-giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018].
+However, lesser research on focused on the impact of structural factors on the choice to donate.
+Moreover, research on individual donor behavior has overwhelming looked at giving to local, rather than international causes.
+While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore individual giving to such causes becauses on individuals may rely on signals or heurestics that differ from the benchmarks that large donors (whether official or private) rely on.
+
 The decision to donate to an NGO is rarely rational.
-In theory, perfectly rational donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation.
-Instead, research has shown that donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs.
+In theory, perfectly rational donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
+Existing research shows that information on the efficiency of NGOs merely steers rather than encourage or discourage overall donations [@ryazanov:efficiency].
+Similarly, the effects of changes in charity watchdog rations and nonprofit accountability systems on individual donors is also mixed - showing that donors do not have the time to research charities thoroughly [@Bekkers:2010; @SzperPrakash:2011].
+Instead, donors respond to a host of heurestics and signals when deciding whether to donate to an NGOs, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
-In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness, structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
 
+We argue that in addition to the above factors that signal an NGO's trustworthiness and deservingness, structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
 We propose that the regulatory relationship between international NGOs and their host governments serves as a signal of NGO trustworthiness and deservingness.
@@
 Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
-These stricter anti-NGO laws can signal to donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
-Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:
+These stricter anti-NGO laws can signal to donors that governments perceive these groups as threatening and may crack down on them.
+
+We argue that donors may process legal crackdowns differently from organizational-level heuristics - such as NGO missions, visions, values- because donors may be able to influence these latter attributes, at least to some extent.
+On the other hand, donors may perceive that they can do little to change the domestic political environment of another country.
+Such crackdowns can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally beseiged NGOs, even if donors are not completely satisfied with some organizational-level features of a group.
+As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:
 
@@
 Countries are more likely to repress NGOs when organizational missions (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
-Each of these organizational characteristics increase the likelihood of crackdown but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.
+Both of these organizational characteristics increase the likelihood of crackdown but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.
 
@@
 
-The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences—can influence donor behavior.
-Donors commonly support programs that have easily measurable goals and successes, and NGOs working on regime-compatible issues like health, education, and humanitarian relief rarely challenge the government [@Bush:2015; @Kiai:2017].
-As such, their programmatic output is easily quantifiable and donors can see the results of their charity more readily.
-In contrast, NGOs working on more contentious human rights issues can pose political challenges to regimes.
+Another heurestic that individual donors may use for determining NGO deservingness is the *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences.[^targeting] Organizations that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
+Further, their programmatic output is easily quantifiable and donors can see the results of their charity more readily [@Bush:2015].
+NGOs working on these issues can also frame their activities as in need of greater support.
+Perception of need, whether through personal experiences or media framing strongly influence individual decisions to donate to relief efforts [@BekkersWiepking:2010, 6-8].
+
+In contrast, donors may shy from donating to groups working on political causes.
+NGOs working on more contentious human rights issues can be challenging to regimes.
 These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources.
-Due to the nature of the political and social issues they work on, programmatic effectiveness is also harder to measure and quantify [@Bush:2015].
 Thus, donors may believe that it is more difficult to improve human rights in the target country and reduce their donations.
@@
 
-The *source of NGO funding* can also influence donor behavior.
-Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003].
-Donors may feel less inclined to contribute to NGOs receiving government funding, as they might perceive that their tax money already funds the organization.
-Government funding can also signal a lack of independence from the government.
-Organizations that receive substantial government funding frequently avoid programming that would question the government even if it were in line with their mission [@Stroup:2012].
-In contrast, donors who see that organizations are privately funded may feel that they can also contribute and help.
+The final heurestic that can influence individual donors that we examine is the *source of NGO funding*.
+Government grants to NGOs can often crowd out private funding for nonprofit organizations[@AndreoniPayne:2003], though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991].
+Donors may feel less inclined to contribute to NGOs receiving home government funds because such funding can signal a lack of independence from the government.
+Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if it were in line with their mission [@Stroup:2012].
+In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help.
 
@@
 As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
-Private donors may be more likely to punish government-funded NGOs that face restrictions.
+Private donors may be less likely to donate to government-funded NGOs that face restrictions.
 This is because legal trouble with the group's main funder could fuel private donor mistrust.
@@
 > **H~3b~**: If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will donate more to them.
+
+In these three sets of hypotheses, we do not assume perfect knowledge among individual donors.
+Donors may not always know about anti-NGO laws in target countries, or who funds an NGO, when they make their contributions.
+Rather, the three heuristics we explore here are potential signals to donors and our intention is to vary these three factors to test how powerful these factors are in comparison to other individual and organizational-level attributes.
+This can ultimately help NGOs optimize their fundraising strategies and tailor their fundraising attempts to private individuals.
 
@@
 Many echoed this respondent, who identified the crackdown condition as one of the reasons for giving the full hypothetical \$100: "I believe the work of such organizations has an urgency that affects many refugees and their families.
-If they can function without being affected by the harsh laws against non-profits, I would want them to have as much help as possible to do their humanitarian work."[^1097165]
+If they can function without being affected by the harsh laws against non-profits, I would want them to have as much help as possible to do their humanitarian work."[^1097165] Thus, legal crackdowns can increase individual donor urgency to support an organization, and this heuristic is potentially processed differently compared to other organization-level heuristics or information from social networks.
 
@@
 
-# Conclusion
+# Discussion: Does NGO crackdown affect individual philanthropy?
 
-Dozens of countries have legally restricted NGO funding and programming.
+Dozens of countries have sought to restrict NGO funding and programming.
 Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors as an additional funding source.
-Do ongoing legal crackdowns influence these donors' decision to donate?
-Our results show that legal restrictions provide donors with an additional signal of NGO deservingness and efficiency and can change both the likelihood that donors will give and the amount they will give.
-While crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
-This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs, and `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)` more to government-funded humanitarian NGOs.
+Since seeking out perfect information about a nonprofit and its activities, especially internationally, is costly and time-consuming, donors use heuristics when deciding whom to support.
+Existing research has shown that donors take cues and heuristis from social netowrks, but can other information cues can influence donor preferences?
+This research note argues that domestic political environments of NGO host countries can serve as one such heuristic.
+Our results show that crackdowns provide donors with an additional signal of NGO deservingness and efficiency and can change both the likelihood that donors will give and the amount they will give.
+We find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
+This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs.
 Anti-NGO crackdowns can thus serve as a signal of NGO effectiveness.
 
-This study makes two important contributions.
-While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid.
-Further, prior literature on the determinants of donation to NGOs focuses predominantly on individual-level factors.
-Our study measures important structural determinants that influence philanthropy and shows how these factors interact with organizational attributes to signal NGO deservingness.
-Additional research should determine the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation—as well as test the generalizability of our findings to other issue areas.
+This research note should be viewed as an exploratory study, and it raises numerous quesitions for future research.
+These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior.
+Future research can also test the generalizability of our findings to other issue areas.
 
-This has several implications for policy and future research.
+These results have several implications for policy.
 NGOs may benefit from publicizing when they are targets of government crackdown.
@@
 citizen, our results show that communicating this information can convince already-likely donors to donate more to besieged groups.
-Our study also highlights the importance of framing NGO operations.
+Further, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
+Moreover, since private funders typically tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.
+
+THIS PART ONLY IF WORDS LEFT: Our study also highlights the importance of framing NGO operations.
 Previous research on human rights micro-mobilization has shown that the way people process information can affect their increased willingness to help others in need [@Slovic:2007].
@@
 However, human rights groups undertake a variety of programs, and communicating the nature of their work and specifying the main target of the organization's efforts can allay the public's fears.
-Finally, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
-Moreover, since private funders typically tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.
 
@@
 [^priors]: See the supplement for details about our prior choices and computational environment.
+
+[^targeting]: While anti-NGO legislation (in the form of barriers to entry, funding, and advocacy) can theoretically tatget all NGOs (or a large subset of them) within a state's borders, in practices, these laws are enforced more selectively against contentious groups that pose threats to states.
+See Chaudhry (2016) and Heiss (2017).
 

### 2020-01-20 manuscript/manuscript.Rmd
Some more edits

@@
 author-note: >-
-  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Visiting Assistant Professor, Romney Institute of Public Service and Ethics, Brigham Young University.
+  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University.
 additional-info: Figures should appear in color online only, not in print.
@@
   mutate_at(vars(delta, p_neq0),
-            funs(ifelse(title == "Funding",
+            list(~ifelse(title == "Funding",
                          str_replace(., "Delta", "Delta_\\\\text{funding}"), .))) %>%
   mutate_at(vars(delta, p_neq0),
-            funs(ifelse(title == "Issue",
+            list(~ifelse(title == "Issue",
                          str_replace(., "Delta", "Delta_\\\\text{issue}"), .)))
@@
 Do legal restrictions on NGOs influence donors' decision to donate?
-Given information asymmetry and time constraints, individual donors often use heurestics to simply their decision-making [@TverskyKahneman:1974].
+Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974].
 While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note, we argue that domestic political environments of NGO host countries can also serve as one such structural heuristic that can influence individual donor decisions.
@@
 
-This research note two important contributions.
+This research note makes two important contributions.
 While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid.
@@
 Substantial research on charitable-giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018].
-However, lesser research on focused on the impact of structural factors on the choice to donate.
+However, little research has focused on the impact of structural factors on the choice to donate.
 Moreover, research on individual donor behavior has overwhelming looked at giving to local, rather than international causes.
-While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore individual giving to such causes becauses on individuals may rely on signals or heurestics that differ from the benchmarks that large donors (whether official or private) rely on.
+While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropic giving because individuals rely on signals and heuristics that differ from the benchmarks that large donors (whether official or private) rely on.
 
@@
 Existing research shows that information on the efficiency of NGOs merely steers rather than encourage or discourage overall donations [@ryazanov:efficiency].
-Similarly, the effects of changes in charity watchdog rations and nonprofit accountability systems on individual donors is also mixed - showing that donors do not have the time to research charities thoroughly [@Bekkers:2010; @SzperPrakash:2011].
-Instead, donors respond to a host of heurestics and signals when deciding whether to donate to an NGOs, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
+Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010; @SzperPrakash:2011].
+Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGOs, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
 
-We argue that in addition to the above factors that signal an NGO's trustworthiness and deservingness, structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
+In addition to the above factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
 We propose that the regulatory relationship between international NGOs and their host governments serves as a signal of NGO trustworthiness and deservingness.
-NGO legislation is not inherently restrictive, and governments frequently use regulations to benignly routinize the behavior of NGOs [@BloodgoodTB].
+NGO legislation is not inherently restrictive, and governments frequently use permissive regulations to benignly routinize the behavior of NGOs [@BloodgoodTB; @DeMattee:2018].
 Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
@@
 
-We argue that donors may process legal crackdowns differently from organizational-level heuristics - such as NGO missions, visions, values- because donors may be able to influence these latter attributes, at least to some extent.
-On the other hand, donors may perceive that they can do little to change the domestic political environment of another country.
-Such crackdowns can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally beseiged NGOs, even if donors are not completely satisfied with some organizational-level features of a group.
+We argue that donors perceive legal crackdowns differently from organizational-level heuristics—such as NGO missions, visions, values—because donors may be able to influence these latter attributes, at least to some extent.
+On the other hand, donors can do little to change the domestic political environment of another country.
+Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organizational-level features of a group.
 As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:
@@
 @fig:causal-path represents this relationship more formally.
-Legal crackdowns (**C**) have a direct effect on donor outcomes (**Y**; donation likelihood and amount) because of their heuristic function.
+Legal crackdowns (**C**) have a direct effect on donor decisions (**Y**; donation likelihood and amount) because of their heuristic function.
 Legal crackdowns do not occur in isolation, however.
@@
 
-Another heurestic that individual donors may use for determining NGO deservingness is the *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences.[^targeting] Organizations that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
+Another heuristic that individual donors may use for determining NGO deservingness is the *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences.[^targeting] Organizations that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
 Further, their programmatic output is easily quantifiable and donors can see the results of their charity more readily [@Bush:2015].
@@
 
-In these three sets of hypotheses, we do not assume perfect knowledge among individual donors.
-Donors may not always know about anti-NGO laws in target countries, or who funds an NGO, when they make their contributions.
-Rather, the three heuristics we explore here are potential signals to donors and our intention is to vary these three factors to test how powerful these factors are in comparison to other individual and organizational-level attributes.
-This can ultimately help NGOs optimize their fundraising strategies and tailor their fundraising attempts to private individuals.
+Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the countries an NGO works in.
+Donors may not always know about anti-NGO laws in target countries or who funds an NGO when they make their contributions.
+Rather, the heuristics we explore here are shortcuts to donor information-gathering.
+To measure the effect of these signals on the propensity and amount of individual donations, we use an experiment to vary the different organizational and structural signals donors are exposed to.
+Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs optimize and tailor their fundraising strategies for private individuals.
 
@@
 
-# Discussion: Does NGO crackdown affect individual philanthropy?
+# Discussion: Do crackdowns on NGOs affect individual philanthropy?
 
@@
 Since seeking out perfect information about a nonprofit and its activities, especially internationally, is costly and time-consuming, donors use heuristics when deciding whom to support.
-Existing research has shown that donors take cues and heuristis from social netowrks, but can other information cues can influence donor preferences?
-This research note argues that domestic political environments of NGO host countries can serve as one such heuristic.
+Existing research has shown that donors take cues and heuristics from social networks, but can other information cues influence donor preferences?
+We argue that domestic political environments of NGO host countries can indeed serve as one such heuristic.
 Our results show that crackdowns provide donors with an additional signal of NGO deservingness and efficiency and can change both the likelihood that donors will give and the amount they will give.
@@
 
-This research note should be viewed as an exploratory study, and it raises numerous quesitions for future research.
+This research note should be viewed as an exploratory study, and it raises numerous questions for future research.
 These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior.
 Future research can also test the generalizability of our findings to other issue areas.
+TODO OTHER THINGS: Crackdown in authoritarian regimes, but there's an increase in restrictive laws in democracies [@Swiney:2019]
 
@@
 
-[^targeting]: While anti-NGO legislation (in the form of barriers to entry, funding, and advocacy) can theoretically tatget all NGOs (or a large subset of them) within a state's borders, in practices, these laws are enforced more selectively against contentious groups that pose threats to states.
-See Chaudhry (2016) and Heiss (2017).
+[^targeting]: While anti-NGO legislation (in the form of barriers to entry, funding, and advocacy) can theoretically target all NGOs (or a large subset of them) within a state's borders, in practices, these laws are enforced more selectively against contentious groups that pose threats to states.
+See @Chaudhry:2016 and @Heiss:2017.
 

### 2020-01-20 manuscript/manuscript.Rmd
More edits to hypothesis section

@@
 Legal crackdowns do not occur in isolation, however.
-Countries are more likely to repress NGOs when organizational missions (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
-Both of these organizational characteristics increase the likelihood of crackdown but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.
+Countries are more likely to repress NGOs both when organizational issue areas (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
+Both of these organizational characteristics thus confound the causal effect of crackdowns on donor decisions and must be accounted for in the analysis—issue areas and funding sources simultaneously influence the likelihood of crackdown while also serving as organizational heuristics that influence donor perceptions of NGO deservingness.
 
@@
 
-Another heuristic that individual donors may use for determining NGO deservingness is the *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences.[^targeting] Organizations that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
+The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences—can serve as an organization-level heuristic.[^targeting] NGOs that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
 Further, their programmatic output is easily quantifiable and donors can see the results of their charity more readily [@Bush:2015].
-NGOs working on these issues can also frame their activities as in need of greater support.
-Perception of need, whether through personal experiences or media framing strongly influence individual decisions to donate to relief efforts [@BekkersWiepking:2010, 6-8].
+NGOs working on these less contentious issues can also frame their activities as in need of greater support—the perception of need, whether through personal experiences or media framing, strongly influences individual decisions to donate to relief efforts [@BekkersWiepking:2010, 6–8].
 
-In contrast, donors may shy from donating to groups working on political causes.
-NGOs working on more contentious human rights issues can be challenging to regimes.
+Issue area contentiousness directly influences legal crackdowns, however, and confounds the heuristic effect of crackdowns on donor behavior (see @fig:causal-path).
+NGOs working on more contentious human rights issues can be challenging to regimes [@Heiss:2016; @Swiney:2019].
 These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources.
-Thus, donors may believe that it is more difficult to improve human rights in the target country and reduce their donations.
+Thus, donors may believe that it is more difficult to improve human rights in the target country and subsequently shy away from donating to NGOs working on political causes.
 
 We hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, and directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
-We use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues:
+We use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues.
 
@@
 
-The final heurestic that can influence individual donors that we examine is the *source of NGO funding*.
-Government grants to NGOs can often crowd out private funding for nonprofit organizations[@AndreoniPayne:2003], though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991].
+The final heuristic that can influence individual donors that we examine is the *source of NGO funding*.
+Government grants to NGOs can often crowd out private funding for nonprofit organizations [@AndreoniPayne:2003; @Brooks:2000], though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
 Donors may feel less inclined to contribute to NGOs receiving home government funds because such funding can signal a lack of independence from the government.
@@
 
-As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding can influence anti-NGO crackdowns (see @fig:causal-path).
+As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding again confounds the effect of anti-NGO crackdowns on donor behavior (see @fig:causal-path).
 As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
-Private donors may be less likely to donate to government-funded NGOs that face restrictions.
-This is because legal trouble with the group's main funder could fuel private donor mistrust.
-Donors thus may be more likely to donate more to NGOs that rely on private funding:
+Individual donors may be less likely to donate to government-funded NGOs that face restrictions, since legal trouble with the organization's primary funder could fuel private donor mistrust (i.e.
+perhaps the NGO did something to deserve crackdown).
+Donors thus may be more likely to donate more to NGOs that rely on private funding.
 
@@
 Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the countries an NGO works in.
-Donors may not always know about anti-NGO laws in target countries or who funds an NGO when they make their contributions.
-Rather, the heuristics we explore here are shortcuts to donor information-gathering.
+Donors do not always know about anti-NGO laws in target countries or who funds an NGO when they make their contributions.
+Moreover, the average donor will not know exactly what "legal crackdown" entails for any given organization (i.e.
+does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?".
+For the sake of this experiment, this ambiguous definition is not an issue.
+The heuristics we explore here are explicitly simplified shortcuts to donor information-gathering.
+Knowing that an organization works with human rights issues (even if they don't know the exact subfield of human rights) should be enough to trigger the issue-based deservingess heuristic.
+Similarly, knowing that an NGO faces legal trouble should be enough to trigger the structural deservingness heuristic.
+
+# Research design
+
 To measure the effect of these signals on the propensity and amount of individual donations, we use an experiment to vary the different organizational and structural signals donors are exposed to.
@@
 
-# Research Design
-
 ## Sample
 
-We test these hypotheses with a vignette-based survey experiment fielded through Amazon's Mechanical Turk.
-Our target population is the portion of Americans hypothetically willing to donate money for human rights and humanitarian work abroad.
+We test these hypotheses with a vignette-based survey experiment fielded through Amazon's Mechanical Turk.[^mturk] Our target population is the portion of Americans hypothetically willing to donate money for human rights and humanitarian work abroad.
 Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples.[^supp]
@@
 
-[^targeting]: While anti-NGO legislation (in the form of barriers to entry, funding, and advocacy) can theoretically target all NGOs (or a large subset of them) within a state's borders, in practices, these laws are enforced more selectively against contentious groups that pose threats to states.
-See @Chaudhry:2016 and @Heiss:2017.
+[^mturk]: TODO: Justify MTurk here.
+
+[^targeting]: While anti-NGO legislation (in the form of barriers to entry, funding, and advocacy) can theoretically target all NGOs (or a large subset of them) within a state's borders, in practices, these laws are enforced more selectively against contentious groups that pose threats to states [see @Chaudhry:2016; @Heiss:2017].
 

### 2020-01-21 analysis/02_analysis.Rmd
Change width of figures

@@
 
-```{r causal-dag, fig.width=10/3, fig.height=2}
+```{r causal-dag, fig.width=4.75, fig.height=2}
 theory_dag <- dagify(Y ~ I + C + F,
@@
   ggsave(., filename = here("analysis", "output", "figures", "causal-path.pdf"),
-         width = 10/3, height = 2, units = "in", device = cairo_pdf) %>% 
+         width = 4.75, height = 2, units = "in", device = cairo_pdf) %>% 
   ggsave(., filename = here("analysis", "output", "figures", "causal-path.png"),
-         width = 10/3, height = 2, units = "in", type = "cairo", dpi = 300)
+         width = 4.75, height = 2, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r plot-likely-diffs, warning=FALSE, fig.width=10/3, fig.height=5.5}
+```{r plot-likely-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
 tidied_diffs_likely <- all_models_likely %>% 
@@
   ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.pdf"),
-         width = 10/3, height = 5.5, units = "in", device = cairo_pdf) %>%
+         width = 4.75, height = 5.5, units = "in", device = cairo_pdf) %>%
   ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.png"),
-         width = 10/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
+         width = 4.75, height = 5.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r plot-amount-diffs, warning=FALSE, fig.width=10/3, fig.height=5.5}
+```{r plot-amount-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
 # This will generate a warning because unnest() puts the crackdown values into
@@
   ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.pdf"),
-         width = 10/3, height = 5.5, units = "in", device = cairo_pdf) %>%
+         width = 4.75, height = 5.5, units = "in", device = cairo_pdf) %>%
   ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.png"),
-         width = 10/3, height = 5.5, units = "in", type = "cairo", dpi = 300)
+         width = 4.75, height = 5.5, units = "in", type = "cairo", dpi = 300)
 ```

### 2020-01-21 analysis/02_analysis.Rmd
Add labels to DAG

@@
                      outcome = "Y",
-                     exposure = "C") %>% 
+                     exposure = "C",
+                     labels = c("Y" = "Outcome (Likelihood of donation & amount donated)", 
+                                "C" = "Anti-NGO legal crackdown", 
+                                "I" = "NGO issue area", 
+                                "F" = "NGO funding source")) %>% 
   tidy_dagitty(layout = "sugiyama")
@@
   geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
+  geom_dag_label_repel(aes(label = label), size = pts(6), box.padding = 0.1, 
+                       direction = "x", seed = 12345,
+                       family = "Roboto Condensed", fontface = "plain") +
   theme_ngos() +

### 2020-01-21 analysis/03_additional-analysis.Rmd
Add original interacted regressions + probit for likelihood collapse

@@
 library(rstan)
+library(rstanarm)
 library(broom)
@@
 library(ipumsr)
+library(huxtable)
 library(here)
@@
 source(here("analysis", "options.R"))
+
+# Print correct huxtable table depending on the type of output.
+#
+# Technically this isn't completely necessary, since huxtable can output a
+# markdown table, which is ostensibly universal for all output types. However,
+# markdown tables are inherently limited in how fancy they can be (e.g. they
+# don't support column spans), so I instead let the regression table use
+# huxtable's fancy formatting for html and PDF and markdown everywhere else.
+if (isTRUE(getOption('knitr.in.progress'))) {
+  file_format <- rmarkdown::all_output_formats(knitr::current_input())
+} else {
+  file_format <- ""
+}
+
+print_hux <- function(x) {
+  if ("html_document" %in% file_format) {
+    print_html(x)
+  } else if ("pdf_document" %in% file_format) {
+    print_latex(x)
+  } else if ("word_document" %in% file_format) {
+    print_md(x)
+  } else {
+    print(x)
+  }
+}
 
@@
 
+# Balance
+
+```{r}
+
+```
+
 # Characteristics of experiment samples
@@
 
+# Results using interaction terms
+
+In our preregistration protocol, we said we'd calculate the differences in group means using a regression model with 3-way interaction terms.
+This was mostly for the sake of simplicity—running one model is easier than running multiple individual tests—but the interpretation is a complicated mess.
+So instead, we ran individual difference in mean tests for the actual paper.
+For the sake of transparency, though, here are the results from the fully interacted regression models.
+
+## Interpreting interactions in models
+
+Ordinarily, people use ANOVA to analyze 3-way, 2 × 2 × 2 factorial designs, [like this](https://mypages.valdosta.edu/mwhatley/3600/2x2x2.htm).
+A more flexible ([yet identical!](https://www.theanalysisfactor.com/why-anova-and-linear-regression-are-the-same-analysis/)) way to do this is to use a regular regression model with interaction terms for each of the conditions, like so (here we use three, since we can use simper models to get averages for the larger umbrella groups, like just crackdowns and crackdown + issue):
+
+- Model 1:
+
+    $$
+    y = \beta_0 + \beta_1 \text{Crackdown}
+    $$
+
+- Model 2:
+
+    $$
+    \begin{aligned}
+    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue } + \\
+    & \beta_3 \text{Crackdown} \times \text{Issue}
+    \end{aligned}
+    $$
+
+- Model 3:
+
+    $$
+    \begin{aligned}
+    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue} + \beta_3 \text{Funding } + \\
+    & \beta_4 \text{Crackdown} \times \text{Issue } + \\
+    & \beta_5 \text{Crackdown} \times \text{Funding } + \\
+    & \beta_6 \text{Issue} \times \text{Funding } + \\
+    & \beta_7 \text{Crackdown} \times \text{Issue} \times \text{Funding}
+    \end{aligned}
+    $$
+
+Adding different combinations of the coefficients provides the average values for each combination of factors, which corresponds to the average likelihood and amount donated.
+
+```{r interaction-interpretation, warning=FALSE, message=FALSE, results="asis"}
+model1 <- "1"
+model2 <- "2"
+model3 <- "3"
+
+interpretation <- tribble(
+  ~Model, ~`Coefficients to add together`,
+  model3, "Intercept",
+  model3, "Intercept + Funding",
+  model2, "Intercept",
+  model3, "Intercept + Issue",
+  model3, "Intercept + Issue + Funding + (Issue × Funding)",
+  model2, "Intercept + Issue",
+  model1, "Intercept",
+  model3, "Intercept + Crackdown",
+  model3, "Intercept + Crackdown + Funding + (Crackdown × Funding)",
+  model2, "Intercept + Crackdown",
+  model3, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
+  model3, "Intercept + Crackdown + Issue + Funding + (Crackdown × Issue) + (Crackdown × Funding) + (Issue × Funding) + (Crackdown × Issue × Funding)",
+  model2, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
+  model1, "Intercept + Crackdown"
+)
+
+conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
+                                group_by(results, crackdown, issue) %>% nest(),
+                                group_by(results, crackdown) %>% nest(),
+                                results %>% nest(data = everything())) %>% 
+  arrange(crackdown, issue, funding) %>% 
+  select(-data) %>% ungroup() %>% 
+  mutate(funding = ifelse(is.na(funding) & !is.na(issue) , "*Total*", as.character(funding)),
+         issue = ifelse(is.na(issue) & !is.na(crackdown), "*Total*", as.character(issue)),
+         crackdown = ifelse(is.na(crackdown), "*Total*", as.character(crackdown))) %>% 
+  group_by(crackdown) %>% 
+  mutate(issue = replace(issue, duplicated(issue), NA)) %>% 
+  ungroup() %>% 
+  mutate(crackdown = replace(crackdown, duplicated(crackdown), NA)) %>% 
+  rename(`Crackdown condition` = crackdown, `Issue condition` = issue,
+         `Funding condition` = funding)
+
+conditions_summary %>% 
+  slice(-n()) %>% 
+  bind_cols(interpretation) %>% 
+  pandoc.table()
+```
+
+## Amount donated
+
+```{r build-models-amount, warning=FALSE, message=FALSE, results="hide", cache=TRUE}
+# Basic interaction models
+m_amount_c <- stan_glm(amount_donate ~ crackdown,
+                       data = results, family = gaussian(),
+                       prior = cauchy(location = 0, scale = 2.5),
+                       prior_intercept = cauchy(location = 0, scale = 10),
+                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)
+m_amount_cif <- update(m_amount_c, . ~ . + 
+                         issue + funding + crackdown * issue + crackdown * funding + 
+                         issue * funding + crackdown * issue * funding)
+# Models with just issue and just funding
+m_amount_i <- update(m_amount_c, . ~ issue)
+m_amount_f <- update(m_amount_c, . ~ funding)
+```
+
+```{r tbl-models-amount, warning=FALSE, results="asis"}
+# Get subset of coefficients
+coefs_to_include <- list(m_amount_c, m_amount_ci, m_amount_cif) %>% 
+  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)
+
+huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
+       coefs = coefs_to_include,
+       statistics = c(Observations = "nobs",
+                       `Posterior sample size` = "pss",
+                       Sigma = "sigma"),
+       stars = NULL) %T>% 
+  print_hux() %>% 
+  to_md(max_width = 100) %>% 
+  cat(file = here("analysis", "output", "tables", "tbl-interactions-amount.md"))
+```
+
+## Likelihood of donation
+
+```{r build-models-likely, warning=FALSE, message=FALSE, reuslts="hide", cache=TRUE}
+# Basic interaction models
+# Weakly informative student t priors, since these coefficients are log-odds
+# See https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations#prior-for-the-regression-coefficients-in-logistic-regression-non-sparse-case and https://arxiv.org/abs/1507.07170
+m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
+                       data = results, family = binomial(link = "logit"),
+                       prior = student_t(3, 0, 2.5),
+                       prior_intercept = student_t(3, 0, 10),
+                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
+
+m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)
+
+m_likely_cif <- update(m_likely_c, . ~ . + 
+                         issue + funding + crackdown * issue + crackdown * funding + 
+                         issue * funding + crackdown * issue * funding)
+
+# Models with just issue and just funding
+m_likely_i <- update(m_likely_c, . ~ issue)
+m_likely_f <- update(m_likely_c, . ~ funding)
+```
+
+```{r tbl-models-likely, warning=FALSE, results="asis"}
+# Get subset of coefficients
+coefs_to_include <- list(m_likely_c, m_likely_ci, m_likely_cif) %>% 
+  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)
+
+huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
+       coefs = coefs_to_include,
+       statistics = c(Observations = "nobs",
+                       `Posterior sample size` = "pss",
+                       Sigma = "sigma"),
+       stars = NULL) %T>% 
+  print_hux() %>% 
+  to_md(max_width = 100) %>% 
+  cat(file = here("analysis", "output", "tables", "tbl-interactions-likelihood.md"))
+```
+
+# Collapsing likelihood variable
+
+To simplify our analysis, we collapse our likelihood scale from a 1-5 Likert scale to a binary variable:
+
+```{r show-collapsed-levels, results="asis"}
+collapsed_likelihood <- tribble(
+  ~`Original answer`, ~`Collapsed answer`,
+  "Extremely likely", "Likely",
+  "Somewhat likely", "Likely",
+  "Neither likely nor unlikely", "Unlikely",
+  "Somewhat unlikely", "Unlikely",
+  "Extremely unlikely", "Unlikely"
+)
+
+collapsed_likelihood %>% 
+  pandoc.table(justify = "ll")
+```
+
+To check that the results are internally consistent when collapsed, we ran an ordered probit model 
+(using Stan) to see if the cutpoints follow the distribution of answers, and they do.
+"Somewhat likely" and above has a cutpoint of > 0.18, meaning that the likelihood is positive on average for both "Somewhat likely" and "Extremely likely."
+
+```{r collapsed-probit, warning=FALSE, message=FALSE, results="hide", cache=TRUE}
+collapsed_oprobit <- stan_polr(donate_likely ~ crackdown, data = results,
+                               prior = R2(0.25, what = "mean"), prior_counts = dirichlet(1),
+                               method = "probit")
+```
+
+```{r show-collapsed-probit, results="asis"}
+huxreg(collapsed_oprobit,
+       coefs = c("Crackdown" = "crackdownCrackdown",
+                 "Cutpoint: Extremely unlikely|Somewhat unlikely" = 
+                   "Extremely unlikely|Somewhat unlikely",
+                 "Cutpoint: Somewhat unlikely|Neither likely nor unlikely" = 
+                   "Somewhat unlikely|Neither likely nor unlikely",
+                 "Cutpoint: Neither likely nor unlikely|Somewhat likely" = 
+                   "Neither likely nor unlikely|Somewhat likely",
+                 "Cutpoint: Somewhat likely|Extremely likely" = 
+                   "Somewhat likely|Extremely likely"),
+       statistics = c(Observations = "nobs",
+                       `Posterior sample size` = "pss"),
+       stars = NULL) %>%
+  set_align(everywhere, 1, "left") %>% 
+  set_align(everywhere, 2, "center") %>% 
+  set_position("left") %>% 
+  set_caption("Ordered probit regression with donation likelihood as outcome variable {#tbl:probit-likelihood}") %T>% 
+  print_hux() %>% 
+  to_md(max_width = 140) %>% 
+  cat(file = here("analysis", "output", "tables", "tbl-probit-likelihood.md"))
+```
+
 # Miscellaneous survey details

### 2020-01-21 manuscript/manuscript.Rmd
More final-ish edits

@@
 - name: Andrew Heiss
-  affiliation: Brigham Young University
-  email: andrew_heiss@byu.edu
+  affiliation: Georgia State University
+  email: aheiss@gsu.edu
   url: https://www.andrewheiss.com/
@@
 
-![Causal diagram showing causes of donor behavior.
-Y = likelihood of donation and amount donated; C = anti-NGO legal crackdown, I = NGO issue area, F = NGO funding source.](output/figures/causal-path.pdf){#fig:causal-path}
+![Causal diagram of the relationship of organizational and structural causes of donor behavior](output/figures/causal-path.pdf){#fig:causal-path}
 
@@
 Issue area contentiousness directly influences legal crackdowns, however, and confounds the heuristic effect of crackdowns on donor behavior (see @fig:causal-path).
-NGOs working on more contentious human rights issues can be challenging to regimes [@Heiss:2016; @Swiney:2019].
+NGOs working on more contentious human rights issues can be challenging to regimes [@Heiss:2017; @Swiney:2019].
 These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources.
-Thus, donors may believe that it is more difficult to improve human rights in the target country and subsequently shy away from donating to NGOs working on political causes.
+Thus, donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on political causes.
 
@@
 Government grants to NGOs can often crowd out private funding for nonprofit organizations [@AndreoniPayne:2003; @Brooks:2000], though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
-Donors may feel less inclined to contribute to NGOs receiving home government funds because such funding can signal a lack of independence from the government.
+Donors may feel less inclined to contribute to NGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
 Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if it were in line with their mission [@Stroup:2012].
@@
 Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the countries an NGO works in.
-Donors do not always know about anti-NGO laws in target countries or who funds an NGO when they make their contributions.
+Donors do not always know about anti-NGO laws in host countries or who funds an NGO when they make their contributions.
 Moreover, the average donor will not know exactly what "legal crackdown" entails for any given organization (i.e.
@@
 We collected two outcome measures: (1) how likely participants would be to donate to IRC (measured with a 5-point scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100.
-We collapsed the likelihood scale into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate.
-We also included an exploratory free response question asking respondents to justify their choice.
+We collapsed the likelihood scale into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate.[^collapse] We also included an exploratory free response question asking respondents to justify their choice.
 
@@
 ```{r child = "output/tables/tbl-likely-diffs.md"}
-
 ```
@@
 ```{r child = "output/tables/tbl-amount-diffs.md"}
-
 ```
@@
 These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior.
-Future research can also test the generalizability of our findings to other issue areas.
-TODO OTHER THINGS: Crackdown in authoritarian regimes, but there's an increase in restrictive laws in democracies [@Swiney:2019]
+Future research can also test the generalizability of our findings to other issue areas and other political contexts.
+For instance, recent research has found a substantial uptick in anti-NGO legislation in democracies where where private foreign donors reside [@Swiney:2019], and this constricting legal space in donors' own countries will likely influence their giving patterns.
 
@@
 
-[^supp]: See the supplement for details about our sample demographics and treatment assignment balance.
+[^supp]: See the online appendix for details about our sample demographics and balance across experimental conditions.
 
-[^priors]: See the supplement for details about our prior choices and computational environment.
+[^collapse]: An ordered probit model in the online appendix shows that results are consistent when using all five possible responses.
 
-[^mturk]: TODO: Justify MTurk here.
+[^priors]: See the online appendix for details about our prior choices and computational environment.
 
-[^targeting]: While anti-NGO legislation (in the form of barriers to entry, funding, and advocacy) can theoretically target all NGOs (or a large subset of them) within a state's borders, in practices, these laws are enforced more selectively against contentious groups that pose threats to states [see @Chaudhry:2016; @Heiss:2017].
+[^mturk]: Samples from Mechanical Turk are not nationally representative and our sample skewed younger and more politically liberal.
+However, because we aimed our study at people who are willing to donate online, we are not overly concerned with these discrepancies.
+Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally comparable (see the online appendix for a lengthier discussion about this research).
+
+[^targeting]: While anti-NGO legislation can theoretically target all NGOs within a state's borders, in practice these laws are enforced more selectively against contentious groups that pose threats to states [see @Chaudhry:2016; @Heiss:2017].
 

### 2020-01-21 manuscript/supplement.Rmd
Get rid of extra page
More final-ish edits

@@
 
-MTurk has become an increasingly popular method for fielding survey experiments on cheap semi-representative national samples, though drawing definitive causal inference from convenience samples is not without issues.
+Amazon's Mechanical Turk (MTurk) has become an increasingly popular method for fielding survey experiments on cheap semi-representative national samples, though drawing definitive causal inference from convenience samples is not without issues.
 Previous research has found that MTurk workers tend to be more liberal, younger, and less racially diverse than the general US population [@CliffordJewellWaggoner:2015; @BerniskyHuberLenz:2012].
-The results from our experiment generally mirror these findings.
-@tbl:exp-sample compares demographic characteristics of our sample with national averages from the US Census's Current Population Survey (CPS) [@IPUMS-CPS:2017].
+The results from our experiment generally mirror these findings, as seen in @tbl:exp-sample, which compares demographic characteristics of our sample with national averages from the US Census's Current Population Survey (CPS) [@IPUMS-CPS:2017].
 For general demographic information, we use the 2017 Annual Social and Economic Supplement (ASEC) to the CPS.
@@
 
-\newpage
-
 As seen in @tbl:exp-sample, our sample is younger, wealthier, and more educated than national averages.
@@
 Finally, some charitably-oriented respondents may have self-selected into the survey, given that the title listed on MTurk mentioned international nonprofit organizations.
+
 We are not overly concerned with these discrepancies, since we aimed our study at those who would be more inclined to donate online.
+Moreover, in an impressive study to test the validity of experiments conducted on non-representative, internet-based samples, @MullinixLeeperDruckman:2015 ran 20 identical experiments on both MTurk and on a nationally representative population sample.
+The results from both types of surveys tracked closely with each other and MTurk-based surveys were able to replicate most of the treatment effects found in national samples.
+Accordingly, they concluded that internet-based population samples are "useful testing grounds for experimental social science" and that they can still lead to substantial progress in generating knowledge and making inferential claims [@MullinixLeeperDruckman:2015, 124].
+MTurk-based studies ultimately do not replace the need for more robust nationally representative samples, which still provide the most robust and accurate evidence for causal claims, but they are a cost-effective method for estimating potential population-level effects.
+Other research corroborates these conclusions—while MTurk samples are not perfectly representative, they are still helpful approximations of representativeness [@BerniskyHuberLenz:2012; @KrupnikovLevine:2014; @CliffordJewellWaggoner:2015; @CoppockLeeperMullinix:2018].
 
@@
 
-## Treatment assignments and CONSORT diagram
+## Treatment assignment balance and CONSORT diagram
 
@@
 
-@fig:consort uses a CONSORT diagram to show the assignment of participants to the eight different experimental conditions.
+@fig:consort and @tbl:experimental-conditions show the assignment of participants to the eight different experimental conditions.
 We excluded participants that (1) did not participate in the experiment through MTurk and (2) failed either attention check.
+
+```{r child = "output/tables/tbl-experimental-conditions.md"}
+```
 
@@
 ```
-
-\newpage

### 2020-01-23 manuscript/supplement.Rmd
Finalish Suparna edits

@@
 
-Amazon's Mechanical Turk (MTurk) has become an increasingly popular method for fielding survey experiments on cheap semi-representative national samples, though drawing definitive causal inference from convenience samples is not without issues.
+Amazon's Mechanical Turk (MTurk) has become an increasingly popular method for fielding survey experiments on semi-representative national samples in an inexpensive manner, though drawing definitive causal inference from convenience samples is not without issues.
 Previous research has found that MTurk workers tend to be more liberal, younger, and less racially diverse than the general US population [@CliffordJewellWaggoner:2015; @BerniskyHuberLenz:2012].

### 2020-01-23 manuscript/manuscript.Rmd
Oops, forgot to include this one too

@@
 abstract: >-
-  State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding and advocacy, has become increasingly pervasive across the globe.
+  Government restrictions on NGOs have become increasingly pervasive across the globe.
+With reduced official aid and foundation funding available for NGOs, and an absence of philanthropic culture in many countries across the Global South, various NGOs are seeking funds from individual private donors in Western countries.
 How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in various developing countries, many NGOs rely on funds from private donors in Western countries.
-Existing research has predominantly focused on individual-level determinants of philanthropy.
-However, we argue that structural factors such as domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness.
-Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO.
-We find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
-We conclude by discussing the implications of our results on the sustainability of civil society organizations working in repressive countries.
+While existing research has shown that donors rely on various heuristics from social networks and organizational-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior.
+Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
+We discuss the implications of our results on the sustainability of organizations working in repressive countries.
 thanks: >-
@@
 Following the 2011 Egyptian uprising, just as domestic non-governmental organizations (NGOs) began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
-Egypt is not alone in its crackdown on NGOs.
-India, Bolivia, Hungary, Russia, and others have imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015].
+Egypt is not alone in this endeavor-India, Bolivia, Hungary, Russia, and others have also imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015].
 Consequently, official aid flows as well as grants from large foundations have considerably decreased to NGOs in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 
-In response to this dramatic shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015].
+In response to this shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015].
 This is because donations from *domestic* donors in repressive countries are unreliable and inconsistent.
-Citizens in the Global South often cannot support local NGOs, may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017], or may be deterred by dismal tax incentives, threats to take away business permits, or a general fear of retribution [@HudsonInstitute:2015].
+Citizens in the Global South often cannot support local NGOs, may prefer channeling funds to groups working on innocuous issues such as health and education over more contentious issues [@DPR:2015; @RPC:2016; @Brechenmacher:2017], or may be deterred by dismal tax incentives or a general fear of retribution [@HudsonInstitute:2015].
 Therefore, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
-By 2016, the amount directed towards civil society groups working in international affairs increased to \$22.03 billion [@givingusa:2017].
-As Daniel Runde pointed out in a statement before a U.S.
-Senate subcommittee on multilateral institutions, “U.S.
-philanthropy is significant [for global philanthropic efforts] but it is mainly Ms.
-Smith and Mr.
-Johnson, [n]ot Mr.
-and Mrs.
-Gates” [@Runde:2017].
+This amount is not insignificant-by 2016, the amount directed towards civil society groups working in international affairs had increased to \$22.03 billion [@givingusa:2017].
 
-Given increased crackdown on NGOs across the world, how do individual donors in the U.S.
+In the face of increased crackdown on NGOs across the world, how do individual donors in the U.S.
 feel about donating to legally besieged NGOs abroad?
@@
 Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974].
-While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note, we argue that domestic political environments of NGO host countries can also serve as one such structural heuristic that can influence individual donor decisions.
-In particular, legal crackdowns on NGOs serve as a heuristic to donors of organizational deservingness and when donors are provided salient information about crackdown on NGOs and its impact on NGO activities, it can influence donor preferences and behavior.
+While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note, we argue that domestic political environments of NGO host countries can serve as one such structural heuristic that can also influence individual donor decisions.
+When donors are provided salient information about crackdown on NGOs and its impact on their activities, it can serve as a heuristic of organizational deservingness, and consequently influence donor preferences and behavior.
 We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
@@
 This research note makes two important contributions.
-While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid.
-Further, while there is a robust existing literature on the individual-level determinants of philanthropy, far less is known about structural determinants that influence philanthropy, particularly towards international causes, and how these factors interact with organizational attributes to signal NGO deservingness.
+While recent work has looked at how crackdowns on NGOs affect official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how this affects private aid.
+Further, while there is a robust existing literature on the individual-level determinants of philanthropy, far less is known about its structural-level determinants, particularly towards international causes, and how these factors interact with organizational attributes to signal NGO deservingness.
 
@@
 Substantial research on charitable-giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018].
-However, little research has focused on the impact of structural factors on the choice to donate.
-Moreover, research on individual donor behavior has overwhelming looked at giving to local, rather than international causes.
-While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropic giving because individuals rely on signals and heuristics that differ from the benchmarks that large donors (whether official or private) rely on.
+However, research on individual donor behavior has overwhelming examined giving to local, rather than international causes.
+While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropic giving because individuals rely on signals and heuristics that may differ from the benchmarks that large donors (whether official or private) rely on.
 
 The decision to donate to an NGO is rarely rational.
-In theory, perfectly rational donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
-Existing research shows that information on the efficiency of NGOs merely steers rather than encourage or discourage overall donations [@ryazanov:efficiency].
+In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
+Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
 Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010; @SzperPrakash:2011].
-Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGOs, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
+Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
 
-In addition to the above factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
-We propose that the regulatory relationship between international NGOs and their host governments serves as a signal of NGO trustworthiness and deservingness.
-NGO legislation is not inherently restrictive, and governments frequently use permissive regulations to benignly routinize the behavior of NGOs [@BloodgoodTB; @DeMattee:2018].
+In addition to the above factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
+We propose that the regulatory relationship between INGOs and their host governments serves as a signal of NGO trustworthiness and deservingness.
+NGO legislation is not inherently restrictive, and governments frequently use laws to regulate the behavior of NGOs [@BloodgoodTB; @DeMattee:2018].
 Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
@@
 Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organizational-level features of a group.
-As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:
+As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated.
 
@@
 Legal crackdowns do not occur in isolation, however.
-Countries are more likely to repress NGOs both when organizational issue areas (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
+Countries are more likely to repress NGOs both when organizational issue areas (**I**) are in tension with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
 Both of these organizational characteristics thus confound the causal effect of crackdowns on donor decisions and must be accounted for in the analysis—issue areas and funding sources simultaneously influence the likelihood of crackdown while also serving as organizational heuristics that influence donor perceptions of NGO deservingness.
@@
 Issue area contentiousness directly influences legal crackdowns, however, and confounds the heuristic effect of crackdowns on donor behavior (see @fig:causal-path).
-NGOs working on more contentious human rights issues can be challenging to regimes [@Heiss:2017; @Swiney:2019].
+NGOs working on more contentious human rights issues can be challenging to regimes [@Heiss:2017].
 These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources.
-Thus, donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on political causes.
-
-We hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, and directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
+Thus, donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
+As such, we hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
 We use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues.
@@
 Donors may feel less inclined to contribute to NGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
-Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if it were in line with their mission [@Stroup:2012].
+Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
 In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help.
@@
 perhaps the NGO did something to deserve crackdown).
-Donors thus may be more likely to donate more to NGOs that rely on private funding.
+Donors thus may be likely to donate more to NGOs that rely on private funding.
 
@@
 
-Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the countries an NGO works in.
+Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the country an NGO operates in.
 Donors do not always know about anti-NGO laws in host countries or who funds an NGO when they make their contributions.
 Moreover, the average donor will not know exactly what "legal crackdown" entails for any given organization (i.e.
-does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?".
-For the sake of this experiment, this ambiguous definition is not an issue.
-The heuristics we explore here are explicitly simplified shortcuts to donor information-gathering.
-Knowing that an organization works with human rights issues (even if they don't know the exact subfield of human rights) should be enough to trigger the issue-based deservingess heuristic.
+does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
+For the sake of this experiment, this ambiguous definition is not a central concern as the heuristics we explore here are explicitly simplified shortcuts to donor information-gathering.
+Knowing that an organization works with human rights issues (even if donors are not familiar with specific kinds of rights) should be enough to trigger the issue-based deservingess heuristic.
 Similarly, knowing that an NGO faces legal trouble should be enough to trigger the structural deservingness heuristic.
@@
 
-To measure the effect of these signals on the propensity and amount of individual donations, we use an experiment to vary the different organizational and structural signals donors are exposed to.
+To measure the effect of structural and organizational-level heuristics on individual donor preferences, we use an experiment to vary the different signals donors are exposed to.
 Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs optimize and tailor their fundraising strategies for private individuals.
@@
 We used the International Rescue Committee (IRC) as our example NGO because its work easily applies to each possible frame.
-IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donation, and it works in countries with and without anti-NGO laws.
+IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donations, and it works in countries with and without anti-NGO laws.
 We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:
@@
 
-Without considering issue or funding, we find that respondents are not more likely to donate to legally besieged international NGOs (H~1a~).
+Without considering issue or funding, we find that respondents are not more likely to donate to legally besieged INGOs (H~1a~).
 As seen in @fig:likely-diffs(A), those exposed to the crackdown condition tend to have a slightly higher probability of donating (`r percent_1(filter(likely, title == "Crackdown")$theta_2)`) than those in the control condition (`r percent_1(filter(likely, title == "Crackdown")$theta_1)`), but the difference is not significant (`r filter(likely, title == "Crackdown")$delta`; `r filter(likely, title == "Crackdown")$p_neq0`).
@@
 
-@fig:likely-diffs(B–C) shows the difference in donation likelihood for both crackdown conditions across NGO issue areas (H~2a~) and funding sources (H~3a~).
+@fig:likely-diffs(B–C) shows the difference in the likelihood of donation for both crackdown conditions across NGO issue areas (H~2a~) and funding sources (H~3a~).
 Crackdown has almost no effect on the likelihood of donating to human rights NGOs (`r filter(likely, title == "Human rights")$p_neq0`).
@@
 We do find some evidence for H~3a~, however.
-Crackdown has little effect on the likelihood of donating to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
+Crackdown has little effect on the likelihood of individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately-funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
 
@@
 @fig:likely-diffs(D) shows the difference in donation likelihood across all experimental conditions.
-When donors know that a human rights organization is primarily government funded, they are more likely to donate in the *absence* of crackdowns than when the NGO faces legal difficulties (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`).
-In contrast, when donors know that an organization is privately funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
+When donors know that a human rights organization is primarily government-funded, they are more likely to donate in the *absence* of crackdowns than when the NGO faces legal difficulties (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`).
+In contrast, when donors know that an organization is privately-funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
 For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting funding and issue frames.
@@
 These results give partial support to H~3a~.
-The source of funding has little influence on the propensity to donate to humanitarian NGOs, but on average, donors are substantially more likely to give to privately-funded human rights NGOs than government-funded organizations.
+The source of funding has little influence on the preferences to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately-funded human rights NGOs than government-funded organizations.
 However, the effect of crackdowns reverses across conditions, as donors appear to both punish government-funded human rights NGOs that face legal difficulties and rally behind privately-funded NGOs facing those same hurdles.
@@
 Informing participants that IRC faces legal hurdles abroad increased donations by `r md_dollar(filter(amount, title == "Crackdown")$mu_diff)` on average, a `r percent_0(filter(amount, title == "Crackdown")$pct_change)` increase from the no crackdown condition (`r filter(amount, title == "Crackdown")$p_neq0`).
-This provides good evidence for H~1b~—donors appear to give more money to besieged international NGOs.
+This provides good evidence for H~1b~—donors appear to give more money to besieged INGOs.
 In contrast, neither issue area nor funding have an effect on the amount donated (`r filter(amount, title == "Issue")$delta`; `r filter(amount, title == "Issue")$p_neq0`; `r filter(amount, title == "Funding")$delta`; `r filter(amount, title == "Funding")$p_neq0`), indicating that crackdown is a more powerful heuristic for determining private donations.
@@
 We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues.
-This finding also applies to the amount donors give.
+This finding also applies to preferences regarding the amount donors donate.
 Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`.
@@
 No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations.
-Donors might assume that an international NGO that receives substantial money from USAID would have the support of the U.S.
+Donors might assume that an INGO which receives substantial money from USAID would have the support of the U.S.
 government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
@@
 Dozens of countries have sought to restrict NGO funding and programming.
-Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors as an additional funding source.
+Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many INGOs have turned to foreign private donors as an additional funding source.
 Since seeking out perfect information about a nonprofit and its activities, especially internationally, is costly and time-consuming, donors use heuristics when deciding whom to support.
-Existing research has shown that donors take cues and heuristics from social networks, but can other information cues influence donor preferences?
+Existing research has shown that donors take cues and heuristics from social networks, but can other informational cues also influence donor preferences?
 We argue that domestic political environments of NGO host countries can indeed serve as one such heuristic.
-Our results show that crackdowns provide donors with an additional signal of NGO deservingness and efficiency and can change both the likelihood that donors will give and the amount they will give.
-We find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
+Our results show that while crackdowns do not directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
 This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs.
@@
 Future research can also test the generalizability of our findings to other issue areas and other political contexts.
-For instance, recent research has found a substantial uptick in anti-NGO legislation in democracies where where private foreign donors reside [@Swiney:2019], and this constricting legal space in donors' own countries will likely influence their giving patterns.
 
@@
 citizen, our results show that communicating this information can convince already-likely donors to donate more to besieged groups.
-Further, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
+Further, if NGOs signal to donors that they receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
 Moreover, since private funders typically tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.
-
-THIS PART ONLY IF WORDS LEFT: Our study also highlights the importance of framing NGO operations.
-Previous research on human rights micro-mobilization has shown that the way people process information can affect their increased willingness to help others in need [@Slovic:2007].
-Our results show that donors are likely to view legally besieged human rights NGOs with suspicion.
-However, human rights groups undertake a variety of programs, and communicating the nature of their work and specifying the main target of the organization's efforts can allay the public's fears.
 

### 2020-01-23 manuscript/manuscript.Rmd
The Great Word Culling is done.

@@
 How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-While existing research has shown that donors rely on various heuristics from social networks and organizational-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior.
+While existing research has shown that donors rely on various heuristics from social networks and organization-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior.
 Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
@@
 Contact: suparna.chaudhry@cnu.edu
-word-count: "4,081"
+word-count: "4,994"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression
@@
 Following the 2011 Egyptian uprising, just as domestic non-governmental organizations (NGOs) began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
-Egypt is not alone in this endeavor-India, Bolivia, Hungary, Russia, and others have also imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015].
-Consequently, official aid flows as well as grants from large foundations have considerably decreased to NGOs in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+Egypt is not alone in this endeavor—India, Bolivia, Hungary, Russia, and others have also imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015].
+Consequently, official aid flows and grants from large foundations to NGOs have considerably decreased in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 
-In response to this shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015].
-This is because donations from *domestic* donors in repressive countries are unreliable and inconsistent.
-Citizens in the Global South often cannot support local NGOs, may prefer channeling funds to groups working on innocuous issues such as health and education over more contentious issues [@DPR:2015; @RPC:2016; @Brechenmacher:2017], or may be deterred by dismal tax incentives or a general fear of retribution [@HudsonInstitute:2015].
-Therefore, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
-This amount is not insignificant-by 2016, the amount directed towards civil society groups working in international affairs had increased to \$22.03 billion [@givingusa:2017].
+In response to this shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding, [@BanksHulmeEdwards:2015] as funding from *domestic* donors in repressive countries is unreliable, inconsistent, and frequently prohibited.
+Citizens in the Global South often cannot support local NGOs, may prefer channeling funds to groups working on innocuous issues such as health and education over more contentious issues, or may be deterred by dismal tax incentives or a general fear of retribution [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
+NGOs have thus increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
+This amount is not insignificant—by 2016, total private giving to civil society organizations working in international affairs had increased to \$22.03 billion [@givingusa:2017].
 
-In the face of increased crackdown on NGOs across the world, how do individual donors in the U.S.
+In the face of increased crackdown on NGOs globally, how do individual donors in the U.S.
 feel about donating to legally besieged NGOs abroad?
@@
 Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974].
-While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note, we argue that domestic political environments of NGO host countries can serve as one such structural heuristic that can also influence individual donor decisions.
-When donors are provided salient information about crackdown on NGOs and its impact on their activities, it can serve as a heuristic of organizational deservingness, and consequently influence donor preferences and behavior.
-We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
-This effect persists when mediated by other organizational-level heuristics like NGO issue area and its main funding sources.
+While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note we argue that domestic political environments of NGO host countries can serve a structural heuristic that influences individual donor decisions.
+When donors are provided salient information about crackdown on NGOs and its impact on their activities, that information can serve as a heuristic of organizational deservingness, and consequently influence donor preferences and behavior.
+We use a survey experiment to measure the effect of crackdowns on stated donor preferences and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
+This effect persists when mediated by other organization-level heuristics like NGO issue area and its main funding sources.
 
@@
 
-Below, we first summarize existing research on the determinants of philanthropic-giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect charitable-giving.
+Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect private philanthropy.
 We then describe our survey and present the results.
@@
 
-Substantial research on charitable-giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018].
-However, research on individual donor behavior has overwhelming examined giving to local, rather than international causes.
-While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropic giving because individuals rely on signals and heuristics that may differ from the benchmarks that large donors (whether official or private) rely on.
+Substantial research on charitable giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018].
+However, research on individual donor behavior has overwhelming examined giving to local—rather than international—causes.
+While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropy because individuals rely on signals and heuristics that may differ from the benchmarks used by large governmental and private donors.
 
@@
 Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
-Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010; @SzperPrakash:2011].
+Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010].
 Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
@@
 
-In addition to the above factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
-We propose that the regulatory relationship between INGOs and their host governments serves as a signal of NGO trustworthiness and deservingness.
+In addition to organizational factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
+We propose that the regulatory relationship between international NGOs (INGOs) and their host governments serves as a signal of NGO trustworthiness and deservingness.
 NGO legislation is not inherently restrictive, and governments frequently use laws to regulate the behavior of NGOs [@BloodgoodTB; @DeMattee:2018].
@@
 
-We argue that donors perceive legal crackdowns differently from organizational-level heuristics—such as NGO missions, visions, values—because donors may be able to influence these latter attributes, at least to some extent.
-On the other hand, donors can do little to change the domestic political environment of another country.
-Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organizational-level features of a group.
+We argue that donors perceive legal crackdowns differently from organization-level heuristics—such as NGO missions, visions, values—because donors may be able to influence these latter attributes, at least to some extent.
+Conversely, donors can do little to change the domestic political environment of another country.
+Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organization-level features of a group.
 As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated.
@@
 
-@fig:causal-path represents this relationship more formally.
+@fig:causal-path represents this relationship formally.
 Legal crackdowns (**C**) have a direct effect on donor decisions (**Y**; donation likelihood and amount) because of their heuristic function.
@@
 
-The final heuristic that can influence individual donors that we examine is the *source of NGO funding*.
-Government grants to NGOs can often crowd out private funding for nonprofit organizations [@AndreoniPayne:2003; @Brooks:2000], though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
-Donors may feel less inclined to contribute to NGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
+The final heuristic we examine is the *source of NGO funding*.
+Government grants to nonprofits can often crowd out private funding, though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
+Donors may feel less inclined to contribute to INGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
 Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
@@
 As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding again confounds the effect of anti-NGO crackdowns on donor behavior (see @fig:causal-path).
-As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
+Accordingly, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
 Individual donors may be less likely to donate to government-funded NGOs that face restrictions, since legal trouble with the organization's primary funder could fuel private donor mistrust (i.e.
@@
 
-To measure the effect of structural and organizational-level heuristics on individual donor preferences, we use an experiment to vary the different signals donors are exposed to.
-Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs optimize and tailor their fundraising strategies for private individuals.
+To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different signals donors are exposed to.
+Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for private individuals.
 
@@
 
-We estimate the mean amount donated in each condition using a *t* distribution [@Kruschke:2013]:
+We estimate the mean amount donated in each condition using a *t* distribution:
 
@@
 These results give partial support to H~3a~.
-The source of funding has little influence on the preferences to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately-funded human rights NGOs than government-funded organizations.
-However, the effect of crackdowns reverses across conditions, as donors appear to both punish government-funded human rights NGOs that face legal difficulties and rally behind privately-funded NGOs facing those same hurdles.
+The source of funding has little influence on the preference to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately-funded human rights NGOs than government-funded organizations.
+Additionally donors appear to both punish government-funded human rights NGOs facing crackdown and rally behind privately-funded NGOs facing those same hurdles.
 Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.
@@
 
-This trend also holds true when accounting for NGO issue area.
+This trend also holds when accounting for NGO issue area.
 The crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance (see @fig:amount-diffs(B–C)).
@@
 
-Combining issue areas and funding sources adds more texture to these results.
+Combining issue areas and funding sources provides more texture.
 We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues.
@@
 These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior.
-Future research can also test the generalizability of our findings to other issue areas and other political contexts.
+Future research can also test the generalizability of our findings to other issue areas and political contexts.
 
@@
 
-[^supp]: See the online appendix for details about our sample demographics and balance across experimental conditions.
+[^supp]: See the online appendix for the text of the survey, as well as details about our sample demographics and balance across experimental conditions.
 
@@
 
-[^mturk]: Samples from Mechanical Turk are not nationally representative and our sample skewed younger and more politically liberal.
-However, because we aimed our study at people who are willing to donate online, we are not overly concerned with these discrepancies.
-Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally comparable (see the online appendix for a lengthier discussion about this research).
+[^mturk]: Samples from Mechanical Turk are not nationally representative.
+However, because we targeted our study at people who are willing to donate online, we are not overly concerned with these discrepancies.
+Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally comparable—see the online appendix for a lengthier discussion about this research.
 

### 2020-01-23 manuscript/pandoc/bin/tabularize.py
Use better self-contained pandoc
Hooray for https://github.com/andrewheiss/portable-pandoc-magic

@@ -1,66 +1,0 @@
-#!/usr/bin/env python3
-
-# Filter to convert pandoc-generated longtable elements to tabular elements.
-#
-# usage: pandoc document.md -o document.tex --filter tabularize.py
-#
-# I copied this from Wagner Macedo's original filter at:
-# https://groups.google.com/forum/#!msg/pandoc-discuss/RUC-tuu_qf0/h-H3RRVt1coJ
-# 
-# I made two adjustments to the original script:
-# - Use `table*` instead of `table` to span two columns in SAGE LaTeX template
-# - Surround table with \small and \normalize to shrink the text a little
-
-import pandocfilters as pf
-
-def latex(s):
-    return pf.RawBlock('latex', s)
-
-def inlatex(s):
-    return pf.RawInline('latex', s)
-
-def tbl_caption(s):
-    return pf.Para([inlatex(r'\caption{')] + s + [inlatex('}')])
-
-def tbl_alignment(s):
-    aligns = {
-        "AlignDefault": 'l',
-        "AlignLeft": 'l',
-        "AlignCenter": 'c',
-        "AlignRight": 'r',
-    }
-    return ''.join([aligns[e['t']] for e in s])
-
-def tbl_headers(s):
-    result = s[0][0]['c'][:]
-    for i in range(1, len(s)):
-        result.append(inlatex(' & '))
-        result.extend(s[i][0]['c'])
-    result.append(inlatex(r' \\\midrule'))
-    return pf.Para(result)
-
-def tbl_contents(s):
-    result = []
-    for row in s:
-        para = []
-        for col in row:
-            para.extend(col[0]['c'])
-            para.append(inlatex(' & '))
-        result.extend(para)
-        result[-1] = inlatex(r' \\' '\n')
-    return pf.Para(result)
-
-def do_filter(k, v, f, m):
-    if k == "Table":
-        return [latex(r'\begin{table*}[ht]' '\n' r'\centering' '\n' r'\small' '\n'),
-                tbl_caption(v[0]),
-                latex(r'\begin{tabular}{@{}%s@{}}' % tbl_alignment(v[1]) +
-                      ('\n' r'\toprule')),
-                tbl_headers(v[3]),
-                tbl_contents(v[4]),
-                latex(r'\bottomrule' '\n' r'\end{tabular}'),
-                latex(r'\end{table*}')]
-
-
-if __name__ == "__main__":
-    pf.toJSONFilter(do_filter)

### 2020-01-23 manuscript/pandoc/bin/word_count.R

@@ -1,37 +1,67 @@
-suppressPackageStartupMessages(library(tidyverse))
+#!/usr/bin/Rscript
+
+# string::stri_count_words() counts, um, words. That's its whole job. But it
+# doesn't count them like Microsoft Word counts them, and academic publishing
+# portals tend to care about Word-like counts. For instance, Word considers
+# hyphenated words to be one word, while stringr counts them as two (and even
+# worse, stringi counts / as word boundaries, so URLs can severely inflate your
+# word count).
+#
+# Also, academic writing typically doesn't count the title, abstract, table
+# text, figure captions, or equations as words in the manuscript (and it
+# SHOULDN'T count bibliographies, but it always seems to ugh).
+#
+# This script parses the rendered manuscript HTML, removes extra elements,
+# adjusts the text so that stringi treats it more like Word, and then provides a
+# more accurate word count.
+
+suppressPackageStartupMessages(library(magrittr))
+suppressPackageStartupMessages(library(stringr))
+suppressPackageStartupMessages(library(purrr))
 suppressPackageStartupMessages(library(rvest))
-suppressPackageStartupMessages(library(here))
 suppressPackageStartupMessages(library(stringi))
 
-ms_raw <- read_html(here("manuscript", "manuscript.html"))
+args <- commandArgs(trailingOnly = TRUE)
+
+if (length(args) < 1) {
+  ms_file <- "paper.html"
+} else {
+  ms_file <- args[1]
+}
+
+# Read the HTML file
+ms_raw <- read_html(ms_file)
 
 # Extract just the article, ignoring title, abstract, etc.
-ms <- ms_raw %>% 
-  html_nodes("article") 
+ms <- ms_raw %>%
+  html_nodes("article")
 
 # Get rid of figures, tables, and math
 xml_remove(ms %>% html_nodes("figure"))
 xml_remove(ms %>% html_nodes("table"))
 xml_remove(ms %>% html_nodes(".display"))  # Block math
-xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>% 
+xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>%
   invisible()
 
 # Go through each child element in the article and extract it
 ms_cleaned_list <- map(html_children(ms), ~ {
-  .x %>% 
-    html_text(trim = TRUE) %>% 
+  .x %>%
[…]

### 2020-01-24 analysis/03_additional-analysis.Rmd
Remove this balance section bc it's in 02_analysis already
Export collapsing variable table

@@
 walk(full_chart, ~ print(.))
-```
-
-# Balance
-
-```{r}
-
 ```
@@
 collapsed_likelihood %>% 
-  pandoc.table(justify = "ll")
+  pandoc.table.return(justify = "ll") %T>%
+  cat(file = here("analysis", "output", "tables", "tbl-collapsed-likelihood.md")) %>% 
+  cat()
 ```
@@
                                prior = R2(0.25, what = "mean"), prior_counts = dirichlet(1),
-                               method = "probit")
+                               method = "probit",
+                               chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
 ```

### 2020-01-24 manuscript/supplement.Rmd
Add collapsing likelihood variable info

@@
 ---
-title: "Supplement to Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
-short-title: Supplement to Charity During Crackdown
+title: "Online appendix for Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
+short-title: Online appendix for Charity During Crackdown
 author:
@@
 \fingroup
+
+# Collapsing likelihood variable
+
+To simplify our analysis, we collapse our likelihood scale from a 1-5 Likert scale to a binary variable:
+
+```{r child = "output/tables/tbl-collapsed-likelihood.md"}
+```
+
+To check that the results are internally consistent when collapsed, we ran an ordered probit model 
+(using Stan) to see if the cutpoints follow the distribution of answers, and they do.
+"Somewhat likely" and above has a cutpoint of > 0.18, meaning that the likelihood is positive on average for both "Somewhat likely" and "Extremely likely."
+
+```{r child = "output/tables/tbl-probit-likelihood.md"}
+```
 

### 2020-01-24 manuscript/manuscript.Rmd
Final edits pre-submission

@@
   url: http://www.suparnachaudhry.com/
-  twitter: SuparnaChaudhry
 - name: Andrew Heiss
@@
   url: https://www.andrewheiss.com/
-  twitter: andrewheiss
 date: "`r format(Sys.time(), '%B %e, %Y')`"
@@
 Contact: suparna.chaudhry@cnu.edu
-word-count: "4,994"
+word-count: "4,999"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression
@@
 We do find some evidence for H~3a~, however.
-Crackdown has little effect on the likelihood of individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately-funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
+Crackdown has little effect on the likelihood of individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
 
@@
 When donors know that a human rights organization is primarily government-funded, they are more likely to donate in the *absence* of crackdowns than when the NGO faces legal difficulties (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`).
-In contrast, when donors know that an organization is privately-funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
+In contrast, when donors know that an organization is privately funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
 For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting funding and issue frames.
@@
 These results give partial support to H~3a~.
-The source of funding has little influence on the preference to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately-funded human rights NGOs than government-funded organizations.
-Additionally donors appear to both punish government-funded human rights NGOs facing crackdown and rally behind privately-funded NGOs facing those same hurdles.
+The source of funding has little influence on the preference to donate to humanitarian NGOs, but on average, donors are substantially more likely to want to give to privately funded human rights NGOs than government-funded organizations.
+Additionally donors appear to both punish government-funded human rights NGOs facing crackdown and rally behind privately funded NGOs facing those same hurdles.
 Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.
@@
 Combining issue areas and funding sources provides more texture.
-We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues.
+We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately funded human rights NGOs when they face legal issues.
 This finding also applies to preferences regarding the amount donors donate.
-Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`.
-Respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).
+Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`.
+Respondents explained that they chose to give additional money to privately funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).
 
@@
 
-In contrast, crackdowns have no substantial effect on the amount donated to privately-funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`).
-No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations.
+In contrast, crackdowns have no substantial effect on the amount donated to privately funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`).
+No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately funded organizations.
 Donors might assume that an INGO which receives substantial money from USAID would have the support of the U.S.
@@
 Our results show that while crackdowns do not directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
-This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs.
+This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately funded human rights NGOs.
 Anti-NGO crackdowns can thus serve as a signal of NGO effectiveness.

### 2020-01-24 README.Rmd
Use most recent abstract

@@
 
-State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding and advocacy, has become increasingly pervasive across the globe.
+Government restrictions on NGOs have become increasingly pervasive across the globe.
+With reduced official aid and foundation funding available for NGOs, and an absence of philanthropic culture in many countries across the Global South, various NGOs are seeking funds from individual private donors in Western countries.
 How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in various developing countries, many NGOs rely on funds from private donors in Western countries.
-Existing research has predominantly focused on individual-level determinants of philanthropy.
-However, we argue that domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness.
-Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO.
-We find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
-We conclude by discussing the implications of our results on the sustainability of civil society organizations working in repressive countries.
+While existing research has shown that donors rely on various heuristics from social networks and organization-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior.
+Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
+We discuss the implications of our results on the sustainability of organizations working in repressive countries.
 
@@
 3.
-You need to compile the Stan c++ binary DLLs before building and installing the actual  **crackdownsphilanthropy** compendium package ([see here for details about why](https://mc-stan.org/rstantools/articles/minimal-rstan-package.html#documentation)).
+You need to compile the Stan C++ binary DLLs before building and installing the actual  **crackdownsphilanthropy** compendium package ([see here for details about why](https://mc-stan.org/rstantools/articles/minimal-rstan-package.html#documentation)).
 Run these two lines in R:

### 2020-06-16 manuscript/manuscript.Rmd
Suparna initial R&R edits

@@
 ---
-title: "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
+title: "Dynamics of international giving: Exploring individual donor preferences"
 short-title: Charity During Crackdown
@@
 - name: Suparna Chaudhry
-  affiliation: Christopher Newport University
-  email: suparna.chaudhry@cnu.edu
+  affiliation: Lewis \& Clark College
+  email: schaudhry@lclark.edu
   url: http://www.suparnachaudhry.com/
@@
   Government restrictions on NGOs have become increasingly pervasive across the globe.
-With reduced official aid and foundation funding available for NGOs, and an absence of philanthropic culture in many countries across the Global South, various NGOs are seeking funds from individual private donors in Western countries.
-How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-While existing research has shown that donors rely on various heuristics from social networks and organization-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior.
-Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
-We discuss the implications of our results on the sustainability of organizations working in repressive countries.
+While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private funding flows.
+How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally?
+Using a survey experiment, we find that learning about repressive NGO regulatory environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits.
+This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and its main funding sources.
+We conclude by discussing the implications of our results on the scholarship and practice of nonprofits using different framing appeals to increase fundraising at a time when traditional funding to such organizations is decreasing.
 thanks: >-
@@
 author-note: >-
-  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University.
+  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Lewis \& Clark College; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University.
 additional-info: Figures should appear in color online only, not in print.
 correspondence: >-
-  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of Political Science, Christopher Newport University, Newport News, VA 23606, 757-594-7821.
-Contact: suparna.chaudhry@cnu.edu
-word-count: "4,999"
+  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of International Affairs, Lewis \& Clark College, 0615 SW Palatine Hill Rd.
+Portland, OR 97219.
+Contact: schaudhry@lclark.edu
+word-count: "FILL"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression
@@
 
-Following the 2011 Egyptian uprising, just as domestic non-governmental organizations (NGOs) began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy.
-Egypt is not alone in this endeavor—India, Bolivia, Hungary, Russia, and others have also imposed funding restrictions on NGOs [@Carothers:2015; @DPR:2015].
-Consequently, official aid flows and grants from large foundations to NGOs have considerably decreased in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+Over the last three decades, governments across the world have sought to limit the work of nonprofits - a phenomenon knowns as `closing civic space' in the policy arena [@Carothers:2015; @DPR:2015].
+Government have enacted laws creating barriers to advocacy, funding, and entry, adversely affecting the work of thousands of NGOs, which often receive a large amount of resources from donors across the world.
+This is particularly the cause in countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency and donors seek out NGOs for projects (Dietrich 2013).
+Consequently, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+While we know there has been a negative impact on public funding flows, we know relatively little about how this crackdown affects private donors, especially individual donors' willingness to donate.
 
-In response to this shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding, [@BanksHulmeEdwards:2015] as funding from *domestic* donors in repressive countries is unreliable, inconsistent, and frequently prohibited.
-Citizens in the Global South often cannot support local NGOs, may prefer channeling funds to groups working on innocuous issues such as health and education over more contentious issues, or may be deterred by dismal tax incentives or a general fear of retribution [@DPR:2015; @RPC:2016; @Brechenmacher:2017].
-NGOs have thus increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy.
+Charitable-giving to nonprofits working in international affairs has been steadily increasing over the past two decades, with a noticeable increase over the last decade.
+Between 2014 and 2016, giving to international affairs increased by 14.1% [@givingusa2017report].
 This amount is not insignificant—by 2016, total private giving to civil society organizations working in international affairs had increased to \$22.03 billion [@givingusa:2017].
+Most notably, a large portion of this is driven by individuals making small-scale donations.
+In 2017, individuals gave $286.7 billion - or approximately 70\% of total giving to international affairs.
+This further increased to $427.71 billion in 2018 - 85.7% of which was through individuals [givingusa:2019].
+Given that a majority of this research is restricted to elite, high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of individual donors.
+What factors affect individual donor preferences on giving to international causes?
+More specifically, how does information about regulatory environments abroad, as well as organizational-level attributes of nonprofits, such as their main focus areas and sources of funding affect donors' willingness to donate internationally?
 
-In the face of increased crackdown on NGOs globally, how do individual donors in the U.S.
-feel about donating to legally besieged NGOs abroad?
-Do legal restrictions on NGOs influence donors' decision to donate?
-Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974].
-While much of this research has focused on heuristics from social networks and organizational practices [@CrosonShang:2011; @Tremblay-BoirePrakash:2017], in this research note we argue that domestic political environments of NGO host countries can serve a structural heuristic that influences individual donor decisions.
-When donors are provided salient information about crackdown on NGOs and its impact on their activities, that information can serve as a heuristic of organizational deservingness, and consequently influence donor preferences and behavior.
-We use a survey experiment to measure the effect of crackdowns on stated donor preferences and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs.
-This effect persists when mediated by other organization-level heuristics like NGO issue area and its main funding sources.
+Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974; @CrosonShang:2011; @Tremblay-BoirePrakash:2017], We leverage an online survey experiment using Amazon's Mechanical Turk to assesss how different structural and organizational-level heuristics affect individual donors' willingness to donate.
+We find that learning about more repressive NGO regulatory environments increases generosity in that already likely donors are willing to donate substantially more to legally restricted NGOs.
 
-This research note makes two important contributions.
-While recent work has looked at how crackdowns on NGOs affect official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how this affects private aid.
-Further, while there is a robust existing literature on the individual-level determinants of philanthropy, far less is known about its structural-level determinants, particularly towards international causes, and how these factors interact with organizational attributes to signal NGO deservingness.
+This generosity persists when mediated by two important organization-level heuristics: NGO issue area and its main funding sources.
+Learning about crackdown increases individuals' willingness to donate to privately funded nonprofits.
+This may be because the survival of the NGO appears to be in question and the donor's assessment might be that their donation actually makes a difference.
+These results are particularly substantive for privately-funded human rights NGOs facing crackdown - with donors showing an increased willingness to not just donate to them, but also to donate more to them.
+While not unsurprising, this does suggest that private donors to human rights NGOs likely know that their work is always challenging to governments, and that such organizations need greater support when facing stricter regulatory environments.
 
+Our study makes a significant contribution to the scholarship and practice on dynamics of individual-giving and indicates the promise and limits of different framing appeals by nonprofits on individuals' willingness to donate.
+First, while factors giving shaping individual-giving to domestic causes have been thoroughly explored in existing literature, the dynamics of internatoinal giving are under-examined in the U.S.
+literature on individual donor preferences.[^exception] It is even more essential to understand as philanthropy to international causes can be harder to motivate because of the number of recipients are larger and far removed from the donor [@CasaleBaumann:2015, 100].
+
+Second, most nonprofits working internationally have traditionally relied on government and foundation funding.
+But in the era of closing civic space, these groups may need to tailor their fundraising strategies to individual donors.
+Framing, or the process through which actors present information to infleunce perceptions of behavior, is particular important in this regard.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to donors considering international charitable-giving.
+Our study looks at the impact of political frames such as regulatory crackdown, and how it interacts with organizational attributes to signal NGO deservingness.
+In doing so, it can help nonprofits frame their appeals.
+
+CHANGE
 Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect private philanthropy.
@@
 
-# Theorizing the effects of crackdown on philanthropy
+#Philanthropy towards international nonprofits
 
-Substantial research on charitable giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011], and more recently, the effect of social networks on philanthropy [@HerzogYang:2018].
+Thousands of international NGOs in the Global South receive funds from a variety of public and private sources each year.[^NGO] Though our focus in this paper is one private funding, it is essential to differentiate between the two sources.
+Public aid (more commonly known as traditional donor aid) channels funds from official aid agencies towards nonprofits through a variety of bilateral and multilateral institutions.
+Private funds, which are comparatively newer international donors compared to traditional donor aid, can come from foundations, private corporations and individuals.
+
+In this paper, we specifically look at individual-level determinants to foreign giving.
+As described in the introduction, this is because [ADD PART ABOUT ANY PUBLIC FIGURES AND HOW IT DECLINING] private-giving to nonprofits working in international affairs has been consistently increasing over this past decade.[^internationalaffairs] Moreover, private giving by individuals has far outstripped giving by private foundations - in 2018, charitable-giving by individuals amounted to $292.09 billion, compared by $75.86 billion by foundations and $20.05 billion by corporations.
+Thus, giving by foundation represented 18\% of all charitable-giving in 2018, which was not only lesser than the proportion of giving by private individuals, but also giving by Bill and Melinda Gates Foundation accounted for more than half of it [givingusa:2019].
+
+Given these substantive amounts, understanding individual-level determinants of giving to international nonprofits is important to investigate as individual private donors may not necessarily mirror public donor choices.
+While there is evidence that citizens generally support the goals of aid agencies (Milner and Tingley 2010), surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
+Further, foreign aid and democracy aid is often considered unresponsive to developments on the ground [@brainard2007, @Carothers:2015] and public aid decisions - especially on final recipients are not easily accessible.
+There may also be heterogeneity within how donor governments allocate funds.
+Emerging donor government differ from established donors in that they demand fewer human rights, governance or environmental conditions preferred by Western donors [@fenglerkharas].
+
+More recent research on the allocation of private aid flows has also found little support for the idea that individual donor behavior mimics that of official donors.
+Desai and Kharas (2018) find that unlike official donors  whotend to channel funds to countries with better institutional quality (control of corruption) and as a performance reward (Bermeo 2011, Dietrich ad Wright 2017), individual donors do not use the same performance-based metrics.
+Rather, individuals are more inclined to donate to groups in countries experiencing a humanitarian crisis - in particular, those driven by natural disasters.
+They go on to conclude that compared to donor agencies, "private donors respond to different project and country characteristics." (517) Given these above reasons, decision-making by the average individual donor may therefore not have the same logic as donor governments and should be investigated on its own terms.
+
+Understanding motivations of individual private donors is also essential because private funding flows towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
+Prior research has demonstrated that restrictions on cross-border funding has reduced official aid and official development assistance to repressive countries (CITE).
+But data from the Foundation Center shows no correlation between amount of funding flows from US private foundations to a given country and that country's score on the Index of Philanthropic Freedom.
+While this index is comparatively new and data is available only 2015 onwards (CHECK), preliminary evidence shows that, "US foundations remain committed to channeling funds to countries where the legal environment is growing increasingly unfriendly." As such, it is imperative to understand whether individual donors mirror the trajectory of foundations when giving internationally, especially to countries with restrictive legal environments.
+
+##Key drivers of individual-level philanthropy
+
+Substantial research on charitable giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011].
 However, research on individual donor behavior has overwhelming examined giving to local—rather than international—causes.
-While most research on giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014], we explore private philanthropy because individuals rely on signals and heuristics that may differ from the benchmarks used by large governmental and private donors.
+This literature has primarily focused on the importance of X main factors, especially when considering charitable behavior towards international causes: (1) the role of social capital and social networks; (2) the role of individual experiences such as higher education and levels of religiosity; and (3) third party certifications.
 
-The decision to donate to an NGO is rarely rational.
+One major area of inquiry in philanthropic studies looks at the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit." (Putnam 1997, 67).
+While quite broad, the literature further concentrates on a specific kind of social capital-associational capital-which refers to, "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
+Prior research has found that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
+Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations.
+This is because volunteering exposes individuals to the need for donations to charities and nonprofits and made them feel more compelled to do so [@hossainlamb2012].
+
+The role of social networks is also important in this regard.
+Looking at relational configurations in social networks, Herzog and Yang find that having both a giver and a solicitor in one's social network increase the likelihood of that individual's charitable-giving.
+
+Individual experiences such as access to higher education and increased religiosity can also impact philanthropic giving.
+Higher education fosters prosocial motivations and also brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
+This in turn has been shown to be particularly vital in giving to international causes.
+Additional education has also been shown to increase abstract thinking [@wiepkingmass, 1978].
+This is particular important for donating to international relief organizations than donating to domestic organizations [@micklewright2009].
+
+Levels of religiosity are also a significant predictor of the likelihood and level of giving.
+People who regularly attention religious services are more likely to have prosocial values, face a stronger norm of charitable-giving, and may feel pressure to conform that group and community standard [@wiepking2010].
+Overall, individuals with higher levels of income, education, and greater religious proclivities have been shown to not only be more likely to give internationally, but also to give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
+
+Finally, information on organizational characteristics and third party certifications can also impact levels of individual charitable-giving, through the results are mixed.
+Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
+The effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010] and that ratings by charity watchdogs do not really affect donor support for these nonprofits (Szper and Prakash 2011).
+
+While a robust literature as shown above looks at the drivers of individual-level philanthropy, it overwhelmingly focusses on giving to local rather than international causes.
+This focus on local or domestic causes means that that the precise causal mechanisms through which cross-border charity can be motivated and mobilized is still under-examined (Desai and Kharas, 517).
+This problem is further compounded by the fact that there is greater paucity of data and diversity of sources regarding international-giving, which further complicates a systematic examination.
+
+Indeed, most research on individual-giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014].[^highnetworth] And recent research has on the average donor finds that, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad." (TB Prakash 2017, 644) And as explained above in section X, private donors do not necessarily mirror the choices made by public donors and that individuals rely on signals and heuristics that may differ from the benchmarks used by large governmental and private donors.
+
+These signals and heuristics, we argue, can be even more important in giving to international causes.
 In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
-Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
-Similarly, the effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010].
 Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
+Nonprofits fundraising internationally may be therefore more reliant on framing.
+Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
+
+#Theorizing the effects of political and organizational frames on individual-giving
 
@@
 
-> **H~1a~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
+> **H~1a~**: If donors learn that NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
 >
-> **H~1b~**: If NGOs face legal crackdowns abroad, then individual donors will donate more to them.
+> **H~1b~**: If donors learn that NGOs face legal crackdowns abroad, then individual donors will donate more to them.
 
@@
 
-The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences—can serve as an organization-level heuristic.[^targeting] NGOs that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
+The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences, can also serve as an organization-level heuristic.[^targeting] NGOs that address humanitarian issues such as relief and development have broader appeal to donors and these issues rarely challenge the government.
 Further, their programmatic output is easily quantifiable and donors can see the results of their charity more readily [@Bush:2015].
-NGOs working on these less contentious issues can also frame their activities as in need of greater support—the perception of need, whether through personal experiences or media framing, strongly influences individual decisions to donate to relief efforts [@BekkersWiepking:2010, 6–8].
+Previous research has shown that that public donors do indeed differentiate between NGO issue areas, especially when these organizations are working in repressive contexts.
+In particular, the Organisation for Economic Cooperation and Development (OECD) donors respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increasing funding for groups working on relatively tamer causes such as health, education and agriculture [CITE US].
 
@@
 These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources.
-Thus, donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
+There is evidence that this a concern for private donors.
+In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many NGOs argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn was hurting women and trans rights organizations.
+Some private funders, these groups argued, were also more likely to fund well-established groups that were more likely to survive crackdown.
+
+However, compared to our existing knowledge on public donors and foundation donors, we lack knowledge about how individual donors respond to frames emphasizing one nonprofit issue area over another, especially a contentious area over a tamer one.
+NGOs working on tamer issues such as health, education, disaster relief, and humanitarian aid can often frame their activities as in need of greater support—the perception of need, whether through personal experiences or media framing.
+This may strongly influence individual decisions to donate to relief efforts [@BekkersWiepking:2010, 6–8].
+Individual donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
+
 As such, we hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
@@
 
-> **H~2a~**: If legally besieged NGOs work on humanitarian issues, then individual donors will be more likely to donate to them.
+> **H~2a~**: If donors learn that legally besieged NGOs work on humanitarian issues, then individual donors will be more likely to donate to them.
 >
-> **H~2b~**: If legally besieged NGOs work on humanitarian issues, then individual donors will donate more to them.
+> **H~2b~**: If donors learn that legally besieged NGOs work on humanitarian issues, then individual donors will donate more to them.
 
@@
 
-> **H~3a~**: If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will be more likely to donate to them.
+> **H~3a~**: If donors learn that legally besieged NGOs do not receive substantial funding from government sources, then individual donors will be more likely to donate to them.
 >
-> **H~3b~**: If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will donate more to them.
+> **H~3b~**: If donors learn that legally besieged NGOs do not receive substantial funding from government sources, then individual donors will donate more to them.
 
@@
 
-# Discussion: Do crackdowns on NGOs affect individual philanthropy?
+ I would encourage you to revisit the hypotheses from the findings.
+Which hypotheses were supported, and which were not?
+Why does it matter whether NGOs are advocating human rights or provide humanitarian assistance, and how much government funding they receive?
+How did participants interpret the term government funding?
+
+## Discussion
+While the results from the survey experiment above allows to hold the organization constant and test for specific hypotheses, there are a few caveats when interpreting these results, generalizing them to other contexts, and considering applied lessons for fundraisers.
+First, the experiment measures preferences (willingness to donate) rather than behavior (actual donations).
+While the former may not always neatly translate into the latter, there is evidence that individuals’ willingness to donate as measured in the experiment translates well into behavior.
+This is because the wording of the survey experiment uses an informational frame, where the focus is on educating the rather by presenting them with facts.
+Prior research has shown that informational frames (as opposed to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy) are important in generating donations (McEntire, Lieby, Kraine 2015).[^frametypes]
+
+Moreover, research has also found that in the case of campaigns for human rights nonprofits, informational frames are a necessary precondition for getting people to act, and people are more likely to donate and undertake other actions when these informational frames are combined with personal frames (McEntire, Lieby, Kraine 2015).[^personalframes] This suggests that if governments attempt to repress international human rights nonprofits, then these organizations can potentially increase their resource flows by using a combination of these two frames.
+The survey instrument used above shows substantive increase in donors' willingness to donate to human rights groups facing crackdown, especially those that are privately-funded, and this result emerges from the use of just informational frames.
+If combined with personal frames, research indicates these donations may further increase.
+
+It is also worth noting that there is evidence, at least domestically, that restrictions on nonprofit activities spur changes in private donors’ actual giving patterns (and not merely their preferences).
+For instance, following the 2016 election, when Texas pledged to remove Planned Parenthood from its Medicaid program and a number of states proposed new restrictions on their work, donations to the organizations increased by over 40 times the usual amount.
+
+your convenience sample captures those relatively more likely to donate to charities, which perhaps allows you to have more specific lessons for fundraisers.
+
+Finally, given that the survey was administered to a convenience sample of Americans, it raises questions about external validity.
+1.
+ADD HOW RESULTS MAY DIFFER FOR REPRESENTATIVE SAMPLE OF AMERICANS.
+2.
+Would a sample of Europeans for instance be so skeptical towards government funding?
+
+# Conclusion
 
@@
 
-This research note should be viewed as an exploratory study, and it raises numerous questions for future research.
-These include determining the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation, but preferences may not reflect actual behavior.
-Future research can also test the generalizability of our findings to other issue areas and political contexts.
+This article should be viewed as an exploratory study.
+While the survey experiment allows us to hold the organization constant and test for specific hypotheses, there are limits to its external validity.
+Future research should look to testing the generalizability of our findings to individual donors in other countries, as well as determining the extent to which these preferences translate into behavior.
+It is also important to explore among thsoe donors who give to international causes - explore the extent to which individuals are likely to give to domestic nonprofits abroad, compared to international nonprofits working in those countries.
 
-These results have several implications for policy.
-NGOs may benefit from publicizing when they are targets of government crackdown.
+These results also have implications for nonprofit fundraising.
+NGOs may benefit from publicizing when they are targets of government crackdown and including that information in their framing appeals.
 While this may not be enough to sway the average U.S.
@@
 Further, if NGOs signal to donors that they receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
-Moreover, since private funders typically tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.
 
@@
 [^8995923]: Response 8995923.
+
+[^internationalaffairs]: Giving USA defines the sector of international affairs to include any nonprofit organization working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
+This classification is based upon the National Taxonomy of Exempt Entities Core which codes groups based upon their field of interest.
+
+[^exceptions]: For exceptions, see @micklewright2009 on UK, @Rajan:2009 on Canada, @wiepking2010 on Netherlands, @CasaleBaumann:2015 on the USA.
+
+[^highnetworth]: High-net worth households are defined as having greater than $200,000 in annual household income and/or with more than $1,000,000 in assets, excluding primary residence.
+
+[^framing]: Framing is the process through which actors present information to influence perceptions or behavior.
+Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [Benford and Snow 2000, Chong and Druckman 2007].
+
+[^frametype]: For more on motivational and personal frames, see Benford and Snow 2000, Gamson 1995
+
+[^personalframes]: Personal frames seek to humanize victims and entice action by invoking an emotional reaction.
+Research has found that people are more likely to be generous when donating to a human rights campaign with a single victim, as opposed to a statistical group of victims (Slovic 2007).
+
+[^NGO]: Nonprofit organizations (which we inter-changeably use with NGOs) are organizations for a public or mutual benefit other than generating profit for the owners or investors (Salamon 1998).
+NGOs can be either domestic i.e.
+an NGO that operates entirely in a single state, or international, more commonly known as INGOs.
+INGOs or international nonprofits, "operate independently of governments, are composed of members from two or more countries, and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors and international institutions." (Tarrow 2001) Unlike domestic NGOs, INGOs often work in countries outside of their main country of origin or headquarters.

### 2020-06-17 manuscript/manuscript.Rmd
My R&R changes

@@
 library(tidyverse)
+library(pander)
 library(scales)
@@
 library(here)
+
+source(here("analysis", "options.R"))
 
@@
 
-Over the last three decades, governments across the world have sought to limit the work of nonprofits - a phenomenon knowns as `closing civic space' in the policy arena [@Carothers:2015; @DPR:2015].
-Government have enacted laws creating barriers to advocacy, funding, and entry, adversely affecting the work of thousands of NGOs, which often receive a large amount of resources from donors across the world.
-This is particularly the cause in countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency and donors seek out NGOs for projects (Dietrich 2013).
-Consequently, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While we know there has been a negative impact on public funding flows, we know relatively little about how this crackdown affects private donors, especially individual donors' willingness to donate.
+Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon commonly known as "closing civic space" [@Carothers:2015; @DPR:2015].
+Repressive governments have enacted laws creating barriers to advocacy, funding, and entry, adversely affecting the work of thousands of NGOs, which typically rely on funding from donors across the world.
+This is particularly the case in countries with weak institutions and poor governance, where international donors typically seek out NGOs to implement their projects, as direct aid transfers to recipient governments pose the risk of misuse and bureaucratic inefficiency [@Dietrich2013].
+As a result of this global crackdown on civil society, however, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+While we know there has been a negative impact on funding from official governmental donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to engage in philanthropy.
 
-Charitable-giving to nonprofits working in international affairs has been steadily increasing over the past two decades, with a noticeable increase over the last decade.
-Between 2014 and 2016, giving to international affairs increased by 14.1% [@givingusa2017report].
+Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades, with a noticeable increase over the last decade.
+Between 2014 and 2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report].
 This amount is not insignificant—by 2016, total private giving to civil society organizations working in international affairs had increased to \$22.03 billion [@givingusa:2017].
-Most notably, a large portion of this is driven by individuals making small-scale donations.
-In 2017, individuals gave $286.7 billion - or approximately 70\% of total giving to international affairs.
-This further increased to $427.71 billion in 2018 - 85.7% of which was through individuals [givingusa:2019].
-Given that a majority of this research is restricted to elite, high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of individual donors.
+Most notably, a large portion of this growth is driven by individuals making small-scale donations.
+In 2017, individuals gave $286.7 billion, or approximately 70% of total giving to international affairs.
+This further increased to $427.71 billion in 2018, 85.7% of which was through individuals [givingusa:2019].
+Much of the existing research on donations to international causes is restricted to elite, high net-worth donors [@USTrust2014], but these large amounts demonstrate that it is imperative to understand the motivations and attributes of more ordinary individual donors.
 What factors affect individual donor preferences on giving to international causes?
-More specifically, how does information about regulatory environments abroad, as well as organizational-level attributes of nonprofits, such as their main focus areas and sources of funding affect donors' willingness to donate internationally?
+More specifically, how does information about regulatory environments abroad, as well as organizational-level attributes of NGOS— such as their main issues of focus and sources of funding—affect donors' willingness to donate internationally?
 
-Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974; @CrosonShang:2011; @Tremblay-BoirePrakash:2017], We leverage an online survey experiment using Amazon's Mechanical Turk to assesss how different structural and organizational-level heuristics affect individual donors' willingness to donate.
+Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974; @CrosonShang:2011; @Tremblay-BoirePrakash:2017], We leverage an online survey experiment using Amazon's Mechanical Turk to assess how different structural and organizational-level heuristics affect individual donors' willingness to donate.
 We find that learning about more repressive NGO regulatory environments increases generosity in that already likely donors are willing to donate substantially more to legally restricted NGOs.
 
-This generosity persists when mediated by two important organization-level heuristics: NGO issue area and its main funding sources.
+This generosity persists when mediated by two important organization-level heuristics: NGO issue area and funding sources.
 Learning about crackdown increases individuals' willingness to donate to privately funded nonprofits.
 This may be because the survival of the NGO appears to be in question and the donor's assessment might be that their donation actually makes a difference.
-These results are particularly substantive for privately-funded human rights NGOs facing crackdown - with donors showing an increased willingness to not just donate to them, but also to donate more to them.
-While not unsurprising, this does suggest that private donors to human rights NGOs likely know that their work is always challenging to governments, and that such organizations need greater support when facing stricter regulatory environments.
+These results are particularly substantive for privately-funded human rights NGOs facing crackdown, with donors showing an increased willingness to not just donate to them, but also to donate more to them.
+While not unsurprising, this does suggest that private donors to human rights NGOs likely know that their work is always challenging to host governments, and that such organizations need greater support when facing stricter regulatory environments.
 
-Our study makes a significant contribution to the scholarship and practice on dynamics of individual-giving and indicates the promise and limits of different framing appeals by nonprofits on individuals' willingness to donate.
-First, while factors giving shaping individual-giving to domestic causes have been thoroughly explored in existing literature, the dynamics of internatoinal giving are under-examined in the U.S.
-literature on individual donor preferences.[^exception] It is even more essential to understand as philanthropy to international causes can be harder to motivate because of the number of recipients are larger and far removed from the donor [@CasaleBaumann:2015, 100].
+Our study makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individuals' willingness to donate.
+First, while factors shaping individual giving to domestic causes have been thoroughly explored in existing literature, the dynamics of international giving and individual donor preferences are less explored.[^exceptions] Understanding the factors driving individual giving is particularly important when when looking at international issues, as philanthropy to international causes can be harder to motivate because of the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
 
@@
 But in the era of closing civic space, these groups may need to tailor their fundraising strategies to individual donors.
-Framing, or the process through which actors present information to infleunce perceptions of behavior, is particular important in this regard.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to donors considering international charitable-giving.
-Our study looks at the impact of political frames such as regulatory crackdown, and how it interacts with organizational attributes to signal NGO deservingness.
-In doing so, it can help nonprofits frame their appeals.
+Framing, or the process through which actors present information to influence perceptions of behavior, is particularly important in this regard.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to donors considering international philanthropy.
+Our study examines the impact of political frames such as regulatory crackdown, and how these frames interact with organizational attributes to signal NGO deservingness.
+Accordingly, our results can help international nonprofits frame their appeals for funding, especially when facing restricted legal space abroad.
 
-CHANGE
-Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect private philanthropy.
-We then describe our survey and present the results.
+Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect how individuals engage in philanthropy.
+We then describe our survey experiment and present the results.
 We conclude with implications for NGOs working in repressive countries and lay out questions ripe for future research.
 
-#Philanthropy towards international nonprofits
+# Philanthropy towards international NGOs
 
@@
 Public aid (more commonly known as traditional donor aid) channels funds from official aid agencies towards nonprofits through a variety of bilateral and multilateral institutions.
-Private funds, which are comparatively newer international donors compared to traditional donor aid, can come from foundations, private corporations and individuals.
+Private funds—which are comparatively newer international donors compared to traditional donor aid—can come from foundations, private corporations, and individuals.
 
-In this paper, we specifically look at individual-level determinants to foreign giving.
-As described in the introduction, this is because [ADD PART ABOUT ANY PUBLIC FIGURES AND HOW IT DECLINING] private-giving to nonprofits working in international affairs has been consistently increasing over this past decade.[^internationalaffairs] Moreover, private giving by individuals has far outstripped giving by private foundations - in 2018, charitable-giving by individuals amounted to $292.09 billion, compared by $75.86 billion by foundations and $20.05 billion by corporations.
-Thus, giving by foundation represented 18\% of all charitable-giving in 2018, which was not only lesser than the proportion of giving by private individuals, but also giving by Bill and Melinda Gates Foundation accounted for more than half of it [givingusa:2019].
+In this paper, we specifically look at individual-level determinants to international philanthropy.
+Private giving to nonprofits working in international affairs has increased consistently over the past decade.[^internationalaffairs] Moreover, donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
+While foundations are often seen as the primary funders of international charities, donations from foundations accounted for only 18% of all charitable giving in 2018—and grants from the Bill and Melinda Gates Foundation accounted for more than half of all foundation giving [@givingusa:2019].
+Individual donors play an incredibly important—and underexplored—role in funding international NGOs.
 
-Given these substantive amounts, understanding individual-level determinants of giving to international nonprofits is important to investigate as individual private donors may not necessarily mirror public donor choices.
-While there is evidence that citizens generally support the goals of aid agencies (Milner and Tingley 2010), surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
-Further, foreign aid and democracy aid is often considered unresponsive to developments on the ground [@brainard2007, @Carothers:2015] and public aid decisions - especially on final recipients are not easily accessible.
+Given these substantive amounts, understanding individual-level determinants of giving to international nonprofits is important to investigate as individual private donors may not necessarily mirror the preferences of official aid agencies.
+While there is evidence that citizens generally support the goals of aid agencies [@MilnerTingley2010], surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
+Further, both foreign aid and democracy aid are often considered unresponsive to political developments in recipient countries [@brainard2007; @Carothers:2015] and public aid decisions—especially about final recipients and amounts—are not easily accessible.
 There may also be heterogeneity within how donor governments allocate funds.
-Emerging donor government differ from established donors in that they demand fewer human rights, governance or environmental conditions preferred by Western donors [@fenglerkharas].
+For instance, unlike established donors like the United States and other OECD countries, emerging donor governments tend to demand fewer human rights, governance, or environmental preconditions [@fenglerkharas].
 
 More recent research on the allocation of private aid flows has also found little support for the idea that individual donor behavior mimics that of official donors.
-Desai and Kharas (2018) find that unlike official donors  whotend to channel funds to countries with better institutional quality (control of corruption) and as a performance reward (Bermeo 2011, Dietrich ad Wright 2017), individual donors do not use the same performance-based metrics.
-Rather, individuals are more inclined to donate to groups in countries experiencing a humanitarian crisis - in particular, those driven by natural disasters.
-They go on to conclude that compared to donor agencies, "private donors respond to different project and country characteristics." (517) Given these above reasons, decision-making by the average individual donor may therefore not have the same logic as donor governments and should be investigated on its own terms.
+@desaikharas find that unlike official donors who tend to channel funds to countries with better institutional quality or as a reward for governmental performance [@Bermeo:2011; @DietrichWright:2015], individual donors do not use the same performance-based metrics.
+Rather, individuals are more inclined to donate to groups in countries experiencing a humanitarian crisis—in particular, crises following natural disasters.
+@desaikharas conclude that compared to donor agencies, "private donors respond to different project and country characteristics" (p.
+517) Given these above reasons, the average individual donor will not follow the same decision-making logic as donor governments, and individual international philanthropy should therefore be investigated on its own terms.
 
-Understanding motivations of individual private donors is also essential because private funding flows towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
-Prior research has demonstrated that restrictions on cross-border funding has reduced official aid and official development assistance to repressive countries (CITE).
+Understanding the motivations of individual private donors is also essential because private funding flows towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
+Prior research has demonstrated that restrictions on cross-border funding has reduced official aid and official development assistance to repressive countries [@citeme].
 But data from the Foundation Center shows no correlation between amount of funding flows from US private foundations to a given country and that country's score on the Index of Philanthropic Freedom.
-While this index is comparatively new and data is available only 2015 onwards (CHECK), preliminary evidence shows that, "US foundations remain committed to channeling funds to countries where the legal environment is growing increasingly unfriendly." As such, it is imperative to understand whether individual donors mirror the trajectory of foundations when giving internationally, especially to countries with restrictive legal environments.
+Additionally, preliminary evidence shows that "US foundations remain committed to channeling funds to countries where the legal environment is growing increasingly unfriendly." [@citeme-too].
+As such, it is imperative to understand whether individual donors mirror the trajectory of foundations when giving internationally, especially to countries with restrictive legal environments.
 
-##Key drivers of individual-level philanthropy
+## Key drivers of individual-level philanthropy
 
@@
 However, research on individual donor behavior has overwhelming examined giving to local—rather than international—causes.
-This literature has primarily focused on the importance of X main factors, especially when considering charitable behavior towards international causes: (1) the role of social capital and social networks; (2) the role of individual experiences such as higher education and levels of religiosity; and (3) third party certifications.
+This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) the role of social capital and social networks; (2) the role of individual experiences such as higher education and levels of religiosity; and (3) third party certifications.
 
-One major area of inquiry in philanthropic studies looks at the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit." (Putnam 1997, 67).
-While quite broad, the literature further concentrates on a specific kind of social capital-associational capital-which refers to, "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
+One major area of inquiry in philanthropic studies looks at the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit" [@Putnam:1995, 67].
+While quite broad, the literature concentrates on "the networks of formal and informal relationships to which people are associated," [@havens2007, 240] or associational capital.
 Prior research has found that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
-Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations.
-This is because volunteering exposes individuals to the need for donations to charities and nonprofits and made them feel more compelled to do so [@hossainlamb2012].
+Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations, since volunteering exposed individuals to the need for charitable donations and made philanthropy more compelling [@hossainlamb2012].
+An individual's social networks also play an important in deciding to donate.
+Looking at relational configurations in social networks, @HerzogYang:2018 find that having both a giver and a solicitor in one's social network increase the likelihood of that individual's charitable giving.
 
-The role of social networks is also important in this regard.
-Looking at relational configurations in social networks, Herzog and Yang find that having both a giver and a solicitor in one's social network increase the likelihood of that individual's charitable-giving.
-
-Individual experiences such as access to higher education and increased religiosity can also impact philanthropic giving.
-Higher education fosters prosocial motivations and also brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
-This in turn has been shown to be particularly vital in giving to international causes.
-Additional education has also been shown to increase abstract thinking [@wiepkingmass, 1978].
-This is particular important for donating to international relief organizations than donating to domestic organizations [@micklewright2009].
-
+Individual experiences such as access to higher education and increased religiosity can also influence philanthropic giving.
+Higher education fosters prosocial motivations and brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
+Education also increases abstract thinking [@wiepkingmaas, 1978], which is particularly important for donating to more distant international relief organizations than donating to local, more visible nonprofits [@Micklewright:2009].
 Levels of religiosity are also a significant predictor of the likelihood and level of giving.
-People who regularly attention religious services are more likely to have prosocial values, face a stronger norm of charitable-giving, and may feel pressure to conform that group and community standard [@wiepking2010].
+People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@wiepking2010].
 Overall, individuals with higher levels of income, education, and greater religious proclivities have been shown to not only be more likely to give internationally, but also to give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
 
-Finally, information on organizational characteristics and third party certifications can also impact levels of individual charitable-giving, through the results are mixed.
+Finally, information about organizational characteristics and third party certifications can also impact levels of individual philanthropy, through results are mixed.
 Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
-The effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010] and that ratings by charity watchdogs do not really affect donor support for these nonprofits (Szper and Prakash 2011).
+The effects of changes in charity watchdog ratings and nonprofit accountability systems on individual donors is also mixed, showing that donors do not have the time to research charities thoroughly [@Bekkers:2010] and that ratings by charity watchdogs do not really affect donor support for these nonprofits [@SzperPrakash:2011].
 
-While a robust literature as shown above looks at the drivers of individual-level philanthropy, it overwhelmingly focusses on giving to local rather than international causes.
-This focus on local or domestic causes means that that the precise causal mechanisms through which cross-border charity can be motivated and mobilized is still under-examined (Desai and Kharas, 517).
-This problem is further compounded by the fact that there is greater paucity of data and diversity of sources regarding international-giving, which further complicates a systematic examination.
+While this robust literature looks at the drivers of individual-level philanthropy, it overwhelmingly focusses on giving to local rather than international causes.
+This domestic focus is warranted, though: on average, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
+However, this focus on domestic philanthropy causes means that that the precise causal mechanisms through which cross-border charity can be motivated and mobilized is still under-examined [@desaikharas, 517].
+This problem is further compounded by the fact that there is greater paucity of data and diversity of sources regarding international philanthropy.
+Indeed, most research on individual-giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014].[^highnetworth] Given the increasing importance of more ordinary individual donations for international NGOs, it is crucial to better understand what motivates private donors to engage in internationally-focused philanthropy.
 
-Indeed, most research on individual-giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014].[^highnetworth] And recent research has on the average donor finds that, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad." (TB Prakash 2017, 644) And as explained above in section X, private donors do not necessarily mirror the choices made by public donors and that individuals rely on signals and heuristics that may differ from the benchmarks used by large governmental and private donors.
-
+As explored previously, individual private donors do not necessarily mirror the choices made by public donors.
+Individuals rely on signals and heuristics that differ from the benchmarks used by large governmental agencies and private foundations.
 These signals and heuristics, we argue, can be even more important in giving to international causes.
@@
 
-#Theorizing the effects of political and organizational frames on individual-giving
+# Theorizing the effects of political and organizational frames on individual giving
 
@@
 Previous research has shown that that public donors do indeed differentiate between NGO issue areas, especially when these organizations are working in repressive contexts.
-In particular, the Organisation for Economic Cooperation and Development (OECD) donors respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increasing funding for groups working on relatively tamer causes such as health, education and agriculture [CITE US].
+In particular, donor agencies in the Organisation for Economic Cooperation and Development (OECD) respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increasing funding for groups working on relatively tamer causes such as health, education and agriculture [@ChaudhryHeiss:2018].
 
@@
 There is evidence that this a concern for private donors.
-In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many NGOs argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn was hurting women and trans rights organizations.
+In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many NGOs argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn hurt women and trans rights organizations.
 Some private funders, these groups argued, were also more likely to fund well-established groups that were more likely to survive crackdown.
@@
 NGOs working on tamer issues such as health, education, disaster relief, and humanitarian aid can often frame their activities as in need of greater support—the perception of need, whether through personal experiences or media framing.
-This may strongly influence individual decisions to donate to relief efforts [@BekkersWiepking:2010, 6–8].
+This may strongly influence individual decisions to donate to relief efforts [@wiepking2010].
 Individual donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
@@
 Government grants to nonprofits can often crowd out private funding, though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
-Donors may feel less inclined to contribute to INGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
-Organizations that receive substantial government funding frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
-In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help.
+Donors may feel less inclined to contribute to NGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
+Organizations that receive substantial funding from their home governments frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
+In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help and that their marginal donation would make a noticeable difference.
 
@@
 
-> **H~3a~**: If donors learn that legally besieged NGOs do not receive substantial funding from government sources, then individual donors will be more likely to donate to them.
+> **H~3a~**: If donors learn that legally besieged NGOs receive substantial funding from government sources, then individual donors will be less likely to donate to them.
 >
-> **H~3b~**: If donors learn that legally besieged NGOs do not receive substantial funding from government sources, then individual donors will donate more to them.
+> **H~3b~**: If donors learn that legally besieged NGOs receive substantial funding from government sources, then individual donors will donate less to them.
 
@@
 Similarly, knowing that an NGO faces legal trouble should be enough to trigger the structural deservingness heuristic.
+Moreover, while many NGOs and nonprofits make information about their funding sources easily accessible through annual reports, donors often do not take the time to track down that information.
+In each of these hypotheses, we assume that donors will not spend additional effort to research the exact details concerning crackdown, issue area, and funding sources.
+Instead, donors rely on signals in basic information about the organization to shape their preferences and behavior.
+
+We also posit that these signals work interactively to shape donor behavior and that combinations of characteristics will have different effects.
+For instance, the effect of crackdown will be different depending if an organization focuses on humanitarian assistance or human rights, or if it receives government funding or not.
+Because it is unclear a priori what these interactive effects will be, we test nested versions of the hypotheses in our analysis.
 
@@
 Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for private individuals.
+Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/).
+We made two minor deviations from the original preregistration, described in detail in the online appendix.[^deviations] The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, and Bayesian priors.
+The analysis is fully reproducible using code and data available at ANONYMIZED.
 
@@
 We test these hypotheses with a vignette-based survey experiment fielded through Amazon's Mechanical Turk.[^mturk] Our target population is the portion of Americans hypothetically willing to donate money for human rights and humanitarian work abroad.
-Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples.[^supp]
+Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples.
+Additionally, the majority of the sample (≈90%) feels favorably toward human rights, humanitarian, and development NGOs.
 
@@
 IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donations, and it works in countries with and without anti-NGO laws.
-We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:
+We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:[^consort]
 
@@
 
-We collected two outcome measures: (1) how likely participants would be to donate to IRC (measured with a 5-point scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100.
+We measured two outcomes: (1) how likely participants would be to donate to IRC (measured with a 5-point scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100.
 We collapsed the likelihood scale into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate.[^collapse] We also included an exploratory free response question asking respondents to justify their choice.
+
+Each of the varied treatments correspond to our hypotheses: crackdown vs.
+no crackdown, humanitarian assistance vs.
+human rights, and government vs.
+nongovernmental funding.
+Participants might misinterpret the vignette and assume that IRC's host governments fund the organization rather than its home government.
+In either case, knowing about government funding should still serve as a signal of the organization's deservingness.
+Similarly, there could be confusion with phrase "private funding", but since we use it as the opposite of government funding, it should still act as a heuristic.
+Free responses tend to confirm the correct interpretation of the vignette, and many respondents explicitly justified their lack of support for IRC because of government funding, as expected ("I see that a large portion of its funding comes from government donors, so I feel it doesn't need me as much."[^6216778])
 
@@
 For our second and third hypotheses we measure the difference in means spread across both issue and funding conditions.
-For additional exploration of the effect of issue and funding, we also measure the effect of crackdown within all combinations of issue and funding conditions.
+For additional exploration of the effect of issue and funding, we also measure the effect of crackdown within nested combinations of issue and funding conditions.
 
-We use two Bayesian models to estimate the effect of crackdown on the likelihood of donating and the amount hypothetically donated.[^priors] We model the proportion of respondents indicating they would likely donate as a binomial distribution:
+We use two Bayesian models to estimate the effect of crackdown on the likelihood of donating and the amount hypothetically donated.
+We model the proportion of respondents indicating they would likely donate as a binomial distribution:
 
@@
 
+@tbl:hypotheses provides a summary of how our results map onto our hypotheses, both individually and nested within each other.
+
+\stgroup
+
+\renewcommand*{\arraystretch}{1.35}
+
+```{r hypothesis-summary, warning=FALSE, message=FALSE, echo=FALSE, results="asis"}
+read_csv(here("data", "manual_data", "hypothesis-summary.csv")) %>%
+  mutate_at(vars(Hypothesis, Expectation),
+            ~str_replace_all(., "zzz", "\\\\\\\n")) %>%
+  pandoc.table(keep.line.breaks = TRUE, style = "grid", justify = "llll",
+                      caption = "Summary of hypotheses and results {#tbl:hypotheses}")
+```
+
+\fingroup
+
 ## Likelihood of donation
@@
 @fig:likely-diffs(B–C) shows the difference in the likelihood of donation for both crackdown conditions across NGO issue areas (H~2a~) and funding sources (H~3a~).
-Crackdown has almost no effect on the likelihood of donating to human rights NGOs (`r filter(likely, title == "Human rights")$p_neq0`).
+Crackdown has almost no effect on the likelihood of donating to human rights NGOs (`r filter(likely, title == "Human rights")$p_neq0`), which is not surprising, since people who donate to these kinds of NGOs likely know that their work is challenging to host governments.
 We hypothesized that the positive crackdown effect would be stronger for humanitarian NGOs, and while crackdown does have a positive effect under the humanitarian frame, the probability this difference is greater than zero is below our 95% threshold (`r filter(likely, title == "Humanitarian assistance")$p_neq0`).
 We do find some evidence for H~3a~, however.
-Crackdown has little effect on the likelihood of individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
+Crackdown has little effect on the likelihood of individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`), possibly because a donor might feel that their marginal donation would make a difference.
 
@@
 @fig:likely-diffs(D) shows the difference in donation likelihood across all experimental conditions.
-When donors know that a human rights organization is primarily government-funded, they are more likely to donate in the *absence* of crackdowns than when the NGO faces legal difficulties (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`).
-In contrast, when donors know that an organization is privately funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
-For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting funding and issue frames.
+When donors know that a human rights organization is primarily government-funded, they are substantially less likely to donate if the organization faces government crackdown abroad, which follows our expected hypotheses for both issue area and funding (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`), and could possibly reflect donor suspicion about the mission and goals of government-funded human rights programming.
+In contrast, when donors know that a human rights organization is privately funded, they are more likely to donate when there is a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
+The private funding heuristic appears to override the dampening in likelihood that should come from focusing on more contentious human rights issues.
+For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting either funding and issue frames—neither of the nested experimental frames play a heuristic role.
 
@@
 Additionally donors appear to both punish government-funded human rights NGOs facing crackdown and rally behind privately funded NGOs facing those same hurdles.
-Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.
+For instance, one respondent who was presented with a government-funded human rights version of IRC explained that "I'm not exactly sure what they did was right or wrong, I think it just seems bad, so I'm less likely to want to donate to them."[^8425616] Other respondents showed increased support when presented with a privately-funded version of IRC, explaining that they would donate a substantial amount because "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds.
 
@@
 
-Crackdowns do not substantially influence donors' *likelihood* to donate, but they do increase the *amount* of money that respondents are willing to contribute (see @fig:amount-diffs(A)).
+On their own, crackdowns do not substantially influence donors' *likelihood* to donate, but they do increase the *amount* of money that respondents are willing to contribute (see @fig:amount-diffs(A)).
 Informing participants that IRC faces legal hurdles abroad increased donations by `r md_dollar(filter(amount, title == "Crackdown")$mu_diff)` on average, a `r percent_0(filter(amount, title == "Crackdown")$pct_change)` increase from the no crackdown condition (`r filter(amount, title == "Crackdown")$p_neq0`).
 This provides good evidence for H~1b~—donors appear to give more money to besieged INGOs.
-In contrast, neither issue area nor funding have an effect on the amount donated (`r filter(amount, title == "Issue")$delta`; `r filter(amount, title == "Issue")$p_neq0`; `r filter(amount, title == "Funding")$delta`; `r filter(amount, title == "Funding")$p_neq0`), indicating that crackdown is a more powerful heuristic for determining private donations.
+In contrast, neither issue area nor funding on their own have an effect on the amount donated (`r filter(amount, title == "Issue")$delta`; `r filter(amount, title == "Issue")$p_neq0`; `r filter(amount, title == "Funding")$delta`; `r filter(amount, title == "Funding")$p_neq0`).
 
@@
 
-This trend also holds when accounting for NGO issue area.
+This trend also holds when nesting crackdown within NGO issue area.
 The crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance (see @fig:amount-diffs(B–C)).
@@
 We also find evidence for H~3b~.
-Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`).
+Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded, as hypothesized, (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`), possibly because the effects cancel each other out—legal crackdowns should increase the amount donated, but reliance on government funding dissuades donors from giving.
 
 Combining issue areas and funding sources provides more texture.
-We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately funded human rights NGOs when they face legal issues.
-This finding also applies to preferences regarding the amount donors donate.
-Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`.
+We previously found that donors less likely to donate to government-funded human rights NGOs and more likely to donate to privately funded human rights NGOs when they face legal issues.
+These trends also apply to preferences in the amount donors donate.
+Respondents were willing to donate `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`.
 Respondents explained that they chose to give additional money to privately funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).
@@
 No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately funded organizations.
-Donors might assume that an INGO which receives substantial money from USAID would have the support of the U.S.
-government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
+Donors might assume that an NGO that receives government funding would have government support when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
 Further research is needed to probe this trend.
 
- I would encourage you to revisit the hypotheses from the findings.
-Which hypotheses were supported, and which were not?
-Why does it matter whether NGOs are advocating human rights or provide humanitarian assistance, and how much government funding they receive?
-How did participants interpret the term government funding?
+# Discussion
 
-## Discussion
-While the results from the survey experiment above allows to hold the organization constant and test for specific hypotheses, there are a few caveats when interpreting these results, generalizing them to other contexts, and considering applied lessons for fundraisers.
+While the results from the survey experiment allows us to hold the organization constant and test for specific hypotheses, there are a few caveats to consider when interpreting these results, generalizing them to other contexts, and applying them to nonprofit fundraising.
 First, the experiment measures preferences (willingness to donate) rather than behavior (actual donations).
-While the former may not always neatly translate into the latter, there is evidence that individuals’ willingness to donate as measured in the experiment translates well into behavior.
-This is because the wording of the survey experiment uses an informational frame, where the focus is on educating the rather by presenting them with facts.
-Prior research has shown that informational frames (as opposed to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy) are important in generating donations (McEntire, Lieby, Kraine 2015).[^frametypes]
+While the former may not always neatly translate into the latter, there is evidence that individuals’ willingness to donate (as measured in the experiment) translates well into behavior.
+The wording of the survey experiment uses an informational frame, where the focus is on educating respondents, rather simply presenting them with facts.
+Prior research has shown that informational frames—as opposed to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy—are important in generating donations [@McEntireLeibyKrain:2015].[^frametypes]
 
-Moreover, research has also found that in the case of campaigns for human rights nonprofits, informational frames are a necessary precondition for getting people to act, and people are more likely to donate and undertake other actions when these informational frames are combined with personal frames (McEntire, Lieby, Kraine 2015).[^personalframes] This suggests that if governments attempt to repress international human rights nonprofits, then these organizations can potentially increase their resource flows by using a combination of these two frames.
+Moreover, prior research has found that informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate and undertake other actions when these informational frames are combined with personal frames [@McEntireLeibyKrain:2015].[^personalframes] This suggests that if governments attempt to repress international human rights nonprofits, then these organizations can potentially increase their resource flows by using a combination of these two frames.
 The survey instrument used above shows substantive increase in donors' willingness to donate to human rights groups facing crackdown, especially those that are privately-funded, and this result emerges from the use of just informational frames.
@@
 It is also worth noting that there is evidence, at least domestically, that restrictions on nonprofit activities spur changes in private donors’ actual giving patterns (and not merely their preferences).
-For instance, following the 2016 election, when Texas pledged to remove Planned Parenthood from its Medicaid program and a number of states proposed new restrictions on their work, donations to the organizations increased by over 40 times the usual amount.
-
-your convenience sample captures those relatively more likely to donate to charities, which perhaps allows you to have more specific lessons for fundraisers.
-
-Finally, given that the survey was administered to a convenience sample of Americans, it raises questions about external validity.
-1.
-ADD HOW RESULTS MAY DIFFER FOR REPRESENTATIVE SAMPLE OF AMERICANS.
-2.
-Would a sample of Europeans for instance be so skeptical towards government funding?
+For instance, following the 2016 U.S.
+presidential election, after Texas pledged to remove Planned Parenthood from its Medicaid program and a number of other states proposed new restrictions on their work, donations to the organization increased by over 40 times the usual amount [@citeme-as-well].
 
@@
 
-Dozens of countries have sought to restrict NGO funding and programming.
-Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many INGOs have turned to foreign private donors as an additional funding source.
-Since seeking out perfect information about a nonprofit and its activities, especially internationally, is costly and time-consuming, donors use heuristics when deciding whom to support.
-Existing research has shown that donors take cues and heuristics from social networks, but can other informational cues also influence donor preferences?
-We argue that domestic political environments of NGO host countries can indeed serve as one such heuristic.
-Our results show that while crackdowns do not directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
-This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately funded human rights NGOs.
+Dozens of countries have sought to restrict NGO funding and programming over the past few decades.
+Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors as an additional funding source.
+Since seeking out perfect information about a nonprofit and its activities—especially international programming—is costly and time-consuming, donors use heuristics when deciding which organizations to support.
+Existing research has shown that donors take cues and heuristics from their social networks and from organizational characteristics like GuideStar ratings.
+In this paper, we argue that other informational cues can influence donor preferences.
+We find that the domestic political environments of NGO host countries can indeed serve as one such heuristic.
+Our results show that while crackdowns do not consistently directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
+This effect persists when mediated by other organizational heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately funded human rights NGOs.
 Anti-NGO crackdowns can thus serve as a signal of NGO effectiveness.
@@
 While the survey experiment allows us to hold the organization constant and test for specific hypotheses, there are limits to its external validity.
+Our sample captures people who are relatively more likely to donate to charities and thus does not reflect the general U.S.
+population.
+Our findings do not apply to the total population—we still know very little about how anti-NGO crackdowns change perceptions of nonprofits in general.
 Future research should look to testing the generalizability of our findings to individual donors in other countries, as well as determining the extent to which these preferences translate into behavior.
-It is also important to explore among thsoe donors who give to international causes - explore the extent to which individuals are likely to give to domestic nonprofits abroad, compared to international nonprofits working in those countries.
+For instance, the nonprofit sector in the U.S.
+relies much more heavily on government funding than in Europe, where large organizations like Amnesty International and Médecins Sans Frontières receive very little support from their home governments [@Stroup:2012], which means that donors in these countries will have different preferences when choosing to donate to government- and privately-funded organizations.
+Future research should also look more narrowly at donors who regularly give to international causes, as these individuals are likely more aware of poltiical trends in the countries where their preferred organizations work.
 
-These results also have implications for nonprofit fundraising.
+Because our sample reflects those who are already willing to donate to charities, these results have important implications for nonprofit fundraising.
 NGOs may benefit from publicizing when they are targets of government crackdown and including that information in their framing appeals.
 While this may not be enough to sway the average U.S.
-citizen, our results show that communicating this information can convince already-likely donors to donate more to besieged groups.
-Further, if NGOs signal to donors that they receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
+donor, our results show that communicating this information can convince already-likely donors to donate more to besieged groups.
+Further, if NGOs signal to donors that they receive a majority of their funding from nongovernmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
+Additionally, since they run the risk of receiving lower support under legal crackdown, human rights organizations that face legal difficulty abroad should communicate why they are under crackdown to mitigate donor mistrust.
 
-[^supp]: See the online appendix for the text of the survey, as well as details about our sample demographics and balance across experimental conditions.
+[^deviations]: First, in the text of our preregistration, we inadvertently only specified non-nested versions of our hypotheses, but in our analysis plan, we describe the nested hypotheses.
+Second, in our analysis plan we stated that we would test for statisitcal differences using regression models with increasing numbers of interaction terms.
+This became unwiedly when interpreting results, though, and we instead simplified the analysis by estimating group means directly.
+The estimates are identical.
+
+[^consort]: The CONSORT diagram in the online appendix shows the balance of respondents across different vignette combinations.
 
@@
 
-[^priors]: See the online appendix for details about our prior choices and computational environment.
-
 [^mturk]: Samples from Mechanical Turk are not nationally representative.
 However, because we targeted our study at people who are willing to donate online, we are not overly concerned with these discrepancies.
-Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally comparable—see the online appendix for a lengthier discussion about this research.
+Moreover, a growing body of research comparing Mechanical Turk with other sampling services finds it generally commensurable—see the online appendix for a lengthier discussion about this research.
 
@@
 
-[^3154467]: Response 3154467.
+[^6216778]: Response 6216778.
 
@@
 
+[^8425616]: Response 8425616.
+
 [^internationalaffairs]: Giving USA defines the sector of international affairs to include any nonprofit organization working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
@@
 
-[^exceptions]: For exceptions, see @micklewright2009 on UK, @Rajan:2009 on Canada, @wiepking2010 on Netherlands, @CasaleBaumann:2015 on the USA.
+[^exceptions]: For exceptions, see @Micklewright:2009 on UK, @Rajan:2009 on Canada, @wiepking2010 on Netherlands, @CasaleBaumann:2015 on the USA.
 
@@
 [^framing]: Framing is the process through which actors present information to influence perceptions or behavior.
-Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [Benford and Snow 2000, Chong and Druckman 2007].
+Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [@BenfordSnow:2000; @ChongDruckman:2007].
 
-[^frametype]: For more on motivational and personal frames, see Benford and Snow 2000, Gamson 1995
+[^frametypes]: For more on motivational and personal frames, see @BenfordSnow:2000 and @Gamson:1995.
 
 [^personalframes]: Personal frames seek to humanize victims and entice action by invoking an emotional reaction.
-Research has found that people are more likely to be generous when donating to a human rights campaign with a single victim, as opposed to a statistical group of victims (Slovic 2007).
+Research has found that people are more likely to be generous when donating to a human rights campaign with a single victim, as opposed to a statistical group of victims [@Slovic:2007].
 
-[^NGO]: Nonprofit organizations (which we inter-changeably use with NGOs) are organizations for a public or mutual benefit other than generating profit for the owners or investors (Salamon 1998).
-NGOs can be either domestic i.e.
-an NGO that operates entirely in a single state, or international, more commonly known as INGOs.
-INGOs or international nonprofits, "operate independently of governments, are composed of members from two or more countries, and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors and international institutions." (Tarrow 2001) Unlike domestic NGOs, INGOs often work in countries outside of their main country of origin or headquarters.
+[^NGO]: Nonprofit organizations (which we interchangeably use with NGOs) are organizations for a public or mutual benefit other than generating profit for the owners or investors [@Salamon:1999].
+NGOs can be either domestic (i.e.
+an NGO that operates entirely in a single state), or international, more commonly known as INGOs.
+INGOs or international nonprofits, "operate independently of governments, are composed of members from two or more countries, and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors and international institutions" [@Tarrow:2001].
+Unlike domestic NGOs, INGOs often work in countries outside of their main country of origin or headquarters.

### 2020-06-18 manuscript/manuscript.Rmd
Severe cutting down pre Suparna

@@
 Contact: schaudhry@lclark.edu
-word-count: "FILL"
+word-count: "8,031"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression
@@
 
-Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon commonly known as "closing civic space" [@Carothers:2015; @DPR:2015].
+Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon known as "closing civic space" [@Carothers:2015; @DPR:2015].
 Repressive governments have enacted laws creating barriers to advocacy, funding, and entry, adversely affecting the work of thousands of NGOs, which typically rely on funding from donors across the world.
@@
 In 2017, individuals gave $286.7 billion, or approximately 70% of total giving to international affairs.
-This further increased to $427.71 billion in 2018, 85.7% of which was through individuals [givingusa:2019].
+This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019].
 Much of the existing research on donations to international causes is restricted to elite, high net-worth donors [@USTrust2014], but these large amounts demonstrate that it is imperative to understand the motivations and attributes of more ordinary individual donors.
 What factors affect individual donor preferences on giving to international causes?
-More specifically, how does information about regulatory environments abroad, as well as organizational-level attributes of NGOS— such as their main issues of focus and sources of funding—affect donors' willingness to donate internationally?
+More specifically, how does information about repressive regulatory environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?
 
-Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@TverskyKahneman:1974; @CrosonShang:2011; @Tremblay-BoirePrakash:2017], We leverage an online survey experiment using Amazon's Mechanical Turk to assess how different structural and organizational-level heuristics affect individual donors' willingness to donate.
+Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
+We use an survey experiment to assess how different structural and organizational-level heuristics affect individual donors' willingness to donate.
 We find that learning about more repressive NGO regulatory environments increases generosity in that already likely donors are willing to donate substantially more to legally restricted NGOs.
 
-This generosity persists when mediated by two important organization-level heuristics: NGO issue area and funding sources.
+This generosity persists when mediated by two important organization-level heuristics: issue area and funding source.
 Learning about crackdown increases individuals' willingness to donate to privately funded nonprofits.
@@
 But in the era of closing civic space, these groups may need to tailor their fundraising strategies to individual donors.
-Framing, or the process through which actors present information to influence perceptions of behavior, is particularly important in this regard.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to donors considering international philanthropy.
+Framing, or the process through which actors present information to influence perceptions of behavior, is particularly important in this regard [@ChongDruckman:2007].
+However, we lack systematic studies of which frames may be effective when making appeals to donors considering international philanthropy.
 Our study examines the impact of political frames such as regulatory crackdown, and how these frames interact with organizational attributes to signal NGO deservingness.
@@
 
-Thousands of international NGOs in the Global South receive funds from a variety of public and private sources each year.[^NGO] Though our focus in this paper is one private funding, it is essential to differentiate between the two sources.
-Public aid (more commonly known as traditional donor aid) channels funds from official aid agencies towards nonprofits through a variety of bilateral and multilateral institutions.
-Private funds—which are comparatively newer international donors compared to traditional donor aid—can come from foundations, private corporations, and individuals.
-
-In this paper, we specifically look at individual-level determinants to international philanthropy.
+Thousands of international NGOs in the Global South receive funds from a variety of public and private sources each year.[^NGO] Though we focus on private funding in this article, it is essential to differentiate between the two sources.
+Public aid, or more traditional donor aid, channels funds from official aid agencies towards nonprofits through a variety of bilateral and multilateral institutions.
+Private funds come from foundations, private corporations, and individuals.
+We are specifically interested in individual-level determinants to private international philanthropy.
 Private giving to nonprofits working in international affairs has increased consistently over the past decade.[^internationalaffairs] Moreover, donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
@@
 While there is evidence that citizens generally support the goals of aid agencies [@MilnerTingley2010], surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
-Further, both foreign aid and democracy aid are often considered unresponsive to political developments in recipient countries [@brainard2007; @Carothers:2015] and public aid decisions—especially about final recipients and amounts—are not easily accessible.
-There may also be heterogeneity within how donor governments allocate funds.
+Further, both foreign aid and democracy aid are often considered unresponsive to political developments in recipient countries [@Carothers:2015] and public aid decisions—especially regarding final recipients and amounts—are not easily accessible.
+There is also heterogeneity in how donor governments allocate funds.
 For instance, unlike established donors like the United States and other OECD countries, emerging donor governments tend to demand fewer human rights, governance, or environmental preconditions [@fenglerkharas].
@@
 Understanding the motivations of individual private donors is also essential because private funding flows towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
-Prior research has demonstrated that restrictions on cross-border funding has reduced official aid and official development assistance to repressive countries [@citeme].
-But data from the Foundation Center shows no correlation between amount of funding flows from US private foundations to a given country and that country's score on the Index of Philanthropic Freedom.
-Additionally, preliminary evidence shows that "US foundations remain committed to channeling funds to countries where the legal environment is growing increasingly unfriendly." [@citeme-too].
-As such, it is imperative to understand whether individual donors mirror the trajectory of foundations when giving internationally, especially to countries with restrictive legal environments.
+While anti-NGO restrictions have reduced official aid to repressive countries [@DupuyPrakash:2018], private foundations have continued to channel funds to countries with unfriendly legal environments [@Foundation-Center:2018].
+Accordingly, it is imperative to understand whether individual donors mirror the trajectory of foundations when giving internationally, especially to organizations facing legal crackdown abroad.
 
-## Key drivers of individual-level philanthropy
+# Key drivers of individual-level philanthropy
 
@@
 However, research on individual donor behavior has overwhelming examined giving to local—rather than international—causes.
-This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) the role of social capital and social networks; (2) the role of individual experiences such as higher education and levels of religiosity; and (3) third party certifications.
+This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) the role of social and associational capital, (2) the role of individual experiences such as higher education and levels of religiosity, and (3) third-party certifications.
 
-One major area of inquiry in philanthropic studies looks at the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit" [@Putnam:1995, 67].
-While quite broad, the literature concentrates on "the networks of formal and informal relationships to which people are associated," [@havens2007, 240] or associational capital.
-Prior research has found that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
+Prior research has found that those who participate in a variety of associations and build social capital are more likely to make larger donations [@hossainlamb2017].
 Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations, since volunteering exposed individuals to the need for charitable donations and made philanthropy more compelling [@hossainlamb2012].
@@
 
-Finally, information about organizational characteristics and third party certifications can also impact levels of individual philanthropy, through results are mixed.
+Finally, information about organizational characteristics and third-party certifications can also impact levels of individual philanthropy, through results are mixed.
 Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
@@
 This domestic focus is warranted, though: on average, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
-However, this focus on domestic philanthropy causes means that that the precise causal mechanisms through which cross-border charity can be motivated and mobilized is still under-examined [@desaikharas, 517].
-This problem is further compounded by the fact that there is greater paucity of data and diversity of sources regarding international philanthropy.
-Indeed, most research on individual-giving to international causes has been restricted to elite, high net-worth donors [@USTrust2014].[^highnetworth] Given the increasing importance of more ordinary individual donations for international NGOs, it is crucial to better understand what motivates private donors to engage in internationally-focused philanthropy.
+Accordingly, there is a lack of data and theory regarding international philanthropy.
+Most research on individual donors to international causes has been restricted to elite, high net-worth donors (those with more than $200,000 in annual income or $1 million in assets) [@USTrust2014].
+Given the increasing importance of more ordinary individual donations for international NGOs, it is crucial to better understand what motivates private donors to engage in internationally-focused philanthropy.
 
-As explored previously, individual private donors do not necessarily mirror the choices made by public donors.
-Individuals rely on signals and heuristics that differ from the benchmarks used by large governmental agencies and private foundations.
-These signals and heuristics, we argue, can be even more important in giving to international causes.
+Individuals rely on heuristics that differ from the benchmarks used by large governmental agencies and private foundations.
+These signals, we argue, can be even more important in giving to international causes.
 In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
-Instead, donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
+Instead, donors respond to a host of heuristics when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
-Nonprofits fundraising internationally may be therefore more reliant on framing.
+Nonprofits fundraising internationally may therefore rely framing to control perceptions.
 Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
@@
 
-To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different signals donors are exposed to.
+To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different frames donors are exposed to.
 Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for private individuals.
 Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/).
-We made two minor deviations from the original preregistration, described in detail in the online appendix.[^deviations] The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, and Bayesian priors.
+The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors.
 The analysis is fully reproducible using code and data available at ANONYMIZED.
@@
 We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy: (1) crackdown/no crackdown, (2) humanitarian assistance/human rights, and (3) government/private funding.
-We used the International Rescue Committee (IRC) as our example NGO because its work easily applies to each possible frame.
+We used the International Rescue Committee (IRC) as our example NGO because it fits within each possible frame.
 IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donations, and it works in countries with and without anti-NGO laws.
-We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:[^consort]
+We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:
 
@@
 
-Without considering issue or funding, we find that respondents are not more likely to donate to legally besieged INGOs (H~1a~).
+In isolation we find that respondents are not more likely to donate to legally besieged INGOs (H~1a~).
 As seen in @fig:likely-diffs(A), those exposed to the crackdown condition tend to have a slightly higher probability of donating (`r percent_1(filter(likely, title == "Crackdown")$theta_2)`) than those in the control condition (`r percent_1(filter(likely, title == "Crackdown")$theta_1)`), but the difference is not significant (`r filter(likely, title == "Crackdown")$delta`; `r filter(likely, title == "Crackdown")$p_neq0`).
@@
 The wording of the survey experiment uses an informational frame, where the focus is on educating respondents, rather simply presenting them with facts.
-Prior research has shown that informational frames—as opposed to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy—are important in generating donations [@McEntireLeibyKrain:2015].[^frametypes]
+Prior research has shown that informational frames—as opposed to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy—are important in generating donations [@McEntireLeibyKrain:2015].
 
-Moreover, prior research has found that informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate and undertake other actions when these informational frames are combined with personal frames [@McEntireLeibyKrain:2015].[^personalframes] This suggests that if governments attempt to repress international human rights nonprofits, then these organizations can potentially increase their resource flows by using a combination of these two frames.
-The survey instrument used above shows substantive increase in donors' willingness to donate to human rights groups facing crackdown, especially those that are privately-funded, and this result emerges from the use of just informational frames.
-If combined with personal frames, research indicates these donations may further increase.
+Moreover, prior research has found that informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate and undertake other actions when these informational frames are combined with personal frames [@McEntireLeibyKrain:2015].[^personalframes] This suggests that if governments attempt to repress international human rights nonprofits, these organizations can potentially increase donations by combining these two frames.
+Our experiment shows a substantial increase in donors' willingness to donate to human rights groups facing crackdown, especially those that are privately-funded, and this result emerges from the use of only informational frames.
+If combined with personal frames, research suggests these donations may further increase.
 
-It is also worth noting that there is evidence, at least domestically, that restrictions on nonprofit activities spur changes in private donors’ actual giving patterns (and not merely their preferences).
-For instance, following the 2016 U.S.
-presidential election, after Texas pledged to remove Planned Parenthood from its Medicaid program and a number of other states proposed new restrictions on their work, donations to the organization increased by over 40 times the usual amount [@citeme-as-well].
+It is also worth noting that there is evidence, at least domestically, that restrictions on nonprofit activities spur changes in private donors' actual giving patterns.
+For instance, after Texas and other states pledged to impose new restrictions on Planned Parenthood following the 2016 election, donations to the organization increased more than 40 times the usual amount [@Cooney:2016].
 
@@
 
-Dozens of countries have sought to restrict NGO funding and programming over the past few decades.
-Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors as an additional funding source.
+In the era of closing civic space, dozens of countries restricted international NGO funding and programming.
+Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many INGOs have turned to foreign private donors as an additional funding source.
 Since seeking out perfect information about a nonprofit and its activities—especially international programming—is costly and time-consuming, donors use heuristics when deciding which organizations to support.
-Existing research has shown that donors take cues and heuristics from their social networks and from organizational characteristics like GuideStar ratings.
-In this paper, we argue that other informational cues can influence donor preferences.
-We find that the domestic political environments of NGO host countries can indeed serve as one such heuristic.
+Existing research has shown that donors take cues from their social networks and from organizational characteristics.
+In this paper, we argue that other informational heuristics can influence donor preferences.
+We find that the domestic political environments of INGO host countries can indeed serve as one such signal.
 Our results show that while crackdowns do not consistently directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
 This effect persists when mediated by other organizational heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately funded human rights NGOs.
-Anti-NGO crackdowns can thus serve as a signal of NGO effectiveness.
 
@@
 relies much more heavily on government funding than in Europe, where large organizations like Amnesty International and Médecins Sans Frontières receive very little support from their home governments [@Stroup:2012], which means that donors in these countries will have different preferences when choosing to donate to government- and privately-funded organizations.
-Future research should also look more narrowly at donors who regularly give to international causes, as these individuals are likely more aware of poltiical trends in the countries where their preferred organizations work.
+Future research should also look more narrowly at donors who regularly give to international causes, as these individuals are likely more aware of political trends in the countries where their preferred organizations work.
 
@@
 Additionally, since they run the risk of receiving lower support under legal crackdown, human rights organizations that face legal difficulty abroad should communicate why they are under crackdown to mitigate donor mistrust.
-
-[^deviations]: First, in the text of our preregistration, we inadvertently only specified non-nested versions of our hypotheses, but in our analysis plan, we describe the nested hypotheses.
-Second, in our analysis plan we stated that we would test for statisitcal differences using regression models with increasing numbers of interaction terms.
-This became unwiedly when interpreting results, though, and we instead simplified the analysis by estimating group means directly.
-The estimates are identical.
-
-[^consort]: The CONSORT diagram in the online appendix shows the balance of respondents across different vignette combinations.
 
@@
 
-[^internationalaffairs]: Giving USA defines the sector of international affairs to include any nonprofit organization working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
-This classification is based upon the National Taxonomy of Exempt Entities Core which codes groups based upon their field of interest.
+[^internationalaffairs]: According to Giving USA, international affairs includes nonprofits working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
 
-[^exceptions]: For exceptions, see @Micklewright:2009 on UK, @Rajan:2009 on Canada, @wiepking2010 on Netherlands, @CasaleBaumann:2015 on the USA.
+[^exceptions]: For exceptions, see @Micklewright:2009 on the UK, @Rajan:2009 on Canada, @wiepking2010 on the Netherlands, and @CasaleBaumann:2015 on the USA.
 
-[^highnetworth]: High-net worth households are defined as having greater than $200,000 in annual household income and/or with more than $1,000,000 in assets, excluding primary residence.
+[^personalframes]: Personal frames humanize victims and entice action by invoking an emotional reaction.
+For instance.
+people are more be generous when donating to a human rights campaign with a single victim, rather than a statistical group of victims [@Slovic:2007].
 
-[^framing]: Framing is the process through which actors present information to influence perceptions or behavior.
-Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [@BenfordSnow:2000; @ChongDruckman:2007].
-
-[^frametypes]: For more on motivational and personal frames, see @BenfordSnow:2000 and @Gamson:1995.
-
-[^personalframes]: Personal frames seek to humanize victims and entice action by invoking an emotional reaction.
-Research has found that people are more likely to be generous when donating to a human rights campaign with a single victim, as opposed to a statistical group of victims [@Slovic:2007].
-
-[^NGO]: Nonprofit organizations (which we interchangeably use with NGOs) are organizations for a public or mutual benefit other than generating profit for the owners or investors [@Salamon:1999].
-NGOs can be either domestic (i.e.
-an NGO that operates entirely in a single state), or international, more commonly known as INGOs.
-INGOs or international nonprofits, "operate independently of governments, are composed of members from two or more countries, and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors and international institutions" [@Tarrow:2001].
-Unlike domestic NGOs, INGOs often work in countries outside of their main country of origin or headquarters.
+[^NGO]: We use the terms nonprofit organizations and NGOs interchangeably.
+We consider international NGOs to be nongovernmental nonprofit organizations with members from two or more countries and that work in countries outside of their home country.

### 2020-06-23 manuscript/manuscript.Rmd
Suparna edits

@@
 abstract: >-
-  Government restrictions on NGOs have become increasingly pervasive across the globe.
-While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private funding flows.
+  Government restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe.
+While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy.
 How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally?
-Using a survey experiment, we find that learning about repressive NGO regulatory environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits.
+Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits.
 This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and its main funding sources.
-We conclude by discussing the implications of our results on the scholarship and practice of nonprofits using different framing appeals to increase fundraising at a time when traditional funding to such organizations is decreasing.
+We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing.
 thanks: >-
@@
 word-count: "8,031"
-keywords: international NGOs, donor behavior, philanthropy, human rights, repression
+keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
 ---
@@
 
-Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon known as "closing civic space" [@Carothers:2015; @DPR:2015].
-Repressive governments have enacted laws creating barriers to advocacy, funding, and entry, adversely affecting the work of thousands of NGOs, which typically rely on funding from donors across the world.
-This is particularly the case in countries with weak institutions and poor governance, where international donors typically seek out NGOs to implement their projects, as direct aid transfers to recipient governments pose the risk of misuse and bureaucratic inefficiency [@Dietrich2013].
-As a result of this global crackdown on civil society, however, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While we know there has been a negative impact on funding from official governmental donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to engage in philanthropy.
+Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon known as "closing civic space" [@Carothers:2015; @DPR:2016].
+Repressive governments have enacted laws creating barriers to advocacy and funding for a variety of NGOs.
+The adverse effects of these laws are particularly felt in countries with weak institutions and poor governance.
+International donors directing aid to these countries typically seek out NGOs to implement their projects, as direct aid transfers to recipient governments pose the risk of misuse and bureaucratic inefficiency [@Dietrich2013].
+However, official aid flows to NGOs have decreased considerably in countries with repressive NGO environments [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+While we know there has been a negative impact on funding from official governmental donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to donate internationally.
 
-Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades, with a noticeable increase over the last decade.
+Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.
 Between 2014 and 2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report].
@@
 This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019].
-Much of the existing research on donations to international causes is restricted to elite, high net-worth donors [@USTrust2014], but these large amounts demonstrate that it is imperative to understand the motivations and attributes of more ordinary individual donors.
+While a lot is known about individuals' motivations for giving locally [@BekkersWiepking:2011], much less is known about motivations to give internationally and these large amounts show the urgency of understanding this phenomenon.
 What factors affect individual donor preferences on giving to international causes?
-More specifically, how does information about repressive regulatory environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?
+More specifically, how does information about repressive NGO environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?
 
 Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
-We use an survey experiment to assess how different structural and organizational-level heuristics affect individual donors' willingness to donate.
+We use a survey experiment fielded in the U.S.
+to assess how different structural and organizational-level heuristics affect these donors' willingness to donate.
 We find that learning about more repressive NGO regulatory environments increases generosity in that already likely donors are willing to donate substantially more to legally restricted NGOs.
@@
 This may be because the survival of the NGO appears to be in question and the donor's assessment might be that their donation actually makes a difference.
-These results are particularly substantive for privately-funded human rights NGOs facing crackdown, with donors showing an increased willingness to not just donate to them, but also to donate more to them.
-While not unsurprising, this does suggest that private donors to human rights NGOs likely know that their work is always challenging to host governments, and that such organizations need greater support when facing stricter regulatory environments.
+These results are particularly substantive for privately-funded human rights NGOs facing crackdown, with donors showing an increased willingness to not just donate to them, but also to donate *more* to them.
+While not unsurprising, this does suggest that private donors to human rights NGOs likely know that their work is always challenging to host governments, and that such organizations need greater support when facing hostile environments.
 
-Our study makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individuals' willingness to donate.
-First, while factors shaping individual giving to domestic causes have been thoroughly explored in existing literature, the dynamics of international giving and individual donor preferences are less explored.[^exceptions] Understanding the factors driving individual giving is particularly important when when looking at international issues, as philanthropy to international causes can be harder to motivate because of the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
+Our study makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individuals' willingness to donate internationally.
+While factors shaping individual giving to domestic causes have been thoroughly explored in existing literature, the dynamics of international giving and individual donor preferences are less explored.[^exceptions] Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
 
@@
 However, we lack systematic studies of which frames may be effective when making appeals to donors considering international philanthropy.
-Our study examines the impact of political frames such as regulatory crackdown, and how these frames interact with organizational attributes to signal NGO deservingness.
+Our study examines the impact of political frames such as regulatory crackdown, and how this frame interacts with organizational attributes to signal NGO deservingness.
 Accordingly, our results can help international nonprofits frame their appeals for funding, especially when facing restricted legal space abroad.
@@
 Public aid, or more traditional donor aid, channels funds from official aid agencies towards nonprofits through a variety of bilateral and multilateral institutions.
-Private funds come from foundations, private corporations, and individuals.
-We are specifically interested in individual-level determinants to private international philanthropy.
+Private funds come from foundations, corporations, and individuals.
+We are specifically interested in individual-level determinants of private international philanthropy.
+
 Private giving to nonprofits working in international affairs has increased consistently over the past decade.[^internationalaffairs] Moreover, donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
-While foundations are often seen as the primary funders of international charities, donations from foundations accounted for only 18% of all charitable giving in 2018—and grants from the Bill and Melinda Gates Foundation accounted for more than half of all foundation giving [@givingusa:2019].
-Individual donors play an incredibly important—and underexplored—role in funding international NGOs.
+While foundations are often seen as the primary funders of international nonprofits, donations from foundations accounted for only 18% of all charitable giving in 2018—and grants from the Bill and Melinda Gates Foundation accounted for more than half of all foundation giving [@givingusa:2019].
+Individual donors thus play an incredibly important—and underexplored—role in funding international NGOs.
 
-Given these substantive amounts, understanding individual-level determinants of giving to international nonprofits is important to investigate as individual private donors may not necessarily mirror the preferences of official aid agencies.
+Given these substantive amounts, understanding individual motivations to donate internationally is important to investigate as individual donor preferences may not necessarily mirror the preferences of official aid agencies.
 While there is evidence that citizens generally support the goals of aid agencies [@MilnerTingley2010], surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
@@
 There is also heterogeneity in how donor governments allocate funds.
-For instance, unlike established donors like the United States and other OECD countries, emerging donor governments tend to demand fewer human rights, governance, or environmental preconditions [@fenglerkharas].
+For instance, unlike established donors such as the United States and other Organisation for Economic Cooperation and Development (OECD) countries, emerging donor governments tend to demand fewer human rights, governance, or environmental preconditions [@fenglerkharas].
 
-More recent research on the allocation of private aid flows has also found little support for the idea that individual donor behavior mimics that of official donors.
+Recent experimental evidence also finds little support for the idea that individual donor behavior mimics that of official donors.
 @desaikharas find that unlike official donors who tend to channel funds to countries with better institutional quality or as a reward for governmental performance [@Bermeo:2011; @DietrichWright:2015], individual donors do not use the same performance-based metrics.
-Rather, individuals are more inclined to donate to groups in countries experiencing a humanitarian crisis—in particular, crises following natural disasters.
-@desaikharas conclude that compared to donor agencies, "private donors respond to different project and country characteristics" (p.
-517) Given these above reasons, the average individual donor will not follow the same decision-making logic as donor governments, and individual international philanthropy should therefore be investigated on its own terms.
+Rather, individuals are more inclined to donate to NGOs in countries experiencing a humanitarian crisis—in particular, crises following natural disasters.
+@desaikharas conclude that compared to donor agencies, "private donors respond to different project and country characteristics." (p.
+517) International philanthropy by individuals should therefore be investigated on its own terms.
 
-Understanding the motivations of individual private donors is also essential because private funding flows towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
+Looking at different funding flows, it is also notable that private funding towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
 While anti-NGO restrictions have reduced official aid to repressive countries [@DupuyPrakash:2018], private foundations have continued to channel funds to countries with unfriendly legal environments [@Foundation-Center:2018].
@@
 
-# Key drivers of individual-level philanthropy
+## Key drivers of individual-level philanthropy
 
@@
 
-Prior research has found that those who participate in a variety of associations and build social capital are more likely to make larger donations [@hossainlamb2017].
-Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations, since volunteering exposed individuals to the need for charitable donations and made philanthropy more compelling [@hossainlamb2012].
+Prior research has found that those who participate in a variety of associations and build social capital are more likely to make charitable donations as well as make larger donations [@hossainlamb2017, @hossainlamb2012].
 An individual's social networks also play an important in deciding to donate.
-Looking at relational configurations in social networks, @HerzogYang:2018 find that having both a giver and a solicitor in one's social network increase the likelihood of that individual's charitable giving.
+Looking at relational configurations in social networks, @HerzogYang:2018 find that having both a giver and a solicitor in one's social network increased the likelihood of that individual's charitable giving.
 
-Individual experiences such as access to higher education and increased religiosity can also influence philanthropic giving.
-Higher education fosters prosocial motivations and brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
-Education also increases abstract thinking [@wiepkingmaas, 1978], which is particularly important for donating to more distant international relief organizations than donating to local, more visible nonprofits [@Micklewright:2009].
-Levels of religiosity are also a significant predictor of the likelihood and level of giving.
-People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@wiepking2010].
+Individual experiences such as access to higher education and increased religiosity can also influence giving [@wiepking2010].
+Higher education fosters pro-social motivations and brings people into social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
+Education also increases abstract thinking [@wiepkingmaas, 1978], which is important for donating to distant international relief organizations than donating to local, more visible nonprofits [@Micklewright:2009].
 Overall, individuals with higher levels of income, education, and greater religious proclivities have been shown to not only be more likely to give internationally, but also to give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
 
-Finally, information about organizational characteristics and third-party certifications can also impact levels of individual philanthropy, through results are mixed.
+Finally, information about organizational characteristics and third-party certifications can also impact levels of individual philanthropy, though results are mixed.
 Existing research shows that information on the efficiency of NGOs merely steers rather than encourages or discourages overall donations [@ryazanov:efficiency].
@@
 
-While this robust literature looks at the drivers of individual-level philanthropy, it overwhelmingly focusses on giving to local rather than international causes.
-This domestic focus is warranted, though: on average, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
-Accordingly, there is a lack of data and theory regarding international philanthropy.
-Most research on individual donors to international causes has been restricted to elite, high net-worth donors (those with more than $200,000 in annual income or $1 million in assets) [@USTrust2014].
-Given the increasing importance of more ordinary individual donations for international NGOs, it is crucial to better understand what motivates private donors to engage in internationally-focused philanthropy.
+Even though these above factors affect individuals' motivations to donate internationally, extant literature on international giving focuses on donating during crises and emergencies.
+However, as @Micklewright:2009 point out, motivations for donating to ongoing international causes differ from donating money to natural disasters or emergency international causes.
+Under ordinary circumstances, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
+However, we lack adequate data and theory regarding international philanthropy.
+Most research on individual donors to international causes has been restricted to elite, high net-worth donors -- those with more than $200,000 in annual income or $1 million in assets [@USTrust2014].
+However, given the increasing funds channeled by individuals to international nonprofits, it is crucial to understand what motivates these donors to donate.
 
@@
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
-Nonprofits fundraising internationally may therefore rely framing to control perceptions.
+Nonprofits fundraising internationally may therefore rely on framing to control perceptions.
 Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
@@
 Conversely, donors can do little to change the domestic political environment of another country.
-Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged NGOs, even if donors are not completely satisfied with some organization-level features of a group.
+Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged groups, even if donors are not completely satisfied with some organization-level features of a group.
 As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated.
@@
 Further, their programmatic output is easily quantifiable and donors can see the results of their charity more readily [@Bush:2015].
-Previous research has shown that that public donors do indeed differentiate between NGO issue areas, especially when these organizations are working in repressive contexts.
-In particular, donor agencies in the Organisation for Economic Cooperation and Development (OECD) respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increasing funding for groups working on relatively tamer causes such as health, education and agriculture [@ChaudhryHeiss:2018].
+Previous research has shown that public donors do indeed differentiate between NGO issue areas, especially when these organizations are working in repressive contexts.
+In particular, donor agencies in the Organisation for Economic Cooperation and Development (OECD) respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increase funding for groups working on relatively tamer causes such as health, education and agriculture [@ChaudhryHeiss:2018].
 
@@
 There is evidence that this a concern for private donors.
-In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many NGOs argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn hurt women and trans rights organizations.
-Some private funders, these groups argued, were also more likely to fund well-established groups that were more likely to survive crackdown.
+In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many groups argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn hurt women and trans rights organizations.
+Some private funders, these groups argued, were also more likely to fund well-established groups that were more likely to survive crackdown [@mamacash].
 
-However, compared to our existing knowledge on public donors and foundation donors, we lack knowledge about how individual donors respond to frames emphasizing one nonprofit issue area over another, especially a contentious area over a tamer one.
-NGOs working on tamer issues such as health, education, disaster relief, and humanitarian aid can often frame their activities as in need of greater support—the perception of need, whether through personal experiences or media framing.
+However, compared to our existing knowledge on public donors and foundation donors, we lack knowledge about how individuals respond to frames emphasizing one nonprofit issue area over another, especially a contentious area over a tamer one.
+NGOs working on tamer issues such as health, education, disaster relief, and humanitarian aid can often frame their activities as in need of greater support.
 This may strongly influence individual decisions to donate to relief efforts [@wiepking2010].
-Individual donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
+On the flip side, ndividual donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
 
@@
 Government grants to nonprofits can often crowd out private funding, though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
-Donors may feel less inclined to contribute to NGOs receiving funds from agencies like USAID because such funding can signal a lack of independence from the government.
+Donors may feel less inclined to contribute to NGOs receiving funds from agencies like United States Agency for International Development (USAID) because such funding can signal a lack of independence from the government.
 Organizations that receive substantial funding from their home governments frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
@@
 Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the country an NGO operates in.
-Donors do not always know about anti-NGO laws in host countries or who funds an NGO when they make their contributions.
 Moreover, the average donor will not know exactly what "legal crackdown" entails for any given organization (i.e.
 does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
-For the sake of this experiment, this ambiguous definition is not a central concern as the heuristics we explore here are explicitly simplified shortcuts to donor information-gathering.
-Knowing that an organization works with human rights issues (even if donors are not familiar with specific kinds of rights) should be enough to trigger the issue-based deservingess heuristic.
+For the sake of this experiment, this ambiguity is not a central concern as the heuristics we explore here are explicitly simplified shortcuts to donor information-gathering.
+Knowing that an organization works with human rights issues (even if donors are not familiar with specific kinds of rights) should be enough to trigger the issue-based deservingness heuristic.
 Similarly, knowing that an NGO faces legal trouble should be enough to trigger the structural deservingness heuristic.
-Moreover, while many NGOs and nonprofits make information about their funding sources easily accessible through annual reports, donors often do not take the time to track down that information.
+Moreover, while many NGOs make information about their operations accessible through annual reports, it is time-consuming to track down that information.
 In each of these hypotheses, we assume that donors will not spend additional effort to research the exact details concerning crackdown, issue area, and funding sources.
-Instead, donors rely on signals in basic information about the organization to shape their preferences and behavior.
+Instead, donors rely on signals and heuristics about the organization to shape their preferences and behavior [@SzperPrakash:2011].
 
@@
 To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different frames donors are exposed to.
-Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for private individuals.
+Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals.
 Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/).
@@
 We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy: (1) crackdown/no crackdown, (2) humanitarian assistance/human rights, and (3) government/private funding.
-We used the International Rescue Committee (IRC) as our example NGO because it fits within each possible frame.
+We used the International Rescue Committee (IRC) as our example NGO because it fits within each possible frame and as such, involves no deception towards respondents.
 IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donations, and it works in countries with and without anti-NGO laws.
@@
 We hypothesized that the positive crackdown effect would be stronger for humanitarian NGOs, and while crackdown does have a positive effect under the humanitarian frame, the probability this difference is greater than zero is below our 95% threshold (`r filter(likely, title == "Humanitarian assistance")$p_neq0`).
+
 We do find some evidence for H~3a~, however.
-Crackdown has little effect on the likelihood of individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`), possibly because a donor might feel that their marginal donation would make a difference.
+Crackdown has little effect on individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
+This is possibly the case because a donor might feel that their marginal donation would make a difference.
 
@@
 @fig:likely-diffs(D) shows the difference in donation likelihood across all experimental conditions.
-When donors know that a human rights organization is primarily government-funded, they are substantially less likely to donate if the organization faces government crackdown abroad, which follows our expected hypotheses for both issue area and funding (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`), and could possibly reflect donor suspicion about the mission and goals of government-funded human rights programming.
+When donors know that a human rights organization is primarily government-funded, they are substantially less likely to donate if the organization faces government crackdown abroad.
+This follows our expected hypotheses for both issue area and funding (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`).
+This finding possibly reflects donor suspicion about the mission and goals of government-funded human rights programming.
+
 In contrast, when donors know that a human rights organization is privately funded, they are more likely to donate when there is a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
@@
 We also find evidence for H~3b~.
-Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded, as hypothesized, (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`), possibly because the effects cancel each other out—legal crackdowns should increase the amount donated, but reliance on government funding dissuades donors from giving.
+Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded, as hypothesized, (`r filter(amount, title == "Private")$p_neq0`).
+However, the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`).
+This is possibly because the effects cancel each other out—legal crackdowns should increase the amount donated, but reliance on government funding dissuades donors from giving, as predicted by the literature showing that governments can crowd out private funding.
 
@@
 No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately funded organizations.
-Donors might assume that an NGO that receives government funding would have government support when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
+Donors might assume that an NGO that receives government funding would have support from the home government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
 Further research is needed to probe this trend.
 
-# Discussion
+## Discussion: Can these preferences translate to behavior?
 
-While the results from the survey experiment allows us to hold the organization constant and test for specific hypotheses, there are a few caveats to consider when interpreting these results, generalizing them to other contexts, and applying them to nonprofit fundraising.
-First, the experiment measures preferences (willingness to donate) rather than behavior (actual donations).
-While the former may not always neatly translate into the latter, there is evidence that individuals’ willingness to donate (as measured in the experiment) translates well into behavior.
-The wording of the survey experiment uses an informational frame, where the focus is on educating respondents, rather simply presenting them with facts.
-Prior research has shown that informational frames—as opposed to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy—are important in generating donations [@McEntireLeibyKrain:2015].
+While the survey experiment allows us to hold the organization constant and test for specific hypotheses, there are a few caveats to consider when interpreting these results and applying them to nonprofit fundraising.
+This is because the experiment measures preferences (willingness to donate) rather than behavior (actual donations).
+However, there is evidence that individuals’ willingness to donate (as measured in the experiment) translates well into behavior.
+The wording of the survey experiment uses an informational frame, where the focus is on educating respondents.
+This is in stark contrast to the use of personal frames, which draw the audience’s attention to the plight of an individual, or motivational frames, which are meant to motivate individuals to act by creating feels of agency and efficacy.[^personalframes] Prior research has shown that informational frames are the most important frames in generating donations [@McEntireLeibyKrain:2015].
 
-Moreover, prior research has found that informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate and undertake other actions when these informational frames are combined with personal frames [@McEntireLeibyKrain:2015].[^personalframes] This suggests that if governments attempt to repress international human rights nonprofits, these organizations can potentially increase donations by combining these two frames.
+Moreover, prior research has found that informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate and undertake other actions when these informational frames are combined with personal frames [@McEntireLeibyKrain:2015].
 Our experiment shows a substantial increase in donors' willingness to donate to human rights groups facing crackdown, especially those that are privately-funded, and this result emerges from the use of only informational frames.
-If combined with personal frames, research suggests these donations may further increase.
+If organizations combined with information with personal frames, research suggests these donations may further increase.
 
@@
 For instance, after Texas and other states pledged to impose new restrictions on Planned Parenthood following the 2016 election, donations to the organization increased more than 40 times the usual amount [@Cooney:2016].
+Thus, donor preferences of increased generosity towards legally beseiged groups abroad also has some domestic parallels.
 
@@
 In the era of closing civic space, dozens of countries restricted international NGO funding and programming.
-Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many INGOs have turned to foreign private donors as an additional funding source.
+Between increasing crackdown on nonprofits and the withdrawal of official governmental aid, many INGOs have turned to foreign private donors as an additional funding source.
 Since seeking out perfect information about a nonprofit and its activities—especially international programming—is costly and time-consuming, donors use heuristics when deciding which organizations to support.
-Existing research has shown that donors take cues from their social networks and from organizational characteristics.
-In this paper, we argue that other informational heuristics can influence donor preferences.
-We find that the domestic political environments of INGO host countries can indeed serve as one such signal.
+In this paper, we argue that informational heuristics about NGOs' legal environments and organizational-level attributes can influence donor preferences for international giving.
+
+Using a survey experiment with respondents in the U.S., we find that the domestic political environments of INGO host countries can indeed serve as one such signal.
 Our results show that while crackdowns do not consistently directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
@@
 Our findings do not apply to the total population—we still know very little about how anti-NGO crackdowns change perceptions of nonprofits in general.
-Future research should look to testing the generalizability of our findings to individual donors in other countries, as well as determining the extent to which these preferences translate into behavior.
+
+Future research should test the generalizability of our findings to individual donors in other countries, as well as determine the extent to which these preferences translate into behavior.
 For instance, the nonprofit sector in the U.S.
-relies much more heavily on government funding than in Europe, where large organizations like Amnesty International and Médecins Sans Frontières receive very little support from their home governments [@Stroup:2012], which means that donors in these countries will have different preferences when choosing to donate to government- and privately-funded organizations.
+relies much more heavily on government funding than in Europe.
+In the latter, large organizations like Amnesty International and Médecins Sans Frontières receive very little support from their home governments [@Stroup:2012].
+This may imply that donors in European countries will have different preferences when choosing to donate to government and privately-funded organizations.
 Future research should also look more narrowly at donors who regularly give to international causes, as these individuals are likely more aware of political trends in the countries where their preferred organizations work.
@@
 
-[^internationalaffairs]: According to Giving USA, international affairs includes nonprofits working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
+[^internationalaffairs]: According to Giving USA, the category of `international affairs' includes nonprofits working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
 
@@
 [^personalframes]: Personal frames humanize victims and entice action by invoking an emotional reaction.
-For instance.
-people are more be generous when donating to a human rights campaign with a single victim, rather than a statistical group of victims [@Slovic:2007].
+For instance, people are more be generous when donating to a human rights campaign with a single victim, rather than a statistical group of victims [@Slovic:2007].
 

### 2020-06-25 manuscript/manuscript.Rmd
Final Suparna edits

@@
 abstract: >-
-  Government restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe.
+  State restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe.
 While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy.
@@
 Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits.
-This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and its main funding sources.
+This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and main funding sources.
 We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing.
@@
 Contact: schaudhry@lclark.edu
-word-count: "8,031"
+word-count: "7,935"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
@@
 However, official aid flows to NGOs have decreased considerably in countries with repressive NGO environments [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While we know there has been a negative impact on funding from official governmental donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to donate internationally.
+While we know there has been a negative impact on funding from official donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to donate internationally.
 
-Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.
-Between 2014 and 2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report].
-This amount is not insignificant—by 2016, total private giving to civil society organizations working in international affairs had increased to \$22.03 billion [@givingusa:2017].
-Most notably, a large portion of this growth is driven by individuals making small-scale donations.
+Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.[^internationalaffairs] Between 2014 and 2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report].
+This amount is not insignificant—by 2016, total private giving to nonprofits working in international affairs had increased to \$22.03 billion [@givingusa:2017].
+Most notably, a large portion of this growth was driven by individuals making small-scale donations.
 In 2017, individuals gave $286.7 billion, or approximately 70% of total giving to international affairs.
@@
 What factors affect individual donor preferences on giving to international causes?
-More specifically, how does information about repressive NGO environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?
+How does information about repressive NGO environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?
 
@@
 We use a survey experiment fielded in the U.S.
-to assess how different structural and organizational-level heuristics affect these donors' willingness to donate.
-We find that learning about more repressive NGO regulatory environments increases generosity in that already likely donors are willing to donate substantially more to legally restricted NGOs.
+to assess how different structural and organizational-level heuristics affect donor preferences.
+We find that learning about repressive NGO environments increases generosity and that already-likely donors are willing to donate substantially more to legally restricted nonprofits.
 
@@
 
-Our study makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individuals' willingness to donate internationally.
-While factors shaping individual giving to domestic causes have been thoroughly explored in existing literature, the dynamics of international giving and individual donor preferences are less explored.[^exceptions] Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
+Our study makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individual donor preferences.
+While factors shaping individual giving to domestic causes have been thoroughly explored in existing literature, the dynamics of international giving are less explored.[^exceptions] Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
 
@@
 However, we lack systematic studies of which frames may be effective when making appeals to donors considering international philanthropy.
-Our study examines the impact of political frames such as regulatory crackdown, and how this frame interacts with organizational attributes to signal NGO deservingness.
+Our study examines the impact of political frames such as regulatory crackdown, and how this frame interacts with organizational attributes to change donor preferences.
 Accordingly, our results can help international nonprofits frame their appeals for funding, especially when facing restricted legal space abroad.
 
-Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns on NGOs may affect how individuals engage in philanthropy.
+Below, we summarize existing research on the determinants of giving to NGOs and lay out our expectations regarding how crackdowns and NGO organizational attributes individuals' philanthropic preferences.
 We then describe our survey experiment and present the results.
@@
 
-Private giving to nonprofits working in international affairs has increased consistently over the past decade.[^internationalaffairs] Moreover, donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
-While foundations are often seen as the primary funders of international nonprofits, donations from foundations accounted for only 18% of all charitable giving in 2018—and grants from the Bill and Melinda Gates Foundation accounted for more than half of all foundation giving [@givingusa:2019].
+Private giving to nonprofits working in international affairs has increased consistently over the past decade.
+Moreover, donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
+While foundations are often seen as the primary funders of international nonprofits, they accounted for only 18% of all charitable giving in 2018—and grants from the Bill and Melinda Gates Foundation accounted for more than half of all foundation giving [@givingusa:2019].
 Individual donors thus play an incredibly important—and underexplored—role in funding international NGOs.
 
-Given these substantive amounts, understanding individual motivations to donate internationally is important to investigate as individual donor preferences may not necessarily mirror the preferences of official aid agencies.
-While there is evidence that citizens generally support the goals of aid agencies [@MilnerTingley2010], surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
+Given these substantive amounts, understanding individual motivations to donate internationally is important as individual donor preferences may not necessarily mirror the preferences of official aid agencies.
+While there is evidence that citizens generally support the goals of aid agencies [@MilnerTingley2010], surveys show that the American public is notoriously misinformed about U.S.
+foreign aid [@norris:2017].
 Further, both foreign aid and democracy aid are often considered unresponsive to political developments in recipient countries [@Carothers:2015] and public aid decisions—especially regarding final recipients and amounts—are not easily accessible.
@@
 Recent experimental evidence also finds little support for the idea that individual donor behavior mimics that of official donors.
-@desaikharas find that unlike official donors who tend to channel funds to countries with better institutional quality or as a reward for governmental performance [@Bermeo:2011; @DietrichWright:2015], individual donors do not use the same performance-based metrics.
+@desaikharas find that unlike official donors who tend to channel funds to countries with better institutional quality or to reward governmental performance [@Bermeo:2011; @DietrichWright:2015], individual donors do not use the same performance-based metrics.
 Rather, individuals are more inclined to donate to NGOs in countries experiencing a humanitarian crisis—in particular, crises following natural disasters.
@@
 
-Looking at different funding flows, it is also notable that private funding towards nonprofits working internationally appear to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
+Looking at different funding flows, it is also notable that private funding towards nonprofits working internationally appears to not be as adversely impacted as public funding flows in the face of the global crackdown on NGOs.
 While anti-NGO restrictions have reduced official aid to repressive countries [@DupuyPrakash:2018], private foundations have continued to channel funds to countries with unfriendly legal environments [@Foundation-Center:2018].
@@
 
-Substantial research on charitable giving has looked at the motivations of private donors, with much of this work focusing on the individual-level determinants of giving [@Wiepking:2010; @BekkersWiepking:2011].
-However, research on individual donor behavior has overwhelming examined giving to local—rather than international—causes.
-This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) the role of social and associational capital, (2) the role of individual experiences such as higher education and levels of religiosity, and (3) third-party certifications.
+Substantial research on charitable giving has looked at the motivations of individual donors [@Wiepking:2010; @BekkersWiepking:2011].
+However, research on individual donor behavior has overwhelmingly examined giving to organizations working locally, rather than internationally.
+This literature has primarily focused on the importance of three main factors, especially when considering international philanthropy: (1) the role of social and associational capital, (2) the role of individual experiences such as higher education and levels of religiosity, and (3) third-party certifications.
 
-Prior research has found that those who participate in a variety of associations and build social capital are more likely to make charitable donations as well as make larger donations [@hossainlamb2017, @hossainlamb2012].
-An individual's social networks also play an important in deciding to donate.
+Prior research has found that those who participate in a variety of associations and build social capital are more likely to make charitable donations as well as make larger donations [@hossainlamb2017].
+An individual's social network also plays an important in deciding to donate.
 Looking at relational configurations in social networks, @HerzogYang:2018 find that having both a giver and a solicitor in one's social network increased the likelihood of that individual's charitable giving.
@@
 Individual experiences such as access to higher education and increased religiosity can also influence giving [@wiepking2010].
-Higher education fosters pro-social motivations and brings people into social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
+Higher education fosters pro-social motivations and brings people into social networks that entail a higher level of solicitation [@BekkersWiepking:2011].
 Education also increases abstract thinking [@wiepkingmaas, 1978], which is important for donating to distant international relief organizations than donating to local, more visible nonprofits [@Micklewright:2009].
@@
 However, we lack adequate data and theory regarding international philanthropy.
-Most research on individual donors to international causes has been restricted to elite, high net-worth donors -- those with more than $200,000 in annual income or $1 million in assets [@USTrust2014].
+Most research on individual donors to international causes has been restricted to elite, high net-worth donors—those with more than $200,000 in annual income or $1 million in assets [@USTrust2014].
 However, given the increasing funds channeled by individuals to international nonprofits, it is crucial to understand what motivates these donors to donate.
@@
 In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
-Instead, donors respond to a host of heuristics when deciding whether to donate to an NGO, since seeking complete information about an organization's deservingness and efficiency is costly and time-consuming.
+Instead, donors respond to a host of heuristics when deciding whether to donate to an NGO, since seeking complete information about an organization is costly and time-consuming.
 These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009].
@@
 
-# Theorizing the effects of political and organizational frames on individual giving
+# Theorizing the effects of structural and organizational frames on individual giving
 
-In addition to organizational factors that signal an NGO's trustworthiness and deservingness, we argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
-We propose that the regulatory relationship between international NGOs (INGOs) and their host governments serves as a signal of NGO trustworthiness and deservingness.
+We argue that structural factors—including whether an organization works abroad and the domestic political environment of the group's host country—can serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017].
+We propose that the regulatory relationship between international NGOs and their host governments serves one such heuristic.
 NGO legislation is not inherently restrictive, and governments frequently use laws to regulate the behavior of NGOs [@BloodgoodTB; @DeMattee:2018].
@@
 
-We argue that donors perceive legal crackdowns differently from organization-level heuristics—such as NGO missions, visions, values—because donors may be able to influence these latter attributes, at least to some extent.
+We argue that donors perceive legal crackdowns differently from organizational-level heuristics—such as NGO missions and programming—because donors may be able to influence these latter attributes, at least to some extent.
 Conversely, donors can do little to change the domestic political environment of another country.
-Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged groups, even if donors are not completely satisfied with some organization-level features of a group.
+Legal crackdowns abroad can signal to donors that the government may eventually target other NGOs as well, which can increase donor urgency to support legally besieged groups, even if donors are not completely satisfied with some organizational-level features of a group.
 As such, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated.
@@
 Countries are more likely to repress NGOs both when organizational issue areas (**I**) are in tension with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015].
-Both of these organizational characteristics thus confound the causal effect of crackdowns on donor decisions and must be accounted for in the analysis—issue areas and funding sources simultaneously influence the likelihood of crackdown while also serving as organizational heuristics that influence donor perceptions of NGO deservingness.
+Both of these organizational characteristics thus confound the causal effect of crackdowns on donor decisions and must be accounted for in the analysis—issue areas and funding sources simultaneously influence the likelihood of crackdown while also serving as organizational heuristics that influence donor preferences.
 
-![Causal diagram of the relationship of organizational and structural causes of donor behavior](output/figures/causal-path.pdf){#fig:causal-path}
+![Causal diagram of the relationship of organizational and structural causes of donor preferences](output/figures/causal-path.pdf){#fig:causal-path}
 
@@
 Previous research has shown that public donors do indeed differentiate between NGO issue areas, especially when these organizations are working in repressive contexts.
-In particular, donor agencies in the Organisation for Economic Cooperation and Development (OECD) respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increase funding for groups working on relatively tamer causes such as health, education and agriculture [@ChaudhryHeiss:2018].
+Donor agencies in OECD countries respond to repressive NGO environments, especially those containing barriers to advocacy, by decreasing funds for groups working on politically sensitive causes such as anti-corruption initiatives, elections, human rights, legal reform and security sector reform, and instead increase funding for groups working on relatively tamer causes such as health, education and agriculture [@ChaudhryHeiss:2018].
 
@@
 There is evidence that this a concern for private donors.
-In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many groups argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn hurt women and trans rights organizations.
+In a survey of women’s NGOs across the globe conducted by Mama Cash and Urgent Action Fund, many groups argued that private donors (especially foundations) were withdrawing from funding sensitive issues in repressive contexts, which in turn hurt women's and trans rights organizations.
 Some private funders, these groups argued, were also more likely to fund well-established groups that were more likely to survive crackdown [@mamacash].
@@
 This may strongly influence individual decisions to donate to relief efforts [@wiepking2010].
-On the flip side, ndividual donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
+On the flip side, individual donors may believe that it is more difficult to improve human rights in the host country and subsequently shy away from donating to NGOs working on contentious causes.
 
 As such, we hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, directed towards the most deserving of need, and are more capable of producing short-term quantifiable results.
-We use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues.
+We use humanitarian NGOs as a proxy for groups working on non-contentious issues and human rights NGOs as a proxy for contentious issues.
 
@@
 Government grants to nonprofits can often crowd out private funding, though evidence is mixed on whether this completely or partially crowds out private dollars [@Steinberg:1991; @Heutel:2014].
-Donors may feel less inclined to contribute to NGOs receiving funds from agencies like United States Agency for International Development (USAID) because such funding can signal a lack of independence from the government.
+Donors may feel less inclined to contribute to NGOs receiving funds from agencies like the United States Agency for International Development (USAID) because such funding can signal a lack of independence from the government.
 Organizations that receive substantial funding from their home governments frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
@@
 As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding again confounds the effect of anti-NGO crackdowns on donor behavior (see @fig:causal-path).
-Accordingly, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
-Individual donors may be less likely to donate to government-funded NGOs that face restrictions, since legal trouble with the organization's primary funder could fuel private donor mistrust (i.e.
-perhaps the NGO did something to deserve crackdown).
+Accordingly, the combination of legal crackdown and funding may affect donor preferences.
+Individual donors may be less likely to donate to government-funded NGOs that face restrictions, since they may believe that legally besieged government-backed NGOs would enjoy the backing of their home government when facing difficulties.
+Legal trouble in the NGO's host country could also indicate mistrust between the home and host government—a dynamic that individuals may not wish to enter with their dollars.
 Donors thus may be likely to donate more to NGOs that rely on private funding.
 
-> **H~3a~**: If donors learn that legally besieged NGOs receive substantial funding from government sources, then individual donors will be less likely to donate to them.
+> **H~3a~**: If donors learn that legally besieged NGOs receive substantial funding from their home government, then individual donors will be less likely to donate to them.
 >
-> **H~3b~**: If donors learn that legally besieged NGOs receive substantial funding from government sources, then individual donors will donate less to them.
+> **H~3b~**: If donors learn that legally besieged NGOs receive substantial funding from their home government, then individual donors will donate less to them.
 
@@
 For the sake of this experiment, this ambiguity is not a central concern as the heuristics we explore here are explicitly simplified shortcuts to donor information-gathering.
-Knowing that an organization works with human rights issues (even if donors are not familiar with specific kinds of rights) should be enough to trigger the issue-based deservingness heuristic.
-Similarly, knowing that an NGO faces legal trouble should be enough to trigger the structural deservingness heuristic.
+Knowing that an organization works on human rights issues (even if donors are not familiar with specific kinds of rights), or knowing that an NGO faces legal trouble abroad should be enough to trigger the effect of these frames on donor preferences.
 Moreover, while many NGOs make information about their operations accessible through annual reports, it is time-consuming to track down that information.
@@
 
-We also posit that these signals work interactively to shape donor behavior and that combinations of characteristics will have different effects.
-For instance, the effect of crackdown will be different depending if an organization focuses on humanitarian assistance or human rights, or if it receives government funding or not.
-Because it is unclear a priori what these interactive effects will be, we test nested versions of the hypotheses in our analysis.
+We also posit that these signals work interactively to shape donor preferences—as seen in @fig:causal-path, issue areas and funding sources each change the probability of NGO crackdown and confound causal relationships.
+As such, the effect of crackdown will be different depending on if an organization focuses on humanitarian assistance or human rights, or if it receives government funding or not.
+Accordingly, we test nested versions of these hypotheses in our analysis.
+it is unclear a priori what these interactive effects will be and which frames are more powerful when nested, though in general we expect the nested hypotheses to have an additive effect (i.e.
+because crackdown and humanitarian assistance should each have a positive effect on preferences on their own, the combination of the two will have a larger positive effect).
 
@@
 Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals.
-Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/).
+Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/?view_only=73bf237f7f5e4e15908bc4160517ccb3](https://osf.io/dx973/?view_only=73bf237f7f5e4e15908bc4160517ccb3).
 The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors.
@@
 We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy: (1) crackdown/no crackdown, (2) humanitarian assistance/human rights, and (3) government/private funding.
-We used the International Rescue Committee (IRC) as our example NGO because it fits within each possible frame and as such, involves no deception towards respondents.
-IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donations, and it works in countries with and without anti-NGO laws.
-We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:
+We used the International Rescue Committee (IRC) as our example NGO because it fits within each possible frame and as such, requires no respondent deception.
+IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donations, and it works in countries with and without anti-NGO laws.[^irc] We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:
 
@@
 We measured two outcomes: (1) how likely participants would be to donate to IRC (measured with a 5-point scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100.
+Research finds that the factors driving donation willingness and amounts differ depending on donor income, pro-social attitudes, self-image, and other psychological benefits [@Wiepking:2007].
+Accordingly, our framing treatments might differ across the two outcomes.
 We collapsed the likelihood scale into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate.[^collapse] We also included an exploratory free response question asking respondents to justify their choice.
@@
 Crackdown has little effect on individual preferences to donate to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).
-This is possibly the case because a donor might feel that their marginal donation would make a difference.
+This is likely because a donor might feel that their marginal donation would make a difference.
+For instance, one respondent reasoned that since IRC "is already receiving funding from governments, so funding from private individuals doesn't seem as necessary.
+I'd prefer to give my money to an organization that is primarily run by private donations."[^6486084]
 
@@
 This finding possibly reflects donor suspicion about the mission and goals of government-funded human rights programming.
+For instance, one respondent in the government and human rights conditions explained that they did not donate because "government donors might have interests that actually hurt refugees, and are donating to have some sway in the organization"[^2560169]
 
 In contrast, when donors know that a human rights organization is privately funded, they are more likely to donate when there is a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`).
-The private funding heuristic appears to override the dampening in likelihood that should come from focusing on more contentious human rights issues.
+As explained previously, each of the heuristics on their own influence the propensity to donate, but we do not yet know how the interaction between heuristics affects donor behavior.
+Here, the private funding heuristic appears to override the dampening in likelihood that should come from focusing on more contentious human rights issues.
 For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting either funding and issue frames—neither of the nested experimental frames play a heuristic role.
@@
 Combining issue areas and funding sources provides more texture.
-We previously found that donors less likely to donate to government-funded human rights NGOs and more likely to donate to privately funded human rights NGOs when they face legal issues.
+We previously found that donors are less likely to donate to government-funded human rights NGOs and more likely to donate to privately funded human rights NGOs when they face legal issues.
 These trends also apply to preferences in the amount donors donate.
@@
 The crackdown condition causes this increase despite some hesitation from respondents who often indicated that government-funded NGOs do not deserve private donations.
-Respondents reasoned since IRC "is already receiving funding from governments, so funding from private individuals doesn't seem as necessary.
-I'd prefer to give my money to an organization that is primarily run by private donations"[^6486084] or because "[m]y tax paying dollars go to the government and if the government is helping to fund it then they are in turn getting some of my money."[^9509936] This hesitation is not universal, however, and in aggregate most respondents chose to give substantially more.
-Many echoed this respondent, who identified the crackdown condition as one of the reasons for giving the full hypothetical \$100: "I believe the work of such organizations has an urgency that affects many refugees and their families.
-If they can function without being affected by the harsh laws against non-profits, I would want them to have as much help as possible to do their humanitarian work."[^1097165] Thus, legal crackdowns can increase individual donor urgency to support an organization, and this heuristic is potentially processed differently compared to other organization-level heuristics or information from social networks.
+Many respondents in the crackdown condition argued that "[m]y tax paying dollars go to the government and if the government is helping to fund it then they are in turn getting some of my money."[^9509936] This hesitation is not universal, however, and in aggregate most respondents chose to give substantially more.
+Many echoed this respondent, who identified the crackdown condition as one of the reasons for giving the full hypothetical \$100: "If they can function without being affected by the harsh laws against non-profits, I would want them to have as much help as possible to do their humanitarian work."[^1097165] Thus, legal crackdowns can increase individual donor urgency to support an organization, and this heuristic is potentially processed differently compared to other organization-level heuristics or information from social networks.
 
 In contrast, crackdowns have no substantial effect on the amount donated to privately funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`).
-No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately funded organizations.
+No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is thus possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately funded organizations.
 Donors might assume that an NGO that receives government funding would have support from the home government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges.
@@
 
-Moreover, prior research has found that informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate and undertake other actions when these informational frames are combined with personal frames [@McEntireLeibyKrain:2015].
+Moreover, informational frames are a necessary precondition for encouraging action in human rights nonprofit campaigns, and individuals are more likely to donate when informational frames are combined with personal frames [@McEntireLeibyKrain:2015].
 Our experiment shows a substantial increase in donors' willingness to donate to human rights groups facing crackdown, especially those that are privately-funded, and this result emerges from the use of only informational frames.
@@
 
-It is also worth noting that there is evidence, at least domestically, that restrictions on nonprofit activities spur changes in private donors' actual giving patterns.
+It is also worth noting that there is evidence, at least domestically, that restrictions on nonprofit activities spur changes in private donors' giving patterns.
 For instance, after Texas and other states pledged to impose new restrictions on Planned Parenthood following the 2016 election, donations to the organization increased more than 40 times the usual amount [@Cooney:2016].
-Thus, donor preferences of increased generosity towards legally beseiged groups abroad also has some domestic parallels.
+Thus, donor preferences of increased generosity towards legally besieged groups abroad also has some domestic parallels.
 
@@
 In the era of closing civic space, dozens of countries restricted international NGO funding and programming.
-Between increasing crackdown on nonprofits and the withdrawal of official governmental aid, many INGOs have turned to foreign private donors as an additional funding source.
+With the consequent withdrawal of official governmental aid, many INGOs have turned to foreign individual donors as an additional funding source.
 Since seeking out perfect information about a nonprofit and its activities—especially international programming—is costly and time-consuming, donors use heuristics when deciding which organizations to support.
@@
 
-Using a survey experiment with respondents in the U.S., we find that the domestic political environments of INGO host countries can indeed serve as one such signal.
-Our results show that while crackdowns do not consistently directly influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
+Using a survey experiment with respondents in the U.S., we find that the domestic political environments of INGO host countries can serve as one such signal.
+Our results show that while crackdowns do not consistently influence individual preferences of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs.
 This effect persists when mediated by other organizational heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, and `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately funded human rights NGOs.
@@
 For instance, the nonprofit sector in the U.S.
-relies much more heavily on government funding than in Europe.
+relies more heavily on government funding than in Europe.
 In the latter, large organizations like Amnesty International and Médecins Sans Frontières receive very little support from their home governments [@Stroup:2012].
@@
 donor, our results show that communicating this information can convince already-likely donors to donate more to besieged groups.
-Further, if NGOs signal to donors that they receive a majority of their funding from nongovernmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown.
-Additionally, since they run the risk of receiving lower support under legal crackdown, human rights organizations that face legal difficulty abroad should communicate why they are under crackdown to mitigate donor mistrust.
+Further, if NGOs signal to donors that they receive a majority of their funding from private sources, they may be able to convince individual donors that their contributions might help the NGO resist the crackdown.
 
@@
 
-[^internationalaffairs]: According to Giving USA, the category of `international affairs' includes nonprofits working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
+[^2560169]: Response 2560169.
+
+[^internationalaffairs]: According to Giving USA, the category of "international affairs" includes nonprofits working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
 
@@
 [^personalframes]: Personal frames humanize victims and entice action by invoking an emotional reaction.
-For instance, people are more be generous when donating to a human rights campaign with a single victim, rather than a statistical group of victims [@Slovic:2007].
+Prior research finds that people are more be generous when donating to a campaign with a single victim, rather than a statistical group of victims [@Slovic:2007].
 
 [^NGO]: We use the terms nonprofit organizations and NGOs interchangeably.
-We consider international NGOs to be nongovernmental nonprofit organizations with members from two or more countries and that work in countries outside of their home country.
+We consider international NGOs to be nongovernmental organizations with members from two or more countries and that work in countries outside of their home country.
+
+[^irc]: Some respondents may have been influenced by prior opinions of IRC. Randomization distributes this bias across the different conditions and likely lessens the threat to validity.

### 2020-06-25 manuscript/manuscript.Rmd
Shiny new title

@@
 ---
-title: "Dynamics of international giving: Exploring individual donor preferences"
+title: "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"
 short-title: Charity During Crackdown

### 2020-09-29 manuscript/manuscript.Rmd
Add all other pre R&R changes

--- 2020-06-25 manuscript/manuscript.Rmd
@@
 ---
-title: "Dynamics of international giving: Exploring individual donor preferences"
-short-title: Charity During Crackdown
+title: "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"
+short-title: Dynamics of International Giving
 author:
 - name: Suparna Chaudhry
-  affiliation: Lewis \& Clark College
+  affiliation: "Lewis & Clark College"
   email: schaudhry@lclark.edu
@@
 Contact: schaudhry@lclark.edu
-word-count: "7,935"
+word-count: "8,012"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
@@
 International donors directing aid to these countries typically seek out NGOs to implement their projects, as direct aid transfers to recipient governments pose the risk of misuse and bureaucratic inefficiency [@Dietrich2013].
-However, official aid flows to NGOs have decreased considerably in countries with repressive NGO environments [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+However, official aid flows to NGOs have decreased considerably in countries that repress NGOs [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 While we know there has been a negative impact on funding from official donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to donate internationally.
 
-Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.[^internationalaffairs] Between 2014 and 2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report].
+Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.[^internationalaffairs] From 2014–2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report].
 This amount is not insignificant—by 2016, total private giving to nonprofits working in international affairs had increased to \$22.03 billion [@givingusa:2017].
@@
 This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019].
-While a lot is known about individuals' motivations for giving locally [@BekkersWiepking:2011], much less is known about motivations to give internationally and these large amounts show the urgency of understanding this phenomenon.
+While much is known about individuals' motivations for giving locally [@BekkersWiepking:2011], much less is known about motivations to give internationally.
+These large amounts show the urgency of understanding this phenomenon.
 What factors affect individual donor preferences on giving to international causes?
@@
 Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals.
-Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/?view_only=73bf237f7f5e4e15908bc4160517ccb3](https://osf.io/dx973/?view_only=73bf237f7f5e4e15908bc4160517ccb3).
+Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://bit.ly/osf-prereg-anon](https://bit.ly/osf-prereg-anon).
 The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors.
@@
 Here, the private funding heuristic appears to override the dampening in likelihood that should come from focusing on more contentious human rights issues.
-For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting either funding and issue frames—neither of the nested experimental frames play a heuristic role.
+For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting either funding or issue frames—neither of the nested experimental frames play a heuristic role.
 

### 2020-09-29 manuscript/supplement.Rmd
Add all other pre R&R changes

@@
 ---
-title: "Online appendix for Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
-short-title: Online appendix for Charity During Crackdown
+title: 'Online appendix for "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"'
+short-title: 'Online appendix for "Dynamics of International Giving"'
 author:
 - name: Suparna Chaudhry
-  affiliation: Christopher Newport University
-  email: suparna.chaudhry@cnu.edu
+  affiliation: "Lewis & Clark College"
+  email: schaudhry@lclark.edu
   url: http://www.suparnachaudhry.com/
@@
 We made two minor deviations from the original preregistration.
-First, in the *text* of our preregistration, we only specified the non-nested versions of our hypotheses:
+First, in the *text* of our preregistration, we inadvertently only specified the non-nested versions of our hypotheses:
 
@@
 
-In our preregistered data analysis *plan*, however, we explained that we will test the interacted versions of the hypotheses (i.e.
+In our preregistered data analysis *plan*, however, we describe the nested and interacted versions of the hypotheses (i.e.
 donors will give more to humanitarian NGOs facing legal crackdowns, etc.).

### 2020-09-29 README.Rmd
Update README

@@
 
-Title <- "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
+Title <- "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"
 Authors <- "Suparna Chaudhry and Andrew Heiss"
@@
 
-[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
+[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Lewis & Clark College  
 [Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University
+
+---
+
+> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).
 
@@
 
-Government restrictions on NGOs have become increasingly pervasive across the globe.
-With reduced official aid and foundation funding available for NGOs, and an absence of philanthropic culture in many countries across the Global South, various NGOs are seeking funds from individual private donors in Western countries.
-How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making?
-While existing research has shown that donors rely on various heuristics from social networks and organization-level attributes, we argue that domestic political environments of NGO host countries can also serve as an important structural-level heuristic that can influence donor behavior.
-Using a survey experiment, we find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad.
-We discuss the implications of our results on the sustainability of organizations working in repressive countries.
+State restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe.
+While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy.
+How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally?
+Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits.
+This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and main funding sources.
+We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing.
 
@@
 
-> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org/10.17605/OSF.IO/FG53W>
+> `r Authors`. `r Year`. "`r Title`"". Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://dx.doi.org/10.17605/OSF.IO/FG53W>
+
+The paper is published at *Nonprofit and Voluntary Sector Quarterly*:
+
+> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).
 
@@
 
-> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org/10.17605/OSF.IO/FG53W>
+> `r Authors`. `r format(Sys.Date(), "%Y")`. *Compendium of R code and data for "`r Title`"*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://dx.doi.org/10.17605/OSF.IO/FG53W>
 

### 2020-09-30 manuscript/manuscript.Rmd
Final minor R3 edits

@@
   url: https://www.andrewheiss.com/
-date: "`r format(Sys.time(), '%B %e, %Y')`"
+date: "September 29, 2020"
 git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
@@
 Given information asymmetry and time constraints, individual donors often use heuristics to simply their decision-making [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
+Framing, or the process through which actors present information to influence perceptions of behavior, is particularly important in this regard [@ChongDruckman:2007], as NGOs' appeals for donations are framed by structural and organizational characteristics.
 We use a survey experiment fielded in the U.S.
@@
 Second, most nonprofits working internationally have traditionally relied on government and foundation funding.
-But in the era of closing civic space, these groups may need to tailor their fundraising strategies to individual donors.
-Framing, or the process through which actors present information to influence perceptions of behavior, is particularly important in this regard [@ChongDruckman:2007].
+In the era of closing civic space, NGOs may need to reframe and tailor their fundraising strategies to individual donors.
 However, we lack systematic studies of which frames may be effective when making appeals to donors considering international philanthropy.
@@
 
-Thousands of international NGOs in the Global South receive funds from a variety of public and private sources each year.[^NGO] Though we focus on private funding in this article, it is essential to differentiate between the two sources.
+Thousands of international NGOs (INGOs) in the Global South receive funds from a variety of public and private sources each year.[^NGO] Though we focus on private funding in this article, it is essential to differentiate between the two sources.
 Public aid, or more traditional donor aid, channels funds from official aid agencies towards nonprofits through a variety of bilateral and multilateral institutions.
@@
 
-Private giving to nonprofits working in international affairs has increased consistently over the past decade.
-Moreover, donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
+Nonprofits working internationally typically rely heavily on official aid from government sources.
+In 2018, for instance, humanitarian INGOs received 81% of their total funding from governments and EU institutions [@Development-Initiatives:2020].
+However, private giving to nonprofits working in international affairs has increased consistently over the past decade.
+Donations from individuals have far outstripped foundation and corporate giving—in 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion by corporations.
 While foundations are often seen as the primary funders of international nonprofits, they accounted for only 18% of all charitable giving in 2018—and grants from the Bill and Melinda Gates Foundation accounted for more than half of all foundation giving [@givingusa:2019].
-Individual donors thus play an incredibly important—and underexplored—role in funding international NGOs.
+Moreover, while government, foundation, and corporate funding is often earmarked for specific purposes, private donations are typically unrestricted funds.[^reviewer-thanks] Individual donors thus play an incredibly important—and underexplored—role in funding international NGOs.
 
@@
 Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals.
-Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://bit.ly/osf-prereg-anon](https://bit.ly/osf-prereg-anon).
+Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://doi.org/10.17605/OSF.IO/DX973>.
 The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors.
-The analysis is fully reproducible using code and data available at ANONYMIZED.
+The analysis is fully reproducible using code and data available at <https://github.com/andrewheiss/ngo-crackdowns-philanthropy> and <https://dx.doi.org/10.17605/OSF.IO/FG53W>.
 
@@
 [^irc]: Some respondents may have been influenced by prior opinions of IRC. Randomization distributes this bias across the different conditions and likely lessens the threat to validity.
+
+[^reviewer-thanks]: We thank an anonymous reviewer for this insight.

### 2020-09-30 manuscript/manuscript.Rmd
Use Zenodo DOI for GitHub repo

@@
 The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors.
-The analysis is fully reproducible using code and data available at <https://github.com/andrewheiss/ngo-crackdowns-philanthropy> and <https://dx.doi.org/10.17605/OSF.IO/FG53W>.
+The analysis is fully reproducible using code and data available at <https://doi.org/10.5281/zenodo.4058986> and <https://dx.doi.org/10.17605/OSF.IO/FG53W>.
 

### 2020-09-30 README.Rmd
Add badges

@@
 > `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).
+
+[![NVSQ DOI](https://img.shields.io/badge/NVSQ%20DOI-Forthcoming-brightgreen)](#) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FFG53W-blue)](https://dx.doi.org/10.17605/OSF.IO/FG53W) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4058987.svg)](https://doi.org/10.5281/zenodo.4058987)
+
+![Preregistered](img/preregistered_large_color.png) &emsp; ![Open data](img/data_large_color.png) &emsp; ![Open](img/materials_large_color.png)
 

### 2020-10-01 analysis/01_clean-data.Rmd
Update to use latest tidyverse conventions
list() instead of funs(); pivot_*() instead of gather() and spread()
Clean up code to work with dplyr 1.0 and friends

@@
 title: "Clean data"
-author: "Andrew Heiss and Suparna Chaudhry"
-date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
+author: "Suparna Chaudhry and Andrew Heiss"
+date: "Last run: `r format(Sys.time(), '%F')`"
 output: 
@@
   mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
-            funs(factor(., levels = favorability, ordered = TRUE))) %>% 
+            list(~factor(., levels = favorability, ordered = TRUE))) %>% 
   mutate(give_charity = factor(give_charity, 
@@
   mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
-            funs(bin = fct_recode(., 
+            list(bin = ~fct_recode(., 
                                    `Not favorable` = "Very unfavorable",

### 2020-10-01 analysis/02_analysis.Rmd
Clean up code to work with dplyr 1.0 and friends

--- 2020-01-21 analysis/02_analysis.Rmd
@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(fig.retina = 3, fig.align = "center")
+```
 
@@
 
-```{r causal-dag, fig.width=4.75, fig.height=2}
+```{r causal-dag, fig.width=4.75, fig.height=2, out.width="70%"}
 theory_dag <- dagify(Y ~ I + C + F,
@@
   geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
+  geom_dag_label_repel(aes(label = label), size = pts(6), box.padding = 0.1, 
+                       direction = "x", seed = 12345,
+                       family = "Roboto Condensed", fontface = "plain") +
+  labs(x = NULL) +
   theme_ngos() +
@@
 
-```{r fig-likelihood-bars, fig.width=9, fig.height=4}
+```{r fig-likelihood-bars, fig.width=9, fig.height=4, out.width="80%"}
 donate_summary <- results %>% 
@@
 
-```{r fig-amount-bars, fig.width=9, fig.height=2.75}
+```{r fig-amount-bars, fig.width=9, fig.height=2.75, out.width="80%"}
 plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
@@
 
-```{r priors-likely, fig.width=2.75, fig.height=1.5, fig.align="center"}
+```{r priors-likely, fig.width=2.75, fig.height=1.5, out.width="50%"}
 likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
@@
 
-```{r plot-likely-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
+```{r plot-likely-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5, out.width="90%"}
 tidied_diffs_likely <- all_models_likely %>% 
@@
 plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
-  geom_halfeyeh(.width = c(0.8, 0.95)) +
+  stat_halfeye(.width = c(0.8, 0.95)) +
   geom_vline(xintercept = 0) +
@@
                              aes(x = .value, y = fct_rev(title))) +
-  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
+  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
   geom_vline(xintercept = 0) +
@@
                              aes(x = .value, y = fct_rev(title))) +
-  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
+  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
   geom_vline(xintercept = 0) +
@@
 plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
-  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
+  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
   geom_vline(xintercept = 0) +
@@
 
-```{r priors-amounts, fig.width=8, fig.height=1.5}
+```{r priors-amounts, fig.width=8, fig.height=1.5, out.width="100%"}
 amount_nu <- ggplot(data = tibble(x = c(0, 200)), aes(x = x)) +
@@
 
-```{r plot-amount-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
-# This will generate a warning because unnest() puts the crackdown values into
-# one column and we cheated by renaming issue and funding as crackdown, so it
-# gets mad when combining the factors in crackdown with those in issue and
-# funding. But because we only care about the diffs, we don't actually need the
-# category labels here, so it's all good.
+```{r plot-amount-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5, out.width="90%"}
+all_models_amount <- all_models_amount %>% 
+  # The `group` and `tidy` columns in each of these nested models contain
+  # ordered factors, but we can't combine them with unnest() directly because
+  # they have different levels (crackdown, issue, and funding), so we need to
+  # make them unordered factors before unnesting
+  mutate(posterior_chains_long = map(
+    posterior_chains_long, ~mutate(., group = factor(group, ordered = FALSE)))
+  ) %>% 
+  mutate(tidy = map(
+    tidy, ~mutate(., group = factor(group, ordered = FALSE)))
+  )
+
 tidied_diffs_amount <- all_models_amount %>% 
@@
   geom_vline(xintercept = 0) +
-  geom_halfeyeh(.width = c(0.8, 0.95)) +
+  stat_halfeye(.width = c(0.8, 0.95)) +
   scale_x_continuous(labels = dollar) +
@@
 plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
-  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
+  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
   geom_vline(xintercept = 0) +
@@
 
-```{r amount-effect-size, warning=FALSE}
+```{r amount-effect-size, warning=FALSE, out.width="80%"}
 # Effect size
@@
 ggplot(tidied_eff_size_amount, aes(x = .value, y = fct_rev(title))) +
-  geom_halfeyeh(.width = c(0.8, 0.95)) +
+  stat_halfeye(.width = c(0.8, 0.95)) +
   geom_vline(xintercept = 0, size = 1) +
@@
   geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
-  coord_cartesian(xlim = c(-0.6, 0.6)) +
+  coord_cartesian(xlim = c(-1, 1)) +
   labs(x = "Cohen's d (effect size)", y = NULL) +

### 2020-10-01 analysis/03_additional-analysis.Rmd
Clean up code to work with dplyr 1.0 and friends

@@
 title: "Additional analysis"
-author: "Andrew Heiss and Suparna Chaudhry"
-date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
+author: "Suparna Chaudhry and Andrew Heiss"
+date: "Last run: `r format(Sys.time(), '%F')`"
 output: 
@@
 library(broom)
+library(broom.mixed)
 library(glue)
@@
 library(gridExtra)
-library(Gmisc)
+library(Gmisc)  # For the CONSORT diagram
 library(pander)
@@
 
-```{r show-save-consort, fig.width=10, fig.height=6}
+```{r show-save-consort, fig.width=10, fig.height=6, out.width="100%"}
 # Ordinarily, you can use grid.grab() to save the output of a grid figure into
@@
 
-  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.95, 
+  tidied <- tidy(mcmc_samples, conf.int = TRUE, conf.level = 0.95, 
                  estimate.method = "median", conf.method = "HPDinterval") %>%
@@
 
-```{r avg-time-plot, fig.height=2.5, fig.width=4}
+```{r avg-time-plot, fig.height=2.5, fig.width=4, out.width="80%"}
 summary_stats <- tableGrob(time_summary, rows = NULL, theme = theme_ngos_table) %>% 
@@
 
+\
+
 # Original computing environment

### 2020-10-01 analysis/index.Rmd
Clean up code to work with dplyr 1.0 and friends

--- 2018-07-16 index.Rmd
@@
 ---
-title: "NGO Crackdowns and Philanthropy"
+title: "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"
 author: "Suparna Chaudhry and Andrew Heiss"
 date: "Last run: `r format(Sys.time(), '%F')`"
-site: safesite::safesite
 ---
 
-\\(•◡•)/
+## Abstract
+
+State restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe.
+While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy.
+How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally?
+Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits.
+This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and main funding sources.
+We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing.

### 2020-10-01 analysis/preregistration.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

--- 2018-07-15 preregistration.Rmd
@@
 title: "Preregistration, design, IRB"
+author: "Suparna Chaudhry and Andrew Heiss"
 date: "Last run: `r format(Sys.time(), '%F')`"
-bibliography: manuscript/bibliography.bib
+bibliography: ../manuscript/bibliography.bib
 ---

### 2020-10-01 analysis/options.R

@@ -1,3 +1,6 @@
+# Turn off summarize messages from dplyr 1.0+
+options(dplyr.summarise.inform = FALSE)
+
 # Universal pandoc options ------------------------------------------------
 
 panderOptions("table.split.table", Inf)

### 2020-10-08 manuscript/manuscript.Rmd
Final changes for NVSQ

@@
   url: https://www.andrewheiss.com/
-date: "September 29, 2020"
+date: "October 7, 2020"
+published: "Forthcoming in *Nonprofit and Voluntary Sector Quarterly* (NVSQ)"
 git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
@@
 thanks: >-
-  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input.
+  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input, as well as the anonymous reviewers at Nonprofit and Voluntary Sector Quarterly (NVSQ) for their excellent feedback.
 We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance.
@@
 Contact: schaudhry@lclark.edu
-word-count: "8,012"
-keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
+word-count: "8,165"
+keywords: nonprofit law, NGO crackdown, international philanthropy, charitable giving, survey experiments
 ---
@@
 Rather, individuals are more inclined to donate to NGOs in countries experiencing a humanitarian crisis—in particular, crises following natural disasters.
-@desaikharas conclude that compared to donor agencies, "private donors respond to different project and country characteristics." (p.
-517) International philanthropy by individuals should therefore be investigated on its own terms.
+@desaikharas conclude that compared to donor agencies, "private donors respond to different project and country characteristics" (p.
+517).
+International philanthropy by individuals should therefore be investigated on its own terms.
 
@@
 NGO legislation is not inherently restrictive, and governments frequently use laws to regulate the behavior of NGOs [@BloodgoodTB; @DeMattee:2018].
-Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
+Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy [@Spires:2020].
 These stricter anti-NGO laws can signal to donors that governments perceive these groups as threatening and may crack down on them.
@@
 Donors may feel less inclined to contribute to NGOs receiving funds from agencies like the United States Agency for International Development (USAID) because such funding can signal a lack of independence from the government.
-Organizations that receive substantial funding from their home governments frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012].
+Organizations that receive substantial funding from their home governments frequently avoid programming that would question the donor government even if such programming is in line with their mission [@Stroup:2012; @YuShenLi:2020].
 In contrast, individual donors who see that organizations are privately funded may feel that they can also contribute and help and that their marginal donation would make a noticeable difference.
@@
 In either case, knowing about government funding should still serve as a signal of the organization's deservingness.
-Similarly, there could be confusion with phrase "private funding", but since we use it as the opposite of government funding, it should still act as a heuristic.
+Similarly, there could be confusion with phrase "private funding," but since we use it as the opposite of government funding, it should still act as a heuristic.
 Free responses tend to confirm the correct interpretation of the vignette, and many respondents explicitly justified their lack of support for IRC because of government funding, as expected ("I see that a large portion of its funding comes from government donors, so I feel it doesn't need me as much."[^6216778])

### 2020-10-08 manuscript/supplement.Rmd
Final changes for NVSQ

@@
   url: https://www.andrewheiss.com/
-date: "`r format(Sys.time(), '%B %e, %Y')`"
+date: "October 7, 2020"
 title-page: false
@@
 
-```{r child = "../analysis/text/experiment_blind.md"}
+```{r child = "../analysis/text/experiment.md"}
 ```

### 2020-11-17 README.Rmd
Move badges up a little
Add links to data and notebook
Add NVSQ DOI

--- 2020-09-29 README.Rmd
@@
 
-> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).
+[![NVSQ DOI](https://img.shields.io/badge/NVSQ%20DOI-10.1177%2F0899764020971045-brightgreen)](https://doi.org/10.1177/0899764020971045) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FFG53W-blue)](https://dx.doi.org/10.17605/OSF.IO/FG53W) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4058987.svg)](https://doi.org/10.5281/zenodo.4058987)
+
+> `r Authors`.
+`r Year`.
+["`r Title`,"](https://doi.org/10.1177/0899764020971045) *Nonprofit and Voluntary Sector Quarterly* (forthcoming), doi: [`10.1177/0899764020971045`](https://doi.org/10.1177/0899764020971045).
+
+**All this project's materials are free and open:**
+
+- [Download the data](#data)
+- [See the analysis notebook website](https://stats.andrewheiss.com/ngo-crackdowns-philanthropy/)
+
+![Preregistered](img/preregistered_large_color.png) &emsp; ![Open data](img/data_large_color.png) &emsp; ![Open](img/materials_large_color.png)
 
@@
 
-> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).
+> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming), doi: [`10.1177/0899764020971045`](https://doi.org/10.1177/0899764020971045).
 
